### 2020-09-28 Latex/Manuscript.pandoc.tex
md conversion to latex #24
- added md2latex.cmd
- Manuscript.pandoc.tex is auto-generated and must be refined

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{document-header}{%
\section{Document Header}\label{document-header}}

\hypertarget{title-proposals}{%
\subsection{Title proposals}\label{title-proposals}}

\begin{itemize}
\tightlist
\item
  Object-Oriented Internet - reactive visualization of asynchronous data
  using AZURE
\item
  Object-Oriented Internet - Azure interoperability
\end{itemize}

\hypertarget{abstract}{%
\subsection{Abstract}\label{abstract}}

\hypertarget{key-words}{%
\subsection{Key words}\label{key-words}}

Azure, Cloud Computing, Object-Oriented Internet, OPC Unified
Architecture, Machine to Machine Communication, Internet of Things, OPC
UA, RxNetworking

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\begin{itemize}
\tightlist
\item
  \textbf{Subject} - A basic matter of thought, discussion,
  investigation, development, etc. Describe the problem and the
  motivation for undertaking the effort to solve the problem.
\item
  \textbf{Goal} What we are going to achieve - the result or achievement
  toward which effort is directed.
\item
  \textbf{Scope} - What we must do to prove the goal have been achieved.
  Extent or range of development, view, outlook, application, operation,
  effectiveness, etc.
\item
  \textbf{Related work} - Any information about available reusable
  deliverables related to this work.
\end{itemize}

\hypertarget{azure-main-technology-features}{%
\section{Azure Main Technology
Features}\label{azure-main-technology-features}}

\begin{itemize}
\tightlist
\item
  \textbf{Selection of the service}
\item
  \textbf{Metadata} - must be discussed in context of the design/run
  time stages.

  \begin{itemize}
  \tightlist
  \item
    \textbf{Device Template (DT)}
  \item
    \textbf{Device Capability Model}
  \item
    \textbf{Interface}
  \item
    \textbf{Digital Twin Definition Language (DTDL)}
  \end{itemize}
\item
  \textbf{Simple, complex and structural data processing}
\item
  \textbf{Connectivity}
\item
  \textbf{How to implement} All about available libraries and tools
\end{itemize}

\hypertarget{ooi-main-technology-features}{%
\section{OOI Main Technology
Features}\label{ooi-main-technology-features}}

\begin{itemize}
\tightlist
\item
  Machinie To Machine communication based on the semantic data
\item
  OOI PubSub Implementation Architecture
\item
  Simple, complex and structural data processing
\end{itemize}

\hypertarget{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity}{%
\section{Azure to Sensors (A2S) connectivity deployment (field level
connectivity)}\label{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity}}

\begin{quote}
The title must be revised
\end{quote}

\begin{itemize}
\tightlist
\item
  \textbf{Architecture} - Domain model presenting relationship between
  the: Azure, PubSub Gateway, Device, Design and development tools
\item
  \textbf{Connectivity} - Describe reactive nature of the Azure
  monitoring process data (telemetry) services.
\item
  \textbf{Deployment phases}

  \begin{itemize}
  \tightlist
  \item
    Design
  \item
    Gateway and devices registration
  \item
    Authentication
  \item
    Device/Service association
  \item
    Device/Application association
  \item
    Establishing session

    \begin{itemize}
    \tightlist
    \item
      Device/Device Template (Device Capability Model) association -
      establishing a semantic-context
    \item
      Security management - establishing security-context
    \end{itemize}
  \item
    Interconnection - exchange of data
  \item
    Maintenance
  \end{itemize}
\end{itemize}

We have selected
\href{https://docs.microsoft.com/azure/iot-central/core/}{IoT Central}
because:

\begin{itemize}
\tightlist
\item
  provides process data visualization user interface
\item
  allows to describe devices using metadata containing telemetry data
  types
\end{itemize}

\hypertarget{gateway-implementation}{%
\section{Gateway implementation}\label{gateway-implementation}}

\begin{itemize}
\tightlist
\item
  Architecture
\item
  Protocol selection and mapping
\item
  Configuration
\item
  Testing
\end{itemize}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

The OPC UA PubSub to Azure gateway (\texttt{AzureGateway})
implementation has been just published on GitHub as the open-source (MIT
licensed) as a part of the more general concept of the Object-Oriented
Internet reactive networking. It is proof of the concept that

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  OPC UA PubSub can be implemented as a powerful standalone package - no
  C/S dependency
\item
  Azure interoperability can be implemented as an out-of-band
  communication (MQTT, AMQP, HTTP) - no PubSub dependency
\item
  Process data functionality can be composable at run-time - no
  programming required
\end{enumerate}

\end{document}

### 2020-09-29 Latex/Manuscript..tex
md conversion to latex #24
- fixes #24

--- 2020-09-28 Latex/Manuscript.pandoc.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\documentclass{article}
+\usepackage{hyperref}
+\usepackage{cite}
+\usepackage{graphicx}
+\usepackage{stfloats}
+\usepackage{url}
+\usepackage{authblk}
 
-\date{}
+\providecommand{\tightlist} { \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+\title{Object-Oriented Internet - Azure interoperability} 
+\author[1]{Mariusz Postół}
+\author[2]{Piotr Szymczak}
+\author[3]{Clemens Vasters}
+\affil[1, 2]{Institute of Information Technology, Lodz University of Technology, Łódź, Poland}
+% \email{mailto:mariusz.postol@p.lodz.pl} 
+\affil[3]{Microsort}
+%\tocauthor{Mariusz Postół}
+%\institute{ Institute of Information Technology, Lodz University of Technology, Łódź, Poland \email{mailto:mariusz.postol@p.lodz.pl} }
 
 \begin{document}
+
+\maketitle
+
+\begin{abstract}
+
+  Information and Communication Technology has provided society with a~vast variety of distributed applications.
+By design, the deployment of this kind of application has to focus primarily on communication.
+This article addresses research results on the systematic approach to the design of the meaningful Machine to Machine (M2M) communication targeting distributed mobile applications in the context of new emerging disciplines, i.e.
+Industry 4.0 and Internet of Things.
+This paper contributes to the design of a new architecture of mobile IoT solutions designed atop of the M2M communication and composed as multi-vendor cyber-physicals systems.
+The described reusable library supporting this architecture designed using the reactive interoperability archetype proves that the concept enables a systematic approach to the development and deployment of software applications against mobile IoT solutions based on international standards.
+Dependency injection and adaptive programming engineering techniques have been engaged to develop a full-featured reference application program and make the proposed solution scalable and robust against deployment environment continuous modifications.
+The article presents an executive summary of the proof of concept and describes selected conceptual and experimental results achieved as an outcome of the open-source project Object-Oriented Internet targeting multi-vendor plug-and-produce interoperability scenario.
+
+%\keywords{Industrial communication \and Industry 4.0 \and Internet of Things \and Machine to Machine Communication \and OPC Unified Architecture}
+
+\end{abstract}
+
+\maketitle
 
@@
 
+\bibliography{Manuscript}
+\bibliographystyle{splncs04}
+
 \end{document}

### 2020-09-29 Latex/Manuscript..tex
Workout Markdown\10.DocumentHeader.md #25
fixes #25

@@
 \providecommand{\tightlist} { \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\providecommand{\keywords}[1]{  \small	  \textbf{\textit{Keywords---}} #1 }
 
 \title{Object-Oriented Internet - Azure interoperability}
+% \title{Object-Oriented Internet - reactive visualization of asynchronous data using AZURE}
 \author[1]{Mariusz Postół}
@@
 
-  Information and Communication Technology has provided society with a~vast variety of distributed applications.
-By design, the deployment of this kind of application has to focus primarily on communication.
-This article addresses research results on the systematic approach to the design of the meaningful Machine to Machine (M2M) communication targeting distributed mobile applications in the context of new emerging disciplines, i.e.
-Industry 4.0 and Internet of Things.
-This paper contributes to the design of a new architecture of mobile IoT solutions designed atop of the M2M communication and composed as multi-vendor cyber-physicals systems.
-The described reusable library supporting this architecture designed using the reactive interoperability archetype proves that the concept enables a systematic approach to the development and deployment of software applications against mobile IoT solutions based on international standards.
-Dependency injection and adaptive programming engineering techniques have been engaged to develop a full-featured reference application program and make the proposed solution scalable and robust against deployment environment continuous modifications.
-The article presents an executive summary of the proof of concept and describes selected conceptual and experimental results achieved as an outcome of the open-source project Object-Oriented Internet targeting multi-vendor plug-and-produce interoperability scenario.
+TBD
 
-%\keywords{Industrial communication \and Industry 4.0 \and Internet of Things \and Machine to Machine Communication \and OPC Unified Architecture}
+\keywords{Azure, Cloud Computing, Object-Oriented Internet, Industrial communication, Industry 4.0, Internet of Things, Machine to Machine Communication, OPC Unified Architecture}
 
@@
 \maketitle
-
-\hypertarget{document-header}{%
-  \section{Document Header}\label{document-header}}
-
-\hypertarget{title-proposals}{%
-  \subsection{Title proposals}\label{title-proposals}}
-
-\begin{itemize}
-  \tightlist
-  \item
-        Object-Oriented Internet - reactive visualization of asynchronous data
-        using AZURE
-  \item
-        Object-Oriented Internet - Azure interoperability
-\end{itemize}
-
-\hypertarget{abstract}{%
-  \subsection{Abstract}\label{abstract}}
-
-\hypertarget{key-words}{%
-  \subsection{Key words}\label{key-words}}
-
-Azure, Cloud Computing, Object-Oriented Internet, OPC Unified
-Architecture, Machine to Machine Communication, Internet of Things, OPC
-UA, RxNetworking
 

### 2020-10-07 Latex/Manuscript.pandoc.tex
Work out Markdown\30.AzureTechnologyFeatures.md #27
- section is ready to be reviewed

@@
 
-\hypertarget{document-header}{%
-\section{Document Header}\label{document-header}}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-\hypertarget{title-proposals}{%
-\subsection{Title proposals}\label{title-proposals}}
+All the time, the Information and Communication Technology is providing
+society with a vast variety of new distributed applications aimed at
+micro and macro optimization of the industrial processes. Obviously, the
+design foundation of this kind of application has to focus primarily on
+communication technologies. Based on the role humans take while using
+these applications they can be grouped as follows:
 
@@
 \item
-  Object-Oriented Internet - reactive visualization of asynchronous data
-  using AZURE
+  \textbf{human-centric} - information origin or ultimate information
+  destination is an operator,
 \item
-  Object-Oriented Internet - Azure interoperability
+  \textbf{machine-centric} - information creation, consumption,
+  networking, and processing are achieved entirely without human
+  interaction.
 \end{itemize}
 
-\hypertarget{abstract}{%
-\subsection{Abstract}\label{abstract}}
+A typical \textbf{human-centric} approach is a web-service supporting,
+for example, a web user interface (UI) to monitor conditions, and manage
+millions of devices and their data in a typical cloud-based IoT
+approach. It is characteristic that, in this case, any uncertainty and
+necessity to make a decision can be relaxed by human interaction.
+Coordination of robots behavior in a work-cell (automation islands) is a
+\textbf{machine-centric} example. In this case, it is essential that any
+human interaction is impractical or even impossible. This
+interconnection scenario requires the machine to machine communication
+(M2M) demanding multi-vendor devices integration.
 
-\hypertarget{key-words}{%
-\subsection{Key words}\label{key-words}}
+From the M2M communication concept, a broader concept of a smart factory
+can be derived. In this concept, the mentioned robots are only executive
+assets of an integrated supervisory control system responsible for macro
+optimization of an industrial process composed into one whole.
+Deployment of the smart factory concept requires a hybrid solution and
+interoperability of the mentioned above heterogeneous environments. This
+approach is called the fourth industrial revolution and coined as
+Industry 4.0. It is worth stressing that machines - or more general
+assets - interconnection is not enough, and additionally, assets
+interoperability has to be expected for the deployment of this concept.
+In this case, muli-vendor integration makes communication
+standardization especially important, namely it is required that the
+payload of the message is standardized to be factored on the gathering
+site and consumed on the ultimate destination site.
 
-Azure, Cloud Computing, Object-Oriented Internet, OPC Unified
-Architecture, Machine to Machine Communication, Internet of Things, OPC
-UA, RxNetworking
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+Highly-distributed solutions used to control real-time process
+aggregating islands of automation (e.g.~virtual power plants producing
+renewable energy) additionally must leverage public communication
+infrastructure, namely the Internet. Internet is a demanding environment
+for highly distributed process control applications designed atop the
+M2M communication paradigm because
 
@@
 \item
-  \textbf{Subject} - A basic matter of thought, discussion,
-  investigation, development, etc. Describe the problem and the
-  motivation for undertaking the effort to solve the problem.
+  it is a globally shareable environment and can be also used by
+  malicious users
 \item
-  \textbf{Goal} What we are going to achieve - the result or achievement
-  toward which effort is directed.
-\item
-  \textbf{Scope} - What we must do to prove the goal have been achieved.
-  Extent or range of development, view, outlook, application, operation,
-  effectiveness, etc.
-\item
-  \textbf{Related work} - Any information about available reusable
-  deliverables related to this work.
+  it offers only non-deterministic communication making integration of
+  islands of automation designed against the real-time requirements a
+  difficult task
 \end{itemize}
 
-\hypertarget{azure-main-technology-features}{%
-\section{Azure Main Technology
-Features}\label{azure-main-technology-features}}
+Today both obstacles can be overcome, and as examples, we have bank
+account remote control and voice over IP in daily use. The first
+application must be fine-tuned in the context of data security, and the
+second is very sensitive on time relationships. Similar approaches could
+be applied to adopt the well known in process control industry concepts:
 
@@
 \item
-  \textbf{Selection of the service}
+  Human Machine Interface (HNI)
 \item
-  \textbf{Metadata} - must be discussed in context of the design/run
-  time stages.
+  Supervisory Control and Data Acquisition (SCADA)
+\item
+  Distributed Control Systems (DCS)
+\end{itemize}
+
+A detailed examination of these solutions is far beyond the scope of
+this article. It is only worth stressing that, by design, all of them
+are designed on the foundation of interactive communication. Interactive
+communication is based on a data polling foundation. In this case, the
+application must follow the interactive behavioral model, because it
+actively polls the data source for more information by pulling data from
+a sequence that represents the process state in time. The application is
+active in the data retrieval process - it controls the pace of the
+retrieval by sending the requests at its convenience. Such a polling
+pattern is similar to visiting the books shop and checking out a book.
+After you are done with the book, you pay another visit to check out
+another one. If the book is not available you must wait, but you may
+read what you selected. The client/server archetype is well suited for
+the mentioned above applications.
+
+After dynamically attaching a new island of automation the control
+application (responsible for the data pulling) must be reconfigured for
+this interoperability scenario. In other words, in this case, the
+interactive relationship cannot be directly applied because the control
+application must be informed on how to pull data from a new source. As a
+result, a plug and produce scenario cannot be seamlessly applied. A
+similar drawback must be overcome if for security reasons suitable
+protection methods have been applied to make network traffic propagation
+asymmetric. It is accomplished using intermediary devices, for example,
+firewalls, to enforce traffic selective availability based on
+predetermined security rules against unauthorized access.
+
+Going further, we shall assume that islands of automation are mobile,
+e.g.~autonomous cars passing a supervisory controlled service area. In
+this case, the behavior of the interconnected assets is particularly
+important concerning the environment in which they must interact. This
+way we have entered the Internet of Things domain of Internet-based
+applications.
+
+If we must bother with the network traffic propagation asymmetry or
+mobility of the asset network attachment-points the reactive
+relationship could relax the problems encountered while the interactive
+approach is applied. In this case, the sessionless publisher-subscriber
+communication archetype is a typical pattern to implement the abstract
+reactive interoperability paradigm. The sessionless archetype is a
+message distribution scenario where senders of messages, called
+publishers, do not send them directly to specific receivers, called
+subscribers, but instead, categorize the published messages into topics
+without knowledge about which subscribers if any, there may be.
+Similarly, subscribers express interest in one or more topics and only
+receive messages that are of interest, without knowledge about which
+publishers, if any, there are. In this scenario, the publishers and
+subscribers are loosely coupled.i.e they are decoupled in time, space
+and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.
+
+If the \textbf{machine-centric} interoperability - making up islands of
+automation - must be monitored and/or controlled by a supervisory system
+cloud computing concept may be recognized as a beneficial solution to
+replace or expand the mentioned above applications, i.e.~HMI, SCADA,
+DCS, etc. Cloud computing is a method to provide a requested
+functionality as a set of services. There are many examples that cloud
+computing is useful to reduce costs and increase robustness. It is also
+valuable in case the process data must be exposed to many stakeholders.
+Following this idea and offering control systems as a service, there is
+required a mechanism created on the service concept and supporting
+abstraction and virtualization - two main pillars of the cloud computing
+paradigm. In the cloud computing concept, virtualization is recognized
+as the possibility to share the services by many users, and abstraction
+hides implementation details.
+
+Deployment of the hybrid solution providing interoperability of the
+\textbf{machine-centric} cyber-physical systems and
+\textbf{human-centric} cloud-based front-end can be implemented applying
+the following scenarios:
 
@@
 \item
-    \textbf{Device Template (DT)}
+  \textbf{direct interconnection} - cloud-based dedicated communication
+  services allow to attache it to the cyber-physical system making up a
+  consistent M2M communication network using an in-bound protocol stack
 \item
-    \textbf{Device Capability Model}
+  \textbf{gateway based interconnection} - typical build-in
+  communication services allows to attache the cloud computing to the
+  cyber-physical system using an out-of-bound protocol stack
+\end{itemize}
+
+By design, the direct approach requires that the cloud has to be
+compliant with the interoperability standard the cyber-physical system
+is built around - it becomes a consistent part of the cyber-physical
+system. Data models, roles, and responsibility differences of both
+solutions make this approach impractical and imposable to be applied in
+typical cases. A more detailed description is covered by the section
+\texttt{Azure\ to\ Sensors\ (A2S)\ connectivity\ deployment}.
+
+This article addresses further research on the integration of the
+cyber-physical systems in the context of new emerging disciplines,
+i.e.~Industry 4.0 (I4.0) and the Internet of Things (IoT). The new
+architecture is proposed for integration of the multi-vendor
+\textbf{machine-centric} cyber-physical system designed atop of M2M
+reactive communication and emerging cloud computing as a
+\textbf{human-centric} front-end. To support the multi-vendor
+environment OPC Unified Architecture interoperability standard has been
+selected. The proposals are backed by proof of concept reference
+implementations. Prototyping addresses Microsoft Azure Cloud as an
+example. The prototyping outcome has been just published on GitHub as
+the open-source (MIT licensed). The proposed solutions have been
+harmonized with the more general concept called the Object-Oriented
+Internet.
+
+The main goal of this article is to provide proof that:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
 \item
-    \textbf{Interface}
+  reactive interoperability M2M communication based on the OPC UA
+  standard can be implemented as a powerful standalone library without
+  dependency on the Client/Server session-oriented archetype
 \item
-    \textbf{Digital Twin Definition Language (DTDL)}
+  Azure interoperability can be implemented as an external part
+  employing out-of-band communication without dependency on the OPC UA
+  implementation
+\item
+  the proposed generic architecture allows that the gateway
+  functionality is composable at run-time - no programming required
+\end{enumerate}
+
+The remainder of this paper is structured as follows. Sect.
+\texttt{Azure\ Main\ Technology\ \ Features} analyzes data presentation
+user interface, available native communication services, and
+data/metadata model offered by the Microsoft Azure. The discussion
+covered by this section is the foundation for selecting services
+utilized to expose process data and suitable protocol stack to support
+interconnection. In Sect.
+\texttt{Object-Oriented\ Internet\ Main\ Technology\ Features} the
+discussion focuses on the generic architecture that is to be used as a
+foundation for further decisions addressing the systematic design of the
+interoperability of the cyber-physical systems and cloud-based
+front-end. Sect.
+\texttt{Azure\ to\ Sensors\ (A2S)\ connectivity\ deployment\ (field\ level\ connectivity)}
+presents the proposed open and reusable software model. It promotes a
+reactive interoperability pattern and a generic approach to establishing
+interoperability-context. A reference implementation of this archetype
+is described in Sect. \texttt{Gateway\ implementation}. The most
+important findings and future work are summarized in Sect.
+\texttt{Conclusions}.
+
+\hypertarget{consider-to-add}{%
+\subsection{Consider to add}\label{consider-to-add}}
+
+\hypertarget{scope}{%
+\subsubsection{Scope}\label{scope}}
+
+What we must do to prove the goal have been achieved. Extent or range of
+development, view, outlook, application, operation, effectiveness, etc.
+
+\hypertarget{related-work}{%
+\subsubsection{Related work}\label{related-work}}
+
+Any information about available reusable deliverables related to this
+work. \# Azure Main Technology Features
+
+\hypertarget{services}{%
+\subsection{Services}\label{services}}
+
+Deployment of the hybrid solution providing interoperability of the
+\textbf{machine-centric} cyber-physical systems designed atop of M2M
+reactive communication and emerging cloud computing as a
+\textbf{human-centric} front-end requires decisions addressing the
+selection of the services supporting web user interface capable to
+expose real-time process data. Service is any autonomous (with own
+identity) software component or module that is interfacing with selected
+cyber-physical systems for data collection, analysis, and also remote
+control. Microsoft Azure is a cloud-based product. It offers a vast
+variety of services. This virtual environment handles an unlimited
+number of users and devices organized using a solution concept. The
+solution aggregates users, devices, services, and required additional
+resources scoping on a selected scenario. The solution is a region that
+provides a scope to the identifiers (the names of devices, users,
+process data entities, etc) inside it. Solutions are used to organize
+deployment entities into logical groups and prevent identity collisions.
+
+The \texttt{IoT\ Central} service provides process data visualization
+user interface. To make this interface meaningful metadata called device
+template is used to describe devices.
+
+Following the assumption that interconnection between the cyber-physical
+system and cloud services is designed based on the gateway concept a
+middleware must be considered aa a coupler. It must be interconnected
+with the cyber-physical system using an in-bound protocol adhering to
+communications requirements (i.e.~protocol profile, data encoding, time
+relationships, etc.) governing communication of the parts making it up.
+At the same time it must support back-and-forth communication transfer
+data to the cloud using out-of-bound native for the cloud services. The
+transfer process requires data conversion from source to destination
+encoding. The `IoT Hub' is a service that supports \texttt{IoT\ Central}
+providing robust messaging solution. This communication is transparent,
+i.e.~it is not data types aware allowing any devices to exchange any
+kind of data. This service is responsible to manage the device
+identities and offers the following protocol stacks: AMQP, MQTT, HTTPS.
+
+Before the process data can be exposed using web user interface the data
+source must be associated with appropriate solution and validated to
+make sure that the security rules are not violated. It is hard to assume
+that the security rules governing the cyber-physical system may be
+applicable to the cloud-based services. The
+\texttt{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper
+service for \texttt{IoT\ Hub} that enables devices registration,
+authentication and authorization of the requested operations including
+but not limiting to data transfer updating the user interface.
+
+It is worth stressing that services interaction can be flexibly
+configured, and as a result the presented above selection of services
+must be recognized as an example only. The `\texttt{IoT\ Central}can be
+also seamlessly integrated with other services as needed. The following
+services could also be considered to build cloud based automation
+solution:
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{Industrial\ IoT} - discovering OPC UA enabled servers in a
+  factory network and register them in Azure IoT Hub implemented using
+  \texttt{IoT\ Edge}
+\item
+  \texttt{Digital\ Twins} - managing the graph of digital twins, which
+  are to represent some real world process or entity
 \end{itemize}
+
+\texttt{Industrial\ IoT} promotes OPC UA client/server archetype used to
+achieve direct and interactive interoperability implemented using
+\texttt{IoT\ Edge} services that allow extracting initial data
+processing to local premises based on the edge concept.
+\texttt{Digital\ Twins} is an emerging concept to use an observer to
+replicate selected process state and behavior. The possibility to add
+value as a result of using these services must be subject to further
+research.
+
+\hypertarget{simple-complex-and-structural-data-processing}{%
+\subsection{Simple, complex and structural data
+processing}\label{simple-complex-and-structural-data-processing}}
+
+System interoperability means the necessity of the information exchange
+between them. The main challenge of interoperability implementation is
+that information is abstract -- it is knowledge describing the process
+in concern state and behavior, e.g.~temperature in a boiler, a car
+speed, an account balance, etc. Unfortunately cyber-physical machines
+cannot be used to process abstraction. It is also impossible to transfer
+abstraction from one place to another.
+
+Fortunately, there is a very simple solution to address that
+impossibility, namely the information must be represented as binary
+stream. In consequence, we can usually use both ones as interchangeable
+terms while talking about ICT systems. Unfortunately, these terms must
+be distinguished in the context of further discussion, because before
+stepping forward we must be aware of the fact that the same information
+could have many different but equivalent representations, namely the
+same information can be successfully represented by a vast variety of
+different binary patterns. For example, 2's Complement and
+Floating-Point binary representations.
+
+It should be nothing new for us, as it is obvious that the same
+information written as a text in regional newspapers in English, German,
+Polish, etc. does not resemble one another, but the text meaning should
+be always the same. To understand a newspaper we must learn the
+appropriate language. To understand the binary data we must have defined
+a data type -- a description how to create an appropriate bits pattern
+(syntax) and rules needed to assign the information (semantics),
+i.e.~make any correct bits stream meaningful. Concluding, to make two
+systems interoperable, a semantic context must be establish. The type
+plays the role of metadata, a set of data that describes other data.
+Metadata term is frequently used if the semantic-context is defined
+using a native language to select built-in types using a general purpose
+graphical user interface.
+
+Using the data type definitions to describe information interchanged
+between communicating parties allows:
+
+\begin{itemize}
+\tightlist
 \item
-  \textbf{Simple, complex and structural data processing}
+  Development user interface against type definition
 \item
-  \textbf{Connectivity}
+  Implementation of the bits-streams conversions functionality in
+  advance
+\end{itemize}
+
+Having defined types in advance, a gateway may provide dedicated
+conversions functionality, e.g.~replacing bits-stream used by the
+cyber-physical system by equivalent for the cloud-based services. The
+Azure offers a vast variety of build-in types ready to be used in common
+cases, but not necessarily they are equivalent counterparts in use by
+the cyber-physical system. Additionaly the data conversion must address
+the following issues:
+
+\begin{itemize}
+\tightlist
 \item
-  \textbf{How to implement} All about available libraries and tools
+  usually to covert types from source to destination the native types
+  must be used by the middleware software
+\item
+  if the out of the box set of types is not capable of fulfilling more
+  demanding needs custom data types may be defined
 \end{itemize}
+
+In any case the implementation of the data conversion algorithms must be
+recognized as an engineering task, and therefore this topic is not
+considered for further discussion.
+
+\hypertarget{metadata---must-be-discussed-in-context-of-the-designrun-time-stages}{%
+\subsection{Metadata - must be discussed in context of the design/run
+time
+stages}\label{metadata---must-be-discussed-in-context-of-the-designrun-time-stages}}
+
+Possibility to import metadat + necessity for types mapping
+=\textgreater{} design time; support by the Infromation Model design
+tool.
+
+\hypertarget{device-template-dt}{%
+\subsubsection{Device Template (DT)}\label{device-template-dt}}
+
+\hypertarget{device-capability-model-dcm}{%
+\subsubsection{Device Capability Model
+(DCM)}\label{device-capability-model-dcm}}
+
+\hypertarget{interface}{%
+\subsubsection{Interface}\label{interface}}
+
+\hypertarget{digital-twin-definition-language-dtdl}{%
+\subsubsection{Digital Twin Definition Language
+(DTDL)}\label{digital-twin-definition-language-dtdl}}
+
+\hypertarget{connectivity}{%
+\subsection{Connectivity}\label{connectivity}}
+
+\hypertarget{how-to-implement}{%
+\subsection{How to implement}\label{how-to-implement}}
+
+All about available libraries and tools
 
@@
 \end{itemize}
+
+Any information about available reusable deliverables related to this
+work.
+
+\hypertarget{iot}{%
+\subsection{IoT}\label{iot}}
+
+Internet of Things is all about
+
+\begin{itemize}
+\tightlist
+\item
+  Mobile data fetching -- how to gather the data from mobile devices
+  (things)
+\item
+  Mobile data subscription -- how to transfer the data over the Internet
+  to a place where it could be subscribed.
+\item
+  Mobile data consumption -- data processing, computation
+\end{itemize}
+
+Mobile data fetching is related to variety of last mile communication
+technologies, for example RFID, WI-FI, VHF, etc. Subscription could be
+supported using messaging systems, e.g.~AMQP. A good candidate to
+leverage consumption is OPC Unified Architecture.
+
+To deploy this scenario
+
+\begin{itemize}
+\tightlist
+\item
+  the mobile data must be sent over the Internet using messages;
+\item
+  the payload of these messages is consumed by an OPC Server responsible
+  to expose it in the Address Space;
+\item
+  the application as an OPC UA client consumes the exposed data and
+  generates revenue for the end-user.The phrase ``Internet of Things''
+  started its life as the title of a presentation made in 1999 and aimed
+  at explaining a new idea of radio frequency identification (RFID) in
+  the context of the supply chain performance. It is clear that it
+  doesn't mean that someone has any right to control how others use the
+  phrase, but my point is that a precise term definition is important
+  for working together on: common rules, architecture, solutions,
+  requirements, capabilities, limitations, etc. In practice having a
+  common definition it is possible to check a selected technology,
+  solution or product capabilities against requirements of the
+  application entitled to use this term.
+\end{itemize}
+
+My proposal of the Internet of Things definition is as follows:
+
+Internet of Things is all about:
+
+\begin{itemize}
+\tightlist
+\item
+  mobile data fetching -- how to gather the data from mobile devices
+  (things);
+\item
+  mobile data subscription -- how to transfer the data over the Internet
+  to a place where it could be processed;
+\item
+  mobile data processing -- how to integrate the data into a selected
+  application to improve process behavioral performance.
+\end{itemize}
+
+Data fetching is related to a variety of last mile communication
+technologies, for example RFID, WI-FI, VHF, Bluetooth, etc. Subscription
+could be supported using messaging systems, e.g.~AMQP, MQTT, etc. A good
+candidate for leveraging data consumption is for example OPC Unified
+Architecture.
 

### 2020-10-08 Latex/jacs-paper-template/jacs-paper-template/jacs-paper-template.tex
Adopt jacs-paper-template #32
- added template to the folder.

% vim:encoding=utf8 ft=tex sts=2 sw=2 et:
% Copyright (c) 2009 Jaroslaw Koszuk
%
% $Id$

\documentclass{jacsart}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{txfonts}

\newtheorem{definition}{Definition}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{corollary}[definition]{Corollary}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{example}[definition]{Example}

\title{Title of the paper submitted to the Journal of Applied Computer
  Science\footnote{put a footnote to the title if necessary}}
\headtitle{Title of the paper submitted to JACS\dots}
\author{Author One\inst{1}, Author Two\inst{1,2}}
\headauthor{A. One, A. Two}
\affiliation{%
  \inst{1}Name of the Unit represented (e.g. Your University)\\
  Faculty/Department/Office Name\\
  Postal Addres with the zip-code\\
  yourid@your.mail.server
  \andinst
  \inst{2}Name of the Unit represented (e.g. Your University)\\
  Faculty/Department/Office Name\\
  Postal Addres with the zip-code\\
  yourid@your.mail.server}
\keywords{keyword 1, keyword 2, keyword 3, keyword, keyword, keyword, keyword, keyword, keyword}

\begin{document}
\maketitle

\begin{abstract}
Each paper should be followed by a compact abstract which points to the main
scopes and the results obtained by the paper. The abstract should be written
with the Times New Roman font, 10 pt, justified, and with the 1cm margin both
left and right side with respect  to the margin of the paper. The abstract should not contain any formulas or references, and should not exceed 200 words. 
\end{abstract}

\section{Title of section}
\indent Journal of Applied Computer Science publishes original papers only. Full
papers not exceeding 22 standard pages (30 lines $\times$ 60 characters), should be
submitted electronically (preferably by e-mail), or on CD. They will not be returned except for
editorial reasons.\\
\indent Contributions should be written in good English and prepared in \LaTeX. The Authors are strongly
encouraged to follow the \LaTeX{} {\tt jacsart.cls} and BiBTeX {\tt
aiaa-jacs.bst} styles included to this template, as far as published at:\newline
{\tt http://www.jacs.ics.p.lodz.pl}.\\
\indent Illustrations (with captions), drawings, tables, diagrams and equations should be
incorporated in the text and numbered consecutively. Mathematical symbols should
be typeset using the math mode of \LaTeX. The references should be
enumerated in order of appearing in text, and formatted as shown in
Section~\ref{bib}, p.~\pageref{bib}, preferably using the BiBTeX style {\tt
aiaa-jacs.bst}.

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nam elit. Etiam
hendrerit. Nulla arcu. Etiam convallis, lectus in feugiat consequat, tortor
orci laoreet erat, in varius leo nisi pharetra orci. Sed arcu elit, semper
pulvinar, tempor vel, rhoncus in, risus. Nunc dignissim massa id dui. Aenean
viverra, odio ac tincidunt adipiscing, augue ligula faucibus velit, ac
sollicitudin lacus tellus sed elit.

\begin{definition} \label{label-of-definition}
The text of your definition goes here
\end{definition}

\begin{theorem} \label{label-of-theorem}
The text of your theorem goes here
\end{theorem}

\begin{proposition} \label{label-of-proposition}
The text of your proposition goes here
\end{proposition}

\begin{corollary} \label{label-of-corollary}
The text of your corollary goes here
\end{corollary}

\begin{proof} \label{label-of-proof}
The text of your proof goes here
\end{proof}

Quisque ultricies\footnote{An example of footnote} tortor non elit. Nunc vestibulum. Donec libero. Sed id quam
auctor odio semper rutrum. Proin convallis neque quis nisl. Praesent tempor
est vel urna. Etiam bibendum ipsum pellentesque felis. Phasellus et sapien
quis sem tincidunt lobortis. Quisque ultricies tincidunt justo. Maecenas at
nibh a urna condimentum fermentum. Duis tempor, ante vel rhoncus fermentum,
velit dui dignissim odio, ut suscipit quam massa eu velit.

Sed placerat ultrices urna. Sed tincidunt eleifend nibh. In scelerisque dictum
enim. Duis sit amet lectus ut lorem hendrerit sodales.

\begin{figure}[!t] %figures should be placed at the top of the page
\centering
\includegraphics[width=0.9\textwidth]{5figivfq}
\caption{This is caption of the figure}
\label{label-of-figure-1}
\end{figure}

Aliquam porttitor, lectus at gravida posuere, purus est pellentesque odio,
interdum auctor pede orci a diam. Pellentesque tincidunt tincidunt sem.
Curabitur ut enim sit amet turpis cursus adipiscing.

\subsection{The title of subsection 1}
Phasellus tincidunt.
Praesent sit amet erat. Maecenas volutpat vehicula dui. Maecenas ligula urna,
cursus ac, egestas in, bibendum at, tellus. In posuere. Nullam orci sem,
hendrerit lobortis, facilisis eget, accumsan non, ipsum. Integer euismod.
Class aptent taciti sociosqu ad litora torquent per conubia nostra, per
inceptos himenaeos. In molestie velit ut purus. Suspendisse id erat. Phasellus
bibendum purus egestas sapien.

\begin{equation} \label{label-of-equation-1}
  e^{i \pi} + 1 = 0
\end{equation}

Donec rhoncus turpis in tellus. Integer tellus. Etiam in lectus ac nunc
placerat interdum. Sed tincidunt porta enim. Aenean at massa a nisi volutpat
bibendum. Vivamus purus.

\begin{eqnarray}
\mu_3(x) = \left\{ 
\begin{array}{cc}
      {x-3 \over 7}, & \mbox{if $3 \leq x \leq 10$} \\
      0, & \mbox{otherwise}
\end{array}
\right.
\end{eqnarray}

Praesent nec leo. Pellentesque sodales arcu ac quam.
Aliquam elit leo, lobortis eget, tincidunt sed, consequat at, elit. Aenean ut
diam. Nulla id nibh nec odio eleifend luctus. Maecenas orci arcu, fermentum
sed, placerat a, aliquet nec, felis.

\subsection{The title of subsection 2}
Donec risus. Aliquam vel nibh. Nulla gravida accumsan quam. Suspendisse
lacinia ligula ut orci. Donec ligula erat, pellentesque sed, fermentum a,
viverra euismod, diam. Integer consectetur, leo eu bibendum iaculis, libero
felis porttitor tortor, nec facilisis augue enim eget ligula. Phasellus ac leo
eu augue sagittis pulvinar. Sed feugiat. Nullam lorem est, sodales sed,
sagittis vitae, viverra sed, magna. Nulla urna magna, volutpat vitae,
fermentum id, ultrices sed, pede. Pellentesque et libero.

\subsubsection{The title of subsubsection} 
Mauris semper quam
eget massa. Nam turpis orci, sollicitudin ac, suscipit et, auctor sit amet,
lacus. Integer ut justo nec ligula rutrum bibendum. Cras vehicula nisl id
magna. Suspendisse ultricies varius mauris.
\begin{eqnarray}
CL(\mbox{$x$ is $l_i$ {\sc and} $l_j$}) = \mu_{S_i \cap
S_j}(x) = & \nonumber \\
= \left[\min\{\underline\mu_{S_i}(x), \underline\mu_{S_j}(x)\},\right. & \left. \min\{\overline\mu_{S_i}(x), \overline\mu_{S_j}(x)\}\right] 
\end{eqnarray}

\paragraph{The title of paragraph}
Integer commodo ipsum vitae enim. Morbi mollis nunc suscipit nisl.
Class aptent taciti sociosqu ad litora torquent per conubia nostra, per
inceptos himenaeos. Nam urna lacus, placerat posuere, dapibus eget, gravida
at, lorem. Aliquam nec justo eu dui semper fringilla.

\subparagraph{The title of subparagraph}
Aliquam vitae urna.

Morbi mattis consectetur ante. Ut ante massa, vestibulum ut, accumsan ac,
convallis quis, orci. Pellentesque at ipsum vitae quam laoreet tristique. Cras
vel nunc. Nulla facilisi. Aliquam erat volutpat. Cras ipsum
odio, gravida sed, aliquet eget, gravida at, pede. Nulla eros tellus, ornare
in, ultrices porttitor, ultricies eget, justo. Etiam porttitor rutrum erat.
Donec quam.

\begin{table}[!t]
\caption{The caption of the table} 
\centering
\begin{tabular}{ | l | l | l | p{5cm} |}
\hline
\bf Day & \bf Min Temp & \bf  Max Temp & \bf Summary \\ \hline
Monday & 11C & 22C & A clear day with lots of sunshine.  
However, the strong breeze will bring down the temperatures. \\ \hline
Tuesday & 9C & 19C & Cloudy with rain, across many northern regions. Clear spells 
across most of Scotland and Northern Ireland, 
but rain reaching the far northwest. \\ \hline
Wednesday & 10C & 21C & Rain will still linger for the morning. 
Conditions will improve by early afternoon and continue 
throughout the evening. \\
\hline
\end{tabular}
\label{label-of-table}
\end{table}

\section{Conclusions}
Ut purus. Nullam facilisis porttitor enim. Vestibulum nulla massa, ultricies
sed, molestie luctus, imperdiet eget, mi. \\
\indent Integer commodo ipsum vitae enim. Morbi mollis nunc suscipit nisl.
Class aptent taciti sociosqu ad litora torquent per conubia nostra, per
inceptos himenaeos. Nam urna lacus, placerat posuere, dapibus eget, gravida
at, lorem. Aliquam nec justo eu dui semper fringilla. Aliquam vitae urna.
Morbi mattis consectetur ante. Ut ante massa, vestibulum ut, accumsan ac,
convallis quis, orci. Pellentesque at ipsum vitae quam laoreet tristique. Cras
vel nunc. Nulla facilisi.\\
\indent Pellentesque fringilla nulla vitae metus varius faucibus. Fusce aliquet
vehicula risus. Donec pulvinar viverra lectus. Nam tristique. Nulla malesuada
metus nec purus. Ut aliquam diam. Phasellus eu dui vel ipsum aliquet
vestibulum. Quisque ullamcorper, ligula in placerat imperdiet, risus risus
malesuada dolor, ut scelerisque ipsum nisi eu urna. Mauris bibendum tortor
condimentum mauris.

\subsection{Some notes on references}\label{bib}
The references should be formatted using the BiBTeX program and the\newline {\tt
aiaa-jacs.bst} style. Here are examples of citing: \cite{sambuc75}, \cite{chiclana04,
bartkiewicz00, atanassov83}.

%%%%%%%%%% USE ____BIBTEX____ TO GENERATE YOUR REFERENCES 
%%%%%%%%%%% PLEASE UNCOMMENT THE TWO FOLLOWING LINES

%%%%%%%%%% please DO NOT use the \bibitem command %%%%%%%%%%%%
%%%%%%%%%% or the {thebibliograhy} environment    %%%%%%%%%%%%

\bibliography{references-jacs} % or any of your reference files with entries 
\bibliographystyle{aiaa-jacs}

\end{document}

### 2020-10-08 Latex/Manuscript.tex
Adopt jacs-paper-template #32
- applied template setting to the Manuscript.tex
- refactoring names

--- 2020-09-29 Latex/Manuscript..tex
@@
-\documentclass{article}
+\documentclass{jacsart}
 \usepackage{hyperref}
 \usepackage{cite}
-\usepackage{graphicx}
 \usepackage{stfloats}
@@
 \usepackage{authblk}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{graphicx}
+\usepackage{amsthm}
+\usepackage{txfonts}
+
+\newtheorem{definition}{Definition}
+\newtheorem{theorem}[definition]{Theorem}
+\newtheorem{corollary}[definition]{Corollary}
+\newtheorem{proposition}[definition]{Proposition}
+\newtheorem{example}[definition]{Example}
 
@@
 % \title{Object-Oriented Internet - reactive visualization of asynchronous data using AZURE}
-\author[1]{Mariusz Postół}
-\author[2]{Piotr Szymczak}
-\author[3]{Clemens Vasters}
-\affil[1, 2]{Institute of Information Technology, Lodz University of Technology, Łódź, Poland}
+\headtitle{OOI - Azure interoperability}
+
+%\author[1]{Mariusz Postół}
+%\author[2]{Piotr Szymczak}
+%\author[3]{Clemens Vasters}
+%\affil[1, 2]{Institute of Information Technology, Lodz University of Technology, Łódź, Poland}
 % \email{mailto:mariusz.postol@p.lodz.pl} 
-\affil[3]{Microsort}
+%\affil[3]{Microsort}
 %\tocauthor{Mariusz Postół}
 %\institute{ Institute of Information Technology, Lodz University of Technology, Łódź, Poland \email{mailto:mariusz.postol@p.lodz.pl} }
+
+\author{Author One\inst{1}, Author Two\inst{1,2}}
+\headauthor{A. One, A. Two}
+\affiliation{%
+  \inst{1}Name of the Unit represented (e.g. Your University)\\
+  Faculty/Department/Office Name\\
+  Postal Addres with the zip-code\\
+  yourid@your.mail.server
+  \andinst
+  \inst{2}Name of the Unit represented (e.g. Your University)\\
+  Faculty/Department/Office Name\\
+  Postal Addres with the zip-code\\
+  yourid@your.mail.server}
+
+\keywords{Azure, Cloud Computing, Object-Oriented Internet, Industrial communication, Industry 4.0, Internet of Things, Machine to Machine Communication, OPC Unified Architecture}
 
@@
 \begin{abstract}
-
-TBD
-
-\keywords{Azure, Cloud Computing, Object-Oriented Internet, Industrial communication, Industry 4.0, Internet of Things, Machine to Machine Communication, OPC Unified Architecture}
-
+Each paper should be followed by a compact abstract which points to the main
+scopes and the results obtained by the paper. The abstract should be written
+with the Times New Roman font, 10 pt, justified, and with the 1cm margin both
+left and right side with respect  to the margin of the paper. The abstract should not contain any formulas or references, and should not exceed 200 words. 
 \end{abstract}
@@
 \bibliography{Manuscript}
-\bibliographystyle{splncs04}
+\bibliographystyle{aiaa-jacs.bst}
 

### 2020-10-08 Latex/Manuscript.pandoc.tex
Adopt jacs-paper-template #32
- fixed #32

@@
 selection of the services supporting web user interface capable to
-expose real-time process data. Service is any autonomous (with own
-identity) software component or module that is interfacing with selected
-cyber-physical systems for data collection, analysis, and also remote
-control. Microsoft Azure is a cloud-based product. It offers a vast
-variety of services. This virtual environment handles an unlimited
-number of users and devices organized using a solution concept. The
-solution aggregates users, devices, services, and required additional
-resources scoping on a selected scenario. The solution is a region that
-provides a scope to the identifiers (the names of devices, users,
-process data entities, etc) inside it. Solutions are used to organize
-deployment entities into logical groups and prevent identity collisions.
+expose real-time process data. In this context, the service is any
+autonomous (with own identity) software component or module that is
+interfacing with selected cyber-physical systems for data collection,
+analysis, and also remote control. Microsoft Azure is a cloud-based
+product. It offers a vast variety of services. This virtual environment
+handles an unlimited number of users and devices organized using a
+solution concept. The solution aggregates users, devices, services, and
+required additional resources scoping on a selected scenario. The
+solution is a region that provides a scope to the identifiers (the names
+of devices, users, process data entities, etc) inside it. Solutions are
+used to organize deployment entities into logical groups and prevent
+identity collisions.
 
-The \texttt{IoT\ Central} service provides process data visualization
+The \texttt{IoT\ Central} service provides a process data visualization
 user interface. To make this interface meaningful metadata called device
@@
 Following the assumption that interconnection between the cyber-physical
-system and cloud services is designed based on the gateway concept a
+system and cloud services is designed based on the gateway concept, a
 middleware must be considered aa a coupler. It must be interconnected
@@
 relationships, etc.) governing communication of the parts making it up.
-At the same time it must support back-and-forth communication transfer
-data to the cloud using out-of-bound native for the cloud services. The
-transfer process requires data conversion from source to destination
-encoding. The `IoT Hub' is a service that supports \texttt{IoT\ Central}
-providing robust messaging solution. This communication is transparent,
-i.e.~it is not data types aware allowing any devices to exchange any
-kind of data. This service is responsible to manage the device
-identities and offers the following protocol stacks: AMQP, MQTT, HTTPS.
+At the same time, it must support back-and-forth data transfer to the
+cloud using out-of-bound native for the cloud services. The transfer
+process requires data conversion from source to destination encoding.
+The \texttt{IoT\ Hub} is a service hosted in the cloud that supports
+\texttt{IoT\ Central} providing a robust messaging solution - it acts as
+a central message hub for bi-directional communication. This
+communication is transparent, i.e.~it is not data types aware allowing
+any devices to exchange any kind of data. This service is responsible to
+manage the devices' identity and it offers the following protocol
+stacks: AMQP, MQTT, HTTPS.
 
-Before the process data can be exposed using web user interface the data
-source must be associated with appropriate solution and validated to
+Before process data can be exposed using a web user interface the data
+source must be associated with an appropriate solution and validated to
 make sure that the security rules are not violated. It is hard to assume
-that the security rules governing the cyber-physical system may be
-applicable to the cloud-based services. The
+that the security rules governing the cyber-physical system may also
+apply to the cloud-based services. In the gateway scenario, they can be
+mapped on each other or entirely independent. The
 \texttt{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper
 service for \texttt{IoT\ Hub} that enables devices registration,
-authentication and authorization of the requested operations including
-but not limiting to data transfer updating the user interface.
+authentication, and authorization of the requested operations including
+but not limited to data transfer updating the user interface.
 
-It is worth stressing that services interaction can be flexibly
-configured, and as a result the presented above selection of services
-must be recognized as an example only. The `\texttt{IoT\ Central}can be
-also seamlessly integrated with other services as needed. The following
-services could also be considered to build cloud based automation
-solution:
+It is worth stressing that interaction of the offered by the Azure
+services can be configured flexibly, and as a result, the presented
+above selection of services must be recognized as an example only. The
+`\texttt{IoT\ Central} can be also seamlessly integrated with other
+services as needed. The following services could also be considered to
+build cloud-based automation solution:
 
@@
   \texttt{Digital\ Twins} - managing the graph of digital twins, which
-  are to represent some real world process or entity
+  are to represent some real-world process or entity
 \end{itemize}
@@
 
-\hypertarget{simple-complex-and-structural-data-processing}{%
-\subsection{Simple, complex and structural data
-processing}\label{simple-complex-and-structural-data-processing}}
+\hypertarget{data-interchange}{%
+\subsection{Data Interchange}\label{data-interchange}}
 
-System interoperability means the necessity of the information exchange
-between them. The main challenge of interoperability implementation is
-that information is abstract -- it is knowledge describing the process
-in concern state and behavior, e.g.~temperature in a boiler, a car
-speed, an account balance, etc. Unfortunately cyber-physical machines
-cannot be used to process abstraction. It is also impossible to transfer
-abstraction from one place to another.
+System components interoperability means the necessity of the
+information exchange between them. The main challenge of
+interoperability implementation is that information is abstract -- it is
+knowledge describing the process in concern state and behavior,
+e.g.~temperature in a boiler, a car speed, an account balance, etc.
+Obviously, abstraction cannot be processed by the cyber-physical
+machines. It is also impossible to transfer abstraction from one place
+to another over the network.
 
-Fortunately, there is a very simple solution to address that
-impossibility, namely the information must be represented as binary
-stream. In consequence, we can usually use both ones as interchangeable
-terms while talking about ICT systems. Unfortunately, these terms must
-be distinguished in the context of further discussion, because before
-stepping forward we must be aware of the fact that the same information
-could have many different but equivalent representations, namely the
-same information can be successfully represented by a vast variety of
-different binary patterns. For example, 2's Complement and
+Fortunately, computer science offers a workaround to address that
+impossibility - the information must be represented as a binary stream.
+In consequence, we can usually use both ones as interchangeable terms
+while talking about ICT systems. Unfortunately, these terms must be
+precisely observed in the context of further discussion, because we must
+be aware of the fact that the same information could have many different
+but equivalent representations. In other words, the same information can
+be represented by a vast variety of different binary patterns. For
+example, numbers may be represented using 2's Complement and
 Floating-Point binary representations.
@@
 It should be nothing new for us, as it is obvious that the same
-information written as a text in regional newspapers in English, German,
+information printed as a text in regional newspapers in English, German,
 Polish, etc. does not resemble one another, but the text meaning should
-be always the same. To understand a newspaper we must learn the
+always be the same. To understand a newspaper we must learn the
 appropriate language. To understand the binary data we must have defined
-a data type -- a description how to create an appropriate bits pattern
-(syntax) and rules needed to assign the information (semantics),
+a data type -- a description of how to create an appropriate bits
+pattern (syntax) and rules needed to assign the information (semantics),
 i.e.~make any correct bits stream meaningful. Concluding, to make two
-systems interoperable, a semantic context must be establish. The type
+systems interoperable, a semantic-context must be established. The type
 plays the role of metadata, a set of data that describes other data.
 Metadata term is frequently used if the semantic-context is defined
-using a native language to select built-in types using a general purpose
-graphical user interface.
+using a native language to select built-in types engaging a
+general-purpose graphical user interface.
 
@@
 \item
-  Development user interface against type definition
+  Development against a type definition of the user interface
 \item
-  Implementation of the bits-streams conversions functionality in
+  Implementation of the functionality of the bits-streams conversion in
   advance
@@
 Having defined types in advance, a gateway may provide dedicated
-conversions functionality, e.g.~replacing bits-stream used by the
-cyber-physical system by equivalent for the cloud-based services. The
-Azure offers a vast variety of build-in types ready to be used in common
-cases, but not necessarily they are equivalent counterparts in use by
-the cyber-physical system. Additionaly the data conversion must address
-the following issues:
+conversions functionality, i.e.~replacing bits-stream used by the
+cyber-physical system by equivalent once for the cloud-based services.
+The Azure offers a vast variety of build-in types ready to be used in
+common cases, but not necessarily there are equivalent counterparts in
+use by the cyber-physical system. Additionally, the data conversion must
+address the following issues:
 
@@
 \item
-  usually to covert types from source to destination the native types
-  must be used by the middleware software
+  usually to covert data from source to destination representation, the
+  middleware software native types must be used
 \item
@@
 
-In any case the implementation of the data conversion algorithms must be
-recognized as an engineering task, and therefore this topic is not
-considered for further discussion.
+Although the data conversion is a run-time gateway task the
+implementation of the conversion algorithms must be recognized as an
+engineering task, and therefore this topic is not considered for further
+discussion.
 
-\hypertarget{metadata---must-be-discussed-in-context-of-the-designrun-time-stages}{%
-\subsection{Metadata - must be discussed in context of the design/run
-time
-stages}\label{metadata---must-be-discussed-in-context-of-the-designrun-time-stages}}
-
-Possibility to import metadat + necessity for types mapping
-=\textgreater{} design time; support by the Infromation Model design
-tool.
-
-\hypertarget{device-template-dt}{%
-\subsubsection{Device Template (DT)}\label{device-template-dt}}
-
-\hypertarget{device-capability-model-dcm}{%
-\subsubsection{Device Capability Model
-(DCM)}\label{device-capability-model-dcm}}
-
-\hypertarget{interface}{%
-\subsubsection{Interface}\label{interface}}
-
-\hypertarget{digital-twin-definition-language-dtdl}{%
-\subsubsection{Digital Twin Definition Language
-(DTDL)}\label{digital-twin-definition-language-dtdl}}
+In \texttt{IoT\ Central} a cyber-physical system is represented as a set
+of devices. The characteristics and behaviors of each of a device kind
+are described by the device template. This Device Template (DT)contains
+also metadata describing the data (called telemetry) exchanged over the
+wire with the cyber-physical system called Device Capability Model
+(DCM). Additionally, the DT contains properties, customization, and
+views definitions used by the service locally. As an option, DCM
+expressed as a JSON can be imported into a Device Template.
+\texttt{IoT\ Central} allows also to create or edit a DCM using the
+dedicated web UI. A JSON file containing DCM can be derived from an
+information model used as a foundation to establish the semantic-context
+applied to achieve interoperability of the devices interconnected as the
+cyber-physical system. DCM development against any external information
+model is a design-time task and should be supported by dedicated
+development tools. In any case, the data interchanged between the cloud
+and the gateway must be compliant with the DCM, hence the middleware
+software must be aware of conversions that must be applied to achieve
+this interoperability.
 
@@
 
-\hypertarget{how-to-implement}{%
-\subsection{How to implement}\label{how-to-implement}}
+From the cloud side, it is proposed to employ the \texttt{IoT\ Hub}
+service to handle the network traffic targeting the cyber-physical
+system. This service offers profiles of the AMQP, MQTT, HTTPS protocol
+stacks. In any case, process data (telemetry) is transparently
+transferred back-and-forth to the upper layer \texttt{IoT\ Central}
+service. Hence, the payload formatting is determined by the DCM
+associated with the \texttt{IoT\ Central} solution. All the mentioned
+protocols are standard ones. Consequently, it is possible to apply any
+available implementation compliant with an appropriate specification to
+achieve connectivity. In this case, all parameters required to establish
+connectivity and security-context is up to the external software
+responsibility. Alternatively, the API offered by the dedicated
+libraries may be used. Using this API the configuration process can be
+reduced significantly. Using these libraries, the selection of the
+communication protocol has an indirect impact on the interoperability
+features, including performance. The connectivity with
+\texttt{IoT\ Hub}, for example, can be obtained using:
 
-All about available libraries and tools
+\begin{itemize}
+\tightlist
+\item
+  \texttt{Microsoft.Azure.Devices} - Service SDK for Azure IoT Devices
+\item
+  \texttt{Microsoft.Azure.Devices.Client}- Device SDK for Azure IoT Hub
+\item
+  \texttt{Microsoft.Azure.Devices.Provisioning.Client} - Provisioning
+  Device Client SDK for Azure IoT Devices
+\item
+  \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Amqp} -
+  Provisioning Device Client AMQP Transport for Azure IoT Devices
+\item
+  \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Http} -
+  Provisioning Device Client Http Transport for Azure IoT Devices
+\item
+  \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Mqtt} -
+  Provisioning Device Client MQTT Transport for Azure IoT Devices
+\item
+  \texttt{Microsoft.Azure.Devices.Shared} - Common code for Azure IoT
+  Device and Service SDKs
+\end{itemize}
 

### 2020-10-08 Latex/Manuscript.tex
Adopt jacs-paper-template #32
- fixed #32

@@
 
-\title{Object-Oriented Internet - Azure interoperability}
+\title{Object-Oriented Internet - Azure Interoperability}
 % \title{Object-Oriented Internet - reactive visualization of asynchronous data using AZURE}
-\headtitle{OOI - Azure interoperability}
+\headtitle{OOI - Azure Interoperability}
 
-%\author[1]{Mariusz Postół}
-%\author[2]{Piotr Szymczak}
-%\author[3]{Clemens Vasters}
-%\affil[1, 2]{Institute of Information Technology, Lodz University of Technology, Łódź, Poland}
-% \email{mailto:mariusz.postol@p.lodz.pl} 
-%\affil[3]{Microsort}
-%\tocauthor{Mariusz Postół}
-%\institute{ Institute of Information Technology, Lodz University of Technology, Łódź, Poland \email{mailto:mariusz.postol@p.lodz.pl} }
-
-\author{Author One\inst{1}, Author Two\inst{1,2}}
+\author{Mariusz Postół\inst{1}, Piotr Szymczak\inst{1}, Clemens Vasters\inst{2}}
 \headauthor{A. One, A. Two}
 \affiliation{%
-  \inst{1}Name of the Unit represented (e.g. Your University)\\
+  \inst{1}Lodz University of Technology\\
+  Institute of Information Technology\\
+  ul. Wólczańska 215, 90-924 Lodz, Poland\\
+  mailto:mariusz.postol@p.lodz.pl
+  \andinst
+  \inst{2}Microsoft\\
   Faculty/Department/Office Name\\
   Postal Addres with the zip-code\\
-  yourid@your.mail.server
-  \andinst
-  \inst{2}Name of the Unit represented (e.g. Your University)\\
-  Faculty/Department/Office Name\\
-  Postal Addres with the zip-code\\
-  yourid@your.mail.server}
+  clemensv@microsoft.com}
 

### 2020-10-08 Latex/20.Introduction.tex
Work out Markdown\20.Introduction.md #26
- convert to latex

--- 2020-10-07 Latex/Manuscript.pandoc.tex
@@
 Any information about available reusable deliverables related to this
-work. \# Azure Main Technology Features
-
-\hypertarget{services}{%
-\subsection{Services}\label{services}}
-
-Deployment of the hybrid solution providing interoperability of the
-\textbf{machine-centric} cyber-physical systems designed atop of M2M
-reactive communication and emerging cloud computing as a
-\textbf{human-centric} front-end requires decisions addressing the
-selection of the services supporting web user interface capable to
-expose real-time process data. Service is any autonomous (with own
-identity) software component or module that is interfacing with selected
-cyber-physical systems for data collection, analysis, and also remote
-control. Microsoft Azure is a cloud-based product. It offers a vast
-variety of services. This virtual environment handles an unlimited
-number of users and devices organized using a solution concept. The
-solution aggregates users, devices, services, and required additional
-resources scoping on a selected scenario. The solution is a region that
-provides a scope to the identifiers (the names of devices, users,
-process data entities, etc) inside it. Solutions are used to organize
-deployment entities into logical groups and prevent identity collisions.
-
-The \texttt{IoT\ Central} service provides process data visualization
-user interface. To make this interface meaningful metadata called device
-template is used to describe devices.
-
-Following the assumption that interconnection between the cyber-physical
-system and cloud services is designed based on the gateway concept a
-middleware must be considered aa a coupler. It must be interconnected
-with the cyber-physical system using an in-bound protocol adhering to
-communications requirements (i.e.~protocol profile, data encoding, time
-relationships, etc.) governing communication of the parts making it up.
-At the same time it must support back-and-forth communication transfer
-data to the cloud using out-of-bound native for the cloud services. The
-transfer process requires data conversion from source to destination
-encoding. The `IoT Hub' is a service that supports \texttt{IoT\ Central}
-providing robust messaging solution. This communication is transparent,
-i.e.~it is not data types aware allowing any devices to exchange any
-kind of data. This service is responsible to manage the device
-identities and offers the following protocol stacks: AMQP, MQTT, HTTPS.
-
-Before the process data can be exposed using web user interface the data
-source must be associated with appropriate solution and validated to
-make sure that the security rules are not violated. It is hard to assume
-that the security rules governing the cyber-physical system may be
-applicable to the cloud-based services. The
-\texttt{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper
-service for \texttt{IoT\ Hub} that enables devices registration,
-authentication and authorization of the requested operations including
-but not limiting to data transfer updating the user interface.
-
-It is worth stressing that services interaction can be flexibly
-configured, and as a result the presented above selection of services
-must be recognized as an example only. The `\texttt{IoT\ Central}can be
-also seamlessly integrated with other services as needed. The following
-services could also be considered to build cloud based automation
-solution:
-
-\begin{itemize}
-\tightlist
-\item
-  \texttt{Industrial\ IoT} - discovering OPC UA enabled servers in a
-  factory network and register them in Azure IoT Hub implemented using
-  \texttt{IoT\ Edge}
-\item
-  \texttt{Digital\ Twins} - managing the graph of digital twins, which
-  are to represent some real world process or entity
-\end{itemize}
-
-\texttt{Industrial\ IoT} promotes OPC UA client/server archetype used to
-achieve direct and interactive interoperability implemented using
-\texttt{IoT\ Edge} services that allow extracting initial data
-processing to local premises based on the edge concept.
-\texttt{Digital\ Twins} is an emerging concept to use an observer to
-replicate selected process state and behavior. The possibility to add
-value as a result of using these services must be subject to further
-research.
-
-\hypertarget{simple-complex-and-structural-data-processing}{%
-\subsection{Simple, complex and structural data
-processing}\label{simple-complex-and-structural-data-processing}}
-
-System interoperability means the necessity of the information exchange
-between them. The main challenge of interoperability implementation is
-that information is abstract -- it is knowledge describing the process
-in concern state and behavior, e.g.~temperature in a boiler, a car
-speed, an account balance, etc. Unfortunately cyber-physical machines
-cannot be used to process abstraction. It is also impossible to transfer
-abstraction from one place to another.
-
-Fortunately, there is a very simple solution to address that
-impossibility, namely the information must be represented as binary
-stream. In consequence, we can usually use both ones as interchangeable
-terms while talking about ICT systems. Unfortunately, these terms must
-be distinguished in the context of further discussion, because before
-stepping forward we must be aware of the fact that the same information
-could have many different but equivalent representations, namely the
-same information can be successfully represented by a vast variety of
-different binary patterns. For example, 2's Complement and
-Floating-Point binary representations.
-
-It should be nothing new for us, as it is obvious that the same
-information written as a text in regional newspapers in English, German,
-Polish, etc. does not resemble one another, but the text meaning should
-be always the same. To understand a newspaper we must learn the
-appropriate language. To understand the binary data we must have defined
-a data type -- a description how to create an appropriate bits pattern
-(syntax) and rules needed to assign the information (semantics),
-i.e.~make any correct bits stream meaningful. Concluding, to make two
-systems interoperable, a semantic context must be establish. The type
-plays the role of metadata, a set of data that describes other data.
-Metadata term is frequently used if the semantic-context is defined
-using a native language to select built-in types using a general purpose
-graphical user interface.
-
-Using the data type definitions to describe information interchanged
-between communicating parties allows:
-
-\begin{itemize}
-\tightlist
-\item
-  Development user interface against type definition
-\item
-  Implementation of the bits-streams conversions functionality in
-  advance
-\end{itemize}
-
-Having defined types in advance, a gateway may provide dedicated
-conversions functionality, e.g.~replacing bits-stream used by the
-cyber-physical system by equivalent for the cloud-based services. The
-Azure offers a vast variety of build-in types ready to be used in common
-cases, but not necessarily they are equivalent counterparts in use by
-the cyber-physical system. Additionaly the data conversion must address
-the following issues:
-
-\begin{itemize}
-\tightlist
-\item
-  usually to covert types from source to destination the native types
-  must be used by the middleware software
-\item
-  if the out of the box set of types is not capable of fulfilling more
-  demanding needs custom data types may be defined
-\end{itemize}
-
-In any case the implementation of the data conversion algorithms must be
-recognized as an engineering task, and therefore this topic is not
-considered for further discussion.
-
-\hypertarget{metadata---must-be-discussed-in-context-of-the-designrun-time-stages}{%
-\subsection{Metadata - must be discussed in context of the design/run
-time
-stages}\label{metadata---must-be-discussed-in-context-of-the-designrun-time-stages}}
-
-Possibility to import metadat + necessity for types mapping
-=\textgreater{} design time; support by the Infromation Model design
-tool.
-
-\hypertarget{device-template-dt}{%
-\subsubsection{Device Template (DT)}\label{device-template-dt}}
-
-\hypertarget{device-capability-model-dcm}{%
-\subsubsection{Device Capability Model
-(DCM)}\label{device-capability-model-dcm}}
-
-\hypertarget{interface}{%
-\subsubsection{Interface}\label{interface}}
-
-\hypertarget{digital-twin-definition-language-dtdl}{%
-\subsubsection{Digital Twin Definition Language
-(DTDL)}\label{digital-twin-definition-language-dtdl}}
-
-\hypertarget{connectivity}{%
-\subsection{Connectivity}\label{connectivity}}
-
-\hypertarget{how-to-implement}{%
-\subsection{How to implement}\label{how-to-implement}}
-
-All about available libraries and tools
-
-\hypertarget{ooi-main-technology-features}{%
-\section{OOI Main Technology
-Features}\label{ooi-main-technology-features}}
-
-\begin{itemize}
-\tightlist
-\item
-  Machinie To Machine communication based on the semantic data
-\item
-  OOI PubSub Implementation Architecture
-\item
-  Simple, complex and structural data processing
-\end{itemize}
-
-Any information about available reusable deliverables related to this
 work.
 
-\hypertarget{iot}{%
-\subsection{IoT}\label{iot}}
-
-Internet of Things is all about
-
-\begin{itemize}
-\tightlist
-\item
-  Mobile data fetching -- how to gather the data from mobile devices
-  (things)
-\item
-  Mobile data subscription -- how to transfer the data over the Internet
-  to a place where it could be subscribed.
-\item
-  Mobile data consumption -- data processing, computation
-\end{itemize}
-
-Mobile data fetching is related to variety of last mile communication
-technologies, for example RFID, WI-FI, VHF, etc. Subscription could be
-supported using messaging systems, e.g.~AMQP. A good candidate to
-leverage consumption is OPC Unified Architecture.
-
-To deploy this scenario
-
-\begin{itemize}
-\tightlist
-\item
-  the mobile data must be sent over the Internet using messages;
-\item
-  the payload of these messages is consumed by an OPC Server responsible
-  to expose it in the Address Space;
-\item
-  the application as an OPC UA client consumes the exposed data and
-  generates revenue for the end-user.The phrase ``Internet of Things''
-  started its life as the title of a presentation made in 1999 and aimed
-  at explaining a new idea of radio frequency identification (RFID) in
-  the context of the supply chain performance. It is clear that it
-  doesn't mean that someone has any right to control how others use the
-  phrase, but my point is that a precise term definition is important
-  for working together on: common rules, architecture, solutions,
-  requirements, capabilities, limitations, etc. In practice having a
-  common definition it is possible to check a selected technology,
-  solution or product capabilities against requirements of the
-  application entitled to use this term.
-\end{itemize}
-
-My proposal of the Internet of Things definition is as follows:
-
-Internet of Things is all about:
-
-\begin{itemize}
-\tightlist
-\item
-  mobile data fetching -- how to gather the data from mobile devices
-  (things);
-\item
-  mobile data subscription -- how to transfer the data over the Internet
-  to a place where it could be processed;
-\item
-  mobile data processing -- how to integrate the data into a selected
-  application to improve process behavioral performance.
-\end{itemize}
-
-Data fetching is related to a variety of last mile communication
-technologies, for example RFID, WI-FI, VHF, Bluetooth, etc. Subscription
-could be supported using messaging systems, e.g.~AMQP, MQTT, etc. A good
-candidate for leveraging data consumption is for example OPC Unified
-Architecture.
-
-\hypertarget{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity}{%
-\section{Azure to Sensors (A2S) connectivity deployment (field level
-connectivity)}\label{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity}}
-
-\begin{quote}
-The title must be revised
-\end{quote}
-
-\begin{itemize}
-\tightlist
-\item
-  \textbf{Architecture} - Domain model presenting relationship between
-  the: Azure, PubSub Gateway, Device, Design and development tools
-\item
-  \textbf{Connectivity} - Describe reactive nature of the Azure
-  monitoring process data (telemetry) services.
-\item
-  \textbf{Deployment phases}
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Design
-  \item
-    Gateway and devices registration
-  \item
-    Authentication
-  \item
-    Device/Service association
-  \item
-    Device/Application association
-  \item
-    Establishing session
-
-    \begin{itemize}
-    \tightlist
-    \item
-      Device/Device Template (Device Capability Model) association -
-      establishing a semantic-context
-    \item
-      Security management - establishing security-context
-    \end{itemize}
-  \item
-    Interconnection - exchange of data
-  \item
-    Maintenance
-  \end{itemize}
-\end{itemize}
-
-We have selected
-\href{https://docs.microsoft.com/azure/iot-central/core/}{IoT Central}
-because:
-
-\begin{itemize}
-\tightlist
-\item
-  provides process data visualization user interface
-\item
-  allows to describe devices using metadata containing telemetry data
-  types
-\end{itemize}
-
-\hypertarget{gateway-implementation}{%
-\section{Gateway implementation}\label{gateway-implementation}}
-
-\begin{itemize}
-\tightlist
-\item
-  Architecture
-\item
-  Protocol selection and mapping
-\item
-  Configuration
-\item
-  Testing
-\end{itemize}
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-The OPC UA PubSub to Azure gateway (\texttt{AzureGateway})
-implementation has been just published on GitHub as the open-source (MIT
-licensed) as a part of the more general concept of the Object-Oriented
-Internet reactive networking. It is proof of the concept that
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  OPC UA PubSub can be implemented as a powerful standalone package - no
-  C/S dependency
-\item
-  Azure interoperability can be implemented as an out-of-band
-  communication (MQTT, AMQP, HTTP) - no PubSub dependency
-\item
-  Process data functionality can be composable at run-time - no
-  programming required
-\end{enumerate}
-
 \end{document}

### 2020-10-08 Latex/30.AzureTechnologyFeatures.tex
Work out Markdown\40.OOITechnologyFeatures.md #28
- convert to latex

--- 2020-09-28 Latex/Manuscript.pandoc.tex
@@
 
-\hypertarget{document-header}{%
-\section{Document Header}\label{document-header}}
+\hypertarget{azure-main-technology-features}{%
+\section{Azure Main Technology
+Features}\label{azure-main-technology-features}}
 
-\hypertarget{title-proposals}{%
-\subsection{Title proposals}\label{title-proposals}}
+\hypertarget{services}{%
+\subsection{Services}\label{services}}
+
+Deployment of the hybrid solution providing interoperability of the
+\textbf{machine-centric} cyber-physical systems designed atop of M2M
+reactive communication and emerging cloud computing as a
+\textbf{human-centric} front-end requires decisions addressing the
+selection of the services supporting web user interface capable to
+expose real-time process data. In this context, the service is any
+autonomous (with own identity) software component or module that is
+interfacing with selected cyber-physical systems for data collection,
+analysis, and also remote control. Microsoft Azure is a cloud-based
+product. It offers a vast variety of services. This virtual environment
+handles an unlimited number of users and devices organized using a
+solution concept. The solution aggregates users, devices, services, and
+required additional resources scoping on a selected scenario. The
+solution serves as a context that provides a scope to the identifiers
+(the names of devices, users, process data entities, etc) inside it.
+Solutions are used to organize deployment entities into logical groups
+and prevent identity collisions.
+
+The \texttt{IoT\ Central} service provides a process data visualization
+user interface. To make this interface meaningful metadata called device
+template is used to describe devices.
+
+Following the assumption that interconnection between the cyber-physical
+system and cloud services is designed based on the gateway concept, a
+middleware must be considered as a coupler. It must be interconnected
+with the cyber-physical system using an in-band protocol adhering to
+communications requirements (i.e.~protocol profile, data encoding, time
+relationships, etc.) governing communication of the parts making it up.
+At the same time, it must support back-and-forth data transfer to the
+cloud using out-of-band native for the cloud services. The transfer
+process requires data conversion from source to destination encoding.
+The \texttt{IoT\ Hub} is a service hosted in the cloud that supports
+\texttt{IoT\ Central} providing a robust messaging solution - it acts as
+a central message hub for bi-directional communication. This
+communication is transparent, i.e.~it is not data types aware allowing
+any devices to exchange any kind of data. This service is responsible to
+manage the devices' identity and it offers the following protocol
+stacks: AMQP, MQTT, HTTPS.
+
+Before process data can be exposed using a web user interface the data
+source must be associated with an appropriate solution and validated to
+make sure that the security rules are not violated. It is hard to assume
+that the security rules governing the cyber-physical system may also
+apply to the cloud-based services. In the gateway scenario, they can be
+mapped on each other or entirely independent. The
+\texttt{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper
+service for \texttt{IoT\ Hub} that enables devices' connection process
+management, upon device providing valid identity attestation it assigns
+the device to an appropriate \texttt{IoT\ Hub} instance and returns to
+the device connection parameters, which allow direct connection with
+given \texttt{IoT\ Hub} service. The device proceeds to use the same
+attestation in \texttt{IoT\ Hub} connection and based on it, is granted
+authorization to selected resources and operations including but not
+limited to data transfer updating the user interface.
+
+It is worth stressing that interaction of the offered by the Azure
+services can be configured flexibly, and as a result, the presented
+above selection of services must be recognized as an example only. The
+\texttt{IoT\ Central} can be also seamlessly integrated with other
+services as needed. The following services could also be considered to
+build cloud-based automation solution:
 
@@
 \item
-  Object-Oriented Internet - reactive visualization of asynchronous data
-  using AZURE
+  \texttt{Industrial\ IoT} - discovering OPC UA enabled servers in a
+  factory network and register them in Azure IoT Hub implemented using
+  \texttt{IoT\ Edge}
 \item
-  Object-Oriented Internet - Azure interoperability
+  \texttt{Digital\ Twins} - managing the graph of digital twins, which
+  are to represent some real-world process or entity
 \end{itemize}
 
-\hypertarget{abstract}{%
-\subsection{Abstract}\label{abstract}}
+\texttt{Industrial\ IoT} promotes OPC UA client/server archetype used to
+achieve direct and interactive interoperability implemented using
+\texttt{IoT\ Edge} services that allow extracting initial data
+processing to local premises based on the edge concept.
+\texttt{Digital\ Twins} is an emerging concept to use an observer to
+replicate selected process state and behavior. The possibility to add
+value as a result of using these services must be subject to further
+research.
 
-\hypertarget{key-words}{%
-\subsection{Key words}\label{key-words}}
+\hypertarget{data-interchange}{%
+\subsection{Data Interchange}\label{data-interchange}}
 
-Azure, Cloud Computing, Object-Oriented Internet, OPC Unified
-Architecture, Machine to Machine Communication, Internet of Things, OPC
-UA, RxNetworking
+System components interoperability means the necessity of the
+information exchange between them. The main challenge of
+interoperability implementation is that information is abstract -- it is
+knowledge describing the process in concern state and behavior,
+e.g.~temperature in a boiler, a car speed, an account balance, etc.
+Obviously, abstraction cannot be processed by the cyber-physical
+machines. It is also impossible to transfer abstraction from one place
+to another over the network.
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+Fortunately, computer science offers a workaround to address that
+impossibility - the information must be represented as a binary stream.
+In consequence, we can usually use both ones as interchangeable terms
+while talking about ICT systems. Unfortunately, these terms must be
+precisely observed in the context of further discussion, because we must
+be aware of the fact that the same information could have many different
+but equivalent representations. In other words, the same information can
+be represented by a vast variety of different binary patterns. For
+example, numbers may be represented using 2's Complement and
+Floating-Point binary representations.
+
+It should be nothing new for us, as it is obvious that the same
+information printed as a text in regional newspapers in English, German,
+Polish, etc. does not resemble one another, but the text meaning should
+always be the same. To understand a newspaper we must learn the
+appropriate language. To understand the binary data we must have defined
+a data type -- a description of how to create an appropriate bits
+pattern (syntax) and rules needed to assign the information (semantics),
+i.e.~make any correct bitstream meaningful. Concluding, to make two
+systems interoperable, a semantic-context must be established. The type
+plays the role of metadata, a set of data that describes other data.
+Metadata term is frequently used if the semantic-context is defined
+using a native language to select built-in types engaging a
+general-purpose graphical user interface.
+
+Using the data type definitions to describe information interchanged
+between communicating parties allows:
 
@@
 \item
-  \textbf{Subject} - A basic matter of thought, discussion,
-  investigation, development, etc. Describe the problem and the
-  motivation for undertaking the effort to solve the problem.
+  Development against a type definition of the user interface
 \item
-  \textbf{Goal} What we are going to achieve - the result or achievement
-  toward which effort is directed.
-\item
-  \textbf{Scope} - What we must do to prove the goal have been achieved.
-  Extent or range of development, view, outlook, application, operation,
-  effectiveness, etc.
-\item
-  \textbf{Related work} - Any information about available reusable
-  deliverables related to this work.
+  Implementation of the functionality of the bitstreams conversion in
+  advance
 \end{itemize}
 
-\hypertarget{azure-main-technology-features}{%
-\section{Azure Main Technology
-Features}\label{azure-main-technology-features}}
+Having defined types in advance, a gateway may provide dedicated
+conversions functionality, i.e.~replacing bitstream used by the
+cyber-physical system by equivalent one for the cloud-based services.
+The Azure offers a vast variety of built-in types ready to be used in
+common cases, but not necessarily there are equivalent counterparts in
+use by the cyber-physical system. Additionally, the data conversion must
+address the following issues:
 
@@
 \item
-  \textbf{Selection of the service}
+  usually to covert data from source to destination representation, the
+  middleware software native types must be used
 \item
-  \textbf{Metadata} - must be discussed in context of the design/run
-  time stages.
+  if the out of the box set of types is not capable of fulfilling more
+  demanding needs, custom data types must be defined
+\end{itemize}
+
+Although the data conversion is a run-time gateway task the
+implementation of the conversion algorithms must be recognized as an
+engineering task, and therefore this topic is not considered for further
+discussion.
+
+In \texttt{IoT\ Central} a cyber-physical system is represented as a set
+of devices. The characteristics and behaviors of each device kind are
+described by the device template. This Device Template (DT) contains
+also metadata describing the data (called telemetry) exchanged over the
+wire with the cyber-physical system called Device Capability Model
+(DCM). Additionally, the DT contains properties, customization, and
+views definitions used by the service locally. As an option, DCM
+expressed as a JSON-LD can be imported into a Device Template.
+\texttt{IoT\ Central} allows also to create and edit a DCM using the
+dedicated web UI. A JSON file containing DCM can be derived from an
+information model used as a foundation to establish the semantic-context
+applied to achieve interoperability of the devices interconnected as the
+cyber-physical system. DCM development against any external information
+model is a design-time task and should be supported by dedicated
+development tools. In any case, the data interchanged between the cloud
+and the gateway must be compliant with the DCM, hence the middleware
+software must be aware of conversions that must be applied to achieve
+this interoperability.
+
+\hypertarget{connectivity}{%
+\subsection{Connectivity}\label{connectivity}}
+
+From the cloud side, it is proposed to employ the \texttt{IoT\ Hub}
+service to handle the network traffic targeting the cyber-physical
+system. This service offers profiles of the AMQP, MQTT, HTTPS protocol
+stacks. In any case, process data (telemetry) is transparently
+transferred back-and-forth to the upper layer \texttt{IoT\ Central}
+service. Hence, the payload formatting is determined by the DCM
+associated with the \texttt{IoT\ Central} solution. All the mentioned
+protocols are standard ones. Consequently, it is possible to apply any
+available implementation compliant with an appropriate specification to
+achieve connectivity. In this case, all parameters required to establish
+connectivity and security-context is up to the external software
+responsibility. Alternatively, the API offered by the dedicated
+libraries may be used. Using this API the configuration process can be
+reduced significantly. Using these libraries, the selection of the
+communication protocol has an indirect impact on the interoperability
+features, including performance. The connectivity with
+\texttt{IoT\ Hub}, for example, can be obtained using:
 
@@
 \item
-    \textbf{Device Template (DT)}
+  \texttt{Microsoft.Azure.Devices} - Service SDK for Azure IoT Devices
 \item
-    \textbf{Device Capability Model}
+  \texttt{Microsoft.Azure.Devices.Client}- Device SDK for Azure IoT Hub
 \item
-    \textbf{Interface}
+  \texttt{Microsoft.Azure.Devices.Shared} - Common code for Azure IoT
+  Device and Service SDKs
 \item
-    \textbf{Digital Twin Definition Language (DTDL)}
-  \end{itemize}
+  \texttt{Microsoft.Azure.Devices.Provisioning.Client} - Provisioning
+  Device Client SDK for Azure IoT Devices
 \item
-  \textbf{Simple, complex and structural data processing}
+  \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Amqp} -
+  Provisioning Device Client AMQP Transport for Azure IoT Devices
 \item
-  \textbf{Connectivity}
+  \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Http} -
+  Provisioning Device Client Http Transport for Azure IoT Devices
 \item
-  \textbf{How to implement} All about available libraries and tools
+  \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Mqtt} -
+  Provisioning Device Client MQTT Transport for Azure IoT Devices
 \end{itemize}
 
-\hypertarget{ooi-main-technology-features}{%
-\section{OOI Main Technology
-Features}\label{ooi-main-technology-features}}
-
-\begin{itemize}
-\tightlist
-\item
-  Machinie To Machine communication based on the semantic data
-\item
-  OOI PubSub Implementation Architecture
-\item
-  Simple, complex and structural data processing
-\end{itemize}
-
-\hypertarget{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity}{%
-\section{Azure to Sensors (A2S) connectivity deployment (field level
-connectivity)}\label{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity}}
-
-\begin{quote}
-The title must be revised
-\end{quote}
-
-\begin{itemize}
-\tightlist
-\item
-  \textbf{Architecture} - Domain model presenting relationship between
-  the: Azure, PubSub Gateway, Device, Design and development tools
-\item
-  \textbf{Connectivity} - Describe reactive nature of the Azure
-  monitoring process data (telemetry) services.
-\item
-  \textbf{Deployment phases}
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Design
-  \item
-    Gateway and devices registration
-  \item
-    Authentication
-  \item
-    Device/Service association
-  \item
-    Device/Application association
-  \item
-    Establishing session
-
-    \begin{itemize}
-    \tightlist
-    \item
-      Device/Device Template (Device Capability Model) association -
-      establishing a semantic-context
-    \item
-      Security management - establishing security-context
-    \end{itemize}
-  \item
-    Interconnection - exchange of data
-  \item
-    Maintenance
-  \end{itemize}
-\end{itemize}
-
-We have selected
-\href{https://docs.microsoft.com/azure/iot-central/core/}{IoT Central}
-because:
-
-\begin{itemize}
-\tightlist
-\item
-  provides process data visualization user interface
-\item
-  allows to describe devices using metadata containing telemetry data
-  types
-\end{itemize}
-
-\hypertarget{gateway-implementation}{%
-\section{Gateway implementation}\label{gateway-implementation}}
-
-\begin{itemize}
-\tightlist
-\item
-  Architecture
-\item
-  Protocol selection and mapping
-\item
-  Configuration
-\item
-  Testing
-\end{itemize}
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-The OPC UA PubSub to Azure gateway (\texttt{AzureGateway})
-implementation has been just published on GitHub as the open-source (MIT
-licensed) as a part of the more general concept of the Object-Oriented
-Internet reactive networking. It is proof of the concept that
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  OPC UA PubSub can be implemented as a powerful standalone package - no
-  C/S dependency
-\item
-  Azure interoperability can be implemented as an out-of-band
-  communication (MQTT, AMQP, HTTP) - no PubSub dependency
-\item
-  Process data functionality can be composable at run-time - no
-  programming required
-\end{enumerate}
-
 \end{document}

### 2020-10-08 Latex/Manuscript.pandoc.tex
Work out Markdown\40.OOITechnologyFeatures.md #28
- convert to latex

@@
 required additional resources scoping on a selected scenario. The
-solution is a region that provides a scope to the identifiers (the names
-of devices, users, process data entities, etc) inside it. Solutions are
-used to organize deployment entities into logical groups and prevent
-identity collisions.
+solution serves as a context that provides a scope to the identifiers
+(the names of devices, users, process data entities, etc) inside it.
+Solutions are used to organize deployment entities into logical groups
+and prevent identity collisions.
 
@@
 system and cloud services is designed based on the gateway concept, a
-middleware must be considered aa a coupler. It must be interconnected
-with the cyber-physical system using an in-bound protocol adhering to
+middleware must be considered as a coupler. It must be interconnected
+with the cyber-physical system using an in-band protocol adhering to
 communications requirements (i.e.~protocol profile, data encoding, time
@@
 At the same time, it must support back-and-forth data transfer to the
-cloud using out-of-bound native for the cloud services. The transfer
+cloud using out-of-band native for the cloud services. The transfer
 process requires data conversion from source to destination encoding.
@@
 \texttt{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper
-service for \texttt{IoT\ Hub} that enables devices registration,
-authentication, and authorization of the requested operations including
-but not limited to data transfer updating the user interface.
+service for \texttt{IoT\ Hub} that enables devices' connection process
+management, upon device providing valid identity attestation it assigns
+the device to an appropriate \texttt{IoT\ Hub} instance and returns to
+the device connection parameters, which allow direct connection with
+given \texttt{IoT\ Hub} service. The device proceeds to use the same
+attestation in \texttt{IoT\ Hub} connection and based on it, is granted
+authorization to selected resources and operations including but not
+limited to data transfer updating the user interface.
 
@@
 above selection of services must be recognized as an example only. The
-`\texttt{IoT\ Central} can be also seamlessly integrated with other
+\texttt{IoT\ Central} can be also seamlessly integrated with other
 services as needed. The following services could also be considered to
@@
 pattern (syntax) and rules needed to assign the information (semantics),
-i.e.~make any correct bits stream meaningful. Concluding, to make two
+i.e.~make any correct bitstream meaningful. Concluding, to make two
 systems interoperable, a semantic-context must be established. The type
@@
 \item
-  Implementation of the functionality of the bits-streams conversion in
+  Implementation of the functionality of the bitstreams conversion in
   advance
@@
 Having defined types in advance, a gateway may provide dedicated
-conversions functionality, i.e.~replacing bits-stream used by the
-cyber-physical system by equivalent once for the cloud-based services.
-The Azure offers a vast variety of build-in types ready to be used in
+conversions functionality, i.e.~replacing bitstream used by the
+cyber-physical system by equivalent one for the cloud-based services.
+The Azure offers a vast variety of built-in types ready to be used in
 common cases, but not necessarily there are equivalent counterparts in
@@
   if the out of the box set of types is not capable of fulfilling more
-  demanding needs custom data types may be defined
+  demanding needs, custom data types must be defined
 \end{itemize}
@@
 In \texttt{IoT\ Central} a cyber-physical system is represented as a set
-of devices. The characteristics and behaviors of each of a device kind
-are described by the device template. This Device Template (DT)contains
+of devices. The characteristics and behaviors of each device kind are
+described by the device template. This Device Template (DT) contains
 also metadata describing the data (called telemetry) exchanged over the
@@
 views definitions used by the service locally. As an option, DCM
-expressed as a JSON can be imported into a Device Template.
-\texttt{IoT\ Central} allows also to create or edit a DCM using the
+expressed as a JSON-LD can be imported into a Device Template.
+\texttt{IoT\ Central} allows also to create and edit a DCM using the
 dedicated web UI. A JSON file containing DCM can be derived from an
@@
 \item
+  \texttt{Microsoft.Azure.Devices.Shared} - Common code for Azure IoT
+  Device and Service SDKs
+\item
   \texttt{Microsoft.Azure.Devices.Provisioning.Client} - Provisioning
@@
   Provisioning Device Client MQTT Transport for Azure IoT Devices
-\item
-  \texttt{Microsoft.Azure.Devices.Shared} - Common code for Azure IoT
-  Device and Service SDKs
 \end{itemize}

### 2020-10-08 Latex/Manuscript.tex
Work out Markdown\40.OOITechnologyFeatures.md #28
- convert to latex

@@
 \author{Mariusz Postół\inst{1}, Piotr Szymczak\inst{1}, Clemens Vasters\inst{2}}
-\headauthor{A. One, A. Two}
+\headauthor{Postół M, Szymczak P, Vasters C}
 \affiliation{%
@@
 
+All the time, the Information and Communication Technology is providing
+society with a vast variety of new distributed applications aimed at
+micro and macro optimization of the industrial processes. Obviously, the
+design foundation of this kind of application has to focus primarily on
+communication technologies. Based on the role humans take while using
+these applications they can be grouped as follows:
+
 \begin{itemize}
@@
 \item
-        \textbf{Subject} - A basic matter of thought, discussion,
-        investigation, development, etc. Describe the problem and the
-        motivation for undertaking the effort to solve the problem.
+  \textbf{human-centric} - information origin or ultimate information
+  destination is an operator,
 \item
-        \textbf{Goal} What we are going to achieve - the result or achievement
-        toward which effort is directed.
+  \textbf{machine-centric} - information creation, consumption,
+  networking, and processing are achieved entirely without human
+  interaction.
+\end{itemize}
+
+A typical \textbf{human-centric} approach is a web-service supporting,
+for example, a web user interface (UI) to monitor conditions, and manage
+millions of devices and their data in a typical cloud-based IoT
+approach. It is characteristic that, in this case, any uncertainty and
+necessity to make a decision can be relaxed by human interaction.
+Coordination of robots behavior in a work-cell (automation islands) is a
+\textbf{machine-centric} example. In this case, it is essential that any
+human interaction is impractical or even impossible. This
+interconnection scenario requires the machine to machine communication
+(M2M) demanding multi-vendor devices integration.
+
+From the M2M communication concept, a broader concept of a smart factory
+can be derived. In this concept, the mentioned robots are only executive
+assets of an integrated supervisory control system responsible for macro
+optimization of an industrial process composed into one whole.
+Deployment of the smart factory concept requires a hybrid solution and
+interoperability of the mentioned above heterogeneous environments. This
+approach is called the fourth industrial revolution and coined as
+Industry 4.0. It is worth stressing that machines - or more general
+assets - interconnection is not enough, and additionally, assets
+interoperability has to be expected for the deployment of this concept.
+In this case, muli-vendor integration makes communication
+standardization especially important, namely it is required that the
+payload of the message is standardized to be factored on the gathering
+site and consumed on the ultimate destination site.
+
+Highly-distributed solutions used to control real-time process
+aggregating islands of automation (e.g.~virtual power plants producing
+renewable energy) additionally must leverage public communication
+infrastructure, namely the Internet. Internet is a demanding environment
+for highly distributed process control applications designed atop the
+M2M communication paradigm because
+
+\begin{itemize}
+\tightlist
 \item
-        \textbf{Scope} - What we must do to prove the goal have been achieved.
-        Extent or range of development, view, outlook, application, operation,
-        effectiveness, etc.
+  it is a globally shareable environment and can be also used by
+  malicious users
 \item
-        \textbf{Related work} - Any information about available reusable
-        deliverables related to this work.
+  it offers only non-deterministic communication making integration of
+  islands of automation designed against the real-time requirements a
+  difficult task
 \end{itemize}
+
+Today both obstacles can be overcome, and as examples, we have bank
+account remote control and voice over IP in daily use. The first
+application must be fine-tuned in the context of data security, and the
+second is very sensitive on time relationships. Similar approaches could
+be applied to adopt the well known in process control industry concepts:
+
+\begin{itemize}
+\tightlist
+\item
+  Human Machine Interface (HNI)
+\item
+  Supervisory Control and Data Acquisition (SCADA)
+\item
+  Distributed Control Systems (DCS)
+\end{itemize}
+
+A detailed examination of these solutions is far beyond the scope of
+this article. It is only worth stressing that, by design, all of them
+are designed on the foundation of interactive communication. Interactive
+communication is based on a data polling foundation. In this case, the
+application must follow the interactive behavioral model, because it
+actively polls the data source for more information by pulling data from
+a sequence that represents the process state in time. The application is
+active in the data retrieval process - it controls the pace of the
+retrieval by sending the requests at its convenience. Such a polling
+pattern is similar to visiting the books shop and checking out a book.
+After you are done with the book, you pay another visit to check out
+another one. If the book is not available you must wait, but you may
+read what you selected. The client/server archetype is well suited for
+the mentioned above applications.
+
+After dynamically attaching a new island of automation the control
+application (responsible for the data pulling) must be reconfigured for
+this interoperability scenario. In other words, in this case, the
+interactive relationship cannot be directly applied because the control
+application must be informed on how to pull data from a new source. As a
+result, a plug and produce scenario cannot be seamlessly applied. A
+similar drawback must be overcome if for security reasons suitable
+protection methods have been applied to make network traffic propagation
+asymmetric. It is accomplished using intermediary devices, for example,
+firewalls, to enforce traffic selective availability based on
+predetermined security rules against unauthorized access.
+
+Going further, we shall assume that islands of automation are mobile,
+e.g.~autonomous cars passing a supervisory controlled service area. In
+this case, the behavior of the interconnected assets is particularly
+important concerning the environment in which they must interact. This
+way we have entered the Internet of Things domain of Internet-based
+applications.
+
+If we must bother with the network traffic propagation asymmetry or
+mobility of the asset network attachment-points the reactive
+relationship could relax the problems encountered while the interactive
+approach is applied. In this case, the sessionless publisher-subscriber
+communication archetype is a typical pattern to implement the abstract
+reactive interoperability paradigm. The sessionless archetype is a
+message distribution scenario where senders of messages, called
+publishers, do not send them directly to specific receivers, called
+subscribers, but instead, categorize the published messages into topics
+without knowledge about which subscribers if any, there may be.
+Similarly, subscribers express interest in one or more topics and only
+receive messages that are of interest, without knowledge about which
+publishers, if any, there are. In this scenario, the publishers and
+subscribers are loosely coupled.i.e they are decoupled in time, space
+and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.
+
+If the \textbf{machine-centric} interoperability - making up islands of
+automation - must be monitored and/or controlled by a supervisory system
+cloud computing concept may be recognized as a beneficial solution to
+replace or expand the mentioned above applications, i.e.~HMI, SCADA,
+DCS, etc. Cloud computing is a method to provide a requested
+functionality as a set of services. There are many examples that cloud
+computing is useful to reduce costs and increase robustness. It is also
+valuable in case the process data must be exposed to many stakeholders.
+Following this idea and offering control systems as a service, there is
+required a mechanism created on the service concept and supporting
+abstraction and virtualization - two main pillars of the cloud computing
+paradigm. In the cloud computing concept, virtualization is recognized
+as the possibility to share the services by many users, and abstraction
+hides implementation details.
+
+Deployment of the hybrid solution providing interoperability of the
+\textbf{machine-centric} cyber-physical systems and
+\textbf{human-centric} cloud-based front-end can be implemented applying
+the following scenarios:
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{direct interconnection} - cloud-based dedicated communication
+  services allow to attache it to the cyber-physical system making up a
+  consistent M2M communication network using an in-bound protocol stack
+\item
+  \textbf{gateway based interconnection} - typical build-in
+  communication services allows to attache the cloud computing to the
+  cyber-physical system using an out-of-bound protocol stack
+\end{itemize}
+
+By design, the direct approach requires that the cloud has to be
+compliant with the interoperability standard the cyber-physical system
+is built around - it becomes a consistent part of the cyber-physical
+system. Data models, roles, and responsibility differences of both
+solutions make this approach impractical and imposable to be applied in
+typical cases. A more detailed description is covered by the section
+\texttt{Azure\ to\ Sensors\ (A2S)\ connectivity\ deployment}.
+
+This article addresses further research on the integration of the
+cyber-physical systems in the context of new emerging disciplines,
+i.e.~Industry 4.0 (I4.0) and the Internet of Things (IoT). The new
+architecture is proposed for integration of the multi-vendor
+\textbf{machine-centric} cyber-physical system designed atop of M2M
+reactive communication and emerging cloud computing as a
+\textbf{human-centric} front-end. To support the multi-vendor
+environment OPC Unified Architecture interoperability standard has been
+selected. The proposals are backed by proof of concept reference
+implementations. Prototyping addresses Microsoft Azure Cloud as an
+example. The prototyping outcome has been just published on GitHub as
+the open-source (MIT licensed). The proposed solutions have been
+harmonized with the more general concept called the Object-Oriented
+Internet.
+
+The main goal of this article is to provide proof that:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  reactive interoperability M2M communication based on the OPC UA
+  standard can be implemented as a powerful standalone library without
+  dependency on the Client/Server session-oriented archetype
+\item
+  Azure interoperability can be implemented as an external part
+  employing out-of-band communication without dependency on the OPC UA
+  implementation
+\item
+  the proposed generic architecture allows that the gateway
+  functionality is composable at run-time - no programming required
+\end{enumerate}
+
+The remainder of this paper is structured as follows. Sect. \ref*{azure-main-technology-features} analyzes data presentation user interface, available native communication services, and
+data/metadata model offered by the Microsoft Azure. The discussion
+covered by this section is the foundation for selecting services
+utilized to expose process data and suitable protocol stack to support
+interconnection. In Sect. \ref*{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a
+foundation for further decisions addressing the systematic design of the
+interoperability of the cyber-physical systems and cloud-based
+front-end. Sect. \ref*{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity} presents the proposed open and reusable software model. It promotes a
+reactive interoperability pattern and a generic approach to establishing
+interoperability-context. A reference implementation of this archetype
+is described in Sect.  \ref*{gateway-implementation}. The most
+important findings and future work are summarized in Sect. \ref*{conclusion}.
+
+\hypertarget{consider-to-add}{%
+\subsection{Consider to add}\label{consider-to-add}}
+
+\hypertarget{scope}{%
+\subsubsection{Scope}\label{scope}}
+
+What we must do to prove the goal have been achieved. Extent or range of
+development, view, outlook, application, operation, effectiveness, etc.
+
+\hypertarget{related-work}{%
+\subsubsection{Related work}\label{related-work}}
+
+Any information about available reusable deliverables related to this
+work.
 
@@
 
-\begin{itemize}
-  \tightlist
-  \item
-        \textbf{Selection of the service}
-  \item
-        \textbf{Metadata} - must be discussed in context of the design/run
-        time stages.
+\hypertarget{services}{%
+\subsection{Services}\label{services}}
+
+Deployment of the hybrid solution providing interoperability of the
+\textbf{machine-centric} cyber-physical systems designed atop of M2M
+reactive communication and emerging cloud computing as a
+\textbf{human-centric} front-end requires decisions addressing the
+selection of the services supporting web user interface capable to
+expose real-time process data. In this context, the service is any
+autonomous (with own identity) software component or module that is
+interfacing with selected cyber-physical systems for data collection,
+analysis, and also remote control. Microsoft Azure is a cloud-based
+product. It offers a vast variety of services. This virtual environment
+handles an unlimited number of users and devices organized using a
+solution concept. The solution aggregates users, devices, services, and
+required additional resources scoping on a selected scenario. The
+solution serves as a context that provides a scope to the identifiers
+(the names of devices, users, process data entities, etc) inside it.
+Solutions are used to organize deployment entities into logical groups
+and prevent identity collisions.
+
+The \texttt{IoT\ Central} service provides a process data visualization
+user interface. To make this interface meaningful metadata called device
+template is used to describe devices.
+
+Following the assumption that interconnection between the cyber-physical
+system and cloud services is designed based on the gateway concept, a
+middleware must be considered as a coupler. It must be interconnected
+with the cyber-physical system using an in-band protocol adhering to
+communications requirements (i.e.~protocol profile, data encoding, time
+relationships, etc.) governing communication of the parts making it up.
+At the same time, it must support back-and-forth data transfer to the
+cloud using out-of-band native for the cloud services. The transfer
+process requires data conversion from source to destination encoding.
+The \texttt{IoT\ Hub} is a service hosted in the cloud that supports
+\texttt{IoT\ Central} providing a robust messaging solution - it acts as
+a central message hub for bi-directional communication. This
+communication is transparent, i.e.~it is not data types aware allowing
+any devices to exchange any kind of data. This service is responsible to
+manage the devices' identity and it offers the following protocol
+stacks: AMQP, MQTT, HTTPS.
+
+Before process data can be exposed using a web user interface the data
+source must be associated with an appropriate solution and validated to
+make sure that the security rules are not violated. It is hard to assume
+that the security rules governing the cyber-physical system may also
+apply to the cloud-based services. In the gateway scenario, they can be
+mapped on each other or entirely independent. The
+\texttt{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper
+service for \texttt{IoT\ Hub} that enables devices' connection process
+management, upon device providing valid identity attestation it assigns
+the device to an appropriate \texttt{IoT\ Hub} instance and returns to
+the device connection parameters, which allow direct connection with
+given \texttt{IoT\ Hub} service. The device proceeds to use the same
+attestation in \texttt{IoT\ Hub} connection and based on it, is granted
+authorization to selected resources and operations including but not
+limited to data transfer updating the user interface.
+
+It is worth stressing that interaction of the offered by the Azure
+services can be configured flexibly, and as a result, the presented
+above selection of services must be recognized as an example only. The
+\texttt{IoT\ Central} can be also seamlessly integrated with other
+services as needed. The following services could also be considered to
+build cloud-based automation solution:
 
@@
 \item
-                \textbf{Device Template (DT)}
+  \texttt{Industrial\ IoT} - discovering OPC UA enabled servers in a
+  factory network and register them in Azure IoT Hub implemented using
+  \texttt{IoT\ Edge}
 \item
-                \textbf{Device Capability Model}
+  \texttt{Digital\ Twins} - managing the graph of digital twins, which
+  are to represent some real-world process or entity
+\end{itemize}
+
+\texttt{Industrial\ IoT} promotes OPC UA client/server archetype used to
+achieve direct and interactive interoperability implemented using
+\texttt{IoT\ Edge} services that allow extracting initial data
+processing to local premises based on the edge concept.
+\texttt{Digital\ Twins} is an emerging concept to use an observer to
+replicate selected process state and behavior. The possibility to add
+value as a result of using these services must be subject to further
+research.
+
+\hypertarget{data-interchange}{%
+\subsection{Data Interchange}\label{data-interchange}}
+
+System components interoperability means the necessity of the
+information exchange between them. The main challenge of
+interoperability implementation is that information is abstract -- it is
+knowledge describing the process in concern state and behavior,
+e.g.~temperature in a boiler, a car speed, an account balance, etc.
+Obviously, abstraction cannot be processed by the cyber-physical
+machines. It is also impossible to transfer abstraction from one place
+to another over the network.
+
+Fortunately, computer science offers a workaround to address that
+impossibility - the information must be represented as a binary stream.
+In consequence, we can usually use both ones as interchangeable terms
+while talking about ICT systems. Unfortunately, these terms must be
+precisely observed in the context of further discussion, because we must
+be aware of the fact that the same information could have many different
+but equivalent representations. In other words, the same information can
+be represented by a vast variety of different binary patterns. For
+example, numbers may be represented using 2's Complement and
+Floating-Point binary representations.
+
+It should be nothing new for us, as it is obvious that the same
+information printed as a text in regional newspapers in English, German,
+Polish, etc. does not resemble one another, but the text meaning should
+always be the same. To understand a newspaper we must learn the
+appropriate language. To understand the binary data we must have defined
+a data type -- a description of how to create an appropriate bits
+pattern (syntax) and rules needed to assign the information (semantics),
+i.e.~make any correct bitstream meaningful. Concluding, to make two
+systems interoperable, a semantic-context must be established. The type
+plays the role of metadata, a set of data that describes other data.
+Metadata term is frequently used if the semantic-context is defined
+using a native language to select built-in types engaging a
+general-purpose graphical user interface.
+
+Using the data type definitions to describe information interchanged
+between communicating parties allows:
+
+\begin{itemize}
+\tightlist
 \item
-                \textbf{Interface}
+  Development against a type definition of the user interface
 \item
-                \textbf{Digital Twin Definition Language (DTDL)}
+  Implementation of the functionality of the bitstreams conversion in
+  advance
 \end{itemize}
+
+Having defined types in advance, a gateway may provide dedicated
+conversions functionality, i.e.~replacing bitstream used by the
+cyber-physical system by equivalent one for the cloud-based services.
+The Azure offers a vast variety of built-in types ready to be used in
+common cases, but not necessarily there are equivalent counterparts in
+use by the cyber-physical system. Additionally, the data conversion must
+address the following issues:
+
+\begin{itemize}
+\tightlist
 \item
-        \textbf{Simple, complex and structural data processing}
+  usually to covert data from source to destination representation, the
+  middleware software native types must be used
 \item
-        \textbf{Connectivity}
+  if the out of the box set of types is not capable of fulfilling more
+  demanding needs, custom data types must be defined
+\end{itemize}
+
+Although the data conversion is a run-time gateway task the
+implementation of the conversion algorithms must be recognized as an
+engineering task, and therefore this topic is not considered for further
+discussion.
+
+In \texttt{IoT\ Central} a cyber-physical system is represented as a set
+of devices. The characteristics and behaviors of each device kind are
+described by the device template. This Device Template (DT) contains
+also metadata describing the data (called telemetry) exchanged over the
+wire with the cyber-physical system called Device Capability Model
+(DCM). Additionally, the DT contains properties, customization, and
+views definitions used by the service locally. As an option, DCM
+expressed as a JSON-LD can be imported into a Device Template.
+\texttt{IoT\ Central} allows also to create and edit a DCM using the
+dedicated web UI. A JSON file containing DCM can be derived from an
+information model used as a foundation to establish the semantic-context
+applied to achieve interoperability of the devices interconnected as the
+cyber-physical system. DCM development against any external information
+model is a design-time task and should be supported by dedicated
+development tools. In any case, the data interchanged between the cloud
+and the gateway must be compliant with the DCM, hence the middleware
+software must be aware of conversions that must be applied to achieve
+this interoperability.
+
+\hypertarget{connectivity}{%
+\subsection{Connectivity}\label{connectivity}}
+
+From the cloud side, it is proposed to employ the \texttt{IoT\ Hub}
+service to handle the network traffic targeting the cyber-physical
+system. This service offers profiles of the AMQP, MQTT, HTTPS protocol
+stacks. In any case, process data (telemetry) is transparently
+transferred back-and-forth to the upper layer \texttt{IoT\ Central}
+service. Hence, the payload formatting is determined by the DCM
+associated with the \texttt{IoT\ Central} solution. All the mentioned
+protocols are standard ones. Consequently, it is possible to apply any
+available implementation compliant with an appropriate specification to
+achieve connectivity. In this case, all parameters required to establish
+connectivity and security-context is up to the external software
+responsibility. Alternatively, the API offered by the dedicated
+libraries may be used. Using this API the configuration process can be
+reduced significantly. Using these libraries, the selection of the
+communication protocol has an indirect impact on the interoperability
+features, including performance. The connectivity with
+\texttt{IoT\ Hub}, for example, can be obtained using:
+
+\begin{itemize}
+\tightlist
 \item
-        \textbf{How to implement} All about available libraries and tools
+  \texttt{Microsoft.Azure.Devices} - Service SDK for Azure IoT Devices
+\item
+  \texttt{Microsoft.Azure.Devices.Client}- Device SDK for Azure IoT Hub
+\item
+  \texttt{Microsoft.Azure.Devices.Shared} - Common code for Azure IoT
+  Device and Service SDKs
+\item
+  \texttt{Microsoft.Azure.Devices.Provisioning.Client} - Provisioning
+  Device Client SDK for Azure IoT Devices
+\item
+  \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Amqp} -
+  Provisioning Device Client AMQP Transport for Azure IoT Devices
+\item
+  \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Http} -
+  Provisioning Device Client Http Transport for Azure IoT Devices
+\item
+  \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Mqtt} -
+  Provisioning Device Client MQTT Transport for Azure IoT Devices
 \end{itemize}

### 2020-10-08 Latex/Manuscript.tex
Work out Markdown\40.OOITechnologyFeatures.md #28
- convert to latex - minor changes
 - current .pdf generated.

@@
 selection of the services supporting web user interface capable to
-expose real-time process data. In this context, the service is any
+expose process data. In this context, the service is any
 autonomous (with own identity) software component or module that is
@@
 attestation in \texttt{IoT\ Hub} connection and based on it, is granted
-authorization to selected resources and operations including but not
+authorization %MP authorization can be applied only to operations ?% to selected resources and operations including but not
 limited to data transfer updating the user interface.
@@
 \item
-  \texttt{Industrial\ IoT} - discovering OPC UA enabled servers in a
-  factory network and register them in Azure IoT Hub implemented using
-  \texttt{IoT\ Edge}
+  \texttt{Industrial\ IoT} - discovering OPC UA enabled servers in a factory network and register them in Azure \texttt{IoT\ Hub} implemented using \texttt{IoT\ Edge}
 \item
-  \texttt{Digital\ Twins} - managing the graph of digital twins, which
-  are to represent some real-world process or entity
+  \texttt{Digital\ Twins} - managing the graph of digital twins, which are to represent some real-world process or entity
 \end{itemize}
@@
 
-Having defined types in advance, a gateway may provide dedicated
-conversions functionality, i.e.~replacing bitstream used by the
-cyber-physical system by equivalent one for the cloud-based services.
-The Azure offers a vast variety of built-in types ready to be used in
-common cases, but not necessarily there are equivalent counterparts in
-use by the cyber-physical system. Additionally, the data conversion must
-address the following issues:
+Having defined types in advance, a gateway may provide dedicated conversions functionality, i.e.~replacing bitstreams used by the cyber-physical system by equivalent ones for the cloud-based services.
+The Azure offers a vast variety of built-in types ready to be used in common cases, but not necessarily there are equivalent counterparts in use by the cyber-physical system.
+Additionally, the data conversion must address the following issues:
 
@@
 In \texttt{IoT\ Central} a cyber-physical system is represented as a set
-of devices. The characteristics and behaviors of each device kind are
+of devices. The characteristics and behavior of each device kind are
 described by the device template. This Device Template (DT) contains
@@
 \item
-  \texttt{Microsoft.Azure.Devices.Client}- Device SDK for Azure IoT Hub
+  \texttt{Microsoft.Azure.Devices.Client}- Device SDK for Azure \texttt{IoT\ Hub}
 \item

### 2020-10-18 Latex/Manuscript.tex
Work out Markdown\50.Sensors2AzureConnectivityDeployment.md #29
- working copy

@@
 Deployment of the smart factory concept requires a hybrid solution and
-interoperability of the mentioned above heterogeneous environments. This
+interconnection of the mentioned above heterogeneous environments. This
 approach is called the fourth industrial revolution and coined as
@@
 interoperability has to be expected for the deployment of this concept.
-In this case, muli-vendor integration makes communication
+In this case, multi-vendor integration makes communication
 standardization especially important, namely it is required that the

### 2020-10-25 Latex/50.Sensors2AzureConnectivityDeployment.tex
Work out Markdown\50.Sensors2AzureConnectivityDeployment.md #29
- added converter to `.tex` format. Final `.tex` document will be generated after reviewing.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{cloud-to-sensors-field-level-connectivity}{%
\section{Cloud to Sensors Field Level
Connectivity}\label{cloud-to-sensors-field-level-connectivity}}

\hypertarget{architecture}{%
\subsection{Architecture}\label{architecture}}

\hypertarget{introduction}{%
\subsubsection{Introduction}\label{introduction}}

As it was explained in Sect 1, to follow the Industry 4.0 concept a
hybrid environment integrating reactive Machine to Machine
interconnection and interactive web-based user interface is required.
The main challenge of the solution in concern is to design a generic but
reusable architecture that addresses interoperability of these diverse
interconnection scenarios ruled by different requirements, namely

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{machine-centric} machine to machine real-time mobile
  interoperability
\item
  \textbf{human-centric} cloud-based front-end
\end{enumerate}

Interconnection of the reactive \textbf{machine-centric} and interactive
\textbf{human-centric} environments can be implemented by applying one
of the following scenarios:

\begin{itemize}
\tightlist
\item
  \textbf{direct interconnection} - cloud-based dedicated communication
  services are engaged to attach it to the cyber-physical system making
  up a consistent M2M communication network using a common protocol
  stack
\item
  \textbf{gateway based interconnection} - native build-in communication
  services allows attaching the cloud to the cyber-physical system using
  an out-of-bound protocol stack
\end{itemize}

In the solution in concern, the interconnection of assets is not enough
hence their interoperability is expected. In this case, using the same
communication stack must be recognized as only a necessary condition. To
support interoperability common data understanding is required. By
design, the direct approach requires that the cloud has to be compliant
with the interoperability standard the cyber-physical system uses. As a
result, it becomes a consistent part of the cyber-physical system.
Additionally, to meet this requirement the cloud and cyber-physical
systems have to establish

\begin{itemize}
\tightlist
\item
  directly the same semantic-context
\item
  directly the same security-context
\end{itemize}

The possibility to establish a common semantic-context in the
multi-vendor environment makes communication standardization especially
important. In this case, it is required that the encoding of the payload
of messages exchanged over the network (Data Transfer Object - TDO) is
standardized so that the payload can be factored on the data-gathering
site and consumed on the ultimate destination data processing sites.
Security between the data origin and ultimate data destination refers to
the protection of messages (security-context) against malicious users.
It is required that communicating parties are using the same
cyber-security measures.

\hypertarget{why-not-direct}{%
\subsubsection{why not direct}\label{why-not-direct}}

The decision to follow the \textbf{direct interconnection} scenario must
be derived from an analysis of the capabilities of available services in
concern. However, for the development strategy of this type of solutions
this analysis can be done partially taking into account two features
that can be considered invariable:

\begin{itemize}
\tightlist
\item
  by design the cloud-based services must be virtual - they are used to
  handle many solutions at the same time
\item
  by design the M2M communication is usually constrained by the
  real-time requirements
\end{itemize}

In practice, the set of assets embedded in the cyber-physical system is
very stable. On the another hand, the virtualization of services means
that they must be very flexible to handle the attachment of new assets
proactively (acting in advance) at run time. As a result, by design, the
cloud services must be repressible to register and authenticate devices
exposing endpoints in the public network to allows the device to access
a provisioning cloud service. It requires that a session over the
Internet has to be established by the data holding asset at a
preparation step.

To meet the requirements of real-time distributed control the
cyber-physical system may use protocols applicable only to local
computer networks (e.g.~multicast IP, Ethernet, TSN, etc.). Because the
cloud services support only protocols handling interconnection over the
Internet the interaction with the cloud requires remote agents,
i.e.~agents attached locally to the M2M network implemented applying one
of the following archetypes:

\begin{itemize}
\tightlist
\item
  \textbf{edge device} - remote cloud agent acting as an intermediary
  for nodes of the cyber-physical network
\item
  \textbf{field level gateway} - a dedicated custom device acting as an
  intermediary for nodes of the cyber-physical network
\item
  \textbf{embedded gateway} - a software part composed into a selected
  node of the cyber-physical network
\end{itemize}

\textbf{Edge device} is a device that connects directly to the cloud
services but acts as an intermediary for other devices called leaf
devices. Additionally, it allows the selection of initial data
processing and execution of them using local resources. The \textbf{edge
device} may be located close to the leaf devices and attached to the
cyber-physical network using protocols applicable only to local computer
networks. In this scenario, it is possible to use a custom protocol
stack to get connected to the \textbf{edge device} with the cloud and
helps to save the bandwidth thanks to sending only the results of local
processing. In this approach, the \textbf{edge device} is part of cloud
vendor products and cannot be recognized as a generic solution that can
be used to connect to other clouds at the same time.

The \textbf{field level gateway} is also build atop of the middleware
concept. The only difference compared with the \textbf{edge device} is
necessity to use officially supported by the cloud vendor services to
get connected. In this scenario the process data may be transferred to
many clouds at the same time provided that the gateway offers this
functionality.

\begin{figure}
\centering
\includegraphics{../.Media/StrategyDomainModel.png}
\caption{Strategy Domain Model}
\end{figure}

Unlike the above described solutions, the \textbf{embedded gateway} is
not derived from the middleware concept. The domain model for this
archetype is presented in the Fig. Promoting separation of concern
design principle, the gateway functionality should be implemented as a
self-contained software part embedded in the \texttt{Networking} service
of the \texttt{Cipher-physical\ node}. Main functionality of this
component is to transfer selected data between
\texttt{Cipher-physical\ network} using \texttt{Networking} services of
an existing \texttt{Cipher-physical\ node} and
\texttt{Cloud-based\ front-end} using officially supported by the cloud
vendor interconnection services.

The \textbf{embedded gateway} archetype relaxes most of the issues
described above: cipher-physical network real-time behavior, data
encoding incompatibility, security-context differences to name only a
few. The main goal of this article is to provide proof that the
\textbf{embedded gateway} archetype implementation is possible based on
a generic architecture that can be used as a foundation for the
integration of the heterogenous environments in concern. The proposed
implementation is designed for selected interoperability standard and
cloud product.

\hypertarget{why-pubsub}{%
\subsection{Why pubsub}\label{why-pubsub}}

To comply with the Industry 4.0 communication criterion, even the lowest
category requires that the product must be addressable over the network
via TCP/UDP or IP and has to support the OPC UA Information Model. As a
result, any product being advertised as Industry 4.0 enabled must be OPC
UA-capable somehow. To support the multi-vendor environment OPC Unified
Architecture interoperability standard has been selected. OPC UA
supports the following two patterns to be used to transfer data between
communicating parties:

\begin{itemize}
\tightlist
\item
  connection-oriented: requires a session that has to be established
  before any data can be sent between sender and receiver
\item
  connectionless-oriented: the sender may start sending messages (called
  packets or datagrams) to the destination without any preceding
  handshake procedure
\end{itemize}

Using the connection-oriented communication pattern it is difficult or
even impossible to gather and process mobile data (Sec. I), which is one
of the Internet of Things paradigms. OPC UA Part 14 PubSub offers the
connectionless approach as an additional option to session based
client-server interoperability and is a consistent part of the OPC UA
specifications suit. As the result it can be recognized as the IoT ready
technology.

\begin{quote}
{[}29{]} Mariusz Postol, UA Part 14: PubSub Main Technology Features in
Object Oriented Internet, https://github.com/mpostol/OPC-UA-OOI, 2019,
DOI: 10.5281/zenodo.1198852
\end{quote}

\hypertarget{why-azure}{%
\subsection{Why Azure}\label{why-azure}}

The presented proposals in the article are backed by proof of concept
reference implementations. For this study, prototyping addresses
Microsoft Azure cloud products. There are many reasons for selecting
Azure to accomplish cloud-based front-end of CFS. Azure offers
Infrastructure as a Service (IaaS) and Platform as a Service (PaaS)
capabilities. As a result, the platform can be used not only as a
cloud-based front-end for CFS. By design, the Azure services are
compliant with Security Development Lifecycle (SDL) an industry-leading
security process. It is also compliant with the new international
standard for cloud privacy, namely ISO 27018. Solutions hosted on Azure
are scaled up to millions of users without any additional coding. For
the development of the CFS front-end, it is essential that Azure
provides very efficient storage services usefully for real-time process
data archival. Azure provides a vast variety of hybrid connections
including but not limited to virtual private networks (VPNs), caches,
content delivery networks (CDNs), ExpressRoute, and IoT dedicated
services that can be directly used to implement cloud-based front-end
for CFS. Because it is also integrated with other Microsoft tools like
Office 365, Outlook, and SharePoint using Azure allows preserving
investment and exporting process data to the mentioned tools. Azure also
offers services supporting analytics and intelligence capabilities for
further improving business processes and decision making. It is the only
cloud platform that offers Blockchain as a Service (BaaS), Machine
Learning, Bots, and Cognitive APIs capabilities.

Azure aids Internet protocols and open standards such as JSON, XML,
SOAP, REST, MQTT, AMQP, and HTTP. A software development kits for C\#,
Java, PHP, and Ruby are available for custom applications. Azure
provides services supporting data exchange over the OPC UA, but they
don't support pubsub compliant with the OPC UA Part-14. Connectivity
services on the network use JSON-based Data Transfer Object encoded
based on schema derived from the solution metadata.

More detailed description of the selected Azure features in context of
the application in concern are covered by the Sec.
\texttt{azure-main-technology-features}.

\hypertarget{why-ooi}{%
\subsection{Why OOI}\label{why-ooi}}

Based on the sessionless and session-oriented communication patterns
examination against the IoT requirements (cite mpostol 2020) it could be
concluded that the connectionless pattern better suites issues related
to the assets mobility and traffic asymmetry that is characteristic for
the application domains in concern. Additionally, to promote
interoperability and address the demands of the M2M communication in the
context of a multi-vendor environment the prototyping should use an
framework that must be compliant with the OPC UA Part 14 PubSub spec.
According to proposed architecture presented in Fig. above to implement
the \texttt{Embedded\ Gateway} as a composable part of the
\texttt{Cipher-physical\ Node} a library implementing
\texttt{Networking} functionality in compliance with mentioned above
specification is a starting point for further development. Additionally
it must be assumed that the library used to deploy
\texttt{Embedded\ Gateway} support dependency injection and be capable
to compose an external part supporting Azure/pubsub gateway
functionality. The composition process must be available without
modification of the core code of an existing library. As a result the
prototyping is to be limited to implementation of the
\texttt{Embedded\ Gateway} software part only.

A library that meets all these requirements has been implemented
consistently with the Object-Oriented Internet paradigm
\texttt{\textbackslash{}footnote\{\textbackslash{}url\{https://github.com/mpostol/OPC-UA-OOI\}\}}
\texttt{\textbackslash{}cite\{RefWorks:doc:5c66740ae4b081adf5804596\}}
worked out in an open-source project. The
\texttt{cite\ \{mpostol\ 2020\}} covers the description of a reference
application program implementation proving that it is possible to design
universal architecture targeting reactive interoperability as a
consistent part of the Object-Oriented Internet concept compliant with
the OPC UA PubSub
\texttt{\textbackslash{}cite\{RefWorks:doc:5d98837de4b055984c0eecf0\}}
international standard. According to the presented implementation and
evaluation, using the dependency injection and late binding, the
application program can be seamlessly adapted to the production
environment and scales well. This approach also improves flexibility and
adaptability of the existing solutions against any modification of the
production environment including but not limited to the selected
interoperability standard change.

Sect. \texttt{OPC\ UA\ PubSub\ Main\ Technology\ Features} provides more
detailed description of this library and new functionality
(\texttt{Embedded\ Gateway} part deployment process.

The following subsections covers description of the current state of
technologies with regards to OPC UA pubsub and Azure cloud-based IoT
enabler.

\hypertarget{review-of-technologies}{%
\subsection{Review of Technologies}\label{review-of-technologies}}

add here subsections related to the Azure and OOI

\end{document}

### 2020-10-29 Latex/Manuscript.tex
Work out Markdown\50.Sensors2AzureConnectivityDeployment.md #29
- ready for review.
Work out Markdown\50.Sensors2AzureConnectivityDeployment.md #29
- integrated into the final latex document

@@
 \usepackage{txfonts}
+\usepackage[textsize=tiny]{todonotes}
 
@@
   Faculty/Department/Office Name\\
-  Postal Addres with the zip-code\\
+  Postal Address with the zip-code\\
   clemensv@microsoft.com}
@@
 \begin{abstract}
-Each paper should be followed by a compact abstract which points to the main
-scopes and the results obtained by the paper. The abstract should be written
-with the Times New Roman font, 10 pt, justified, and with the 1cm margin both
-left and right side with respect  to the margin of the paper. The abstract should not contain any formulas or references, and should not exceed 200 words. 
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Sed luctus neque eu erat pulvinar rutrum.
+Sed id congue leo.
+Pellentesque ornare enim libero, convallis eleifend turpis rhoncus ac.
+Proin eget pellentesque dolor.
+Phasellus lacinia velit eget faucibus iaculis.
+Pellentesque consequat erat non urna scelerisque cursus.
+Donec urna nisi, pulvinar a nisl eu, lobortis sollicitudin nulla.
+Proin tempus risus vel lacinia vestibulum.
+Praesent eget nisi lorem.
+Nam rutrum lectus vulputate dolor venenatis eleifend.
+Sed dolor lacus, cursus non enim tincidunt, auctor hendrerit orci.
+Donec venenatis ultrices est, nec molestie lorem.
+Morbi eleifend mattis ex, eget mollis leo blandit ut.
+Nulla sed felis posuere, gravida dui sed, iaculis neque.
+Donec ante purus, rhoncus eu neque tristique, pretium elementum purus.
+
+Sed euismod maximus consequat.
+Pellentesque nec leo ligula.
+Aenean id lorem ac nisi blandit ultrices sit amet nec velit.
+Vestibulum bibendum ipsum vulputate quam suscipit, eu tincidunt diam imperdiet.
+Nunc vel turpis ut tortor bibendum ullamcorper sed ut magna.
+Sed sit amet quam ut lacus pretium ullamcorper.
+Fusce feugiat ornare mollis.
+Vestibulum sagittis velit id augue tempus, in vestibulum velit bibendum.
+Curabitur ac aliquet mi.
+Aliquam erat volutpat.
+Cras quis dignissim est, ac gravida.
 \end{abstract}
@@
 \maketitle
+
+\listoftodos[TODO list]
 
@@
 solutions make this approach impractical and imposable to be applied in
-typical cases. A more detailed description is covered by the section
-\texttt{Azure\ to\ Sensors\ (A2S)\ connectivity\ deployment}.
+typical cases. A more detailed description is covered by the Sect.~\ref*{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity}.
 
@@
 
-The remainder of this paper is structured as follows. Sect. \ref*{azure-main-technology-features} analyzes data presentation user interface, available native communication services, and
-data/metadata model offered by the Microsoft Azure. The discussion
-covered by this section is the foundation for selecting services
-utilized to expose process data and suitable protocol stack to support
-interconnection. In Sect. \ref*{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a
-foundation for further decisions addressing the systematic design of the
-interoperability of the cyber-physical systems and cloud-based
-front-end. Sect. \ref*{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity} presents the proposed open and reusable software model. It promotes a
-reactive interoperability pattern and a generic approach to establishing
-interoperability-context. A reference implementation of this archetype
-is described in Sect.  \ref*{gateway-implementation}. The most
-important findings and future work are summarized in Sect. \ref*{conclusion}.
+The remainder of this paper is structured as follows.
+Sect.~\ref*{azure-main-technology-features} \todo{Overfull must be fixed} analyzes data presentation user interface, available native communication services, and data/metadata model offered by the Microsoft Azure.
+The discussion covered by this section is the foundation for selecting services utilized to expose process data and suitable protocol stack to support interconnection.
+In Sect.~\ref*{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a foundation for further decisions addressing the systematic design of the interoperability of the cyber-physical systems and cloud-based front-end.
+Sect.~\ref*{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity} presents the proposed open and reusable software model.
+It promotes a reactive interoperability pattern and a generic approach to establishing interoperability-context.
+A reference implementation of this archetype is described in Sect.~\ref*{gateway-implementation}.
+The most important findings and future work are summarized in Sect.~\ref*{architecture} \todo{overfull}.
 
@@
 
+\hypertarget{cloud-to-sensors-field-level-connectivity}{%
+\section{Cloud to Sensors Field Level Connectivity}\label{cloud-to-sensors-field-level-connectivity}}
+
+\hypertarget{architecture}{%
+\subsection{Architecture}\label{architecture}}
+
+As it was explained in Sect.~\ref*{introduction}, to follow the Industry 4.0 concept a hybrid environment integrating reactive Machine to Machine
+interconnection and interactive web-based user interface is required.
+The main challenge of the solution in concern is to design a generic but
+reusable architecture that addresses interoperability of these diverse
+interconnection scenarios ruled by different requirements, namely
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  \textbf{machine-centric} machine to machine real-time mobile
+  interoperability
+\item
+  \textbf{human-centric} cloud-based front-end
+\end{enumerate}
+
+Interconnection of the reactive \textbf{machine-centric} and interactive \textbf{human-centric} environments can be implemented by applying one of the following scenarios \todo{overfull}:
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{direct interconnection} - cloud-based dedicated communication
+  services are engaged to attach it to the cyber-physical system making
+  up a consistent M2M communication network using a common protocol
+  stack
+\item
+  \textbf{gateway based interconnection} - native build-in communication
+  services allows attaching the cloud to the cyber-physical system using
+  an out-of-bound protocol stack
+\end{itemize}
+
+In the solution in concern, the interconnection of assets is not enough
+hence their interoperability is expected. In this case, using the same
+communication stack must be recognized as only a necessary condition. To
+support interoperability common data understanding is required. By
+design, the direct approach requires that the cloud has to be compliant
+with the interoperability standard the cyber-physical system uses. As a
+result, it becomes a consistent part of the cyber-physical system.
+Additionally, to meet this requirement the cloud and cyber-physical
+systems have to establish
+
+\begin{itemize}
+\tightlist
+\item
+  directly the same semantic-context
+\item
+  directly the same security-context
+\end{itemize}
+
+The possibility to establish a common semantic-context in the
+multi-vendor environment makes communication standardization especially
+important. In this case, it is required that the encoding of the payload
+of messages exchanged over the network (Data Transfer Object - TDO) is
+standardized so that the payload can be factored on the data-gathering
+site and consumed on the ultimate destination data processing sites.
+Security between the data origin and ultimate data destination refers to
+the protection of messages (security-context) against malicious users.
+It is required that communicating parties are using the same
+cyber-security measures.
+
+The decision to follow the \textbf{direct interconnection} scenario must
+be derived from an analysis of the capabilities of available services in
+concern. However, for the development strategy of this type of solutions
+this analysis can be done partially taking into account two features
+that can be considered invariable:
+
+\begin{itemize}
+\tightlist
+\item
+  by design the cloud-based services must be virtual - they are used to
+  handle many solutions at the same time
+\item
+  by design the M2M communication is usually constrained by the
+  real-time requirements
+\end{itemize}
+
+In practice, the set of assets embedded in the cyber-physical system is
+very stable. On the another hand, the virtualization of services means
+that they must be very flexible to handle the attachment of new assets
+proactively (acting in advance) at run time. As a result, by design, the
+cloud services must be repressible to register and authenticate devices
+exposing endpoints in the public network to allows the device to access
+a provisioning cloud service. It requires that a session over the
+Internet has to be established by the data holding asset at a
+preparation step.
+
+To meet the requirements of real-time distributed control the
+cyber-physical system may use protocols applicable only to local
+computer networks (e.g.~multicast IP, Ethernet, TSN, etc.). Because the
+cloud services support only protocols handling interconnection over the
+Internet the interaction with the cloud requires remote agents,
+i.e.~agents attached locally to the M2M network implemented applying one
+of the following archetypes:
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{edge device} - remote cloud agent acting as an intermediary
+  for nodes of the cyber-physical network
+\item
+  \textbf{field level gateway} - a dedicated custom device acting as an
+  intermediary for nodes of the cyber-physical network
+\item
+  \textbf{embedded gateway} - a software part composed into a selected
+  node of the cyber-physical network
+\end{itemize}
+
+\textbf{Edge device} is a device that connects directly to the cloud
+services but acts as an intermediary for other devices called leaf
+devices. Additionally, it allows the selection of initial data
+processing and execution of them using local resources. The \textbf{edge
+device} may be located close to the leaf devices and attached to the
+cyber-physical network using protocols applicable only to local computer
+networks. In this scenario, it is possible to use a custom protocol
+stack to get connected to the \textbf{edge device} with the cloud and
+helps to save the bandwidth thanks to sending only the results of local
+processing. In this approach, the \textbf{edge device} is part of cloud
+vendor products and cannot be recognized as a generic solution that can
+be used to connect to other clouds at the same time.
+
+The \textbf{field level gateway} is also build atop of the middleware
+concept. The only difference compared with the \textbf{edge device} is
+necessity to use officially supported by the cloud vendor services to
+get connected. In this scenario the process data may be transferred to
+many clouds at the same time provided that the gateway offers this
+functionality.
+
+\begin{figure}
+\centering
+\includegraphics{../.Media/StrategyDomainModel.png}
+\caption{Strategy Domain Model}\label{StrategyDomainModel}
+\end{figure}
+
+Unlike the above described solutions, the \textbf{embedded gateway} is
+not derived from the middleware concept. The domain model for this
+archetype is presented in the Fig. Promoting separation of concern
+design principle, the gateway functionality should be implemented as a
+self-contained software part embedded in the \texttt{Networking} service
+of the \texttt{Cipher-physical\ node}. Main functionality of this
+component is to transfer selected data between
+\texttt{Cyber-physical\ network} using \texttt{Networking} services of
+an existing \texttt{Cyber-physical\ node} and
+\texttt{Cloud-based\ front-end} using officially supported by the cloud
+vendor interconnection services.
+
+The \textbf{embedded gateway} archetype relaxes most of the issues
+described above: cipher-physical network real-time behavior, data
+encoding incompatibility, security-context differences to name only a
+few. The main goal of this article is to provide proof that the
+\textbf{embedded gateway} archetype implementation is possible based on
+a generic architecture that can be used as a foundation for the
+integration of the heterogenous environments in concern. The proposed
+implementation is designed for selected interoperability standard and
+cloud product.
+
+To comply with the Industry 4.0 communication criterion it is required that the product must be addressable over the network via TCP/UDP or IP and has to support the OPC UA Information Model.
+As a result, any product being advertised as Industry 4.0 enabled must be OPC UA-capable somehow.
+To support the multi-vendor environment OPC Unified Architecture interoperability standard has been selected.
+OPC UA supports the following two patterns to be used to transfer data between communicating parties:
+
+\begin{itemize}
+\tightlist
+\item
+  connection-oriented: requires a session that has to be established before any data can be sent between sender and receiver
+\item
+  connectionless-oriented: the sender may start sending messages (called packets or datagrams) to the destination without any preceding handshake procedure
+\end{itemize}
+
+Using the connection-oriented communication pattern it is difficult or
+even impossible to gather and process mobile data (Sec. I), which is one
+of the Internet of Things paradigms.
+OPC UA Part 14 PubSub \todo{add ref} \footnote{Mariusz Postol, UA Part 14: PubSub Main Technology Features in Object Oriented Internet, https://github.com/mpostol/OPC-UA-OOI, 2019, DOI: 10.5281/zenodo.1198852} offers the
+connectionless approach as an additional option to session based
+client-server interoperability and is a consistent part of the OPC UA
+specifications suit. As the result it can be recognized as the IoT ready
+technology.
+
+The presented proposals in the article are backed by proof of concept
+reference implementations. For this study, prototyping addresses
+Microsoft Azure cloud products. There are many reasons for selecting
+Azure to accomplish cloud-based front-end of CFS. Azure offers
+Infrastructure as a Service (IaaS) and Platform as a Service (PaaS)
+capabilities. As a result, the platform can be used not only as a
+cloud-based front-end for CFS. By design, the Azure services are
+compliant with Security Development Lifecycle (SDL) an industry-leading
+security process. It is also compliant with the new international
+standard for cloud privacy, namely ISO 27018. Solutions hosted on Azure
+are scaled up to millions of users without any additional coding. For
+the development of the CFS front-end, it is essential that Azure
+provides very efficient storage services usefully for real-time process
+data archival. Azure provides a vast variety of hybrid connections
+including but not limited to virtual private networks (VPNs), caches,
+content delivery networks (CDNs), ExpressRoute, and IoT dedicated
+services that can be directly used to implement cloud-based front-end
+for CFS. Because it is also integrated with other Microsoft tools like
+Office 365, Outlook, and SharePoint using Azure allows preserving
+investment and exporting process data to the mentioned tools. Azure also
+offers services supporting analytics and intelligence capabilities for
+further improving business processes and decision making. It is the only
+cloud platform that offers Blockchain as a Service (BaaS), Machine
+Learning, Bots, and Cognitive APIs capabilities.
+
+Azure aids Internet protocols and open standards such as JSON, XML,
+SOAP, REST, MQTT, AMQP, and HTTP. A software development kits for C\#,
+Java, PHP, and Ruby are available for custom applications. Azure
+provides services supporting data exchange over the OPC UA, but they
+don't support pubsub compliant with the OPC UA Part-14. Connectivity
+services on the network use JSON-based Data Transfer Object encoded
+based on schema derived from the solution metadata.
+
+More detailed description of the selected Azure features in context of
+the application in concern are covered by the Sec.
+\texttt{azure-main-technology-features}.
+
+Based on the sessionless and session-oriented communication patterns
+examination against the IoT requirements  \cite{mpostol2020} 
+it could be
+concluded that the connectionless pattern better suites issues related
+to the assets mobility and traffic asymmetry that is characteristic for
+the application domains in concern. Additionally, to promote
+interoperability and address the demands of the M2M communication in the
+context of a multi-vendor environment the prototyping should use an
+framework that must be compliant with the OPC UA Part 14 PubSub spec.
+According to proposed architecture presented in Fig. above to implement
+the \texttt{Embedded\ Gateway} as a composable part of the
+\texttt{Cipher-physical\ Node} a library implementing
+\texttt{Networking} functionality in compliance with mentioned above
+specification is a starting point for further development. Additionally
+it must be assumed that the library used to deploy
+\texttt{Embedded\ Gateway} support dependency injection and be capable
+to compose an external part supporting Azure/pubsub gateway
+functionality. The composition process must be available without
+modification of the core code of an existing library. As a result the
+prototyping is to be limited to implementation of the
+\texttt{Embedded\ Gateway} software part only.
+
+A library that meets all these requirements has been implemented consistently with the Object-Oriented Internet paradigm \cite{RefWorks:doc:5c66740ae4b081adf5804596} 
+worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }. The \cite{mpostol2020} 
+covers the description of a reference application program implementation proving that it is possible to design
+universal architecture targeting reactive interoperability as a
+consistent part of the Object-Oriented Internet concept compliant with
+the OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} international standard. According to the presented implementation and
+evaluation, using the dependency injection and late binding, the
+application program can be seamlessly adapted to the production
+environment and scales well. This approach also improves flexibility and
+adaptability of the existing solutions against any modification of the
+production environment including but not limited to the selected
+interoperability standard change.
+
+Sect.~\ref*{ooi-main-technology-features} provides more detailed description of this library and new functionality (\texttt{Embedded\ Gateway} \todo{refine the text} part deployment process.
+
+The following subsections covers description of the current state of technologies with regards to OPC UA pubsub and Azure cloud-based IoT enabler.
+
 \hypertarget{azure-main-technology-features}{%
-\section{Azure Main Technology
-Features}\label{azure-main-technology-features}}
+\subsection{Azure Main Technology Features}\label{azure-main-technology-features}}
 
 \hypertarget{services}{%
-\subsection{Services}\label{services}}
+\subsubsection{Services}\label{services}}
 
@@
 attestation in \texttt{IoT\ Hub} connection and based on it, is granted
-authorization %MP authorization can be applied only to operations ?% to selected resources and operations including but not
-limited to data transfer updating the user interface.
+authorization to selected resources \todo{MP authorization can be applied only to operations?} and operations including but not limited to data transfer updating the user interface.
 
@@
 \hypertarget{data-interchange}{%
-\subsection{Data Interchange}\label{data-interchange}}
+\subsubsection{Data Interchange}\label{data-interchange}}
 
@@
 \hypertarget{connectivity}{%
-\subsection{Connectivity}\label{connectivity}}
+\subsubsection{Connectivity}\label{connectivity}}
 
@@
 \hypertarget{ooi-main-technology-features}{%
-  \section{OOI Main Technology
-    Features}\label{ooi-main-technology-features}}
+\subsection{OOI Main Technology Features}\label{ooi-main-technology-features}}
 
@@
 
-\hypertarget{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity}{%
-  \section{Azure to Sensors (A2S) connectivity deployment (field level
-    connectivity)}\label{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity}}
-
-\begin{quote}
-  The title must be revised
-\end{quote}
-
-\begin{itemize}
-  \tightlist
-  \item
-        \textbf{Architecture} - Domain model presenting relationship between
-        the: Azure, PubSub Gateway, Device, Design and development tools
-  \item
-        \textbf{Connectivity} - Describe reactive nature of the Azure
-        monitoring process data (telemetry) services.
-  \item
-        \textbf{Deployment phases}
-
-        \begin{itemize}
-          \tightlist
-          \item
-                Design
-          \item
-                Gateway and devices registration
-          \item
-                Authentication
-          \item
-                Device/Service association
-          \item
-                Device/Application association
-          \item
-                Establishing session
-
-                \begin{itemize}
-                  \tightlist
-                  \item
-                        Device/Device Template (Device Capability Model) association -
-                        establishing a semantic-context
-                  \item
-                        Security management - establishing security-context
-                \end{itemize}
-          \item
-                Interconnection - exchange of data
-          \item
-                Maintenance
-        \end{itemize}
-\end{itemize}
-
-We have selected
-\href{https://docs.microsoft.com/azure/iot-central/core/}{IoT Central}
-because:
-
-\begin{itemize}
-  \tightlist
-  \item
-        provides process data visualization user interface
-  \item
-        allows to describe devices using metadata containing telemetry data
-        types
-\end{itemize}
-
 \hypertarget{gateway-implementation}{%
-  \section{Gateway implementation}\label{gateway-implementation}}
+\section{Azure - Object-Oriented Internet interoperability Implementation}\label{gateway-implementation}}
 
@@
   \item
-        OPC UA PubSub can be implemented as a powerful standalone package - no
-        C/S dependency
+        OPC UA PubSub can be implemented as a powerful standalone package - no C/S dependency
   \item
@@
 
-\bibliography{Manuscript}
+\bibliography{Manuscript.bib}
 \bibliographystyle{aiaa-jacs.bst}

### 2020-10-30 Latex/Manuscript.tex
Work out Markdown\50.Sensors2AzureConnectivityDeployment.md #29
- reviewed after integration

@@
 solutions make this approach impractical and imposable to be applied in
-typical cases. A more detailed description is covered by the Sect.~\ref*{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity}.
+typical cases. A more detailed description is covered by the Sect.~\ref*{cloud-to-sensors-field-level-connectivity}.
 
@@
 The remainder of this paper is structured as follows.
-Sect.~\ref*{azure-main-technology-features} \todo{Overfull must be fixed} analyzes data presentation user interface, available native communication services, and data/metadata model offered by the Microsoft Azure.
+Sect.~\ref*{cloud-to-sensors-field-level-connectivity} presents the proposed open and reusable software model.
+It promotes a reactive interoperability pattern and a generic approach to establishing interoperability-context.
+Sect.~\ref*{azure-main-technology-features} analyzes data presentation user interface, available native communication services, and data/metadata model offered by the Microsoft Azure.
 The discussion covered by this section is the foundation for selecting services utilized to expose process data and suitable protocol stack to support interconnection.
 In Sect.~\ref*{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a foundation for further decisions addressing the systematic design of the interoperability of the cyber-physical systems and cloud-based front-end.
-Sect.~\ref*{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity} presents the proposed open and reusable software model.
-It promotes a reactive interoperability pattern and a generic approach to establishing interoperability-context.
 A reference implementation of this archetype is described in Sect.~\ref*{gateway-implementation}.
@@
 
-As it was explained in Sect.~\ref*{introduction}, to follow the Industry 4.0 concept a hybrid environment integrating reactive Machine to Machine
-interconnection and interactive web-based user interface is required.
-The main challenge of the solution in concern is to design a generic but
-reusable architecture that addresses interoperability of these diverse
-interconnection scenarios ruled by different requirements, namely
+As it was explained in Sect.~, to follow the Industry 4.0 concept a hybrid environment integrating reactive Machine to Machine interconnection and interactive web-based user interface is required (\ref*{introduction}).
+The main challenge of the solution in concern is to design a generic but reusable architecture that addresses interoperability of these diverse interconnection scenarios ruled by different requirements, namely
 
@@
 
-Interconnection of the reactive \textbf{machine-centric} and interactive \textbf{human-centric} environments can be implemented by applying one of the following scenarios \todo{overfull}:
+Interconnection of the reactive \textbf{machine-centric} and interactive \textbf{human-centric} environments can be implemented by applying one of the following scenarios:\todo{overfull}
 
 \begin{itemize}
-\tightlist
-\item
-  \textbf{direct interconnection} - cloud-based dedicated communication
-  services are engaged to attach it to the cyber-physical system making
-  up a consistent M2M communication network using a common protocol
-  stack
-\item
-  \textbf{gateway based interconnection} - native build-in communication
-  services allows attaching the cloud to the cyber-physical system using
-  an out-of-bound protocol stack
+  \item \textbf{direct interconnection} (tightly coupled scenario) - cloud-based dedicated communication services are engaged to attach it to the cyber-physical system making up a consistent M2M communication network using a common protocol stack
+  \item \textbf{gateway based interconnection} (loosely coupled scenario) - native build-in communication services allows attaching the cloud to the cyber-physical system using an out-of-bound protocol stack
 \end{itemize}
 
-In the solution in concern, the interconnection of assets is not enough
-hence their interoperability is expected. In this case, using the same
-communication stack must be recognized as only a necessary condition. To
-support interoperability common data understanding is required. By
-design, the direct approach requires that the cloud has to be compliant
-with the interoperability standard the cyber-physical system uses. As a
-result, it becomes a consistent part of the cyber-physical system.
-Additionally, to meet this requirement the cloud and cyber-physical
-systems have to establish
+In the solution in concern, the interconnection of assets is not enough hence their interoperability is expected.
+In this case, using the same communication stack must be recognized as only a necessary condition.
+To support interoperability common data understanding is required.
+By design, the direct approach requires that the cloud has to be compliant
+with the interoperability standard the cyber-physical system uses.
+As a result, it becomes a consistent communication node of the cyber-physical system.
+Additionally, to meet this requirement the cloud and cyber-physical systems have to establish directly
 
 \begin{itemize}
-\tightlist
-\item
-  directly the same semantic-context
-\item
-  directly the same security-context
+  \item the same semantic-context
+  \item the same security-context
 \end{itemize}
 
-The possibility to establish a common semantic-context in the
-multi-vendor environment makes communication standardization especially
-important. In this case, it is required that the encoding of the payload
-of messages exchanged over the network (Data Transfer Object - TDO) is
-standardized so that the payload can be factored on the data-gathering
+The possibility to establish a common semantic-context in the multi-vendor environment makes communication standardization especially important.
+In this case, it is required that the encoding of the messages payload exchanged over the network (Data Transfer Object - TDO) is standardized so that the payload can be factored on the data-gathering
 site and consumed on the ultimate destination data processing sites.
-Security between the data origin and ultimate data destination refers to
-the protection of messages (security-context) against malicious users.
-It is required that communicating parties are using the same
-cyber-security measures.
+Security between the data origin and ultimate data destination refers to the protection of messages (security-context) against malicious users.
+It is required that communicating parties are using the same cyber-security measures.
 
-The decision to follow the \textbf{direct interconnection} scenario must
-be derived from an analysis of the capabilities of available services in
-concern. However, for the development strategy of this type of solutions
-this analysis can be done partially taking into account two features
-that can be considered invariable:
+The decision to follow the \textbf{direct interconnection} scenario must be derived from an analysis of the capabilities of available services in concern.
+However, for the development strategy of this type of solutions this analysis can be done partially taking into account two features that can be considered invariable:
 
 \begin{itemize}
-\tightlist
-\item
-  by design the cloud-based services must be virtual - they are used to
-  handle many solutions at the same time
-\item
-  by design the M2M communication is usually constrained by the
-  real-time requirements
+  \item by design the cloud-based services must be virtual - they are used to handle many solutions at the same time
+  \item by design the M2M communication is usually constrained by the real-time requirements
 \end{itemize}
 
-In practice, the set of assets embedded in the cyber-physical system is
-very stable. On the another hand, the virtualization of services means
-that they must be very flexible to handle the attachment of new assets
-proactively (acting in advance) at run time. As a result, by design, the
-cloud services must be repressible to register and authenticate devices
-exposing endpoints in the public network to allows the device to access
-a provisioning cloud service. It requires that a session over the
-Internet has to be established by the data holding asset at a
-preparation step.
+In practice, the set of assets embedded in the cyber-physical system is very stable.
+On the another hand, the virtualization of services means that they must be very flexible to handle the attachment of new assets proactively (acting in advance) at run time.
+As a result, by design, the cloud services must be repressible to register and authenticate devices exposing endpoints in the public network to allows the device to access a provisioning cloud service.
+It requires that a session over the Internet has to be established by the data holding asset at a preparation step.
 
-To meet the requirements of real-time distributed control the
-cyber-physical system may use protocols applicable only to local
-computer networks (e.g.~multicast IP, Ethernet, TSN, etc.). Because the
-cloud services support only protocols handling interconnection over the
-Internet the interaction with the cloud requires remote agents,
-i.e.~agents attached locally to the M2M network implemented applying one
-of the following archetypes:
+To meet the requirements of real-time distributed control the cyber-physical system may use protocols applicable only to local computer networks (e.g.~multicast IP, Ethernet, TSN, etc.).
+Because the cloud services support only protocols handling interconnection over the Internet the interaction with the cloud requires remote agents, i.e.~agents attached locally to the M2M network and implemented by applying one of the following archetypes:
 
 \begin{itemize}
-\tightlist
-\item
-  \textbf{edge device} - remote cloud agent acting as an intermediary
-  for nodes of the cyber-physical network
-\item
-  \textbf{field level gateway} - a dedicated custom device acting as an
-  intermediary for nodes of the cyber-physical network
-\item
-  \textbf{embedded gateway} - a software part composed into a selected
-  node of the cyber-physical network
+  \item \textbf{edge device} - remote cloud agent acting as an intermediaryfor nodes of the cyber-physical network
+  \item \textbf{field level gateway} - a dedicated custom device acting as an intermediary for nodes of the cyber-physical network
+  \item \textbf{embedded gateway} - a software part composed into a selected node of the cyber-physical network
 \end{itemize}
@@
 not derived from the middleware concept. The domain model for this
-archetype is presented in the Fig. Promoting separation of concern
+archetype is presented in the Fig.~\ref*{StrategyDomainModel} Promoting separation of concern
 design principle, the gateway functionality should be implemented as a
 self-contained software part embedded in the \texttt{Networking} service
-of the \texttt{Cipher-physical\ node}. Main functionality of this
+of the \texttt{Cyber-physical\ node}. Main functionality of this
 component is to transfer selected data between
@@
 The \textbf{embedded gateway} archetype relaxes most of the issues
-described above: cipher-physical network real-time behavior, data
+described above: \texttt{Cyber-physical\ network} real-time behavior, data
 encoding incompatibility, security-context differences to name only a
@@
 
-To comply with the Industry 4.0 communication criterion it is required that the product must be addressable over the network via TCP/UDP or IP and has to support the OPC UA Information Model.
+To comply with the Industry 4.0 communication criterion it is required that any product must be addressable over the network via TCP/UDP or IP and has to support the OPC UA Information Model.
 As a result, any product being advertised as Industry 4.0 enabled must be OPC UA-capable somehow.
@@
   \tightlist
-\item
-  connection-oriented: requires a session that has to be established before any data can be sent between sender and receiver
-\item
-  connectionless-oriented: the sender may start sending messages (called packets or datagrams) to the destination without any preceding handshake procedure
+  \item \textbf{session-oriented}: requires a session that has to be established before any data can be sent between sender and receiver
+  \item \textbf{sessionless-oriented}: the sender may start sending messages (called packets or datagrams) to the destination without any preceding handshake procedure
 \end{itemize}
 
-Using the connection-oriented communication pattern it is difficult or
+Using the session-oriented communication pattern it is difficult or
 even impossible to gather and process mobile data (Sec. I), which is one
 of the Internet of Things paradigms.
-OPC UA Part 14 PubSub \todo{add ref} \footnote{Mariusz Postol, UA Part 14: PubSub Main Technology Features in Object Oriented Internet, https://github.com/mpostol/OPC-UA-OOI, 2019, DOI: 10.5281/zenodo.1198852} offers the
-connectionless approach as an additional option to session based
-client-server interoperability and is a consistent part of the OPC UA
-specifications suit. As the result it can be recognized as the IoT ready
-technology.
+OPC UA Part 14 PubSub \cite*{RefWorks:doc:5d98837de4b055984c0eecf0} \todo{add ref: Mariusz Postol, UA Part 14: PubSub Main Technology Features in Object Oriented Internet, https://github.com/mpostol/OPC-UA-OOI, 2019, DOI: 10.5281/zenodo.1198852} offers the sessionless approach as an additional option to session based client-server interoperability relationship and is a consistent part of the OPC UA specifications suit.
+As the result it can be recognized as the IoT ready technology.
 
@@
 Microsoft Azure cloud products. There are many reasons for selecting
-Azure to accomplish cloud-based front-end of CFS. Azure offers
+Azure to accomplish cloud-based front-end of Cyber-Physical System (CFS). Azure offers
 Infrastructure as a Service (IaaS) and Platform as a Service (PaaS)
@@
 
-More detailed description of the selected Azure features in context of
-the application in concern are covered by the Sec.
-\texttt{azure-main-technology-features}.
+More detailed description of the selected Azure features in context of the application in concern are covered by the Sec.~\ref*{azure-main-technology-features}.
 
-Based on the sessionless and session-oriented communication patterns
-examination against the IoT requirements  \cite{mpostol2020} 
-it could be
-concluded that the connectionless pattern better suites issues related
-to the assets mobility and traffic asymmetry that is characteristic for
-the application domains in concern. Additionally, to promote
-interoperability and address the demands of the M2M communication in the
-context of a multi-vendor environment the prototyping should use an
-framework that must be compliant with the OPC UA Part 14 PubSub spec.
-According to proposed architecture presented in Fig. above to implement
-the \texttt{Embedded\ Gateway} as a composable part of the
-\texttt{Cipher-physical\ Node} a library implementing
-\texttt{Networking} functionality in compliance with mentioned above
-specification is a starting point for further development. Additionally
-it must be assumed that the library used to deploy
-\texttt{Embedded\ Gateway} support dependency injection and be capable
-to compose an external part supporting Azure/pubsub gateway
-functionality. The composition process must be available without
-modification of the core code of an existing library. As a result the
-prototyping is to be limited to implementation of the
-\texttt{Embedded\ Gateway} software part only.
+Based on the sessionless and session-oriented communication patterns examination against the IoT requirements \cite{mpostol2020} it could be concluded that the connectionless pattern better suites issues related to the assets mobility and traffic asymmetry that is characteristic for the application domains in concern.
+Additionally, to promote
+interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use an
+framework that must be compliant with the OPC UA Part 14 PubSub spec \cite{RefWorks:doc:5d98837de4b055984c0eecf0}.
+According to proposed architecture presented in Fig.~\ref*{StrategyDomainModel} to implement the \texttt{Embedded\ Gateway} as a composable part of the \texttt{Cyber-physical\ Node} a library implementing \texttt{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
+Additionally it must be assumed that the library used to deploy \texttt{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/pubsub gateway functionality.
+The composition process must be available without modification of the core code of an existing library.
+As a result the prototyping is to be limited to implementation of the \texttt{Embedded\ Gateway} software part only.
 
@@
 
-Sect.~\ref*{ooi-main-technology-features} provides more detailed description of this library and new functionality (\texttt{Embedded\ Gateway} \todo{refine the text} part deployment process.
+Sect.~\ref*{ooi-main-technology-features} provides more detailed description of this library and part deployment process to implement new functionality supporting (\texttt{Embedded\ Gateway}.
 

### 2020-10-30 Latex/Manuscript.tex
Work out Markdown\50.Sensors2AzureConnectivityDeployment.md #29
- final latex text formating
- fnal review

fixes #29

@@
 Deployment of the hybrid solution providing interoperability of the
-\textbf{machine-centric} cyber-physical systems and
+\textbf{machine-centric} CFSs and
 \textbf{human-centric} cloud-based front-end can be implemented applying
@@
             \textbf{direct interconnection} - cloud-based dedicated communication
-        services allow to attache it to the cyber-physical system making up a
+            services allow to attache it to the CFS making up a
             consistent M2M communication network using an in-bound protocol stack
@@
             communication services allows to attache the cloud computing to the
-        cyber-physical system using an out-of-bound protocol stack
+            CFS using an out-of-bound protocol stack
 \end{itemize}
@@
 By design, the direct approach requires that the cloud has to be
-compliant with the interoperability standard the cyber-physical system
+compliant with the interoperability standard the CFS
 is built around - it becomes a consistent part of the cyber-physical
@@
 This article addresses further research on the integration of the
-cyber-physical systems in the context of new emerging disciplines,
+CFSs in the context of new emerging disciplines,
 i.e.~Industry 4.0 (I4.0) and the Internet of Things (IoT). The new
 architecture is proposed for integration of the multi-vendor
-\textbf{machine-centric} cyber-physical system designed atop of M2M
+\textbf{machine-centric} CFS designed atop of M2M
 reactive communication and emerging cloud computing as a
@@
 The discussion covered by this section is the foundation for selecting services utilized to expose process data and suitable protocol stack to support interconnection.
-In Sect.~\ref*{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a foundation for further decisions addressing the systematic design of the interoperability of the cyber-physical systems and cloud-based front-end.
+In Sect.~\ref*{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a foundation for further decisions addressing the systematic design of the interoperability of the CFSs and cloud-based front-end.
 A reference implementation of this archetype is described in Sect.~\ref*{gateway-implementation}.
-The most important findings and future work are summarized in Sect.~\ref*{architecture} \todo{overfull}.
+The most important findings and future work are summarized in Sect.~\ref*{architecture}.
 
@@
 
-Any information about available reusable deliverables related to this
-work.
+Any information about available reusable deliverables related to this work.
 
@@
 
-As it was explained in Sect.~, to follow the Industry 4.0 concept a hybrid environment integrating reactive Machine to Machine interconnection and interactive web-based user interface is required (\ref*{introduction}).
+As it was explained in Sect.~\ref*{introduction}, to follow the Industry 4.0 concept a hybrid environment integrating reactive Machine to Machine interconnection and interactive web-based user interface is required (\ref*{introduction}).
 The main challenge of the solution in concern is to design a generic but reusable architecture that addresses interoperability of these diverse interconnection scenarios ruled by different requirements, namely
@@
 \begin{enumerate}
-  \def\labelenumi{\arabic{enumi}.}
-  \tightlist
-  \item
-        \textbf{machine-centric} machine to machine real-time mobile
-        interoperability
-  \item
-        \textbf{human-centric} cloud-based front-end
+      \item \textbf{machine-centric} machine to machine real-time mobile interoperability
+      \item \textbf{human-centric} cloud-based front-end
 \end{enumerate}
 
-Interconnection of the reactive \textbf{machine-centric} and interactive \textbf{human-centric} environments can be implemented by applying one of the following scenarios:\todo{overfull}
+Interconnection of the reactive \textbf{machine - centric} and interactive \textbf{human - centric} environments can be implemented by applying one of the following scenarios:
 
 \begin{itemize}
-  \item \textbf{direct interconnection} (tightly coupled scenario) - cloud-based dedicated communication services are engaged to attach it to the cyber-physical system making up a consistent M2M communication network using a common protocol stack
-  \item \textbf{gateway based interconnection} (loosely coupled scenario) - native build-in communication services allows attaching the cloud to the cyber-physical system using an out-of-bound protocol stack
+      \item \textbf{direct interconnection} (tightly coupled scenario) - cloud-based dedicated communication services are engaged to attach it to the CFS making up a consistent M2M communication network using a common protocol stack
+      \item \textbf{gateway based interconnection} (loosely coupled scenario) - native build-in communication services allows attaching the cloud to the CFS using an out-of-bound protocol stack
 \end{itemize}
@@
 By design, the direct approach requires that the cloud has to be compliant
-with the interoperability standard the cyber-physical system uses.
-As a result, it becomes a consistent communication node of the cyber-physical system.
-Additionally, to meet this requirement the cloud and cyber-physical systems have to establish directly
+with the interoperability standard the CFS uses.
+As a result, it becomes a consistent communication node of the CFS.
+Additionally, to meet this requirement the cloud and CFSs have to establish directly the same
 
 \begin{itemize}
-  \item the same semantic-context
-  \item the same security-context
+      \item semantic-context
+      \item security-context
 \end{itemize}
@@
 
-In practice, the set of assets embedded in the cyber-physical system is very stable.
+In practice, the set of assets embedded in the CFS is very stable.
 On the another hand, the virtualization of services means that they must be very flexible to handle the attachment of new assets proactively (acting in advance) at run time.
@@
 
-To meet the requirements of real-time distributed control the cyber-physical system may use protocols applicable only to local computer networks (e.g.~multicast IP, Ethernet, TSN, etc.).
+To meet the requirements of real-time distributed control the CFS may use protocols applicable only to local computer networks (e.g.~multicast IP, Ethernet, TSN, etc.).
 Because the cloud services support only protocols handling interconnection over the Internet the interaction with the cloud requires remote agents, i.e.~agents attached locally to the M2M network and implemented by applying one of the following archetypes:
@@
       \item \textbf{edge device} - remote cloud agent acting as an intermediaryfor nodes of the cyber-physical network
-  \item \textbf{field level gateway} - a dedicated custom device acting as an intermediary for nodes of the cyber-physical network
+      \item \textbf{field level gateway} - a dedicated custom agent acting as an intermediary for nodes of the cyber-physical network
       \item \textbf{embedded gateway} - a software part composed into a selected node of the cyber-physical network
@@
 
-\textbf{Edge device} is a device that connects directly to the cloud
-services but acts as an intermediary for other devices called leaf
-devices. Additionally, it allows the selection of initial data
-processing and execution of them using local resources. The \textbf{edge
-  device} may be located close to the leaf devices and attached to the
-cyber-physical network using protocols applicable only to local computer
-networks. In this scenario, it is possible to use a custom protocol
-stack to get connected to the \textbf{edge device} with the cloud and
-helps to save the bandwidth thanks to sending only the results of local
-processing. In this approach, the \textbf{edge device} is part of cloud
-vendor products and cannot be recognized as a generic solution that can
-be used to connect to other clouds at the same time.
+\textbf{Edge device} is a device that connects directly to the cloud services but acts as an intermediary for other devices called leaf devices.
+Additionally, it allows the selection of initial data processing and execution of them using local resources.
+The \textbf{edge device} may be located close to the leaf devices and attached to the cyber-physical network using protocols applicable only to local computer networks.
+In this scenario, it is possible to use a custom protocol stack to get connected to the \textbf{edge device} with the cloud and helps to save the bandwidth thanks to sending only the results of local processing.
+In this approach, the \textbf{edge device} is part of cloud vendor products and cannot be recognized as a generic solution that can be used to connect to other clouds at the same time.
 
@@
 
-Unlike the above described solutions, the \textbf{embedded gateway} is
-not derived from the middleware concept. The domain model for this
-archetype is presented in the Fig.~\ref*{StrategyDomainModel} Promoting separation of concern
-design principle, the gateway functionality should be implemented as a
-self-contained software part embedded in the \texttt{Networking} service
-of the \texttt{Cyber-physical\ node}. Main functionality of this
-component is to transfer selected data between
-\texttt{Cyber-physical\ network} using \texttt{Networking} services of
-an existing \texttt{Cyber-physical\ node} and
-\texttt{Cloud-based\ front-end} using officially supported by the cloud
-vendor interconnection services.
+Unlike the above described solutions, the \textbf{embedded gateway} is not derived from the middleware concept.
+The domain model for this archetype is presented in the Fig.~\ref*{StrategyDomainModel}.
+Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \texttt{Networking} service of the \texttt{Cyber-physical\ node}.
+Main functionality of this component is to transfer selected data between \texttt{Cyber-physical\ network} using \texttt{Networking} services of an existing \texttt{Cyber-physical\ node} and \texttt{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
 
-The \textbf{embedded gateway} archetype relaxes most of the issues
-described above: \texttt{Cyber-physical\ network} real-time behavior, data
-encoding incompatibility, security-context differences to name only a
-few. The main goal of this article is to provide proof that the
-\textbf{embedded gateway} archetype implementation is possible based on
-a generic architecture that can be used as a foundation for the
-integration of the heterogenous environments in concern. The proposed
-implementation is designed for selected interoperability standard and
-cloud product.
+The \textbf{embedded gateway} archetype relaxes most of the issues described above: \texttt{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security-context differences to name only a few.
+The main goal of this article is to provide proof that the \textbf{embedded gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogenous environments in concern.
+The proposed implementation is designed for selected interoperability standard and cloud product.
 
@@
 of the Internet of Things paradigms.
-OPC UA Part 14 PubSub \cite*{RefWorks:doc:5d98837de4b055984c0eecf0} \todo{add ref: Mariusz Postol, UA Part 14: PubSub Main Technology Features in Object Oriented Internet, https://github.com/mpostol/OPC-UA-OOI, 2019, DOI: 10.5281/zenodo.1198852} offers the sessionless approach as an additional option to session based client-server interoperability relationship and is a consistent part of the OPC UA specifications suit.
+OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} \todo{add ref: Mariusz Postol, UA Part 14: PubSub Main Technology Features in Object Oriented Internet, https://github.com/mpostol/OPC-UA-OOI, 2019, DOI: 10.5281/zenodo.1198852} offers the sessionless approach as an additional option to session based client-server interoperability relationship and is a consistent part of the OPC UA specifications suit.
 As the result it can be recognized as the IoT ready technology.
@@
 Based on the sessionless and session-oriented communication patterns examination against the IoT requirements \cite{mpostol2020} it could be concluded that the connectionless pattern better suites issues related to the assets mobility and traffic asymmetry that is characteristic for the application domains in concern.
-Additionally, to promote
-interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use an
-framework that must be compliant with the OPC UA Part 14 PubSub spec \cite{RefWorks:doc:5d98837de4b055984c0eecf0}.
-According to proposed architecture presented in Fig.~\ref*{StrategyDomainModel} to implement the \texttt{Embedded\ Gateway} as a composable part of the \texttt{Cyber-physical\ Node} a library implementing \texttt{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
+Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub spec \cite{RefWorks:doc:5d98837de4b055984c0eecf0}.
+According to proposed architecture (Fig.~\ref*{StrategyDomainModel}) to implement the \texttt{Embedded\ Gateway} as a composable part of the \texttt{Cyber-physical\ Node} a library implementing \texttt{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
 Additionally it must be assumed that the library used to deploy \texttt{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/pubsub gateway functionality.
@@
 
-A library that meets all these requirements has been implemented consistently with the Object-Oriented Internet paradigm \cite{RefWorks:doc:5c66740ae4b081adf5804596}
-worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }. The \cite{mpostol2020}
-covers the description of a reference application program implementation proving that it is possible to design
-universal architecture targeting reactive interoperability as a
-consistent part of the Object-Oriented Internet concept compliant with
-the OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} international standard. According to the presented implementation and
-evaluation, using the dependency injection and late binding, the
-application program can be seamlessly adapted to the production
-environment and scales well. This approach also improves flexibility and
-adaptability of the existing solutions against any modification of the
-production environment including but not limited to the selected
-interoperability standard change.
+A library that meets all these requirements has been implemented consistently with the Object-Oriented Internet paradigm \cite{RefWorks:doc:5c66740ae4b081adf5804596} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }.
+The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the Object-Oriented Internet concept compliant withthe OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} international standard.
+According to the presented implementation andevaluation, using the dependency injection and late binding, theapplication program can be seamlessly adapted to the production environment and scales well.
+This approach also improves flexibility and adaptability of the existing solutions against any modification of the production environment including but not limited to the selected interoperability standard change.
 
-Sect.~\ref*{ooi-main-technology-features} provides more detailed description of this library and part deployment process to implement new functionality supporting (\texttt{Embedded\ Gateway}.
+Sect.~\ref*{ooi-main-technology-features} provides a more detailed description of this library and an external part deployment process that is to be used to implement new functionality supporting \texttt{Embedded\ Gateway}.
 
@@
 Deployment of the hybrid solution providing interoperability of the
-\textbf{machine-centric} cyber-physical systems designed atop of M2M
+\textbf{machine-centric} Cyber-Physical Systems (CFS) designed atop of M2M
 reactive communication and emerging cloud computing as a
@@
 autonomous (with own identity) software component or module that is
-interfacing with selected cyber-physical systems for data collection,
+interfacing with selected (CFS) for data collection,
 analysis, and also remote control. Microsoft Azure is a cloud-based
@@
 middleware must be considered as a coupler. It must be interconnected
-with the cyber-physical system using an in-band protocol adhering to
+with the (CFS) using an in-band protocol adhering to
 communications requirements (i.e.~protocol profile, data encoding, time
@@
 
-Before process data can be exposed using a web user interface the data
-source must be associated with an appropriate solution and validated to
-make sure that the security rules are not violated. It is hard to assume
-that the security rules governing the cyber-physical system may also
-apply to the cloud-based services. In the gateway scenario, they can be
-mapped on each other or entirely independent. The
-\texttt{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper
-service for \texttt{IoT\ Hub} that enables devices' connection process
-management, upon device providing valid identity attestation it assigns
-the device to an appropriate \texttt{IoT\ Hub} instance and returns to
-the device connection parameters, which allow direct connection with
-given \texttt{IoT\ Hub} service. The device proceeds to use the same
-attestation in \texttt{IoT\ Hub} connection and based on it, is granted
-authorization to selected resources \todo{MP authorization can be applied only to operations?} and operations including but not limited to data transfer updating the user interface.
+Before process data can be exposed using a web user interface the data source must be associated with an appropriate solution and validated to make sure that the security rules are not violated.
+It is hard to assume that the security rules governing the CFS may also apply to the cloud-based services.
+In the gateway scenario, they can be mapped on each other or entirely independent.
+The \texttt{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper service for \texttt{IoT\ Hub} that enables devices' connection process management, upon device providing valid identity attestation it assigns the device to an appropriate \texttt{IoT\ Hub} instance and returns to the device connection parameters, which allow direct connection with given \texttt{IoT\ Hub} service.
+The device proceeds to use the same attestation in \texttt{IoT\ Hub} connection and based on it, is granted authorization to selected operations including but not limited to data transfer and updating the user interface.
 
@@
 \begin{itemize}
-  \tightlist
-  \item
-        \texttt{Industrial\ IoT} - discovering OPC UA enabled servers in a factory network and register them in Azure \texttt{IoT\ Hub} implemented using \texttt{IoT\ Edge}
-  \item
-        \texttt{Digital\ Twins} - managing the graph of digital twins, which are to represent some real-world process or entity
+      \item \texttt{Industrial\ IoT} - discovering OPC UA enabled servers in a factory network and register them in Azure \texttt{IoT\ Hub} implemented using \texttt{IoT\ Edge}
+      \item \texttt{Digital\ Twins} - managing the graph of digital twins, which are to represent some real-world process or entity
 \end{itemize}
@@
 
-Having defined types in advance, a gateway may provide dedicated conversions functionality, i.e.~replacing bitstreams used by the cyber-physical system by equivalent ones for the cloud-based services.
-The Azure offers a vast variety of built-in types ready to be used in common cases, but not necessarily there are equivalent counterparts in use by the cyber-physical system.
+Having defined types in advance, a gateway may provide dedicated conversions functionality, i.e.~replacing bitstreams used by the CFS by equivalent ones for the cloud-based services.
+The Azure offers a vast variety of built-in types ready to be used in common cases, but not necessarily there are equivalent counterparts in use by the CFS.
 Additionally, the data conversion must address the following issues:
@@
 
-In \texttt{IoT\ Central} a cyber-physical system is represented as a set
+In \texttt{IoT\ Central} a CFS is represented as a set
 of devices. The characteristics and behavior of each device kind are
@@
 also metadata describing the data (called telemetry) exchanged over the
-wire with the cyber-physical system called Device Capability Model
+wire with the CFS called Device Capability Model
 (DCM). Additionally, the DT contains properties, customization, and
@@
 applied to achieve interoperability of the devices interconnected as the
-cyber-physical system. DCM development against any external information
+CFS. DCM development against any external information
 model is a design-time task and should be supported by dedicated

### 2020-10-30 Latex/Manuscript.tex
Work out Markdown\20.Introduction.md #26
- final latex review
- fixes #26

@@
 
-\hypertarget{introduction}{%
-      \section{Introduction}\label{introduction}}
+\section{Introduction}\label{introduction}
 
-All the time, the Information and Communication Technology is providing
-society with a vast variety of new distributed applications aimed at
-micro and macro optimization of the industrial processes. Obviously, the
-design foundation of this kind of application has to focus primarily on
-communication technologies. Based on the role humans take while using
-these applications they can be grouped as follows:
+All the time, the Information and Communication Technology is providing society with a vast variety of new distributed applications aimed at micro and macro optimization of the industrial processes.
+Obviously, the design foundation of this kind of application has to focus primarily on communication technologies.
+Based on the role humans take while using these applications they can be grouped as follows:
 
 \begin{itemize}
-      \tightlist
-      \item
-            \textbf{human-centric} - information origin or ultimate information
-            destination is an operator,
-      \item
-            \textbf{machine-centric} - information creation, consumption,
-            networking, and processing are achieved entirely without human
-            interaction.
+      \item \textbf{human-centric} - information origin or ultimate information destination is an operator,
+      \item \textbf{machine-centric} - information creation, consumption, networking, and processing are achieved entirely without human interaction.
 \end{itemize}
 
-A typical \textbf{human-centric} approach is a web-service supporting,
-for example, a web user interface (UI) to monitor conditions, and manage
-millions of devices and their data in a typical cloud-based IoT
-approach. It is characteristic that, in this case, any uncertainty and
-necessity to make a decision can be relaxed by human interaction.
-Coordination of robots behavior in a work-cell (automation islands) is a
-\textbf{machine-centric} example. In this case, it is essential that any
-human interaction is impractical or even impossible. This
-interconnection scenario requires the machine to machine communication
-(M2M) demanding multi-vendor devices integration.
+A typical \textbf{human-centric} approach is a web-service supporting, for example, a web user interface (UI) to monitor conditions, and manage millions of devices and their data in a typical cloud-based IoT approach.
+It is characteristic that, in this case, any uncertainty and necessity to make a decision can be relaxed by human interaction.
+Coordination of robots behavior in a work-cell (automation islands) is a \textbf{machine-centric} example.
+In this case, it is essential that any human interaction is impractical or even impossible.
+This interconnection scenario requires the machine to machine communication (M2M) demanding multi-vendor devices integration.
 
-From the M2M communication concept, a broader concept of a smart factory
-can be derived. In this concept, the mentioned robots are only executive
-assets of an integrated supervisory control system responsible for macro
-optimization of an industrial process composed into one whole.
-Deployment of the smart factory concept requires a hybrid solution and
-interconnection of the mentioned above heterogeneous environments. This
-approach is called the fourth industrial revolution and coined as
-Industry 4.0. It is worth stressing that machines - or more general
-assets - interconnection is not enough, and additionally, assets
-interoperability has to be expected for the deployment of this concept.
-In this case, multi-vendor integration makes communication
-standardization especially important, namely it is required that the
-payload of the message is standardized to be factored on the gathering
-site and consumed on the ultimate destination site.
+From the M2M communication concept, a broader concept of a smart factory can be derived.
+In this concept, the mentioned robots are only executive assets of an integrated supervisory control system responsible for macro optimization of an industrial process composed into one whole.
+Deployment of the smart factory concept requires a hybrid solution and interconnection of the mentioned above heterogeneous environments.
+This approach is called the fourth industrial revolution and coined as Industry 4.0.
+It is worth stressing that machines - or more general assets - interconnection is not enough, and additionally, assets interoperability has to be expected for the deployment of this concept.
+In this case, multi-vendor integration makes communication standardization especially important, namely it is required that the payload of the message is standardized to be factored on the data  gathering site and consumed on the ultimate destination site.
 
-Highly-distributed solutions used to control real-time process
-aggregating islands of automation (e.g.~virtual power plants producing
-renewable energy) additionally must leverage public communication
-infrastructure, namely the Internet. Internet is a demanding environment
-for highly distributed process control applications designed atop the
-M2M communication paradigm because
+Highly-distributed solutions used to control real-time process aggregating islands of automation (e.g.~virtual power plants producing renewable energy) additionally must leverage public communication infrastructure, namely the Internet.
+Internet is a demanding environment for highly distributed process control applications designed atop the M2M communication paradigm because
+\begin{itemize}
+      \item it is a globally shareable environment and can be also used by malicious users
+      \item it offers only non-deterministic communication making integration of islands of automation designed against the real-time requirements a difficult task
+\end{itemize}
+
+Today both obstacles can be overcome, and as examples, we have bank account remote control and voice over IP in daily use.
+The first application must be fine-tuned in the context of data security, and the second is very sensitive on time relationships.
+Similar approaches could be applied to adopt the well known in process control industry concepts:
 
 \begin{itemize}
-      \tightlist
-      \item
-            it is a globally shareable environment and can be also used by
-            malicious users
-      \item
-            it offers only non-deterministic communication making integration of
-            islands of automation designed against the real-time requirements a
-            difficult task
+      \item  Human Machine Interface (HNI)
+      \item Supervisory Control and Data Acquisition (SCADA)
+      \item Distributed Control Systems (DCS)
 \end{itemize}
 
-Today both obstacles can be overcome, and as examples, we have bank
-account remote control and voice over IP in daily use. The first
-application must be fine-tuned in the context of data security, and the
-second is very sensitive on time relationships. Similar approaches could
-be applied to adopt the well known in process control industry concepts:
+A detailed examination of these solutions is far beyond the scope of this article.
+It is only worth stressing that, by design, all of them are designed on the foundation of interactive communication.
+Interactive communication is based on a data polling foundation.
+In this case, the application must follow the interactive behavioral model, because it actively polls the data source for more information by pulling data from a sequence that represents the process state in time.
+The application is active in the data retrieval process - it controls the pace of the retrieval by sending the requests at its convenience.
+Such a polling pattern is similar to visiting the books shop and checking out a book.
+After you are done with the book, you pay another visit to check out another one.
+If the book is not available you must wait, but you may read what you selected.
+The client/server archetype is well suited for the mentioned above applications.
+
+After dynamically attaching a new island of automation the control application (responsible for the data pulling) must be reconfigured for this interoperability scenario.
+In other words, in this case, the interactive communication relationship cannot be directly applied because the control application must be informed on how to pull data from a new source.
+As a result, a plug and produce scenario cannot be seamlessly applied.
+A similar drawback must be overcome if for security reasons suitable protection methods have been applied to make network traffic propagation asymmetric.
+It is accomplished using intermediary devices, for example, firewalls, to enforce traffic selective availability based on predetermined security rules against unauthorized access.
+
+Going further, we shall assume that islands of automation are mobile, e.g.~autonomous cars passing a supervisory controlled service area.
+In this case, the behavior of the interconnected assets is particularly important concerning the environment in which they must interact.
+This way we have entered the Internet of Things domain of Internet-based applications.
+
+If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship could relax the problems encountered while the interactive approach is applied.
+In this case, the sessionless publisher-subscriber communication relationship is a typical pattern to implement the abstract reactive interoperability paradigm.
+The sessionless relationship is a message distribution scenario where senders of messages, called publishers, do not send them directly to specific receivers, called subscribers, but instead, categorize the published messages into topics without knowledge about which subscribers if any, there may be.
+Similarly, subscribers express interest in one or more topics and only receive messages that are of interest, without knowledge about which publishers, if any, there are.
+In this scenario, the publishers and subscribers are loosely coupled.i.e they are decoupled in time, space and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.
+
+If the \textbf{machine-centric} interoperability - making up islands of automation - must be monitored and/or controlled by a supervisory system cloud computing concept may be recognized as a beneficial solution to replace or expand the mentioned above applications, i.e.~HMI, SCADA, DCS, etc.
+Cloud computing is a method to provide a requested functionality as a set of services.
+There are many examples that cloud computing is useful to reduce costs and increase robustness.
+It is also valuable in case the process data must be exposed to many stakeholders.
+Following this idea and offering control systems as a service, there is required a mechanism created on the service concept and supporting abstraction and virtualization - two main pillars of the cloud computing paradigm.
+In the cloud computing concept, virtualization is recognized as the possibility to share the services by many users, and abstraction hides implementation details.
+
+Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} cyber-physical system (CFS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios:
 
 \begin{itemize}
-      \tightlist
-      \item
-            Human Machine Interface (HNI)
-      \item
-            Supervisory Control and Data Acquisition (SCADA)
-      \item
-            Distributed Control Systems (DCS)
+      \item \textbf{direct interconnection} - cloud-based dedicated communication services allow to attache it to the CFS making up a consistent M2M communication network using an in-bound protocol stack
+      \item \textbf{gateway based interconnection} - typical build-in communication services allows to attache the cloud computing to the CFS using an out-of-bound protocol stack
 \end{itemize}
 
-A detailed examination of these solutions is far beyond the scope of
-this article. It is only worth stressing that, by design, all of them
-are designed on the foundation of interactive communication. Interactive
-communication is based on a data polling foundation. In this case, the
-application must follow the interactive behavioral model, because it
-actively polls the data source for more information by pulling data from
-a sequence that represents the process state in time. The application is
-active in the data retrieval process - it controls the pace of the
-retrieval by sending the requests at its convenience. Such a polling
-pattern is similar to visiting the books shop and checking out a book.
-After you are done with the book, you pay another visit to check out
-another one. If the book is not available you must wait, but you may
-read what you selected. The client/server archetype is well suited for
-the mentioned above applications.
+By design, the direct approach requires that the cloud has to be compliant with the interoperability standard the CFS is built upon - it becomes a consistent part of the CFS.
+Data models, roles, and responsibility differences of both solutions make this approach impractical or even imposable to be applied in typical cases.
+A more detailed description is covered by the Sect.~\ref*{cloud-to-sensors-field-level-connectivity}.
 
-After dynamically attaching a new island of automation the control
-application (responsible for the data pulling) must be reconfigured for
-this interoperability scenario. In other words, in this case, the
-interactive relationship cannot be directly applied because the control
-application must be informed on how to pull data from a new source. As a
-result, a plug and produce scenario cannot be seamlessly applied. A
-similar drawback must be overcome if for security reasons suitable
-protection methods have been applied to make network traffic propagation
-asymmetric. It is accomplished using intermediary devices, for example,
-firewalls, to enforce traffic selective availability based on
-predetermined security rules against unauthorized access.
-
-Going further, we shall assume that islands of automation are mobile,
-e.g.~autonomous cars passing a supervisory controlled service area. In
-this case, the behavior of the interconnected assets is particularly
-important concerning the environment in which they must interact. This
-way we have entered the Internet of Things domain of Internet-based
-applications.
-
-If we must bother with the network traffic propagation asymmetry or
-mobility of the asset network attachment-points the reactive
-relationship could relax the problems encountered while the interactive
-approach is applied. In this case, the sessionless publisher-subscriber
-communication archetype is a typical pattern to implement the abstract
-reactive interoperability paradigm. The sessionless archetype is a
-message distribution scenario where senders of messages, called
-publishers, do not send them directly to specific receivers, called
-subscribers, but instead, categorize the published messages into topics
-without knowledge about which subscribers if any, there may be.
-Similarly, subscribers express interest in one or more topics and only
-receive messages that are of interest, without knowledge about which
-publishers, if any, there are. In this scenario, the publishers and
-subscribers are loosely coupled.i.e they are decoupled in time, space
-and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.
-
-If the \textbf{machine-centric} interoperability - making up islands of
-automation - must be monitored and/or controlled by a supervisory system
-cloud computing concept may be recognized as a beneficial solution to
-replace or expand the mentioned above applications, i.e.~HMI, SCADA,
-DCS, etc. Cloud computing is a method to provide a requested
-functionality as a set of services. There are many examples that cloud
-computing is useful to reduce costs and increase robustness. It is also
-valuable in case the process data must be exposed to many stakeholders.
-Following this idea and offering control systems as a service, there is
-required a mechanism created on the service concept and supporting
-abstraction and virtualization - two main pillars of the cloud computing
-paradigm. In the cloud computing concept, virtualization is recognized
-as the possibility to share the services by many users, and abstraction
-hides implementation details.
-
-Deployment of the hybrid solution providing interoperability of the
-\textbf{machine-centric} CFSs and
-\textbf{human-centric} cloud-based front-end can be implemented applying
-the following scenarios:
-
-\begin{itemize}
-      \tightlist
-      \item
-            \textbf{direct interconnection} - cloud-based dedicated communication
-            services allow to attache it to the CFS making up a
-            consistent M2M communication network using an in-bound protocol stack
-      \item
-            \textbf{gateway based interconnection} - typical build-in
-            communication services allows to attache the cloud computing to the
-            CFS using an out-of-bound protocol stack
-\end{itemize}
-
-By design, the direct approach requires that the cloud has to be
-compliant with the interoperability standard the CFS
-is built around - it becomes a consistent part of the cyber-physical
-system. Data models, roles, and responsibility differences of both
-solutions make this approach impractical and imposable to be applied in
-typical cases. A more detailed description is covered by the Sect.~\ref*{cloud-to-sensors-field-level-connectivity}.
-
-This article addresses further research on the integration of the
-CFSs in the context of new emerging disciplines,
-i.e.~Industry 4.0 (I4.0) and the Internet of Things (IoT). The new
-architecture is proposed for integration of the multi-vendor
-\textbf{machine-centric} CFS designed atop of M2M
-reactive communication and emerging cloud computing as a
-\textbf{human-centric} front-end. To support the multi-vendor
-environment OPC Unified Architecture interoperability standard has been
-selected. The proposals are backed by proof of concept reference
-implementations. Prototyping addresses Microsoft Azure Cloud as an
-example. The prototyping outcome has been just published on GitHub as
-the open-source (MIT licensed). The proposed solutions have been
-harmonized with the more general concept called the Object-Oriented
-Internet.
+This article addresses further research on the integration of the CFSs in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Internet of Things (IoT).
+The new architecture is proposed for integration of the multi-vendor \textbf{machine-centric} CFS designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end.
+To support the multi-vendor environment OPC Unified Architecture interoperability standard has been selected.
+The proposals are backed by proof of concept reference implementations.
+Prototyping addresses Microsoft Azure Cloud as an example.
+The prototyping outcome has been just published on GitHub as the open-source (MIT licensed).
+The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.
 
@@
 \begin{enumerate}
-      \def\labelenumi{\arabic{enumi}.}
-      \tightlist
-      \item
-            reactive interoperability M2M communication based on the OPC UA
-            standard can be implemented as a powerful standalone library without
-            dependency on the Client/Server session-oriented archetype
-      \item
-            Azure interoperability can be implemented as an external part
-            employing out-of-band communication without dependency on the OPC UA
-            implementation
-      \item
-            the proposed generic architecture allows that the gateway
-            functionality is composable at run-time - no programming required
+      \item  reactive interoperability M2M communication based on the OPC UA standard can be implemented as a powerful standalone library without dependency on the Client/Server session-oriented archetype
+      \item Azure interoperability can be implemented as an external part employing out-of-band communication without dependency on the OPC UA implementation
+      \item the proposed generic architecture allows that the gateway functionality is implemented as composable part at run-time part - no programming required
 \end{enumerate}
@@
 It promotes a reactive interoperability pattern and a generic approach to establishing interoperability-context.
-Sect.~\ref*{azure-main-technology-features} analyzes data presentation user interface, available native communication services, and data/metadata model offered by the Microsoft Azure.
-The discussion covered by this section is the foundation for selecting services utilized to expose process data and suitable protocol stack to support interconnection.
-In Sect.~\ref*{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a foundation for further decisions addressing the systematic design of the interoperability of the CFSs and cloud-based front-end.
 A reference implementation of this archetype is described in Sect.~\ref*{gateway-implementation}.
-The most important findings and future work are summarized in Sect.~\ref*{architecture}.
+The most important findings and future work are summarized in Sect.~\ref*{conclusion}.
 
-\hypertarget{consider-to-add}{%
-      \subsection{Consider to add}\label{consider-to-add}}
+\section{Cloud to Sensors Field Level Connectivity}\label{cloud-to-sensors-field-level-connectivity}
 
-\hypertarget{scope}{%
-      \subsubsection{Scope}\label{scope}}
-
-What we must do to prove the goal have been achieved. Extent or range of
-development, view, outlook, application, operation, effectiveness, etc.
-
-\hypertarget{related-work}{%
-      \subsubsection{Related work}\label{related-work}}
-
-Any information about available reusable deliverables related to this work.
-
-\hypertarget{cloud-to-sensors-field-level-connectivity}{%
-      \section{Cloud to Sensors Field Level Connectivity}\label{cloud-to-sensors-field-level-connectivity}}
-
-\hypertarget{architecture}{%
-      \subsection{Architecture}\label{architecture}}
+\subsection{Architecture}\label{architecture}
 
@@
 To support interoperability common data understanding is required.
-By design, the direct approach requires that the cloud has to be compliant
-with the interoperability standard the CFS uses.
+By design, the direct approach requires that the cloud has to be compliant with the interoperability standard the CFS uses.
 As a result, it becomes a consistent communication node of the CFS.
@@
 The possibility to establish a common semantic-context in the multi-vendor environment makes communication standardization especially important.
-In this case, it is required that the encoding of the messages payload exchanged over the network (Data Transfer Object - TDO) is standardized so that the payload can be factored on the data-gathering
-site and consumed on the ultimate destination data processing sites.
+In this case, it is required that the encoding of the messages payload exchanged over the network (Data Transfer Object - TDO) is standardized so that the payload can be factored on the data-gathering site and consumed on the ultimate destination data processing sites.
 Security between the data origin and ultimate data destination refers to the protection of messages (security-context) against malicious users.
@@
 
-The \textbf{field level gateway} is also build atop of the middleware
-concept. The only difference compared with the \textbf{edge device} is
-necessity to use officially supported by the cloud vendor services to
-get connected. In this scenario the process data may be transferred to
-many clouds at the same time provided that the gateway offers this
-functionality.
+The \textbf{field level gateway} is also build atop of the middleware concept.
+The only difference compared with the \textbf{edge device} is necessity to use officially supported by the cloud vendor services to get connected.
+In this scenario the process data may be transferred to many clouds at the same time provided that the gateway offers this functionality.
 
@@
 
-Using the session-oriented communication pattern it is difficult or
-even impossible to gather and process mobile data (Sec. I), which is one
-of the Internet of Things paradigms.
+Using the session-oriented communication pattern it is difficult or even impossible to gather and process mobile data (Sec.~\ref*{introduction} ), which is one of the Internet of Things paradigms.
 OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} \todo{add ref: Mariusz Postol, UA Part 14: PubSub Main Technology Features in Object Oriented Internet, https://github.com/mpostol/OPC-UA-OOI, 2019, DOI: 10.5281/zenodo.1198852} offers the sessionless approach as an additional option to session based client-server interoperability relationship and is a consistent part of the OPC UA specifications suit.
@@
 
-The presented proposals in the article are backed by proof of concept
-reference implementations. For this study, prototyping addresses
-Microsoft Azure cloud products. There are many reasons for selecting
-Azure to accomplish cloud-based front-end of Cyber-Physical System (CFS). Azure offers
-Infrastructure as a Service (IaaS) and Platform as a Service (PaaS)
-capabilities. As a result, the platform can be used not only as a
-cloud-based front-end for CFS. By design, the Azure services are
-compliant with Security Development Lifecycle (SDL) an industry-leading
-security process. It is also compliant with the new international
-standard for cloud privacy, namely ISO 27018. Solutions hosted on Azure
-are scaled up to millions of users without any additional coding. For
-the development of the CFS front-end, it is essential that Azure
-provides very efficient storage services usefully for real-time process
-data archival. Azure provides a vast variety of hybrid connections
-including but not limited to virtual private networks (VPNs), caches,
-content delivery networks (CDNs), ExpressRoute, and IoT dedicated
-services that can be directly used to implement cloud-based front-end
-for CFS. Because it is also integrated with other Microsoft tools like
-Office 365, Outlook, and SharePoint using Azure allows preserving
-investment and exporting process data to the mentioned tools. Azure also
-offers services supporting analytics and intelligence capabilities for
-further improving business processes and decision making. It is the only
-cloud platform that offers Blockchain as a Service (BaaS), Machine
-Learning, Bots, and Cognitive APIs capabilities.
+The presented proposals in the article are backed by proof of concept reference implementations.
+For this study, prototyping addresses Microsoft Azure cloud products.
+There are many reasons for selecting Azure to accomplish cloud-based front-end of Cyber-Physical System (CFS).
+Azure offers Infrastructure as a Service (IaaS) and Platform as a Service (PaaS) capabilities.
+As a result, the platform can be used not only as a cloud-based front-end for CFS.
+By design, the Azure services are compliant with Security Development Lifecycle (SDL) an industry-leading security process.
+It is also compliant with the new international standard for cloud privacy, namely ISO 27018.
+Solutions hosted on Azure are scaled up to millions of users without any additional coding.
+For the development of the CFS front-end, it is essential that Azure provides very efficient storage services usefully for real-time process data archival.
+Azure provides a vast variety of hybrid connections including but not limited to virtual private networks (VPNs), caches, content delivery networks (CDNs), ExpressRoute, and IoT dedicated services that can be directly used to implement cloud-based front-end for CFS.
+Because it is also integrated with other Microsoft tools like Office 365, Outlook, and SharePoint using Azure allows preserving investment and exporting process data to the mentioned tools.
+Azure also offers services supporting analytics and intelligence capabilities for further improving business processes and decision making.
+It is the only cloud platform that offers Blockchain as a Service (BaaS), Machine Learning, Bots, and Cognitive APIs capabilities.
 
-Azure aids Internet protocols and open standards such as JSON, XML,
-SOAP, REST, MQTT, AMQP, and HTTP. A software development kits for C\#,
-Java, PHP, and Ruby are available for custom applications. Azure
-provides services supporting data exchange over the OPC UA, but they
-don't support pubsub compliant with the OPC UA Part-14. Connectivity
-services on the network use JSON-based Data Transfer Object encoded
-based on schema derived from the solution metadata.
+Azure aids Internet protocols and open standards such as JSON, XML, SOAP, REST, MQTT, AMQP, and HTTP.
+A software development kits for C\#, Java, PHP, and Ruby are available for custom applications.
+Azure provides services supporting data exchange over the OPC UA, but they don't support pubsub compliant with the OPC UA Part-14.
+Connectivity services on the network use JSON-based Data Transfer Object encoded based on schema derived from the solution metadata.
 
@@
 
-The following subsections covers description of the current state of technologies with regards to OPC UA pubsub and Azure cloud-based IoT enabler.
+The following subsections cover the description of the current state of technologies with regards to Azure cloud-based IoT enabler and OPC UA pubsub.
+Sect.~\ref*{azure-main-technology-features} analyzes data presentation user interface, available native communication services, and data/metadata model offered by the Microsoft Azure.
+The discussion covered by this section is the foundation for selecting services utilized to expose process data and suitable protocol stack to support interconnection.
+In Sect.~\ref*{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a foundation for further decisions addressing the systematic design of the interoperability of the CFSs and cloud-based front-end.
 
-\hypertarget{azure-main-technology-features}{%
-      \subsection{Azure Main Technology Features}\label{azure-main-technology-features}}
+\subsection{Azure Main Technology Features}\label{azure-main-technology-features}
 
-\hypertarget{services}{%
-      \subsubsection{Services}\label{services}}
+\subsubsection{Services}\label{services}
 
@@
 
-\hypertarget{data-interchange}{%
-      \subsubsection{Data Interchange}\label{data-interchange}}
+\subsubsection{Data Interchange}\label{data-interchange}
 
@@
 
-\hypertarget{connectivity}{%
-      \subsubsection{Connectivity}\label{connectivity}}
+\subsubsection{Connectivity}\label{connectivity}
 
@@
 
-\hypertarget{ooi-main-technology-features}{%
-      \subsection{OOI Main Technology Features}\label{ooi-main-technology-features}}
+\subsection{OOI Main Technology Features}\label{ooi-main-technology-features}
 
@@
       \tightlist
-      \item
-            Machinie To Machine communication based on the semantic data
-      \item
-            OOI PubSub Implementation Architecture
-      \item
-            Simple, complex and structural data processing
+      \item Machinie To Machine communication based on the semantic data
+      \item OOI PubSub Implementation Architecture
+      \item Simple, complex and structural data processing
 \end{itemize}
 
-\hypertarget{gateway-implementation}{%
-      \section{Azure - Object-Oriented Internet interoperability Implementation}\label{gateway-implementation}}
+\section{Azure - Object-Oriented Internet interoperability Implementation}\label{gateway-implementation}
+
+\todo{Add any information about available reusable deliverables related to this work.}
 
@@
 
-\hypertarget{conclusion}{%
-      \section{Conclusion}\label{conclusion}}
+\section{Conclusion}\label{conclusion}
 

### 2020-11-01 Latex/Manuscript.tex
Work out Markdown\30.AzureTechnologyFeatures.md #27

@@
 
-Deployment of the hybrid solution providing interoperability of the
-\textbf{machine-centric} Cyber-Physical Systems (CFS) designed atop of M2M
-reactive communication and emerging cloud computing as a
-\textbf{human-centric} front-end requires decisions addressing the
-selection of the services supporting web user interface capable to
-expose process data. In this context, the service is any
-autonomous (with own identity) software component or module that is
-interfacing with selected (CFS) for data collection,
-analysis, and also remote control. Microsoft Azure is a cloud-based
-product. It offers a vast variety of services. This virtual environment
-handles an unlimited number of users and devices organized using a
-solution concept. The solution aggregates users, devices, services, and
-required additional resources scoping on a selected scenario. The
-solution serves as a context that provides a scope to the identifiers
-(the names of devices, users, process data entities, etc) inside it.
-Solutions are used to organize deployment entities into logical groups
-and prevent identity collisions.
+Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical Systems (CFS) designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end requires decisions addressing the selection of the services supporting web user interface capable to expose process data.
+In this context, the service is any autonomous (with own identity) software component or module that is interfacing with selected (CFS) for data collection, analysis, and also remote control.
+Microsoft Azure is a cloud-based product.
+It offers a vast variety of services.
+This virtual environment handles an unlimited number of users and devices organized using a solution concept.
+The solution aggregates users, devices, services, and required additional resources scoping on a selected scenario.
+The solution serves as a context that provides a scope to the identifiers (the names of devices, users, process data entities, etc) inside it.
+Solutions are used to organize deployment entities into logical groups and prevent identity collisions.
 

### 2020-11-01 Latex/Manuscript.tex
Work out Markdown\40.OOITechnologyFeatures.md #28
- added text from the OOI-RI-MPostolManuscript.ICCS2020\OOI-RI-MPostolManuscript.tex

@@
 
+This section covers an analysis of how to use the proposed domain model (Sect.
+\ref*{sec.DomainModel}) to make strategic design decisions and distribute functionality to reusable loosely coupled parts using the dependency injection software engineering and adaptive programming using the approach proposed in~\cite{RefWorks:doc:5d9796cbe4b0f66c52dccf04}.
+
+\begin{wrapfigure}{R}{0.55\textwidth}
+  \includegraphics[width=0.53\textwidth]{UADataApplicationArchitecture.eps} 
+  \caption{Reactive interoperability implementation}\label{fig_rii}
+\end{wrapfigure}
+
+The \emph{Reactive Interoperability} concept has been implemented as an open-source library named \textit{SemanticData} in the project Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596} designed to be a~foundation for developing application programs that are taking part in the message-centric communication pattern.
+From the above discussion, we can learn that the main design decisions must concern standardization and flexibility.
+Standardization needs the selection of an international interoperability specification to make the library ready to be adopted by the multi-vendor environment.
+Flexibility requires an architecture that promotes the polymorphic independent implementation of essential functions.
+
+Piece by piece integration of a cyber-physical system using multi-vendor products requires that M2M communication employs international standards as the interoperability foundation.
+Following the presented conclusions, OPC Unified Architecture Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} is selected in this respect.
+By design, this standard should support the required publisher-subscriber communication pattern.
+Unfortunately, as it is pointed-out in Sect.~\ref*{sec.DomainModel}, it covers only partially the requirements of the applications concerned.
+It must be stressed that by design it provides only an abstract specification.
+Abstract means that the standard must not limit the implementation strategy.
+This relationship shall be recognized as the proof of concept to verify that the implementation of the proposed model is feasible to be compliant with the selected standard as envisioned and open to support all functionality required to establish the interoperability context.
+
+For many parts of the \emph{Reactive Application} domain model (Sect.
+\ref*{sec.DomainModel}) a polymorphic approach to implementation is required.
+To promote the polymorphic ready solution the following concepts have been adopted:
+
+\begin{itemize}
+  \item \textbf{separation of concerns} - to allow an independent development of the parts~\cite{RefWorks:doc:5d92609be4b02eb43d372bd1},
+  \item \textbf{dependency injection} - to allow late binding of separately implemented parts~\cite{RefWorks:doc:5d925b77e4b030b4e0596f5d}.
+\end{itemize}
+
+In Fig.~\ref*{fig_rii} the implementation architecture of the \emph{Reactive Application} is proposed.
+The common functionality has been implemented as the Software Development Kit (SDK) available as the NuGet package \cite{RefWorks:doc:5c66740ae4b081adf5804596}.
+To promote the polymorphic approach, it has the factory class \emph{DataManagementSetup} that is a placeholder to gather all injection points used to compose external parts.
+To be injected the parts must be compliant with appropriate contracts expressed as the following interfaces representing the following functionality:
+
+\begin{itemize}
+  \item \emph{IBindingFactory} - bidirectional data exchange with the underlying process,
+  \item \emph{IConfigurationDataFactory} - the configuration data access,
+  \item \emph{IMessageHandlerFactory} - pushing the \emph{Message} entities to/pulling from \emph{Distribution Channel} (Fig.~\ref*{fig_DomainModel}),
+  \item \emph{IEncodingFactory} - searching a dictionary containing value converters.
+\end{itemize}
+
+It is expected that the functionality implementation represented by these interfaces is provided as external composable parts.
+
+\subsection{Process Data Access}\label{process-data-access}
+
+The \emph{DataRepository} represents data holding assets in the \emph{Reactive Application} and, following the proposed architecture, the \emph{IBindingFactory} interface is implemented by this external part.
+It captures functionality responsible for accessing the process data from \emph{LocalResources}.
+The \emph{LocalResources} represents an external part that has a very broad usage purpose.
+For example, it may be any kind of the process data source/destination, i.e.~\emph{Raw Data} or \emph{Address Space Management} (Fig.
+\ref*{fig_archit}).
+By design, the \emph{DataRepository} and associated entities, i.e.~\emph{Local Resources}, \emph{Consumer}, \emph{Producer} have been implemented as external parts, and consequently, the application scope may cover practically any concern that can be separated from the core \emph{Reactive Application} implementation.
+
+Depending on the expected network role the library supports the external implementation of:
+
+\begin{itemize}
+  \item \emph{Consumer} - entities processing data from incoming messages,
+  \item \emph{Producer} - entities gathering process data and populating outgoing messages.
+\end{itemize}
+
+The \emph{Consumer} and \emph{Producer} parts are derived from the \emph{DataRepository} (Fig.~\ref*{fig_rii}).
+The \emph{Consumer} uses the \emph{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from the \emph{Distribution Channel}.
+The received data may be processed or driven to any data destination.
+The \emph{Producer} mirrors the \emph{Consumer} functionality and, after reading data from an associated source, populates the \emph{Message} using the gathered data.
+
+\subsection{Configuration Management}\label{configuration-management}
+
+Based on the domain model analysis we can infer that the interoperability of communicating parties requires establishing a~semantic-context and security-context between them in advance.
+The \emph{Topic} based semantic-context is a foundation to ensure a common understanding of the process data encoded into the \emph{Message} instances.
+On the other hand, the security-context assures mutually shared security artifacts (i.e.~cipher algorithms, keys, etc.) used to protect the \emph{Message} as one whole.
+Both are necessary for handling messages.
+It is assumed that the security-context is established on top of the semantic-context.
+In that approach, the data is recognized as a principal of the security measures and the topic is regarded as a name of a collection containing the \emph{Message} instances that are to be protected using the associated security-context independently of the endpoints that produce or consume them.
+
+Therefore, a prerequisite for establishing interoperability of the communicating parties is an underlying semantic-context that must be created at the preparation step.
+In the proposed implementation, realization of this step is based on the configuration using the implementation of the \emph{IConfigurationDataFactory} interface.
+
+Decoupling of this functionality implementation from the functionality activation using an abstract contract and late binding mechanism allows:
+
+\begin{itemize}
+  \item implementation of practically any configuration management scenario,
+  \item modification of this functionality later after releasing the library or deploying the application program in the production environment.
+\end{itemize}
+
+The preparation phase concerns all the parts composed to make a running instance of the application program using the dependency injection approach to allow separate development and late binding.
+This approach makes any modification straightforward at any development and maintenance stage.
+From the end-user point of view, the composition process of the running program using independently developed parts is invisible.
+Because in any case a single program instance is created in a typical approach, we shall expect a commonly shared configuration mechanism providing mutually exclusive parameters to separately developed parts.
+This scenario has been addressed by the proposed implementation thanks to making the configuration expandable.
+
+\subsection{Distribution Channel Access}\label{distribution-channel-access}
+
+Messages preparation and the pull/push operations, which are essential to get access to \emph{Distribution Channel} require an implementation of the interfaces \emph{IEncodingFactory} and \emph{IMessageHandlerFactory}.
+
+The \emph{IEncodingFactory} is used by the SDK to encode and decode the \emph{Message} entities.
+To make the parties associated with the same \emph{Distribution Channel} interoperable they all must use the same \emph{Message} syntax.
+Implementation of the \emph{IEncodingFactory} should address one of the options defined in the specification: JSON or binary.
+
+The \emph{IMessageHandlerFactory} creates object supporting operations: pull incoming messages from and push outgoing messages to adjacent \emph{Intermediary} embedded in an abstract \emph{Distribution Channel} (Fig.~\ref*{fig_DomainModel}).
+To fulfill this task it has to use a concrete protocol stack.
+The OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0}~specification lists the following protocol stacks:
+
+\begin{itemize}
+  \item \emph{UDP} - UDP protocol~\cite{RefWorks:doc:5d8e1874e4b0bc72a68f0d11} that is used to transport UADP NetworkMessages,
+  \item \emph{Ethernet} - Ethernet-based protocol that is used to transport UADP NetworkMessages,
+  \item \emph{AMQP} - Advanced Message Queuing Protocol (AMQP) \cite{RefWorks:doc:5d91d2d9e4b0bc72a68ffe06} that is used to transport JSON and UADP NetworkMessage,
+  \item \emph{MQTT} - Message Queue Telemetry Transport (MQTT) \cite{RefWorks:doc:5d91e158e4b02eb43d36bb97} that is used to transport JSON and UADP NetworkMessage.
+\end{itemize}
+
+The library \cite{RefWorks:doc:5c66740ae4b081adf5804596} contains a reference implementation of the \emph{IMessageHandlerFactory} for the \emph{UDP} protocol.
+Because the UDP protocol is used as the \emph{Distribution Channel}, the external filtering of massages is possible only based on the IP address.
+In this case, the destination port and multicast IP address combination may be recognized as the \emph{Topic} (Sect.
+\ref*{sec.DomainModel}).
+Unfortunately, the PubSub specification doesn't provide any mapping outline addressing the question of how to express \emph{Topic} for a particular underlying communication stack.
+Additionally, it seems difficult or even impossible to create any directory services based on the IP addressing mechanism because it is used for nodes identification and localization on the global network, but not to express data semantics (data meaning).
+To overcome this limitation it is proposed to use globally unique identifiers of types defined in compliance with OPC UA Information Model~\cite{RefWorks:doc:5ac86c99e4b009947bbb87c9, RefWorks:doc:5ac86c98e4b009947bbb874c} as the \emph{Topic} entities to establish semantic-context and security- context of the reactive assets interoperability.
+In this approach, the filtering and multiplexing functionality must be embedded locally in the implementation of the UDP communication stack.
+
+It is worth stressing that the proposed separation of concerns and dependency injection approach make the architecture ready to utilize \emph{ANY Protocol} that supports transparent data transfer over the wire (Fig.
+\ref*{fig_rii}).
+
 \begin{itemize}

### 2020-11-05 Latex/Manuscript.tex
Work out Markdown\40.OOITechnologyFeatures.md #28
- work in progress- ready to be merged

--- 2020-11-01 Latex/Manuscript.tex
@@
 The domain model for this archetype is presented in the Fig.~\ref*{StrategyDomainModel}.
-Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \texttt{Networking} service of the \texttt{Cyber-physical\ node}.
-Main functionality of this component is to transfer selected data between \texttt{Cyber-physical\ network} using \texttt{Networking} services of an existing \texttt{Cyber-physical\ node} and \texttt{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
+Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \textit{Networking} service of the \textit{Cyber-physical\ node}.
+Main functionality of this component is to transfer selected data between \textit{Cyber-physical\ network} using \textit{Networking} services of an existing \textit{Cyber-physical\ node} and \textit{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
 
-The \textbf{embedded gateway} archetype relaxes most of the issues described above: \texttt{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security-context differences to name only a few.
+The \textbf{embedded gateway} archetype relaxes most of the issues described above: \textit{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security-context differences to name only a few.
 The main goal of this article is to provide proof that the \textbf{embedded gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogenous environments in concern.
@@
 Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub spec \cite{RefWorks:doc:5d98837de4b055984c0eecf0}.
-According to proposed architecture (Fig.~\ref*{StrategyDomainModel}) to implement the \texttt{Embedded\ Gateway} as a composable part of the \texttt{Cyber-physical\ Node} a library implementing \texttt{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
-Additionally it must be assumed that the library used to deploy \texttt{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/pubsub gateway functionality.
+According to proposed architecture (Fig.~\ref*{StrategyDomainModel}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ Node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
+Additionally it must be assumed that the library used to deploy \textit{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/pubsub gateway functionality.
 The composition process must be available without modification of the core code of an existing library.
-As a result the prototyping is to be limited to implementation of the \texttt{Embedded\ Gateway} software part only.
+As a result the prototyping is to be limited to implementation of the \textit{Embedded\ Gateway} software part only.
 
@@
 
-Sect.~\ref*{ooi-main-technology-features} provides a more detailed description of this library and an external part deployment process that is to be used to implement new functionality supporting \texttt{Embedded\ Gateway}.
+Sect.~\ref*{ooi-main-technology-features} provides a more detailed description of this library and an external part deployment process that is to be used to implement new functionality supporting \textit{Embedded\ Gateway}.
 
@@
 
-The \texttt{IoT\ Central} service provides a process data visualization
+The \textit{IoT\ Central} service provides a process data visualization
 user interface. To make this interface meaningful metadata called device
@@
 process requires data conversion from source to destination encoding.
-The \texttt{IoT\ Hub} is a service hosted in the cloud that supports
-\texttt{IoT\ Central} providing a robust messaging solution - it acts as
+The \textit{IoT\ Hub} is a service hosted in the cloud that supports
+\textit{IoT\ Central} providing a robust messaging solution - it acts as
 a central message hub for bi-directional communication. This
@@
 In the gateway scenario, they can be mapped on each other or entirely independent.
-The \texttt{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper service for \texttt{IoT\ Hub} that enables devices' connection process management, upon device providing valid identity attestation it assigns the device to an appropriate \texttt{IoT\ Hub} instance and returns to the device connection parameters, which allow direct connection with given \texttt{IoT\ Hub} service.
-The device proceeds to use the same attestation in \texttt{IoT\ Hub} connection and based on it, is granted authorization to selected operations including but not limited to data transfer and updating the user interface.
+The \textit{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper service for \textit{IoT\ Hub} that enables devices' connection process management, upon device providing valid identity attestation it assigns the device to an appropriate \textit{IoT\ Hub} instance and returns to the device connection parameters, which allow direct connection with given \textit{IoT\ Hub} service.
+The device proceeds to use the same attestation in \textit{IoT\ Hub} connection and based on it, is granted authorization to selected operations including but not limited to data transfer and updating the user interface.
 
@@
 above selection of services must be recognized as an example only. The
-\texttt{IoT\ Central} can be also seamlessly integrated with other
+\textit{IoT\ Central} can be also seamlessly integrated with other
 services as needed. The following services could also be considered to
@@
 \begin{itemize}
-      \item \texttt{Industrial\ IoT} - discovering OPC UA enabled servers in a factory network and register them in Azure \texttt{IoT\ Hub} implemented using \texttt{IoT\ Edge}
-      \item \texttt{Digital\ Twins} - managing the graph of digital twins, which are to represent some real-world process or entity
+      \item \textit{Industrial\ IoT} - discovering OPC UA enabled servers in a factory network and register them in Azure \textit{IoT\ Hub} implemented using \textit{IoT\ Edge}
+      \item \textit{Digital\ Twins} - managing the graph of digital twins, which are to represent some real-world process or entity
 \end{itemize}
 
-\texttt{Industrial\ IoT} promotes OPC UA client/server archetype used to
+\textit{Industrial\ IoT} promotes OPC UA client/server archetype used to
 achieve direct and interactive interoperability implemented using
-\texttt{IoT\ Edge} services that allow extracting initial data
+\textit{IoT\ Edge} services that allow extracting initial data
 processing to local premises based on the edge concept.
-\texttt{Digital\ Twins} is an emerging concept to use an observer to
+\textit{Digital\ Twins} is an emerging concept to use an observer to
 replicate selected process state and behavior. The possibility to add
@@
 
-In \texttt{IoT\ Central} a CFS is represented as a set
+In \textit{IoT\ Central} a CFS is represented as a set
 of devices. The characteristics and behavior of each device kind are
@@
 expressed as a JSON-LD can be imported into a Device Template.
-\texttt{IoT\ Central} allows also to create and edit a DCM using the
+\textit{IoT\ Central} allows also to create and edit a DCM using the
 dedicated web UI. A JSON file containing DCM can be derived from an
@@
 
-From the cloud side, it is proposed to employ the \texttt{IoT\ Hub}
+From the cloud side, it is proposed to employ the \textit{IoT\ Hub}
 service to handle the network traffic targeting the cyber-physical
@@
 stacks. In any case, process data (telemetry) is transparently
-transferred back-and-forth to the upper layer \texttt{IoT\ Central}
+transferred back-and-forth to the upper layer \textit{IoT\ Central}
 service. Hence, the payload formatting is determined by the DCM
-associated with the \texttt{IoT\ Central} solution. All the mentioned
+associated with the \textit{IoT\ Central} solution. All the mentioned
 protocols are standard ones. Consequently, it is possible to apply any
@@
 features, including performance. The connectivity with
-\texttt{IoT\ Hub}, for example, can be obtained using:
+\textit{IoT\ Hub}, for example, can be obtained using:
 
 \begin{itemize}
-      \tightlist
-      \item
-            \texttt{Microsoft.Azure.Devices} - Service SDK for Azure IoT Devices
-      \item
-            \texttt{Microsoft.Azure.Devices.Client}- Device SDK for Azure \texttt{IoT\ Hub}
-      \item
-            \texttt{Microsoft.Azure.Devices.Shared} - Common code for Azure IoT
+      \item \textit{Microsoft.Azure.Devices} - Service SDK for Azure IoT Devices
+      \item \textit{Microsoft.Azure.Devices.Client}- Device SDK for Azure \textit{IoT\ Hub}
+      \item \textit{Microsoft.Azure.Devices.Shared} - Common code for Azure IoT
             Device and Service SDKs
-      \item
-            \texttt{Microsoft.Azure.Devices.Provisioning.Client} - Provisioning
+      \item \textit{Microsoft.Azure.Devices.Provisioning.Client} - Provisioning
             Device Client SDK for Azure IoT Devices
-      \item
-            \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Amqp} -
-            Provisioning Device Client AMQP Transport for Azure IoT Devices
-      \item
-            \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Http} -
-            Provisioning Device Client Http Transport for Azure IoT Devices
-      \item
-            \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Mqtt} -
-            Provisioning Device Client MQTT Transport for Azure IoT Devices
+      \item \textit{Microsoft.Azure.Devices.Provisioning.Transport.Amqp} - Provisioning Device Client AMQP Transport for Azure IoT Devices
+      \item \textit{Microsoft.Azure.Devices.Provisioning.Transport.Http} - Provisioning Device Client Http Transport for Azure IoT Devices
+      \item \textit{Microsoft.Azure.Devices.Provisioning.Transport.Mqtt} - Provisioning Device Client MQTT Transport for Azure IoT Devices
 \end{itemize}
@@
 
+The \emph{Reactive Interoperability} (Sect.
+\ref*{introduction}) concept has been implemented as an open-source library named \textit{UAOOI.Networking.SemanticData} (SDK) under an umbrella of the project Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.
+The library is designed to be a foundation for developing application programs that are taking part in a message-centric communication pattern and interconnected using the reactive networking concept.
+The diagram in Fig.~\ref*{UADataApplicationArchitecture} shows the relationship between the library \textit{SDK} and external parts composing any reactive networking application (\textit{Reactive\ Application}).
+The \textit{Reactive Application} is an aggregation of \textit{Producer} and \textit{Consumer} parts.
+They must support access to real-time process data, hence they are recognized as an extension of \textit{DataRepository} class.
+To implement the \textit{DataRepository} dedicated implementation of the \textit{IBinding} interface should be provided to create a bridge between CFS and an external row data represented by the \textit{LocalResources} class.
+A more in-depth description of the \textit{OOI Reactive Application} library enabling data exchange over a network using the reactive networking pattern is in \cite{mpostol2020}.
+
+\begin{figure}     
+      \centering 
+      \includegraphics[width=5cm]{../.Media/UADataApplicationArchitecture.png} 
+      \caption{Reactive interoperability implementation}\label{UADataApplicationArchitecture}
+\end{figure}
+
+From the above discussion, we can learn that the main design decisions must concern standardization and flexibility.
+Standardization needs the selection of an international interoperability specification to make the library ready to be adopted by the multi-vendor environment.
+Flexibility requires an architecture that promotes the polymorphic independent implementation of essential functions.
+
+Piece by piece integration of a cyber-physical system using multi-vendor products requires that M2M communication employs international standards as the interoperability foundation.
+OPC Unified Architecture Part 14 PubSub has been selected in this respect (Sect.
+\ref*{architecture}).
+By design, this standard should support the required publisher-subscriber communication pattern.
+It must be stressed, that by design, the specification provides only an abstract interoperability definition.
+Abstract means that the standard must not limit the implementation strategy.
+
+Many parts in the domain model presented in Fig.~\ref*{UADataApplicationArchitecture} requires a polymorphic approach to implementation.
+To promote the polymorphic ready solution the following concepts have been adopted:
+
 \begin{itemize}
-      \tightlist
-      \item Machinie To Machine communication based on the semantic data
-      \item OOI PubSub Implementation Architecture
-      \item Simple, complex and structural data processing
+  \item \textbf{separation of concerns} - to allow an independent development of the parts~\cite{RefWorks:doc:5d92609be4b02eb43d372bd1},
+  \item \textbf{dependency injection} - to allow late binding of separately implemented parts~\cite{RefWorks:doc:5d925b77e4b030b4e0596f5d}.
+\end{itemize}
+
+To promote the polymorphic approach, the library has a factory class called \emph{DataManagementSetup} that is a placeholder to gather all injection points used to compose external parts.
+To be injected the parts must be compliant with an appropriate contract expressed as the following interfaces:
+
+\begin{itemize}
+  \item \emph{IBindingFactory} - bidirectional data exchange with the underlying process,
+  \item \emph{IConfigurationDataFactory} - the configuration data access,
+  \item \emph{IMessageHandlerFactory} - pushing the \emph{Message} entities to/pulling from \emph{Distribution Channel},
+  \item \emph{IEncodingFactory} - searching a dictionary containing value converters.
+\end{itemize}
+
+It is expected that the functionality implementation expressed by these interfaces is provided as independent external composable parts.
+The composition is accomplished at run time, and the effective application functionality depends essentially on reusable loosely coupled parts composed using the dependency injection software engineering and adaptive programming concept \todo{cite{RefWorks:doc:5d9796cbe4b0f66c52dccf04}}.
+
+The \textit{DataRepository} represents data holding assets in the \textit{Reactive Application} implementing the \textit{IBindingFactory} interface.
+It captures functionality responsible for accessing the external process data from \textit{LocalResources}.
+The \textit{LocalResources} represents an external part that has a very broad usage purpose.
+For example, it may be any kind of the process data source/destination, i.e.
+raw data (e.g.
+PLC internal registers), OPC UA Address Space Management, cloud, file, database, graphical user interface.
+
+Depending on the expected network role the library supports the implementation of:
+
+\begin{itemize}
+  \item \textit{Consumer} - entities processing data from incoming messages,
+  \item \textit{Producer} - entities gathering process data and populating outgoing messages.
+\end{itemize}
+
+The \textit{Consumer} and \textit{Producer} classes are derived from the \textit{DataRepository} (Fig.~\ref*{UADataApplicationArchitecture}).
+The \textit{Consumer} uses the \textit{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
+The received data may be processed or driven to any data destination, e.g.
+cloud-based front-end.
+The \textit{Producer} mirrors the \textit{Consumer} functionality and, after reading data from an associated source, populates the \emph{Message} using the gathered data.
+
+By design, the \textit{DataRepository} and associated entities, i.e.~\textit{Local Resources}, \textit{Consumer}, \textit{Producer} are embeded in external parts, and consequently, the application scope may cover practically any concern that can be separated from the core \textit{Reactive Application} implementation.
+
+The application startup phase concerns all the parts composed to make a running instance of the application program using the dependency injection approach to allow separate development and late binding.
+This approach makes any modification straightforward at any development and maintenance stage.
+From the end-user point of view, the composition process of the running program using independently developed parts is invisible.
+Because in any case a single program instance is created in a typical approach, we shall expect a commonly shared configuration mechanism providing mutually exclusive parameters to separately developed parts.
+This scenario has been addressed by the proposed implementation thanks to making the configuration expandable.
+
+From the discusion covered by the Sect.
+\ref*{architecture} we can infer that the interoperability of communicating parties requires establishing a semantic-context and security-context between them.
+If the received data is driven to any external data destination (e.g.
+cloud-based front-end) using out-of-band protocol the semantic-context and security contex must be also defined for this inetroperability relationship.
+There are a vaste varity of possibilities how to define these contexts.
+Anyway, the most common starting point is a configuration.
+The proposed approach to instantiate the application as a set odf composable parts is very usful in this respect because in makes possible to expand the core configuration functionality and adopt it to be helpful also in this case.
+Therefore, the semantic-context may be created based on the configuration using the implementation of the \textit{IConfigurationDataFactory} interface.
+
+Concluding, decoupling of this functionality implementation using an abstract contract and late binding mechanism allows:
+
+\begin{itemize}
+  \item implementation of practically any configuration management scenario,
+  \item modification of this functionality later after releasing the library or deploying the application program in the production environment.
 \end{itemize}
@@
 
+\todo{prepare section: \textit{Object-Oriented Internet interoperability Implementation}}
 \todo{Add any information about available reusable deliverables related to this work.}
@@
 
-The OPC UA PubSub to Azure gateway (\texttt{AzureGateway})
+The OPC UA PubSub to Azure gateway (\textit{AzureGateway})
 implementation has been just published on GitHub as the open-source (MIT

### 2020-11-07 Latex/Manuscript.tex

@@
 \begin{abstract}
-
-      Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Sed luctus neque eu erat pulvinar rutrum.
-Sed id congue leo.
-Pellentesque ornare enim libero, convallis eleifend turpis rhoncus ac.
-Proin eget pellentesque dolor.
-Phasellus lacinia velit eget faucibus iaculis.
-Pellentesque consequat erat non urna scelerisque cursus.
-Donec urna nisi, pulvinar a nisl eu, lobortis sollicitudin nulla.
-Proin tempus risus vel lacinia vestibulum.
-Praesent eget nisi lorem.
-Nam rutrum lectus vulputate dolor venenatis eleifend.
-Sed dolor lacus, cursus non enim tincidunt, auctor hendrerit orci.
-Donec venenatis ultrices est, nec molestie lorem.
-Morbi eleifend mattis ex, eget mollis leo blandit ut.
-Nulla sed felis posuere, gravida dui sed, iaculis neque.
-Donec ante purus, rhoncus eu neque tristique, pretium elementum purus.
-
-      Sed euismod maximus consequat.
-Pellentesque nec leo ligula.
-Aenean id lorem ac nisi blandit ultrices sit amet nec velit.
-Vestibulum bibendum ipsum vulputate quam suscipit, eu tincidunt diam imperdiet.
-Nunc vel turpis ut tortor bibendum ullamcorper sed ut magna.
-Sed sit amet quam ut lacus pretium ullamcorper.
-Fusce feugiat ornare mollis.
-Vestibulum sagittis velit id augue tempus, in vestibulum velit bibendum.
-Curabitur ac aliquet mi.
-Aliquam erat volutpat.
-Cras quis dignissim est, ac gravida.
+      TBD
 \end{abstract}
@@
 
-Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} cyber-physical system (CFS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios:
+Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} cyber-physical system (CPS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios:
 
 \begin{itemize}
-      \item \textbf{direct interconnection} - cloud-based dedicated communication services allow to attache it to the CFS making up a consistent M2M communication network using an in-bound protocol stack
-      \item \textbf{gateway based interconnection} - typical build-in communication services allows to attache the cloud computing to the CFS using an out-of-bound protocol stack
+      \item \textbf{direct interconnection} - cloud-based dedicated communication services allow to attache it to the CPS making up a consistent M2M communication network using an in-bound protocol stack
+      \item \textbf{gateway based interconnection} - typical build-in communication services allows to attache the cloud computing to the CPS using an out-of-bound protocol stack
 \end{itemize}
 
-By design, the direct approach requires that the cloud has to be compliant with the interoperability standard the CFS is built upon - it becomes a consistent part of the CFS.
+By design, the direct approach requires that the cloud has to be compliant with the interoperability standard the CPS is built upon - it becomes a consistent part of the CPS.
 Data models, roles, and responsibility differences of both solutions make this approach impractical or even imposable to be applied in typical cases.
@@
 
-This article addresses further research on the integration of the CFSs in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Internet of Things (IoT).
-The new architecture is proposed for integration of the multi-vendor \textbf{machine-centric} CFS designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end.
+This article addresses further research on the integration of the CPS in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Internet of Things (IoT).
+The new architecture is proposed for integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end.
 To support the multi-vendor environment OPC Unified Architecture interoperability standard has been selected.
@@
 It promotes a reactive interoperability pattern and a generic approach to establishing interoperability-context.
-A reference implementation of this archetype is described in Sect.~\ref*{gateway-implementation}.
+A reference implementation of this archetype is described in Sect.~\ref*{sect.gateway-implementation}.
 The most important findings and future work are summarized in Sect.~\ref*{conclusion}.
@@
 \begin{itemize}
-      \item \textbf{direct interconnection} (tightly coupled scenario) - cloud-based dedicated communication services are engaged to attach it to the CFS making up a consistent M2M communication network using a common protocol stack
-      \item \textbf{gateway based interconnection} (loosely coupled scenario) - native build-in communication services allows attaching the cloud to the CFS using an out-of-bound protocol stack
+      \item \textbf{direct interconnection} (tightly coupled scenario) - cloud-based dedicated communication services are engaged to attach it to the CPS making up a consistent M2M communication network using a common protocol stack
+      \item \textbf{gateway based interconnection} (loosely coupled scenario) - native build-in communication services allows attaching the cloud to the CPS using an out-of-bound protocol stack
 \end{itemize}
@@
 To support interoperability common data understanding is required.
-By design, the direct approach requires that the cloud has to be compliant with the interoperability standard the CFS uses.
-As a result, it becomes a consistent communication node of the CFS.
-Additionally, to meet this requirement the cloud and CFSs have to establish directly the same
+By design, the direct approach requires that the cloud has to be compliant with the interoperability standard the CPS uses.
+As a result, it becomes a consistent communication node of the CPS.
+Additionally, to meet this requirement the cloud and CPS have to establish directly the same
 
@@
 
-In practice, the set of assets embedded in the CFS is very stable.
+In practice, the set of assets embedded in the CPS is very stable.
 On the another hand, the virtualization of services means that they must be very flexible to handle the attachment of new assets proactively (acting in advance) at run time.
@@
 
-To meet the requirements of real-time distributed control the CFS may use protocols applicable only to local computer networks (e.g.~multicast IP, Ethernet, TSN, etc.).
+To meet the requirements of real-time distributed control the CPS may use protocols applicable only to local computer networks (e.g.~multicast IP, Ethernet, TSN, etc.).
 Because the cloud services support only protocols handling interconnection over the Internet the interaction with the cloud requires remote agents, i.e.~agents attached locally to the M2M network and implemented by applying one of the following archetypes:
@@
 \begin{itemize}
-      \item \textbf{edge device} - remote cloud agent acting as an intermediaryfor nodes of the cyber-physical network
+      \item \textbf{edge device} - remote cloud agent acting as an intermediary for nodes of the cyber-physical network
       \item \textbf{field level gateway} - a dedicated custom agent acting as an intermediary for nodes of the cyber-physical network
@@
 For this study, prototyping addresses Microsoft Azure cloud products.
-There are many reasons for selecting Azure to accomplish cloud-based front-end of Cyber-Physical System (CFS).
+There are many reasons for selecting Azure to accomplish cloud-based front-end of Cyber-Physical System (CPS).
 Azure offers Infrastructure as a Service (IaaS) and Platform as a Service (PaaS) capabilities.
-As a result, the platform can be used not only as a cloud-based front-end for CFS.
+As a result, the platform can be used not only as a cloud-based front-end for CPS.
 By design, the Azure services are compliant with Security Development Lifecycle (SDL) an industry-leading security process.
@@
 Solutions hosted on Azure are scaled up to millions of users without any additional coding.
-For the development of the CFS front-end, it is essential that Azure provides very efficient storage services usefully for real-time process data archival.
-Azure provides a vast variety of hybrid connections including but not limited to virtual private networks (VPNs), caches, content delivery networks (CDNs), ExpressRoute, and IoT dedicated services that can be directly used to implement cloud-based front-end for CFS.
+For the development of the CPS front-end, it is essential that Azure provides very efficient storage services usefully for real-time process data archival.
+Azure provides a vast variety of hybrid connections including but not limited to virtual private networks (VPNs), caches, content delivery networks (CDNs), ExpressRoute, and IoT dedicated services that can be directly used to implement cloud-based front-end for CPS.
 Because it is also integrated with other Microsoft tools like Office 365, Outlook, and SharePoint using Azure allows preserving investment and exporting process data to the mentioned tools.
@@
 A library that meets all these requirements has been implemented consistently with the Object-Oriented Internet paradigm \cite{RefWorks:doc:5c66740ae4b081adf5804596} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }.
-The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the Object-Oriented Internet concept compliant withthe OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} international standard.
-According to the presented implementation andevaluation, using the dependency injection and late binding, theapplication program can be seamlessly adapted to the production environment and scales well.
+The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the Object-Oriented Internet concept compliant with the OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} international standard.
+According to the presented implementation and evaluation, using the dependency injection and late binding, the application program can be seamlessly adapted to the production environment and scales well.
 This approach also improves flexibility and adaptability of the existing solutions against any modification of the production environment including but not limited to the selected interoperability standard change.
@@
 The discussion covered by this section is the foundation for selecting services utilized to expose process data and suitable protocol stack to support interconnection.
-In Sect.~\ref*{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a foundation for further decisions addressing the systematic design of the interoperability of the CFSs and cloud-based front-end.
+In Sect.~\ref*{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a foundation for further decisions addressing the systematic design of the interoperability of the CPS and cloud-based front-end.
 
@@
 
-Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical Systems (CFS) designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end requires decisions addressing the selection of the services supporting web user interface capable to expose process data.
-In this context, the service is any autonomous (with own identity) software component or module that is interfacing with selected (CFS) for data collection, analysis, and also remote control.
+Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical Systems (CPS) designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end requires decisions addressing the selection of the services supporting web user interface capable to expose process data.
+In this context, the service is any autonomous (with own identity) software component or module that is interfacing with selected (CPS) for data collection, analysis, and also remote control.
 Microsoft Azure is a cloud-based product.
@@
 middleware must be considered as a coupler. It must be interconnected
-with the (CFS) using an in-band protocol adhering to
+with the (CPS) using an in-band protocol adhering to
 communications requirements (i.e.~protocol profile, data encoding, time
@@
 Before process data can be exposed using a web user interface the data source must be associated with an appropriate solution and validated to make sure that the security rules are not violated.
-It is hard to assume that the security rules governing the CFS may also apply to the cloud-based services.
+It is hard to assume that the security rules governing the CPS may also apply to the cloud-based services.
 In the gateway scenario, they can be mapped on each other or entirely independent.
@@
 \begin{itemize}
-      \tightlist
-      \item
-            Development against a type definition of the user interface
-      \item
-            Implementation of the functionality of the bitstreams conversion in
-            advance
+      \item Development against a type definition of the user interface
+      \item Implementation of the functionality of the bitstreams conversion in advance
 \end{itemize}
 
-Having defined types in advance, a gateway may provide dedicated conversions functionality, i.e.~replacing bitstreams used by the CFS by equivalent ones for the cloud-based services.
-The Azure offers a vast variety of built-in types ready to be used in common cases, but not necessarily there are equivalent counterparts in use by the CFS.
+Having defined types in advance, a gateway may provide dedicated conversions functionality, i.e.~replacing bitstreams used by the CPS by equivalent ones for the cloud-based services.
+The Azure offers a vast variety of built-in types ready to be used in common cases, but not necessarily there are equivalent counterparts in use by the CPS.
 Additionally, the data conversion must address the following issues:
@@
 \begin{itemize}
-      \tightlist
-      \item
-            usually to covert data from source to destination representation, the
-            middleware software native types must be used
-      \item
-            if the out of the box set of types is not capable of fulfilling more
-            demanding needs, custom data types must be defined
+      \item usually to covert data from source to destination representation, the middleware software native types must be used
+      \item if the out of the box set of types is not capable of fulfilling more demanding needs, custom data types must be defined
 \end{itemize}
@@
 
-In \textit{IoT\ Central} a CFS is represented as a set
+In \textit{IoT\ Central} a CPS is represented as a set
 of devices. The characteristics and behavior of each device kind are
@@
 also metadata describing the data (called telemetry) exchanged over the
-wire with the CFS called Device Capability Model
+wire with the CPS called Device Capability Model
 (DCM). Additionally, the DT contains properties, customization, and
@@
 applied to achieve interoperability of the devices interconnected as the
-CFS. DCM development against any external information
+CPS. DCM development against any external information
 model is a design-time task and should be supported by dedicated
@@
       \item \textit{Microsoft.Azure.Devices.Client}- Device SDK for Azure \textit{IoT\ Hub}
-      \item \textit{Microsoft.Azure.Devices.Shared} - Common code for Azure IoT
-            Device and Service SDKs
-      \item \textit{Microsoft.Azure.Devices.Provisioning.Client} - Provisioning
-            Device Client SDK for Azure IoT Devices
+      \item \textit{Microsoft.Azure.Devices.Shared} - Common code for Azure IoT Device and Service SDK
+      \item \textit{Microsoft.Azure.Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
       \item \textit{Microsoft.Azure.Devices.Provisioning.Transport.Amqp} - Provisioning Device Client AMQP Transport for Azure IoT Devices
@@
 
-The \emph{Reactive Interoperability} (Sect.
-\ref*{introduction}) concept has been implemented as an open-source library named \textit{UAOOI.Networking.SemanticData} (SDK) under an umbrella of the project Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.
+To promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub (Sect.
+\ref*{architecture}) and support the \emph{Reactive Interoperability} (Sect.
+\ref*{introduction}) concept.
+A framework compliant with this requirements has been implemented as an open-source library named \textit{UAOOI.Networking.SemanticData} (SDK) under an umbrella of the project Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.
 The library is designed to be a foundation for developing application programs that are taking part in a message-centric communication pattern and interconnected using the reactive networking concept.
@@
 They must support access to real-time process data, hence they are recognized as an extension of \textit{DataRepository} class.
-To implement the \textit{DataRepository} dedicated implementation of the \textit{IBinding} interface should be provided to create a bridge between CFS and an external row data represented by the \textit{LocalResources} class.
+To implement the \textit{DataRepository} dedicated implementation of the \textit{IBinding} interface should be provided to create a bridge between CPS and an external row data represented by the \textit{LocalResources} class.
 A more in-depth description of the \textit{OOI Reactive Application} library enabling data exchange over a network using the reactive networking pattern is in \cite{mpostol2020}.
@@
 
-By design, the \textit{DataRepository} and associated entities, i.e.~\textit{Local Resources}, \textit{Consumer}, \textit{Producer} are embeded in external parts, and consequently, the application scope may cover practically any concern that can be separated from the core \textit{Reactive Application} implementation.
+By design, the \textit{DataRepository} and associated entities, i.e.~\textit{Local Resources}, \textit{Consumer}, \textit{Producer} are embedded in external parts, and consequently, the application scope may cover practically any concern that can be separated from the core \textit{Reactive Application} implementation.
 
@@
 
-From the discusion covered by the Sect.
+From the discussion covered by the Sect.
 \ref*{architecture} we can infer that the interoperability of communicating parties requires establishing a semantic-context and security-context between them.
 If the received data is driven to any external data destination (e.g.
-cloud-based front-end) using out-of-band protocol the semantic-context and security contex must be also defined for this inetroperability relationship.
-There are a vaste varity of possibilities how to define these contexts.
-Anyway, the most common starting point is a configuration.
-The proposed approach to instantiate the application as a set odf composable parts is very usful in this respect because in makes possible to expand the core configuration functionality and adopt it to be helpful also in this case.
+cloud-based front-end) using out-of-band protocol semantic-context and security context must be defined for this interoperability relationship.
+There are a vast variety of possibilities for how to define these contexts.
+Anyway, the most common starting point is the configuration.
+The proposed approach to instantiate the application as a set of composable parts is very useful in this respect because it makes it possible to expand the core configuration functionality and adapt it to be helpful also in this case.
 Therefore, the semantic-context may be created based on the configuration using the implementation of the \textit{IConfigurationDataFactory} interface.
@@
 
-\section{Azure - Object-Oriented Internet interoperability Implementation}\label{gateway-implementation}
+\section{Azure - Object-Oriented Internet interoperability Implementation}\label{sect.gateway-implementation}
 

### 2020-11-07 Latex/Manuscript.tex
Work out Markdown\60.GatewayImplementation.md #35
- created Markdown/60.GatewayImplementation.md

@@
 
-\keywords{Azure, Cloud Computing, Object-Oriented Internet, Industrial communication, Industry 4.0, Internet of Things, Machine to Machine Communication, OPC Unified Architecture}
+\keywords{ Azure, Cloud Computing, Object-Oriented Internet, Industrial communication, Industry 4.0, Internet of Things, Machine to Machine Communication, OPC Unified Architecture,
+           Reactive Networking (RxNetworking)  }
 

### 2020-11-07 Latex/60.GatewayImplementation.tex
Work out Markdown\60.GatewayImplementation.md #35
- integrate with other sections

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{azure-gateway-datarepository-implementation}{%
\section{Azure Gateway DataRepository Implementation}\label{azure-gateway-datarepository-implementation}}

\hypertarget{preface}{%
\subsection{Preface}\label{preface}}

This section describes an example implementation of an OPC UA PubSub to Azure gateway. This gateway is implemented as a composable part of the Reactive Networking Application (\texttt{RxNetworking\ App}). The \texttt{RxNetworking\ App} is an aggregation of \texttt{Producer} and \texttt{Consumer} entities derived from \texttt{DataRepository}. They must provide interconnection to real-time process data, hence they are recognized as an extension of the \texttt{DataRepository} class. \texttt{AzureGateway} part fulfills the \texttt{Consumer} role and uses out-of-band communication to push process data to the cloud.

\hypertarget{architecture}{%
\subsection{Architecture}\label{architecture}}

Domain model presenting relationship between the: Azure, PubSub Gateway, Device, Design and development tools

The \texttt{AzureGateway} functional package has been implemented based on the \texttt{Consumer} concept. This particular \texttt{Consumer} implements \texttt{IBindingFactory} interface to gather the data recovered from the \texttt{Message} instances pulled from the \texttt{Distribution\ Channel}. The received data is driven to the Azure services using configured out-of-band' protocol. An instance of the \texttt{IBindingFactory} is responsible to create objects implementing \texttt{IBinding} that can be used by the \texttt{Consumer} to forward the data retrieved from \texttt{NetworkMessag} received over the wire to Azure services.

The proposed implementation of the Azure gateway proves that the \texttt{DataRepository} and associated entities, i.e.~\texttt{Local\ Resources}, \texttt{Consumer}, \texttt{Producer} can be implemented as external parts, and consequently, the application scope may cover practically any concern that can be separated from the core PubSub communication engine implementation.

The article provides an introductory understanding of the steps required to implement the \texttt{Consumer} role of \texttt{OOI\ Reactive\ Application}. The \texttt{ReferenceApplication} is an example application of \texttt{Semantic-Data} reactive networking based on {[}OPC UA PubSub{]}{[}OPC.UA.PubSub{]} specification. The document {[}OPC UA PubSub Main Technology Features{]}{[}PubSubMTF{]} covers a description of selected fetuses relevant to this specification.

It is proof of the concept that out-of-band communication for OPC UA PubSub can be implemented based on the \texttt{DataRepository} concept.

Here are steps undertook to implement the \texttt{Consumer} role in the application:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \texttt{DataManagementSetup}: this class has been overridden by the \texttt{PartDataManagementSetup} class and it initializes the communication and binds data fields recovered form messages to local resources.
\item
  \texttt{IEncodingFactory} and \texttt{IMessageHandlerFactory}: have been implemented in independent libraries and \texttt{Consumer} doesn't depend on this implementation - current implementation of the interfaces is localized as services using an instance of the \texttt{IServiceLocator} interface.
\item
  \texttt{IBindingFactory}: has been implemented in the class \texttt{PartBindingFactory} that is responsible to gather the data recovered from the \texttt{Message} instances pulled from the \texttt{Distribution\ Channel}. The received data is driven to the Azure services using configured out-of-band protocol.
\item
  \texttt{IConfigurationFactory}: the class \texttt{PartConfigurationFactory} implements this interface to be used for the configuration file opening.
\end{enumerate}

\hypertarget{datamanagementsetup-implementation}{%
\subsubsection{\texorpdfstring{\texttt{DataManagementSetup} implementation}{DataManagementSetup implementation}}\label{datamanagementsetup-implementation}}

The \texttt{PartDataManagementSetup} constructor initializes all properties, which are injection points of all parts composing this role.

In this example, it is assumed that \href{https://www.nuget.org/packages/CommonServiceLocator}{\texttt{ServiceLocator}} is implemented to resolve references to any external services.

Finally the \texttt{DataManagementSetup.Start()} method is called to initialize the infrastructure, enable all associations and start pumping the data.

\hypertarget{ibindingfactory-implementation}{%
\subsubsection{\texorpdfstring{\texttt{IBindingFactory} implementation}{IBindingFactory implementation}}\label{ibindingfactory-implementation}}

Implementation of this interface is a basic step to implement \texttt{Consumer} functionality. The \texttt{DataRepository} represents data holding assets in the \texttt{RxNetworking\ App} and, following the proposed architecture, the \texttt{IBindingFactory} interface is implemented by this external part. It captures functionality responsible for accessing the process data represented by the \texttt{LocalResources}. The \texttt{LocalResources} represents the external part that has a very broad usage purpose. For example, it may be any kind of process data source/destination, and to name a few \texttt{Raw\ Data}, \texttt{OPC\ UA\ Address\ Space\ Management}, and \texttt{Azure} services in this case.

\hypertarget{configuration}{%
\subsection{Configuration}\label{configuration}}

\hypertarget{iconfigurationfactory-implementation}{%
\subsubsection{\texorpdfstring{\texttt{IConfigurationFactory} implementation}{IConfigurationFactory implementation}}\label{iconfigurationfactory-implementation}}

Implementation of this interface is straightforward and based entirely on the library UAOOI.Configuration.Networking available as the NuGet package. In a typical scenario, this implementation should not be considered for further modification. The only open question is how to provide the name of the file containing the configuration of this role.

\hypertarget{protocol-selection}{%
\subsection{Protocol selection}\label{protocol-selection}}

From the description covered by the Sec. and the Sec. the Azure supports the HTTP, AMQP, MQTT, but the PubSub Ethernet, UDP, AMQP, MQTT. If the Ethernet or UDP has been selected to build interconnection based on PubSub direc interoperability with the PubSub is impossible because the Azure doesn't offer these protocol as native communication services.

\hypertarget{data-mapping}{%
\subsection{data mapping}\label{data-mapping}}

For both the schema is different Data Transfer Object encoding

The Azure uses JSON based Data Transfer Object encoding and schema defined based on the solution metadata. The pubsub uses json and binary Data Transfer Object encoding. If JSON is used possibility to establish semantic context depends on the Azure metadata definition. In case PubSub uses binary encoding establishing interconnection is impossible.

\hypertarget{security}{%
\subsection{Security}\label{security}}

Azure and PubSub uses different security mechanism so establishing directly security context is impossible at all

\hypertarget{deployment-phases}{%
\subsection{Deployment phases}\label{deployment-phases}}

\begin{itemize}
\tightlist
\item
  Design
\item
  Gateway and devices registration
\item
  Authentication
\item
  Device/Service association
\item
  Device/Application association
\item
  Establishing session

  \begin{itemize}
  \tightlist
  \item
    Device/Device Template (Device Capability Model) association - establishing a semantic-context
  \item
    Security management - establishing security-context
  \end{itemize}
\item
  Interconnection - exchange of data
\item
  Maintenance
\end{itemize}

\end{document}

### 2020-11-07 Latex/Manuscript.pandoc.tex
Work out Markdown\60.GatewayImplementation.md #35
- integrate with other sections

@@
 \urlstyle{same} % disable monospaced font for URLs
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\newenvironment{Shaded}{}{}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{#1}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{#1}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{#1}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
 
+\hypertarget{reactive-machine-to-machine-communication-state-of-the-art}{%
+\section{Reactive Machine to Machine communication state of the
+art}\label{reactive-machine-to-machine-communication-state-of-the-art}}
+
+\hypertarget{opc-ua-pubsub-main-technology-features}{%
+\subsection{OPC UA PubSub Main Technology
+Features}\label{opc-ua-pubsub-main-technology-features}}
+
 \hypertarget{ooi-main-technology-features}{%
-\section{OOI Main Technology
+\subsection{OOI Main Technology
 Features}\label{ooi-main-technology-features}}
 
-\begin{itemize}
-\tightlist
-\item
-  Machinie To Machine communication based on the semantic data
+To address multi-vendor environment a standard solution is required.
+=\textgreater{} PubSub. The specyfication is abstrack, so concrete
+oimplementation has been selected OOI.
+
+\begin{itemize}
+\tightlist
+\item
+  Protocol stack
+\item
+  DataTypes binary and JSON encoding
+\item
+  Data Transfer Object embedded in the NetworkMessage
+\end{itemize}
+
+\hypertarget{problem}{%
+\subsection{Problem}\label{problem}}
+
+As stated in Sec. 1 the interoperability of the \textbf{machine-centric}
+cyber-physical systems and \textbf{human-centric} cloud-based front-end
+can be implemented applying one of the following scenarios:
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{direct interconnection} - cloud-based dedicated communication
+  services allow to attach it to the cyber-physical system making up a
+  consistent M2M communication network using its protocol stack
+\item
+  \textbf{gateway based interconnection} - native build-in communication
+  services allows attaching the cloud to the cyber-physical system using
+  an out-of-bound protocol stack
+\end{itemize}
+
+By design, the direct approach requires that the cloud has to be
+compliant with the interoperability standard the cyber-physical system
+uses. As a result, it becomes a consistent part of the cyber-physical
+system.
+
+Data models, roles, and responsibility differences of both solutions
+make this approach imposable or impractical in typical cases.
+
+This article addresses further research on the integration of the
+cyber-physical systems in the context of new emerging disciplines,
+i.e.~Industry 4.0 (I4.0) and the Internet of Things (IoT). The new
+architecture is proposed for integration of the multi-vendor
+\textbf{machine-centric} cyber-physical system designed atop of M2M
+reactive communication and emerging cloud computing as a
+\textbf{human-centric} front-end. To support the multi-vendor
+environment OPC Unified Architecture interoperability standard has been
+selected. The proposals are backed by proof of concept reference
+implementations. Prototyping addresses Microsoft Azure Cloud as an
+example. The prototyping outcome has been just published on GitHub as
+the open-source (MIT licensed). The proposed solutions have been
+harmonized with the more general concept called the Object-Oriented
+Internet.
+
+how to interconnect two completely different environment:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  machine-centric reactive interoperability addressing real-time mobile
+  applications
+\item
+  human-centric interactive web based user graphical interface
+\end{enumerate}
+
+\hypertarget{architecture-scenarios}{%
+\subsection{Architecture scenarios}\label{architecture-scenarios}}
+
+\begin{itemize}
+\tightlist
+\item
+  tightly coupled - treat Azure as tightly coupled communication part of
+  the m2m
+\item
+  loosely coupled - use gateway as the intensional man in the middle
+\end{itemize}
+
+\hypertarget{requirements}{%
+\subsection{Requirements}\label{requirements}}
+
+\begin{itemize}
+\tightlist
+\item
+  standard base
+\item
+  reactive interoperability (sessionless)
+\item
+  gateway architecture
+
+  \begin{itemize}
+  \tightlist
+  \item
+    gateway is part of the M2M communication network (in-baud )
+  \item
+    out-of-band communication - asynchronous data exchange
+  \item
+    semantic-context integration (types mapping)
+  \item
+    security context independency
+  \item
+    separation of concerns - composable implementation
+  \end{itemize}
+\end{itemize}
+
+\hypertarget{library-selection-against-the-problem}{%
+\subsection{Library selection against the
+problem}\label{library-selection-against-the-problem}}
+
+It is real a The defined in sec.~problem is engineering challenge is how
+to interconnect two completely different environment:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  machine centric reactive interoperability addressing real-time mobile
+  applications
+\item
+  human centric interactive web based user graphical interface
+\end{enumerate}
+
+Why reactive interoperability
+
+\begin{itemize}
+\tightlist
+\item
+  data mobility
+\item
+  network trafik asymmetry
+\item
+  serverless implementation (self contained implementation)
+\end{itemize}
+
+\hypertarget{sessionless}{%
+\subsection{Sessionless}\label{sessionless}}
+
+\begin{itemize}
+\tightlist
+\item
+  Without a session; taking the form of a series of isolated requests.
+\item
+  System having virtual session manager used sessionless-oriented
+  protocol to communicate with user device via wireless channel and
+  session-oriented protocol to communicate with host server
+\end{itemize}
+
+\hypertarget{library-description-targeting-reactive-interoperability}{%
+\subsection{Library description targeting reactive
+interoperability}\label{library-description-targeting-reactive-interoperability}}
+
+In Fig. fig\_archit a generic architecture of the Machine to Machine
+(M2M) interoperability is presented. A detailed description of this
+model is covered by \cite{RefWorks:doc:5d6cdbbbe4b082ad50f3a83e}, but in
+this section, the most important features of this model have been
+abstracted to settle a foundation for further discussion related to
+systematic design, development, and deployment of the mobile
+applications compliant with the more general IoT concept. The main aim
+is the examination of how the model addresses challenges defined in
+Section \ref*{sec.intro}.
+
+\hypertarget{mobility}{%
+\subsection{Mobility}\label{mobility}}
+
+For any generic solution addressing the development and deployment of
+the cyber-physical system the data holder mobility behavior must be
+considered apart from the described above features. Mobile data means
+that it may come from mobile devices or be generated in unpredictable
+attachment points.
+
+If the data origin holding asset is a mobile device it means that we
+must deal with the dynamic Internet attachment point. A typical example
+of this scenario is portable monitoring or control of the underlying
+process, for example, a portable healthcare solution. Another scenario
+is ad hoc interconnected data holder assets, for example, cars entering
+a service area.
+
+In case the generation places of data are arbitrary it means that the
+data appearance must be recognized and processed as an event. A good
+example of this scenario is a product (e.g.\textasciitilde hygiene
+products, cosmetics, drugs, cars, cigarettes) global tracking system -
+an application domain where the Internet of Things (IoT) term has been
+coined
+\cite{RefWorks:doc:5d87d1c9e4b0bc72a68d7b46, RefWorks:doc:5d87d02be4b0e88bdacab9a7}.
+In this context, the IoT is all about:
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{mobile data fetching} - how to gather data from mobile things
+  (data holder assets)
+\item
+  \textbf{mobile data distribution} - how to transfer the data over the
+  Internet to all places where it could be processed
+\item
+  \textbf{mobile data processing} - how to integrate consistently the
+  partial data into a selected application as one whole to improve
+  selected process performance
+\end{itemize}
+
+One of the arguments for the Internet of Things is allowing distributed
+yet interlinked devices, machines, and objects (data holders) to
+interact with each other without relying on human interaction to set-up
+and commission the embedded intelligence.
+
+In case any kind of mobility has to be considered the next engineering
+challenge is dynamic discoverability on the network and the possibility
+of establishing semantic and security context of the parts composing the
+cyber-physical distributed application.
+
+\begin{itemize}
+\tightlist
+\item
+  Machine To Machine communication based on the semantic-data
 \item
@@
 
-Mobile data fetching is related to variety of last mile communication
-technologies, for example RFID, WI-FI, VHF, etc. Subscription could be
-supported using messaging systems, e.g.~AMQP. A good candidate to
-leverage consumption is OPC Unified Architecture.
-
 To deploy this scenario
@@
 \item
-  the payload of these messages is consumed by an OPC Server responsible
-  to expose it in the Address Space;
+  the payload of these messages is consumed by a ultimate destination
+  responsible to process it according to the solution scenario,
+  e.g.~displacing recovered data using web UI
 \item
   the application as an OPC UA client consumes the exposed data and
-  generates revenue for the end-user.The phrase ``Internet of Things''
-  started its life as the title of a presentation made in 1999 and aimed
-  at explaining a new idea of radio frequency identification (RFID) in
-  the context of the supply chain performance. It is clear that it
-  doesn't mean that someone has any right to control how others use the
-  phrase, but my point is that a precise term definition is important
-  for working together on: common rules, architecture, solutions,
-  requirements, capabilities, limitations, etc. In practice having a
-  common definition it is possible to check a selected technology,
-  solution or product capabilities against requirements of the
-  application entitled to use this term.
-\end{itemize}
+  generates revenue for the end-user.
+\end{itemize}
+
+The phrase ``Internet of Things'' started its life as the title of a
+presentation made in 1999 and aimed at explaining a new idea of radio
+frequency identification (RFID) in the context of the supply chain
+performance. It is clear that it doesn't mean that someone has any right
+to control how others use the phrase, but my point is that a precise
+term definition is important for working together on: common rules,
+architecture, solutions, requirements, capabilities, limitations, etc.
+In practice having a common definition it is possible to check a
+selected technology, solution or product capabilities against
+requirements of the application entitled to use this term.
 
@@
 
-Internet of Things is all about:
-
-\begin{itemize}
-\tightlist
-\item
-  mobile data fetching -- how to gather the data from mobile devices
-  (things);
-\item
-  mobile data subscription -- how to transfer the data over the Internet
-  to a place where it could be processed;
-\item
-  mobile data processing -- how to integrate the data into a selected
-  application to improve process behavioral performance.
-\end{itemize}
-
-Data fetching is related to a variety of last mile communication
-technologies, for example RFID, WI-FI, VHF, Bluetooth, etc. Subscription
-could be supported using messaging systems, e.g.~AMQP, MQTT, etc. A good
-candidate for leveraging data consumption is for example OPC Unified
-Architecture.
-
-\hypertarget{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity}{%
-\section{Azure to Sensors (A2S) connectivity deployment (field level
-connectivity)}\label{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity}}
+\hypertarget{from-ooi-ri-mpostolmanuscript.tex}{%
+\subsection{from
+OOI-RI-MPostolManuscript.tex}\label{from-ooi-ri-mpostolmanuscript.tex}}
+
+\hypertarget{reactive-interoperability-implementation}{%
+\subsubsection{Reactive Interoperability
+Implementation}\label{reactive-interoperability-implementation}}
+
+This section covers an analysis of how to use the proposed domain model
+\texttt{\textbackslash{}cite\{mpostol2020\}} to make strategic design
+decisions and distribute functionality to reusable loosely coupled parts
+using the dependency injection software engineering and adaptive
+programming using the approach proposed in
+\texttt{\textbackslash{}cite\{RefWorks:doc:5d9796cbe4b0f66c52dccf04\}}.
+
+The \textbf{Reactive Interoperability} concept has been implemented as
+an open-source library named \texttt{SemanticData} in the project
+Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}
+designed to be a foundation for developing application programs that are
+taking part in the message-centric communication pattern. From the above
+discussion, we can learn that the main design decisions must concern
+standardization and flexibility. Standardization needs the selection of
+an international interoperability specification to make the library
+ready to be adopted by the multi-vendor environment. Flexibility
+requires an architecture that promotes the polymorphic independent
+implementation of essential functions.
+
+Piece by piece integration of a cyber-physical system using multi-vendor
+products requires that M2M communication employs international standards
+as the interoperability foundation. Following the presented conclusions,
+OPC Unified Architecture Part 14 PubSub
+\cite{RefWorks:doc:5d98837de4b055984c0eecf0} is selected in this
+respect. By design, this standard supports the required
+publisher-subscriber communication pattern. It must be stressed that by
+design it provides only an abstract specification. Abstract means that
+the standard must not limit the implementation strategy. This
+relationship shall be recognized as the proof of concept to verify that
+the implementation of the proposed model is feasible to be compliant
+with the selected standard as envisioned and open to support all
+functionality required to establish the interoperability context.
+
+For many parts of the \textbf{Reactive Application} domain model (Sect.
+\ref*{sec.DomainModel}) a polymorphic approach to implementation is
+required. To promote the polymorphic ready solution the following
+concepts have been adopted:
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{separation\ of\ concerns} - to allow an independent
+  development of the parts \cite{RefWorks:doc:5d92609be4b02eb43d372bd1},
+\item
+  \texttt{dependency\ injection} - to allow late binding of separately
+  implemented parts \cite{RefWorks:doc:5d925b77e4b030b4e0596f5d}.
+\end{itemize}
+
+In Fig. the implementation architecture of the \textbf{Reactive
+Application} is proposed. The common functionality has been implemented
+as the Software Development Kit (SDK) available as the NuGet package
+\texttt{\textbackslash{}cite\{RefWorks:doc:5c66740ae4b081adf5804596\}}.
+To promote the polymorphic approach, it has the factory class
+\texttt{DataManagementSetup} that is a placeholder to gather all
+injection points used to compose external parts. To be injected the
+parts must be compliant with appropriate contracts expressed as the
+following interfaces representing the following functionality:
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{IBindingFactory} - bidirectional data exchange with the
+  underlying process,
+\item
+  \texttt{IConfigurationDataFactory} - the configuration data access,
+\item
+  \texttt{IMessageHandlerFactory} - pushing the \textbf{Message}
+  entities to/pulling from \emph{Distribution Channel} (Fig.
+  \ref*{fig_DomainModel}),
+\item
+  \texttt{IEncodingFactory} - searching a dictionary containing value
+  converters.
+\end{itemize}
+
+It is expected that the functionality implementation represented by
+these interfaces is provided as external composable parts.
+
+\hypertarget{process-data-access}{%
+\paragraph{Process Data Access}\label{process-data-access}}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{label\{process-data-access\}}
+\end{Highlighting}
+\end{Shaded}
+
+The \emph{DataRepository} represents data holding assets in the
+\emph{Reactive Application} and, following the proposed architecture,
+the \emph{IBindingFactory} interface is implemented by this external
+part. It captures functionality responsible for accessing the process
+data from \emph{LocalResources}. The \emph{LocalResources} represents an
+external part that has a very broad usage purpose. For example, it may
+be any kind of the process data source/destination, i.e.~\emph{Raw Data}
+or \emph{Address Space Management} (Fig. \ref*{fig_archit}). By design,
+the \emph{DataRepository} and associated entities,
+i.e.~\emph{Local Resources}, \emph{Consumer}, \emph{Producer} have been
+implemented as external parts, and consequently, the application scope
+may cover practically any concern that can be separated from the core
+\emph{Reactive Application} implementation.
+
+Depending on the expected network role the library supports the external
+implementation of:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{\textbackslash{}begin}\NormalTok{\{}\ExtensionTok{itemize}\NormalTok{\}}
+  \FunctionTok{\textbackslash{}item} \FunctionTok{\textbackslash{}emph}\NormalTok{\{Consumer\} - entities processing data from incoming messages,}
+  \FunctionTok{\textbackslash{}item} \FunctionTok{\textbackslash{}emph}\NormalTok{\{Producer\} - entities gathering process data and populating outgoing messages.}
+\KeywordTok{\textbackslash{}end}\NormalTok{\{}\ExtensionTok{itemize}\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+The \texttt{Consumer} and \texttt{Producer} parts are derived from the
+\texttt{DataRepository} Fig. The \texttt{Consumer} uses the
+\texttt{IBindingFactory} to gather the data recovered from the
+\textbf{Message} instances pulled from the \textbf{Distribution
+Channel}. The received data may be processed or driven to any data
+destination. The \texttt{Producer} mirrors the \texttt{Consumer}
+functionality and, after reading data from an associated source,
+populates the \texttt{Message} using the gathered data.
+
+\hypertarget{cloud-to-sensors-field-level-connectivity}{%
+\section{Cloud to Sensors Field Level
+Connectivity}\label{cloud-to-sensors-field-level-connectivity}}
+
+\hypertarget{architecture}{%
+\subsection{Architecture}\label{architecture}}
+
+\hypertarget{introduction-1}{%
+\subsubsection{Introduction}\label{introduction-1}}
+
+As it was explained in Sect 1, to follow the Industry 4.0 concept a
+hybrid environment integrating reactive Machine to Machine
+interconnection and interactive web-based user interface is required.
+The main challenge of the solution in concern is to design a generic but
+reusable architecture that addresses interoperability of these diverse
+interconnection scenarios ruled by different requirements, namely
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  \textbf{machine-centric} machine to machine real-time mobile
+  interoperability
+\item
+  \textbf{human-centric} cloud-based front-end
+\end{enumerate}
+
+Interconnection of the reactive \textbf{machine-centric} and interactive
+\textbf{human-centric} environments can be implemented by applying one
+of the following scenarios:
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{direct interconnection} - cloud-based dedicated communication
+  services are engaged to attach it to the cyber-physical system making
+  up a consistent M2M communication network using a common protocol
+  stack
+\item
+  \textbf{gateway based interconnection} - native build-in communication
+  services allows attaching the cloud to the cyber-physical system using
+  an out-of-bound protocol stack
+\end{itemize}
+
+In the solution in concern, the interconnection of assets is not enough
+hence their interoperability is expected. In this case, using the same
+communication stack must be recognized as only a necessary condition. To
+support interoperability common data understanding is required. By
+design, the direct approach requires that the cloud has to be compliant
+with the interoperability standard the cyber-physical system uses. As a
+result, it becomes a consistent part of the cyber-physical system.
+Additionally, to meet this requirement the cloud and cyber-physical
+systems have to establish
+
+\begin{itemize}
+\tightlist
+\item
+  directly the same semantic-context
+\item
+  directly the same security-context
+\end{itemize}
+
+The possibility to establish a common semantic-context in the
+multi-vendor environment makes communication standardization especially
+important. In this case, it is required that the encoding of the payload
+of messages exchanged over the network (Data Transfer Object - TDO) is
+standardized so that the payload can be factored on the data-gathering
+site and consumed on the ultimate destination data processing sites.
+Security between the data origin and ultimate data destination refers to
+the protection of messages (security-context) against malicious users.
+It is required that communicating parties are using the same
+cyber-security measures.
+
+\hypertarget{why-not-direct}{%
+\subsubsection{why not direct}\label{why-not-direct}}
+
+The decision to follow the \textbf{direct interconnection} scenario must
+be derived from an analysis of the capabilities of available services in
+concern. However, for the development strategy of this type of solutions
+this analysis can be done partially taking into account two features
+that can be considered invariable:
+
+\begin{itemize}
+\tightlist
+\item
+  by design the cloud-based services must be virtual - they are used to
+  handle many solutions at the same time
+\item
+  by design the M2M communication is usually constrained by the
+  real-time requirements
+\end{itemize}
+
+In practice, the set of assets embedded in the cyber-physical system is
+very stable. On the another hand, the virtualization of services means
+that they must be very flexible to handle the attachment of new assets
+proactively (acting in advance) at run time. As a result, by design, the
+cloud services must be repressible to register and authenticate devices
+exposing endpoints in the public network to allows the device to access
+a provisioning cloud service. It requires that a session over the
+Internet has to be established by the data holding asset at a
+preparation step.
+
+To meet the requirements of real-time distributed control the
+cyber-physical system may use protocols applicable only to local
+computer networks (e.g.~multicast IP, Ethernet, TSN, etc.). Because the
+cloud services support only protocols handling interconnection over the
+Internet the interaction with the cloud requires remote agents,
+i.e.~agents attached locally to the M2M network implemented applying one
+of the following archetypes:
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{edge device} - remote cloud agent acting as an intermediary
+  for nodes of the cyber-physical network
+\item
+  \textbf{field level gateway} - a dedicated custom device acting as an
+  intermediary for nodes of the cyber-physical network
+\item
+  \textbf{embedded gateway} - a software part composed into a selected
+  node of the cyber-physical network
+\end{itemize}
+
+\textbf{Edge device} is a device that connects directly to the cloud
+services but acts as an intermediary for other devices called leaf
+devices. Additionally, it allows the selection of initial data
+processing and execution of them using local resources. The \textbf{edge
+device} may be located close to the leaf devices and attached to the
+cyber-physical network using protocols applicable only to local computer
+networks. In this scenario, it is possible to use a custom protocol
+stack to get connected to the \textbf{edge device} with the cloud and
+helps to save the bandwidth thanks to sending only the results of local
+processing. In this approach, the \textbf{edge device} is part of cloud
+vendor products and cannot be recognized as a generic solution that can
+be used to connect to other clouds at the same time.
+
+The \textbf{field level gateway} is also build atop of the middleware
+concept. The only difference compared with the \textbf{edge device} is
+necessity to use officially supported by the cloud vendor services to
+get connected. In this scenario the process data may be transferred to
+many clouds at the same time provided that the gateway offers this
+functionality.
+
+\begin{figure}
+\centering
+\includegraphics{../.Media/StrategyDomainModel.png}
+\caption{Strategy Domain Model}
+\end{figure}
+
+Unlike the above described solutions, the \textbf{embedded gateway} is
+not derived from the middleware concept. The domain model for this
+archetype is presented in the Fig. Promoting separation of concern
+design principle, the gateway functionality should be implemented as a
+self-contained software part embedded in the \texttt{Networking} service
+of the \texttt{Cipher-physical\ node}. Main functionality of this
+component is to transfer selected data between
+\texttt{Cyber-physical\ network} using \texttt{Networking} services of
+an existing \texttt{Cyber-physical\ node} and
+\texttt{Cloud-based\ front-end} using officially supported by the cloud
+vendor interconnection services.
+
+The \textbf{embedded gateway} archetype relaxes most of the issues
+described above: cipher-physical network real-time behavior, data
+encoding incompatibility, security-context differences to name only a
+few. The main goal of this article is to provide proof that the
+\textbf{embedded gateway} archetype implementation is possible based on
+a generic architecture that can be used as a foundation for the
+integration of the heterogenous environments in concern. The proposed
+implementation is designed for selected interoperability standard and
+cloud product.
+
+\hypertarget{why-pubsub}{%
+\subsection{Why pubsub}\label{why-pubsub}}
+
+To comply with the Industry 4.0 communication criterion, even the lowest
+category requires that the product must be addressable over the network
+via TCP/UDP or IP and has to support the OPC UA Information Model. As a
+result, any product being advertised as Industry 4.0 enabled must be OPC
+UA-capable somehow. To support the multi-vendor environment OPC Unified
+Architecture interoperability standard has been selected. OPC UA
+supports the following two patterns to be used to transfer data between
+communicating parties:
+
+\begin{itemize}
+\tightlist
+\item
+  connection-oriented: requires a session that has to be established
+  before any data can be sent between sender and receiver
+\item
+  connectionless-oriented: the sender may start sending messages (called
+  packets or datagrams) to the destination without any preceding
+  handshake procedure
+\end{itemize}
+
+Using the connection-oriented communication pattern it is difficult or
+even impossible to gather and process mobile data (Sec. I), which is one
+of the Internet of Things paradigms. OPC UA Part 14 PubSub offers the
+connectionless approach as an additional option to session based
+client-server interoperability and is a consistent part of the OPC UA
+specifications suit. As the result it can be recognized as the IoT ready
+technology.
 
 \begin{quote}
-The title must be revised
+{[}29{]} Mariusz Postol, UA Part 14: PubSub Main Technology Features in
+Object Oriented Internet, https://github.com/mpostol/OPC-UA-OOI, 2019,
+DOI: 10.5281/zenodo.1198852
 \end{quote}
 
-\begin{itemize}
-\tightlist
-\item
-  \textbf{Architecture} - Domain model presenting relationship between
-  the: Azure, PubSub Gateway, Device, Design and development tools
-\item
-  \textbf{Connectivity} - Describe reactive nature of the Azure
-  monitoring process data (telemetry) services.
-\item
-  \textbf{Deployment phases}
+\hypertarget{why-azure}{%
+\subsection{Why Azure}\label{why-azure}}
+
+The presented proposals in the article are backed by proof of concept
+reference implementations. For this study, prototyping addresses
+Microsoft Azure cloud products. There are many reasons for selecting
+Azure to accomplish cloud-based front-end of CFS. Azure offers
+Infrastructure as a Service (IaaS) and Platform as a Service (PaaS)
+capabilities. As a result, the platform can be used not only as a
+cloud-based front-end for CFS. By design, the Azure services are
+compliant with Security Development Lifecycle (SDL) an industry-leading
+security process. It is also compliant with the new international
+standard for cloud privacy, namely ISO 27018. Solutions hosted on Azure
+are scaled up to millions of users without any additional coding. For
+the development of the CFS front-end, it is essential that Azure
+provides very efficient storage services usefully for real-time process
+data archival. Azure provides a vast variety of hybrid connections
+including but not limited to virtual private networks (VPNs), caches,
+content delivery networks (CDNs), ExpressRoute, and IoT dedicated
+services that can be directly used to implement cloud-based front-end
+for CFS. Because it is also integrated with other Microsoft tools like
+Office 365, Outlook, and SharePoint using Azure allows preserving
+investment and exporting process data to the mentioned tools. Azure also
+offers services supporting analytics and intelligence capabilities for
+further improving business processes and decision making. It is the only
+cloud platform that offers Blockchain as a Service (BaaS), Machine
+Learning, Bots, and Cognitive APIs capabilities.
+
+Azure aids Internet protocols and open standards such as JSON, XML,
+SOAP, REST, MQTT, AMQP, and HTTP. A software development kits for C\#,
+Java, PHP, and Ruby are available for custom applications. Azure
+provides services supporting data exchange over the OPC UA, but they
+don't support pubsub compliant with the OPC UA Part-14. Connectivity
+services on the network use JSON-based Data Transfer Object encoded
+based on schema derived from the solution metadata.
+
+More detailed description of the selected Azure features in context of
+the application in concern are covered by the Sec.
+\texttt{azure-main-technology-features}.
+
+\hypertarget{why-ooi}{%
+\subsection{Why OOI}\label{why-ooi}}
+
+Based on the sessionless and session-oriented communication patterns
+examination against the IoT requirements (cite mpostol 2020) it could be
+concluded that the connectionless pattern better suites issues related
+to the assets mobility and traffic asymmetry that is characteristic for
+the application domains in concern. Additionally, to promote
+interoperability and address the demands of the M2M communication in the
+context of a multi-vendor environment the prototyping should use an
+framework that must be compliant with the OPC UA Part 14 PubSub spec.
+According to proposed architecture presented in Fig. above to implement
+the \texttt{Embedded\ Gateway} as a composable part of the
+\texttt{Cipher-physical\ Node} a library implementing
+\texttt{Networking} functionality in compliance with mentioned above
+specification is a starting point for further development. Additionally
+it must be assumed that the library used to deploy
+\texttt{Embedded\ Gateway} support dependency injection and be capable
+to compose an external part supporting Azure/pubsub gateway
+functionality. The composition process must be available without
+modification of the core code of an existing library. As a result the
+prototyping is to be limited to implementation of the
+\texttt{Embedded\ Gateway} software part only.
+
+A library that meets all these requirements has been implemented
+consistently with the Object-Oriented Internet paradigm
+\texttt{\textbackslash{}footnote\{\textbackslash{}url\{https://github.com/mpostol/OPC-UA-OOI\}\}}
+\texttt{\textbackslash{}cite\{RefWorks:doc:5c66740ae4b081adf5804596\}}
+worked out in an open-source project. The
+\texttt{cite\ \{mpostol\ 2020\}} covers the description of a reference
+application program implementation proving that it is possible to design
+universal architecture targeting reactive interoperability as a
+consistent part of the Object-Oriented Internet concept compliant with
+the OPC UA PubSub
+\texttt{\textbackslash{}cite\{RefWorks:doc:5d98837de4b055984c0eecf0\}}
+international standard. According to the presented implementation and
+evaluation, using the dependency injection and late binding, the
+application program can be seamlessly adapted to the production
+environment and scales well. This approach also improves flexibility and
+adaptability of the existing solutions against any modification of the
+production environment including but not limited to the selected
+interoperability standard change.
+
+Sect. \texttt{OPC\ UA\ PubSub\ Main\ Technology\ Features} provides more
+detailed description of this library and new functionality
+(\texttt{Embedded\ Gateway} part deployment process.
+
+The following subsections covers description of the current state of
+technologies with regards to OPC UA pubsub and Azure cloud-based IoT
+enabler.
+
+\hypertarget{review-of-technologies}{%
+\subsection{Review of Technologies}\label{review-of-technologies}}
+
+add here subsections related to the Azure and OOI
+
+\hypertarget{azure-gateway-datarepository-implementation}{%
+\section{Azure Gateway DataRepository
+Implementation}\label{azure-gateway-datarepository-implementation}}
+
+\hypertarget{preface}{%
+\subsection{Preface}\label{preface}}
+
+This section describes an example implementation of an OPC UA PubSub to
+Azure gateway. This gateway is implemented as a composable part of the
+Reactive Networking Application (\texttt{RxNetworking\ App}). The
+\texttt{RxNetworking\ App} is an aggregation of \texttt{Producer} and
+\texttt{Consumer} entities derived from \texttt{DataRepository}. They
+must provide interconnection to real-time process data, hence they are
+recognized as an extension of the \texttt{DataRepository} class.
+\texttt{AzureGateway} part fulfills the \texttt{Consumer} role and uses
+out-of-band communication to push process data to the cloud.
+
+\hypertarget{architecture-1}{%
+\subsection{Architecture}\label{architecture-1}}
+
+Domain model presenting relationship between the: Azure, PubSub Gateway,
+Device, Design and development tools
+
+The \texttt{AzureGateway} functional package has been implemented based
+on the \texttt{Consumer} concept. This particular \texttt{Consumer}
+implements \texttt{IBindingFactory} interface to gather the data
+recovered from the \texttt{Message} instances pulled from the
+\texttt{Distribution\ Channel}. The received data is driven to the Azure
+services using configured out-of-band' protocol. An instance of the
+\texttt{IBindingFactory} is responsible to create objects implementing
+\texttt{IBinding} that can be used by the \texttt{Consumer} to forward
+the data retrieved from \texttt{NetworkMessag} received over the wire to
+Azure services.
+
+The proposed implementation of the Azure gateway proves that the
+\texttt{DataRepository} and associated entities,
+i.e.~\texttt{Local\ Resources}, \texttt{Consumer}, \texttt{Producer} can
+be implemented as external parts, and consequently, the application
+scope may cover practically any concern that can be separated from the
+core PubSub communication engine implementation.
+
+The article provides an introductory understanding of the steps required
+to implement the \texttt{Consumer} role of
+\texttt{OOI\ Reactive\ Application}. The \texttt{ReferenceApplication}
+is an example application of \texttt{Semantic-Data} reactive networking
+based on {[}OPC UA PubSub{]}{[}OPC.UA.PubSub{]} specification. The
+document {[}OPC UA PubSub Main Technology Features{]}{[}PubSubMTF{]}
+covers a description of selected fetuses relevant to this specification.
+
+It is proof of the concept that out-of-band communication for OPC UA
+PubSub can be implemented based on the \texttt{DataRepository} concept.
+
+Here are steps undertook to implement the \texttt{Consumer} role in the
+application:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  \texttt{DataManagementSetup}: this class has been overridden by the
+  \texttt{PartDataManagementSetup} class and it initializes the
+  communication and binds data fields recovered form messages to local
+  resources.
+\item
+  \texttt{IEncodingFactory} and \texttt{IMessageHandlerFactory}: have
+  been implemented in independent libraries and \texttt{Consumer}
+  doesn't depend on this implementation - current implementation of the
+  interfaces is localized as services using an instance of the
+  \texttt{IServiceLocator} interface.
+\item
+  \texttt{IBindingFactory}: has been implemented in the class
+  \texttt{PartBindingFactory} that is responsible to gather the data
+  recovered from the \texttt{Message} instances pulled from the
+  \texttt{Distribution\ Channel}. The received data is driven to the
+  Azure services using configured out-of-band protocol.
+\item
+  \texttt{IConfigurationFactory}: the class
+  \texttt{PartConfigurationFactory} implements this interface to be used
+  for the configuration file opening.
+\end{enumerate}
+
+\hypertarget{datamanagementsetup-implementation}{%
+\subsubsection{\texorpdfstring{\texttt{DataManagementSetup}
+implementation}{DataManagementSetup implementation}}\label{datamanagementsetup-implementation}}
+
+The \texttt{PartDataManagementSetup} constructor initializes all
+properties, which are injection points of all parts composing this role.
+
+In this example, it is assumed that
+\href{https://www.nuget.org/packages/CommonServiceLocator}{\texttt{ServiceLocator}}
+is implemented to resolve references to any external services.
+
+Finally the \texttt{DataManagementSetup.Start()} method is called to
+initialize the infrastructure, enable all associations and start pumping
+the data.
+
+\hypertarget{ibindingfactory-implementation}{%
+\subsubsection{\texorpdfstring{\texttt{IBindingFactory}
+implementation}{IBindingFactory implementation}}\label{ibindingfactory-implementation}}
+
+Implementation of this interface is a basic step to implement
+\texttt{Consumer} functionality. The \texttt{DataRepository} represents
+data holding assets in the \texttt{RxNetworking\ App} and, following the
+proposed architecture, the \texttt{IBindingFactory} interface is
+implemented by this external part. It captures functionality responsible
+for accessing the process data represented by the
+\texttt{LocalResources}. The \texttt{LocalResources} represents the
+external part that has a very broad usage purpose. For example, it may
+be any kind of process data source/destination, and to name a few
+\texttt{Raw\ Data}, \texttt{OPC\ UA\ Address\ Space\ Management}, and
+\texttt{Azure} services in this case.
+
+\hypertarget{configuration}{%
+\subsection{Configuration}\label{configuration}}
+
+\hypertarget{iconfigurationfactory-implementation}{%
+\subsubsection{\texorpdfstring{\texttt{IConfigurationFactory}
+implementation}{IConfigurationFactory implementation}}\label{iconfigurationfactory-implementation}}
+
+Implementation of this interface is straightforward and based entirely
+on the library UAOOI.Configuration.Networking available as the NuGet
+package. In a typical scenario, this implementation should not be
+considered for further modification. The only open question is how to
+provide the name of the file containing the configuration of this role.
+
+\hypertarget{protocol-selection}{%
+\subsection{Protocol selection}\label{protocol-selection}}
+
+From the description covered by the Sec. and the Sec. the Azure supports
+the HTTP, AMQP, MQTT, but the PubSub Ethernet, UDP, AMQP, MQTT. If the
+Ethernet or UDP has been selected to build interconnection based on
+PubSub direc interoperability with the PubSub is impossible because the
+Azure doesn't offer these protocol as native communication services.
+
+\hypertarget{data-mapping}{%
+\subsection{data mapping}\label{data-mapping}}
+
+For both the schema is different Data Transfer Object encoding
+
+The Azure uses JSON based Data Transfer Object encoding and schema
+defined based on the solution metadata. The pubsub uses json and binary
+Data Transfer Object encoding. If JSON is used possibility to establish
+semantic context depends on the Azure metadata definition. In case
+PubSub uses binary encoding establishing interconnection is impossible.
+
+\hypertarget{security}{%
+\subsection{Security}\label{security}}
+
+Azure and PubSub uses different security mechanism so establishing
+directly security context is impossible at all
+
+\hypertarget{deployment-phases}{%
+\subsection{Deployment phases}\label{deployment-phases}}
 
@@
   Maintenance
-  \end{itemize}
-\end{itemize}
-
-We have selected
-\href{https://docs.microsoft.com/azure/iot-central/core/}{IoT Central}
-because:
-
-\begin{itemize}
-\tightlist
-\item
-  provides process data visualization user interface
-\item
-  allows to describe devices using metadata containing telemetry data
-  types
-\end{itemize}
-
-\hypertarget{gateway-implementation}{%
-\section{Gateway implementation}\label{gateway-implementation}}
-
-\begin{itemize}
-\tightlist
-\item
-  Architecture
-\item
-  Protocol selection and mapping
-\item
-  Configuration
-\item
-  Testing
 \end{itemize}
@@
 
+\hypertarget{from-ooi-ri-mpostolmanuscript.tex-1}{%
+\subsection{From
+OOI-RI-MPostolManuscript.tex}\label{from-ooi-ri-mpostolmanuscript.tex-1}}
+
+The described solution proves that it is possible tio implement Azure
+couple as \ldots{}
+
+The \emph{DataRepository} represents data holding assets in the
+\emph{Reactive Application} and, following the proposed architecture,
+the \emph{IBindingFactory} interface is implemented by this external
+part. It captures functionality responsible for accessing the process
+data from \emph{LocalResources}. The \emph{LocalResources} represents an
+external part that has a very broad usage purpose. For example, it may
+be any kind of the process data source/destination,
+i.e.\textasciitilde{}\emph{Raw Data} or \emph{Address Space Management}
+(Fig. \ref*{fig_archit}). By design, the \emph{DataRepository} and
+associated entities, i.e.\textasciitilde{}\emph{Local Resources},
+\emph{Consumer}, \emph{Producer} have been implemented as external
+parts, and consequently, the application scope may cover practically any
+concern that can be separated from the core \emph{Reactive Application}
+implementation.
+
 \end{document}

### 2020-11-07 Latex/Manuscript.tex
Work out Markdown\60.GatewayImplementation.md #35
- integrate with other sections

@@
 
-\todo{prepare section: \textit{Object-Oriented Internet interoperability Implementation}}
 \todo{Add any information about available reusable deliverables related to this work.}
 
+\subsection{Preface}\label{preface}
+
+This section describes an example implementation of an OPC UA PubSub to Azure gateway.
+This gateway is implemented as a composable part of the Reactive Networking Application (\textit{RxNetworking\ App}).
+The \textit{RxNetworking\ App} is an aggregation of \textit{Producer} and \textit{Consumer} entities derived from \textit{DataRepository}.
+They must provide interconnection to real-time process data, hence they are recognized as an extension of the \textit{DataRepository} class.
+\textit{AzureGateway} part fulfills the \textit{Consumer} role and uses out-of-band communication to push process data to the cloud.
+
+\subsection{Architecture}\label{architecture}
+
+Domain model presenting relationship between the: Azure, PubSub Gateway, Device, Design and development tools
+
+The \textit{AzureGateway} functional package has been implemented based on the \textit{Consumer} concept.
+This particular \textit{Consumer} implements \textit{IBindingFactory} interface to gather the data recovered from the \textit{Message} instances pulled from the \textit{Distribution\ Channel}.
+The received data is driven to the Azure services using configured out-of-band' protocol.
+An instance of the \textit{IBindingFactory} is responsible to create objects implementing \textit{IBinding} that can be used by the \textit{Consumer} to forward the data retrieved from \textit{NetworkMessage} received over the wire to Azure services.
+
+The proposed implementation of the Azure gateway proves that the \textit{DataRepository} and associated entities, i.e.~\textit{Local\ Resources}, \textit{Consumer}, \textit{Producer} can be implemented as external parts, and consequently, the application scope may cover practically any concern that can be separated from the core PubSub communication engine implementation.
+
+The article provides an introductory understanding of the steps required to implement the \textit{Consumer} role of \textit{OOI\ Reactive\ Application}.
+The \textit{ReferenceApplication} is an example application of \textit{Semantic-Data} reactive networking based on {[}OPC UA PubSub{]}{[}OPC.UA.PubSub{]} specification.
+The document {[}OPC UA PubSub Main Technology Features{]}{[}PubSubMTF{]} covers a description of selected fetuses relevant to this specification.
+
+It is proof of the concept that out-of-band communication for OPC UA PubSub can be implemented based on the \textit{DataRepository} concept.
+
+Here are steps undertook to implement the \textit{Consumer} role in the application:
+
+\begin{enumerate}
+      \item \textit{DataManagementSetup}: this class has been overridden by the \textit{PartDataManagementSetup} class and it initializes the communication and binds data fields recovered form messages to local resources.
+      \item \textit{IEncodingFactory} and \textit{IMessageHandlerFactory}: have been implemented in independent libraries and \textit{Consumer} doesn't depend on this implementation - current implementation of the interfaces is localized as services using an instance of the \textit{IServiceLocator} interface.
+      \item \textit{IBindingFactory}: has been implemented in the class \textit{PartBindingFactory} that is responsible to gather the data recovered from the \textit{Message} instances pulled from the \textit{Distribution\ Channel}.
+The received data is driven to the Azure services using configured out-of-band protocol.
+      \item \textit{IConfigurationFactory}: the class \textit{PartConfigurationFactory} implements this interface to be used for the configuration file opening.
+\end{enumerate}
+
+\subsubsection{\texorpdfstring{\textit{DataManagementSetup} implementation}{DataManagementSetup implementation}}\label{datamanagementsetup-implementation}
+
+The \textit{PartDataManagementSetup} constructor initializes all properties, which are injection points of all parts composing this role.
+
+In this example, it is assumed that \href{https://www.nuget.org/packages/CommonServiceLocator}{\textit{ServiceLocator}} is implemented to resolve references to any external services.
+
+Finally the \textit{DataManagementSetup.Start()} method is called to initialize the infrastructure, enable all associations and start pumping the data.
+
+\subsubsection{\texorpdfstring{\textit{IBindingFactory} implementation}{IBindingFactory implementation}}\label{ibindingfactory-implementation}
+
+Implementation of this interface is a basic step to implement \textit{Consumer} functionality.
+The \textit{DataRepository} represents data holding assets in the \textit{RxNetworking\ App} and, following the proposed architecture, the \textit{IBindingFactory} interface is implemented by this external part.
+It captures functionality responsible for accessing the process data represented by the \textit{LocalResources}.
+The \textit{LocalResources} represents the external part that has a very broad usage purpose.
+For example, it may be any kind of process data source/destination, and to name a few \textit{Raw\ Data}, \textit{OPC\ UA\ Address\ Space\ Management}, and \textit{Azure} services in this case.
+
+\subsection{Configuration}\label{configuration}
+
+\subsubsection{\texorpdfstring{\textit{IConfigurationFactory} implementation}{IConfigurationFactory implementation}}\label{iconfigurationfactory-implementation}
+
+Implementation of this interface is straightforward and based entirely on the library UAOOI.Configuration.Networking available as the NuGet package.
+In a typical scenario, this implementation should not be considered for further modification.
+The only open question is how to provide the name of the file containing the configuration of this role.
+
+\subsection{Protocol selection}\label{protocol-selection}
+
+From the description covered by the Sec.
+and the Sec.
+the Azure supports the HTTP, AMQP, MQTT, but the PubSub Ethernet, UDP, AMQP, MQTT.
+If the Ethernet or UDP has been selected to build interconnection based on PubSub direc interoperability with the PubSub is impossible because the Azure doesn't offer these protocol as native communication services.
+
+\subsection{data mapping}\label{data-mapping}
+
+For both the schema is different Data Transfer Object encoding
+
+The Azure uses JSON based Data Transfer Object encoding and schema defined based on the solution metadata.
+The pubsub uses json and binary Data Transfer Object encoding.
+If JSON is used possibility to establish semantic context depends on the Azure metadata definition.
+In case PubSub uses binary encoding establishing interconnection is impossible.
+
+\subsection{Security}\label{security}
+
+Azure and PubSub uses different security mechanism so establishing directly security context is impossible at all
+
+\subsection{Deployment phases}\label{deployment-phases}
+
 \begin{itemize}
-      \tightlist
-      \item
-            Architecture
-      \item
-            Protocol selection and mapping
-      \item
-            Configuration
-      \item
-            Testing
+      \item Design
+      \item Gateway and devices registration
+      \item Authentication
+      \item Device/Service association
+      \item Device/Application association
+      \item Establishing session
+            \begin{itemize}
+                  \item Device/Device Template (Device Capability Model) association - establishing a semantic-context
+                  \item Security management - establishing security-context
+            \end{itemize}
+      \item Interconnection - exchange of data
+      \item Maintenance
 \end{itemize}
@@
 
-The OPC UA PubSub to Azure gateway (\textit{AzureGateway})
-implementation has been just published on GitHub as the open-source (MIT
-licensed) as a part of the more general concept of the Object-Oriented
-Internet reactive networking. It is proof of the concept that
+The OPC UA PubSub to Azure gateway (\textit{AzureGateway}) implementation has been just published on GitHub as the open-source (MIT licensed) as a part of the more general concept of the Object-Oriented Internet reactive networking.
+It is proof of the concept that
 
@@
       \tightlist
-      \item
-            OPC UA PubSub can be implemented as a powerful standalone package - no C/S dependency
-      \item
-            Azure interoperability can be implemented as an out-of-band
-            communication (MQTT, AMQP, HTTP) - no PubSub dependency
-      \item
-            Process data functionality can be composable at run-time - no
-            programming required
+      \item OPC UA PubSub can be implemented as a powerful standalone package - no C/S dependency
+      \item Azure interoperability can be implemented as an out-of-band communication (MQTT, AMQP, HTTP) - no PubSub dependency
+      \item Process data functionality can be composable at run-time - no programming required
 \end{enumerate}

### 2020-11-14 Latex/Manuscript.tex
Work out Markdown\60.GatewayImplementation.md #35
- integrate with other sections - working copy

@@
 A reference implementation of this archetype is described in Sect.~\ref*{sect.gateway-implementation}.
-The most important findings and future work are summarized in Sect.~\ref*{conclusion}.
+The most important findings and future work are summarized in Sect.~\ref*{section.conclusion}.
 
@@
 
-\subsection{Architecture}\label{architecture}
+\subsection{Architecture}\label{subs.architecture}
 
@@
       \includegraphics{../.Media/StrategyDomainModel.png}
-      \caption{Strategy Domain Model}\label{StrategyDomainModel}
+      \caption{Strategy Domain Model}\label{figure.StrategyDomainModel}
 \end{figure}
@@
 Unlike the above described solutions, the \textbf{embedded gateway} is not derived from the middleware concept.
-The domain model for this archetype is presented in the Fig.~\ref*{StrategyDomainModel}.
+The domain model for this archetype is presented in the Fig.~\ref*{subs.architecture}.
 Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \textit{Networking} service of the \textit{Cyber-physical\ node}.
@@
 The \textbf{embedded gateway} archetype relaxes most of the issues described above: \textit{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security-context differences to name only a few.
-The main goal of this article is to provide proof that the \textbf{embedded gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogenous environments in concern.
+The main goal of this article is to provide proof that the \textbf{embedded gateway} archetype implementation is possible based on a generic subs.architecture that can be used as a foundation for the integration of the heterogenous environments in concern.
 The proposed implementation is designed for selected interoperability standard and cloud product.
@@
 Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub spec \cite{RefWorks:doc:5d98837de4b055984c0eecf0}.
-According to proposed architecture (Fig.~\ref*{StrategyDomainModel}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ Node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
+According to proposed architecture (Fig.~\ref*{subs.architecture}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ Node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
 Additionally it must be assumed that the library used to deploy \textit{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/pubsub gateway functionality.
@@
 To promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub (Sect.
-\ref*{architecture}) and support the \emph{Reactive Interoperability} (Sect.
+\ref*{subs.architecture}) and support the \emph{Reactive Interoperability} (Sect.
 \ref*{introduction}) concept.
@@
 The library is designed to be a foundation for developing application programs that are taking part in a message-centric communication pattern and interconnected using the reactive networking concept.
-The diagram in Fig.~\ref*{UADataApplicationArchitecture} shows the relationship between the library \textit{SDK} and external parts composing any reactive networking application (\textit{Reactive\ Application}).
+The diagram in Fig.~\ref*{figure.UADataApplicationArchitecture} shows the relationship between the library \textit{SDK} and external parts composing any reactive networking application (\textit{Reactive\ Application}).
 The \textit{Reactive Application} is an aggregation of \textit{Producer} and \textit{Consumer} parts.
@@
       \includegraphics[width=5cm]{../.Media/UADataApplicationArchitecture.png}
-      \caption{Reactive interoperability implementation}\label{UADataApplicationArchitecture}
+      \caption{Reactive interoperability implementation}\label{figure.UADataApplicationArchitecture}
 \end{figure}
@@
 OPC Unified Architecture Part 14 PubSub has been selected in this respect (Sect.
-\ref*{architecture}).
+\ref*{subs.architecture}).
 By design, this standard should support the required publisher-subscriber communication pattern.
@@
 
-Many parts in the domain model presented in Fig.~\ref*{UADataApplicationArchitecture} requires a polymorphic approach to implementation.
+Many parts in the domain model presented in Fig.~\ref*{figure.UADataApplicationArchitecture} requires a polymorphic approach to implementation.
 To promote the polymorphic ready solution the following concepts have been adopted:
@@
 
-The \textit{Consumer} and \textit{Producer} classes are derived from the \textit{DataRepository} (Fig.~\ref*{UADataApplicationArchitecture}).
+The \textit{Consumer} and \textit{Producer} classes are derived from the \textit{DataRepository} (Fig.~\ref*{figure.UADataApplicationArchitecture}).
 The \textit{Consumer} uses the \textit{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
@@
 From the discussion covered by the Sect.
-\ref*{architecture} we can infer that the interoperability of communicating parties requires establishing a semantic-context and security-context between them.
+\ref*{subs.architecture} we can infer that the interoperability of communicating parties requires establishing a semantic-context and security-context between them.
 If the received data is driven to any external data destination (e.g.
@@
 
-\subsection{Preface}\label{preface}
+\subsection{Preface}
 
@@
 
-\subsection{Architecture}\label{architecture}
+\subsection{Architecture}
 
-Domain model presenting relationship between the: Azure, PubSub Gateway, Device, Design and development tools
+Domain model presenting relationship between the Azure \textit{Cloud-based\ front-end} and \textit{Cyber-physical\ node} attached to the \textit{Cyber-physical\ node} is presented in Fig.
+\ref*{} \textit{Cloud-based Front-end} and Cyber-physical node, PubSub Gateway, Device, Design and development tools
 
@@
 The article provides an introductory understanding of the steps required to implement the \textit{Consumer} role of \textit{OOI\ Reactive\ Application}.
-The \textit{ReferenceApplication} is an example application of \textit{Semantic-Data} reactive networking based on {[}OPC UA PubSub{]}{[}OPC.UA.PubSub{]} specification.
-The document {[}OPC UA PubSub Main Technology Features{]}{[}PubSubMTF{]} covers a description of selected fetuses relevant to this specification.
+The \textit{ReferenceApplication} is an example application of \textit{Semantic-Data} reactive networking based on OPC UA PubSub\cite{RefWorks:doc:5d98837de4b055984c0eecf0} \todo{cite OPC UA PubSub Main Technology Features}.
 
@@
 
-\subsubsection{\texorpdfstring{\textit{DataManagementSetup} implementation}{DataManagementSetup implementation}}\label{datamanagementsetup-implementation}
+The class \textit{DataManagementSetup} constructor initializes all properties, which are injection points of all parts composing this role.
 
-The \textit{PartDataManagementSetup} constructor initializes all properties, which are injection points of all parts composing this role.
-
-In this example, it is assumed that \href{https://www.nuget.org/packages/CommonServiceLocator}{\textit{ServiceLocator}} is implemented to resolve references to any external services.
+In this example, it is assumed that \textit{ServiceLocator} \footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} } is implemented to resolve references to any external services.
 
 Finally the \textit{DataManagementSetup.Start()} method is called to initialize the infrastructure, enable all associations and start pumping the data.
-
-\subsubsection{\texorpdfstring{\textit{IBindingFactory} implementation}{IBindingFactory implementation}}\label{ibindingfactory-implementation}
 
@@
 
-\subsection{Configuration}\label{configuration}
+\subsection{Configuration}
 
@@
 
-\subsection{Protocol selection}\label{protocol-selection}
+\subsection{Protocol selection}
 
-From the description covered by the Sec.
-and the Sec.
-the Azure supports the HTTP, AMQP, MQTT, but the PubSub Ethernet, UDP, AMQP, MQTT.
-If the Ethernet or UDP has been selected to build interconnection based on PubSub direc interoperability with the PubSub is impossible because the Azure doesn't offer these protocol as native communication services.
+The Azure supports the HTTP, AMQP, MQTT (Sec.
+\ref*{azure-main-technology-features}).
+On other hand the PubSub supports Ethernet, UDP, AMQP, MQTT {Sect.
+\ref*{subs.architecture}}.
+If the Ethernet or UDP has been selected to build interconnection based on PubSub direc interoperability between the Azure and PubSub is impossible because the mentioned protocols are not offered as the native communication services.
 
-\subsection{data mapping}\label{data-mapping}
+\subsection{data mapping}
 
@@
 
-\subsection{Security}\label{security}
+\subsection{Security}
 
@@
 
-\subsection{Deployment phases}\label{deployment-phases}
+\subsection{Deployment phases}
 
@@
       \item Interconnection - exchange of data
-      \item Maintenance
+      \item Communication maintenance
 \end{itemize}
 
-\section{Conclusion}\label{conclusion}
+\section{Conclusion}\label{section.conclusion}
 

### 2020-11-15 Latex/Manuscript.tex
Work out Markdown\60.GatewayImplementation.md #35
- refine the text and add final content - added and improved UML diagrams

@@
       \centering
-      \includegraphics{../.Media/StrategyDomainModel.png}
+      \includegraphics[width=8cm]{../.Media/StrategyDomainModel.png}
       \caption{Strategy Domain Model}\label{figure.StrategyDomainModel}
@@
 Unlike the above described solutions, the \textbf{embedded gateway} is not derived from the middleware concept.
-The domain model for this archetype is presented in the Fig.~\ref*{subs.architecture}.
+The domain model for this archetype is presented in the Fig.~\ref*{figure.StrategyDomainModel}.
 Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \textit{Networking} service of the \textit{Cyber-physical\ node}.
@@
       \centering
-      \includegraphics[width=5cm]{../.Media/UADataApplicationArchitecture.png}
+      \includegraphics[width=8cm]{../.Media/UADataApplicationArchitecture.png}
       \caption{Reactive interoperability implementation}\label{figure.UADataApplicationArchitecture}
@@
 
+\begin{figure}
+      \centering
+      \includegraphics[width=8cm]{../.Media/ImplementationDomainModel.png}
+      \caption{Implementation Architecture}\label{figure.ImplementationDomainModel}
+\end{figure}
+
 \subsection{Architecture}
 
-Domain model presenting relationship between the Azure \textit{Cloud-based\ front-end} and \textit{Cyber-physical\ node} attached to the \textit{Cyber-physical\ node} is presented in Fig.
-\ref*{} \textit{Cloud-based Front-end} and Cyber-physical node, PubSub Gateway, Device, Design and development tools
+A generic domain model presenting relationship between the Azure \textit{Cloud-based\ front-end} and \textit{Cyber-physical\ node} attached to the \textit{Cyber-physical\ network} is presented in Fig.
+\ref*{figure.StrategyDomainModel}.
+As it was pointed out in the Sect.
+\ref*{subs.architecture} using OPC UA PubSub the aggregation of nodes by the network is loosely coupled, i.e.
+nodes can be added and removed from the network dynamically, and nodes may represent mobile data holding assets.
+
+\begin{figure}
+      \centering
+      \includegraphics[width=\textwidth]{../.Media/ImplementationArchitecture.png}
+      \caption{Implementation Architecture}\label{figure.ImplementationArchitecture}
+\end{figure}
+
+%) \textit{Cloud-based Front-end} and Cyber-physical node, PubSub Gateway, Device, Design and development tools
 
@@
 
+\begin{figure}
+      \centering
+      \includegraphics[width=\textwidth]{../.Media/AzureGateway.png}
+      \caption{Implementation Architecture}\label{figure.AzureGateway}
+\end{figure}
+
 For both the schema is different Data Transfer Object encoding
@@
 
+The propose architecture enable possibility to interconnect the cloud-based services with the Cyber-physical network.
+This solution is in contrast to to the architecture presented in OPC UA Part 1 and Part 14.
+
 \begin{enumerate}

### 2020-11-19 Latex/Manuscript.tex
Work out Markdown\40.OOITechnologyFeatures.md #28
- final latex text formatting
- fnal review of the .pdf

- fixes #28

@@
 
-\section{Cloud to Sensors Field Level Connectivity}\label{cloud-to-sensors-field-level-connectivity}
+\section{Sensors to Cloud Field Level Connectivity}\label{cloud-to-sensors-field-level-connectivity}
 
@@
       \includegraphics[width=8cm]{../.Media/StrategyDomainModel.png}
-      \caption{Strategy Domain Model}\label{figure.StrategyDomainModel}
+      \caption{Strategy Domain Model}\label{figure1.StrategyDomainModel}
 \end{figure}
@@
 Unlike the above described solutions, the \textbf{embedded gateway} is not derived from the middleware concept.
-The domain model for this archetype is presented in the Fig.~\ref*{figure.StrategyDomainModel}.
+The domain model for this archetype is presented in the Fig.~\ref*{figure1.StrategyDomainModel}.
 Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \textit{Networking} service of the \textit{Cyber-physical\ node}.
@@
 Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub spec \cite{RefWorks:doc:5d98837de4b055984c0eecf0}.
-According to proposed architecture (Fig.~\ref*{subs.architecture}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ Node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
+According to proposed architecture (Fig.~\ref*{figure1.StrategyDomainModel}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ Node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
 Additionally it must be assumed that the library used to deploy \textit{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/pubsub gateway functionality.
@@
 The library is designed to be a foundation for developing application programs that are taking part in a message-centric communication pattern and interconnected using the reactive networking concept.
-The diagram in Fig.~\ref*{figure.UADataApplicationArchitecture} shows the relationship between the library \textit{SDK} and external parts composing any reactive networking application (\textit{Reactive\ Application}).
+The diagram in Fig.~\ref*{figure2.UADataApplicationArchitecture} shows the relationship between the library \textit{SDK} and external parts composing any reactive networking application (\textit{Reactive\ Application}).
 The \textit{Reactive Application} is an aggregation of \textit{Producer} and \textit{Consumer} parts.
@@
       \includegraphics[width=8cm]{../.Media/UADataApplicationArchitecture.png}
-      \caption{Reactive interoperability implementation}\label{figure.UADataApplicationArchitecture}
+      \caption{Reactive interoperability implementation}\label{figure2.UADataApplicationArchitecture}
 \end{figure}
@@
 
-Many parts in the domain model presented in Fig.~\ref*{figure.UADataApplicationArchitecture} requires a polymorphic approach to implementation.
+Many parts in the domain model presented in Fig.~\ref*{figure2.UADataApplicationArchitecture} requires a polymorphic approach to implementation.
 To promote the polymorphic ready solution the following concepts have been adopted:
@@
       \item \emph{IConfigurationDataFactory} - the configuration data access,
-      \item \emph{IMessageHandlerFactory} - pushing the \emph{Message} entities to/pulling from \emph{Distribution Channel},
+      \item \emph{IMessageHandlerFactory} - pushing the \emph{Message} entities to/pulling from the wire,
       \item \emph{IEncodingFactory} - searching a dictionary containing value converters.
@@
 It is expected that the functionality implementation expressed by these interfaces is provided as independent external composable parts.
-The composition is accomplished at run time, and the effective application functionality depends essentially on reusable loosely coupled parts composed using the dependency injection software engineering and adaptive programming concept \todo{cite{RefWorks:doc:5d9796cbe4b0f66c52dccf04}}.
+The composition is accomplished at run time, and the effective application functionality depends essentially on reusable loosely coupled parts composed applying the dependency injection software engineering and adaptive programming concept \todo{cite{RefWorks:doc:5d9796cbe4b0f66c52dccf04}}.
 
@@
 
-The \textit{Consumer} and \textit{Producer} classes are derived from the \textit{DataRepository} (Fig.~\ref*{figure.UADataApplicationArchitecture}).
+The \textit{Consumer} and \textit{Producer} classes are derived from the \textit{DataRepository} (Fig.~\ref*{figure2.UADataApplicationArchitecture}).
 The \textit{Consumer} uses the \textit{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
@@
 If the received data is driven to any external data destination (e.g.
-cloud-based front-end) using out-of-band protocol semantic-context and security context must be defined for this interoperability relationship.
+cloud-based front-end) using out-of-band protocol semantic-context and security-context must be defined for this interoperability relationship.
 There are a vast variety of possibilities for how to define these contexts.
@@
 
+\todo{replace RxNetworking by Reactive Application}
 This section describes an example implementation of an OPC UA PubSub to Azure gateway.
@@
       \includegraphics[width=8cm]{../.Media/ImplementationDomainModel.png}
-      \caption{Implementation Architecture}\label{figure.ImplementationDomainModel}
+      \caption{Implementation Architecture}\label{figure3.ImplementationDomainModel}
 \end{figure}
@@
 A generic domain model presenting relationship between the Azure \textit{Cloud-based\ front-end} and \textit{Cyber-physical\ node} attached to the \textit{Cyber-physical\ network} is presented in Fig.
-\ref*{figure.StrategyDomainModel}.
+\ref*{figure1.StrategyDomainModel}.
 As it was pointed out in the Sect.
@@
       \includegraphics[width=\textwidth]{../.Media/ImplementationArchitecture.png}
-      \caption{Implementation Architecture}\label{figure.ImplementationArchitecture}
+      \caption{Implementation Architecture}\label{figure4.ImplementationArchitecture}
 \end{figure}
@@
 
-The article provides an introductory understanding of the steps required to implement the \textit{Consumer} role of \textit{OOI\ Reactive\ Application}.
+\todo{review intro}The article provides an introductory understanding of the steps required to implement the \textit{Consumer} role of \textit{OOI\ Reactive\ Application}.
 The \textit{ReferenceApplication} is an example application of \textit{Semantic-Data} reactive networking based on OPC UA PubSub\cite{RefWorks:doc:5d98837de4b055984c0eecf0} \todo{cite OPC UA PubSub Main Technology Features}.
@@
 It captures functionality responsible for accessing the process data represented by the \textit{LocalResources}.
-The \textit{LocalResources} represents the external part that has a very broad usage purpose.
+\todo{duplacted text} The \textit{LocalResources} represents the external part that has a very broad usage purpose.
 For example, it may be any kind of process data source/destination, and to name a few \textit{Raw\ Data}, \textit{OPC\ UA\ Address\ Space\ Management}, and \textit{Azure} services in this case.
@@
 
-\subsubsection{\texorpdfstring{\textit{IConfigurationFactory} implementation}{IConfigurationFactory implementation}}\label{iconfigurationfactory-implementation}
-
-Implementation of this interface is straightforward and based entirely on the library UAOOI.Configuration.Networking available as the NuGet package.
+Implementation of the \textit{IConfigurationFactory} interface is straightforward and based entirely on the library UAOOI.Configuration.Networking available as the NuGet package.
 In a typical scenario, this implementation should not be considered for further modification.
@@
 On other hand the PubSub supports Ethernet, UDP, AMQP, MQTT {Sect.
-\ref*{subs.architecture}}.
+\ref*{ooi-main-technology-features}}.
 If the Ethernet or UDP has been selected to build interconnection based on PubSub direc interoperability between the Azure and PubSub is impossible because the mentioned protocols are not offered as the native communication services.
@@
       \includegraphics[width=\textwidth]{../.Media/AzureGateway.png}
-      \caption{Implementation Architecture}\label{figure.AzureGateway}
+      \caption{Implementation Architecture}\label{figure5.AzureGateway}
 \end{figure}

### 2020-11-21 Latex/Manuscript.tex
Work out Markdown\60.GatewayImplementation.md #35
- working copy

@@
 It is expected that the functionality implementation expressed by these interfaces is provided as independent external composable parts.
-The composition is accomplished at run time, and the effective application functionality depends essentially on reusable loosely coupled parts composed applying the dependency injection software engineering and adaptive programming concept \todo{cite{RefWorks:doc:5d9796cbe4b0f66c52dccf04}}.
+The composition is accomplished at run time, and the effective application functionality depends essentially on reusable loosely coupled parts composed applying the dependency injection software engineering and adaptive programming concept.
+\todo{cite{RefWorks:doc:5d9796cbe4b0f66c52dccf04}}
 
@@
 
-\section{Azure - Object-Oriented Internet interoperability Implementation}\label{sect.gateway-implementation}
-
-\todo{Add any information about available reusable deliverables related to this work.}
+\section{Azure - Object-Oriented Internet Interoperability Implementation}\label{sect.gateway-implementation}
 
@@
 
-\todo{replace RxNetworking by Reactive Application}
-This section describes an example implementation of an OPC UA PubSub to Azure gateway.
-This gateway is implemented as a composable part of the Reactive Networking Application (\textit{RxNetworking\ App}).
-The \textit{RxNetworking\ App} is an aggregation of \textit{Producer} and \textit{Consumer} entities derived from \textit{DataRepository}.
-They must provide interconnection to real-time process data, hence they are recognized as an extension of the \textit{DataRepository} class.
-\textit{AzureGateway} part fulfills the \textit{Consumer} role and uses out-of-band communication to push process data to the cloud.
+A generic domain model presenting relationship between the Azure \textit{Cloud-based\ Front-end} and \textit{Cyber-physical\ node} attached to the \textit{Cyber-physical\ network} is presented in Fig.
+\ref*{figure1.StrategyDomainModel}.
+It is proposed to implement the \textit{Cyber-physical\ node} by adopting the \textit{Reactive Application} archetype compliant with the reactive interoperability concept (Fig.
+\ref*{figure2.UADataApplicationArchitecture}) described in the Sect.
+\ref*{ooi-main-technology-features}.
+Merging selected entities of this archetype into the proposed domain model (Fig.
+\ref*{figure1.StrategyDomainModel}) lead to a relationship model expressed as the diagram presented in Fig.
+\ref*{figure3.ImplementationDomainModel}.
+In this approach, the \textit{Reactive Application} contains at least the \textit{Consumer} entity.
+In the proposed approach the \textit{Embedded Gateway} is implemented as a composable part derived from the \textit{Consumer} role.
 
@@
 
-\subsection{Architecture}
+In final implementation architecture (Fig.
+\ref*{figure4.ImplementationArchitecture}) the \textit{Consumer} has been implemented by the \textit{PartDataManagementSetup} that is derived from \textit{DatManagementSetup} embedded in the library \textit{Networking} removed from the diagram for the sake of simplicity.
+It is a basic step to implement the \textit{Consumer} role functionality.
+The class \textit{PartDataManagementSetup} initializes all properties, which are injection points of all parts composing this role.
+The \textit{PartDataManagementSetup} extents functionality of the \textit{DatManagementSetup} based on the following associated classes
 
-A generic domain model presenting relationship between the Azure \textit{Cloud-based\ front-end} and \textit{Cyber-physical\ node} attached to the \textit{Cyber-physical\ network} is presented in Fig.
-\ref*{figure1.StrategyDomainModel}.
-As it was pointed out in the Sect.
-\ref*{subs.architecture} using OPC UA PubSub the aggregation of nodes by the network is loosely coupled, i.e.
-nodes can be added and removed from the network dynamically, and nodes may represent mobile data holding assets.
+\begin{enumerate}
+      \item \textit{PartConfigurationFactory} - implements the interface \textit{IConfigurationFactory} to get access to the application configuration
+      \item \textit{PartBindingFactory} - implements the interface textit{IBindingFactory} to gather the data recovered from the \textit{Message} instances pulled from the wire
+      \item \textit{CommunicationContext} - handling communication with the Azure services
+\end{enumerate}
+
+Implementation of the \textit{IConfigurationFactory} interface is straightforward and based entirely on the \textit{Networking} library.
+In a typical scenario, this implementation should not be considered for further modification.
+The only open question is how to provide the name of the file containing the configuration.
+
+By design, the \textit{PartBindingFactory} implements the \textit{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
+The received data is driven to \textit{CommunicationContext}.
+
+By design it implements the \textit{IBindingFactory} \todo{add IBindingFactory to fig.} to gather the data recovered from the \emph{Message} instances pulled from a network.
+The received data is driven to the Azure services using configured out-of-band protocol.
+
+\textit{IEncodingFactory} and \textit{IMessageHandlerFactory} interfaces have been implemented in independent libraries and ae not considered for any modifications to provide \textit{Embedded Gateway} functionality.
+The current implementation of the interfaces is localized at run time as services using an instance of the \textit{IServiceLocator} interface.
+In this example, it is assumed that \textit{ServiceLocator} \footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} } is implemented to resolve references to any external services.
 
@@
 
-%) \textit{Cloud-based Front-end} and Cyber-physical node, PubSub Gateway, Device, Design and development tools
-
-The \textit{AzureGateway} functional package has been implemented based on the \textit{Consumer} concept.
-This particular \textit{Consumer} implements \textit{IBindingFactory} interface to gather the data recovered from the \textit{Message} instances pulled from the \textit{Distribution\ Channel}.
-The received data is driven to the Azure services using configured out-of-band' protocol.
-An instance of the \textit{IBindingFactory} is responsible to create objects implementing \textit{IBinding} that can be used by the \textit{Consumer} to forward the data retrieved from \textit{NetworkMessage} received over the wire to Azure services.
-
-The proposed implementation of the Azure gateway proves that the \textit{DataRepository} and associated entities, i.e.~\textit{Local\ Resources}, \textit{Consumer}, \textit{Producer} can be implemented as external parts, and consequently, the application scope may cover practically any concern that can be separated from the core PubSub communication engine implementation.
-
-\todo{review intro}The article provides an introductory understanding of the steps required to implement the \textit{Consumer} role of \textit{OOI\ Reactive\ Application}.
-The \textit{ReferenceApplication} is an example application of \textit{Semantic-Data} reactive networking based on OPC UA PubSub\cite{RefWorks:doc:5d98837de4b055984c0eecf0} \todo{cite OPC UA PubSub Main Technology Features}.
-
-It is proof of the concept that out-of-band communication for OPC UA PubSub can be implemented based on the \textit{DataRepository} concept.
-
-Here are steps undertook to implement the \textit{Consumer} role in the application:
-
-\begin{enumerate}
-      \item \textit{DataManagementSetup}: this class has been overridden by the \textit{PartDataManagementSetup} class and it initializes the communication and binds data fields recovered form messages to local resources.
-      \item \textit{IEncodingFactory} and \textit{IMessageHandlerFactory}: have been implemented in independent libraries and \textit{Consumer} doesn't depend on this implementation - current implementation of the interfaces is localized as services using an instance of the \textit{IServiceLocator} interface.
-      \item \textit{IBindingFactory}: has been implemented in the class \textit{PartBindingFactory} that is responsible to gather the data recovered from the \textit{Message} instances pulled from the \textit{Distribution\ Channel}.
-The received data is driven to the Azure services using configured out-of-band protocol.
-      \item \textit{IConfigurationFactory}: the class \textit{PartConfigurationFactory} implements this interface to be used for the configuration file opening.
-\end{enumerate}
-
-The class \textit{DataManagementSetup} constructor initializes all properties, which are injection points of all parts composing this role.
-
-In this example, it is assumed that \textit{ServiceLocator} \footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} } is implemented to resolve references to any external services.
-
-Finally the \textit{DataManagementSetup.Start()} method is called to initialize the infrastructure, enable all associations and start pumping the data.
-
-Implementation of this interface is a basic step to implement \textit{Consumer} functionality.
 The \textit{DataRepository} represents data holding assets in the \textit{RxNetworking\ App} and, following the proposed architecture, the \textit{IBindingFactory} interface is implemented by this external part.
@@
 
-\subsection{Configuration}
-
-Implementation of the \textit{IConfigurationFactory} interface is straightforward and based entirely on the library UAOOI.Configuration.Networking available as the NuGet package.
-In a typical scenario, this implementation should not be considered for further modification.
-The only open question is how to provide the name of the file containing the configuration of this role.
+It initializes the out-of-band communication stack and binds data fields recovered from messages to an Azure data converter and message encoder.
 
 \subsection{Protocol selection}
+
+\todo{Add any information about available reusable deliverables related to this work.}
 
@@
 
+As it was pointed out in the Sect.
+\ref*{subs.architecture} using OPC UA PubSub the aggregation of nodes by the network is loosely coupled, i.e.
+nodes can be added and removed from the network dynamically, and nodes may represent mobile data holding assets.
+
+It is worth stressing that based on this approach only dedicated functionality related to communication with the cloud must be implemented. This way, the reusability of the library is promoted.
+
 The OPC UA PubSub to Azure gateway (\textit{AzureGateway}) implementation has been just published on GitHub as the open-source (MIT licensed) as a part of the more general concept of the Object-Oriented Internet reactive networking.
@@
 \begin{enumerate}
-      \def\labelenumi{\arabic{enumi}.}
-      \tightlist
       \item OPC UA PubSub can be implemented as a powerful standalone package - no C/S dependency

### 2020-11-21 Latex/Manuscript.tex
Work out Markdown\60.GatewayImplementation.md #35
- working copy

@@
       \includegraphics[width=8cm]{../.Media/StrategyDomainModel.png}
-      \caption{Strategy Domain Model}\label{figure1.StrategyDomainModel}
+      \caption{Concept Domain Model}\label{figure1.StrategyDomainModel}
 \end{figure}
@@
 Merging selected entities of this archetype into the proposed domain model (Fig.
-\ref*{figure1.StrategyDomainModel}) lead to a relationship model expressed as the diagram presented in Fig.
+\ref*{figure1.StrategyDomainModel}) lead to a model expressed as the diagram presented in Fig.
 \ref*{figure3.ImplementationDomainModel}.
-In this approach, the \textit{Reactive Application} contains at least the \textit{Consumer} entity.
-In the proposed approach the \textit{Embedded Gateway} is implemented as a composable part derived from the \textit{Consumer} role.
+In the proposed approach the \textit{Embedded Gateway} is derived from the \textit{Consumer} role embedded as as a composable part agregatem by the \textit{Reactive Application}.
 
@@
       \includegraphics[width=8cm]{../.Media/ImplementationDomainModel.png}
-      \caption{Implementation Architecture}\label{figure3.ImplementationDomainModel}
+      \caption{Architecture Domain Model}\label{figure3.ImplementationDomainModel}
 \end{figure}
 
-In final implementation architecture (Fig.
-\ref*{figure4.ImplementationArchitecture}) the \textit{Consumer} has been implemented by the \textit{PartDataManagementSetup} that is derived from \textit{DatManagementSetup} embedded in the library \textit{Networking} removed from the diagram for the sake of simplicity.
-It is a basic step to implement the \textit{Consumer} role functionality.
+In the final deployment architecture (Fig.
+\ref*{figure4.ImplementationArchitecture}) the \textit{Consumer} role has been realized by the \textit{PartDataManagementSetup} that is derived from \textit{DatManagementSetup} embedded in the library \textit{Networking} removed from the diagram for the sake of simplicity.
+It is a basic step for implementation of the \textit{Consumer} role functionality.
 The class \textit{PartDataManagementSetup} initializes all properties, which are injection points of all parts composing this role.
-The \textit{PartDataManagementSetup} extents functionality of the \textit{DatManagementSetup} based on the following associated classes
+It extents functionality of the \textit{DatManagementSetup} based on the following associated classes
 
 \begin{enumerate}
-      \item \textit{PartConfigurationFactory} - implements the interface \textit{IConfigurationFactory} to get access to the application configuration
-      \item \textit{PartBindingFactory} - implements the interface textit{IBindingFactory} to gather the data recovered from the \textit{Message} instances pulled from the wire
-      \item \textit{CommunicationContext} - handling communication with the Azure services
+      \item \textit{PartConfigurationFactory} - to get access to the application configuration
+      \item \textit{PartBindingFactory} - to gather the data recovered from the \textit{Message} instances pulled from the wire
+      \item \textit{CommunicationContext} - to handling communication with the Azure services (Sect. \ref*{sub.AzureInteroperability})
 \end{enumerate}
 
-Implementation of the \textit{IConfigurationFactory} interface is straightforward and based entirely on the \textit{Networking} library.
+In this case, the implementation of the \textit{IConfigurationFactory} interface is straightforward and based entirely on the \textit{Networking} library.
 In a typical scenario, this implementation should not be considered for further modification.
-The only open question is how to provide the name of the file containing the configuration.
+It is ready to provide all necessary configuration parameter to establish semantic and security contexts related to Azure interoperability.
 
-By design, the \textit{PartBindingFactory} implements the \textit{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
-The received data is driven to \textit{CommunicationContext}.
+The \textit{PartBindingFactory} implements the \textit{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
+The received data is driven to \textit{CommunicationContext} for further processing and pushing to cloud-based services to the Azure services using configured out-of-band protocol.
 
-By design it implements the \textit{IBindingFactory} \todo{add IBindingFactory to fig.} to gather the data recovered from the \emph{Message} instances pulled from a network.
-The received data is driven to the Azure services using configured out-of-band protocol.
-
-\textit{IEncodingFactory} and \textit{IMessageHandlerFactory} interfaces have been implemented in independent libraries and ae not considered for any modifications to provide \textit{Embedded Gateway} functionality.
+\textit{IEncodingFactory} and \textit{IMessageHandlerFactory} interfaces (Fig.
+\ref*{figure2.UADataApplicationArchitecture} have been implemented in independent libraries and ae not considered for any modifications to deploy \textit{Embedded Gateway} functionality.
 The current implementation of the interfaces is localized at run time as services using an instance of the \textit{IServiceLocator} interface.
@@
 
-The \textit{DataRepository} represents data holding assets in the \textit{RxNetworking\ App} and, following the proposed architecture, the \textit{IBindingFactory} interface is implemented by this external part.
+The Azure interconnection is realized using the \textit{CommunicationContext}.
+It establish the out-of-band communication stack and implements message encoder.
+The encoded data is gathered from the \textit{PartBindingFactory} using the \textit{IDTOProvider} that defines a contract used to pull data transfer object created from a selected subscription.
+
+binds data fields recovered from messages to an Azure data converter and message encoder.
+
+% consider to remove: The \textit{DataRepository} represents data holding assets in the \textit{RxNetworking\ App} and, following the proposed architecture, the \textit{IBindingFactory} interface is implemented by this external part.
 It captures functionality responsible for accessing the process data represented by the \textit{LocalResources}.
@@
 
-It initializes the out-of-band communication stack and binds data fields recovered from messages to an Azure data converter and message encoder.
-
-\subsection{Protocol selection}
+\subsection{Out-of-band Protocol Selection}
 
@@
 
-\subsection{data mapping}
-
-\begin{figure}
-      \centering
-      \includegraphics[width=\textwidth]{../.Media/AzureGateway.png}
-      \caption{Implementation Architecture}\label{figure5.AzureGateway}
-\end{figure}
+\subsection{Data Mapping}
 

### 2020-11-21 Latex/Manuscript.tex
Work out Markdown\60.GatewayImplementation.md #35
- working copy

@@
 \ref*{figure3.ImplementationDomainModel}.
-In the proposed approach the \textit{Embedded Gateway} is derived from the \textit{Consumer} role embedded as as a composable part agregatem by the \textit{Reactive Application}.
+In the proposed approach the \textit{Embedded Gateway} is derived from the \textit{Consumer} role embedded as as a composable part aggregated by the \textit{Reactive Application}.
 
@@
       \item \textit{PartBindingFactory} - to gather the data recovered from the \textit{Message} instances pulled from the wire
-      \item \textit{CommunicationContext} - to handling communication with the Azure services (Sect. \ref*{sub.AzureInteroperability})
+      \item \textit{CommunicationContext} - to handling communication with the Azure services
 \end{enumerate}
 
-In this case, the implementation of the \textit{IConfigurationFactory} interface is straightforward and based entirely on the \textit{Networking} library.
-In a typical scenario, this implementation should not be considered for further modification.
-It is ready to provide all necessary configuration parameter to establish semantic and security contexts related to Azure interoperability.
+In this case, the implementation of the \textit{IConfigurationFactory} interface is based entirely on the \textit{Networking} library.
+In this scenario, this implementation should not be considered for further modification.
+It is ready to provide all necessary configuration parameters to establish semantic and security contexts related to Azure interoperability.
 
@@
 \ref*{figure2.UADataApplicationArchitecture} have been implemented in independent libraries and ae not considered for any modifications to deploy \textit{Embedded Gateway} functionality.
-The current implementation of the interfaces is localized at run time as services using an instance of the \textit{IServiceLocator} interface.
-In this example, it is assumed that \textit{ServiceLocator} \footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} } is implemented to resolve references to any external services.
+The current implementation of the mentioned interfaces is localized at run time as services using an instance of the \textit{IServiceLocator}.
+In this example, it is assumed that \textit{IServiceLocator} \footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} } is implemented to resolve references to any external services.
 
@@
 
+\hyphenation{IDTOPro-vider}
+
 The Azure interconnection is realized using the \textit{CommunicationContext}.
@@
 The encoded data is gathered from the \textit{PartBindingFactory} using the \textit{IDTOProvider} that defines a contract used to pull data transfer object created from a selected subscription.
-
-binds data fields recovered from messages to an Azure data converter and message encoder.
-
-% consider to remove: The \textit{DataRepository} represents data holding assets in the \textit{RxNetworking\ App} and, following the proposed architecture, the \textit{IBindingFactory} interface is implemented by this external part.
-It captures functionality responsible for accessing the process data represented by the \textit{LocalResources}.
-\todo{duplacted text} The \textit{LocalResources} represents the external part that has a very broad usage purpose.
-For example, it may be any kind of process data source/destination, and to name a few \textit{Raw\ Data}, \textit{OPC\ UA\ Address\ Space\ Management}, and \textit{Azure} services in this case.
 

### 2020-11-22 Latex/Manuscript.tex
Work out Markdown\60.GatewayImplementation.md #35
- working copy
Work out Markdown\60.GatewayImplementation.md #35
- refine the text and add final content.
-

@@
 It offers a vast variety of services.
-This virtual environment handles an unlimited number of users and devices organized using a solution concept.
+This virtual environment handles an unlimited number of users and devices organized using a solution container concept.
 The solution aggregates users, devices, services, and required additional resources scoping on a selected scenario.
-The solution serves as a context that provides a scope to the identifiers (the names of devices, users, process data entities, etc) inside it.
+It also serves as a context that provides a scope to the identifiers (the names of devices, users, process data entities, etc) inside it.
 Solutions are used to organize deployment entities into logical groups and prevent identity collisions.
@@
 
-Following the assumption that interconnection between the cyber-physical
-system and cloud services is designed based on the gateway concept, a
-middleware must be considered as a coupler. It must be interconnected
-with the (CPS) using an in-band protocol adhering to
-communications requirements (i.e.~protocol profile, data encoding, time
-relationships, etc.) governing communication of the parts making it up.
-At the same time, it must support back-and-forth data transfer to the
-cloud using out-of-band native for the cloud services. The transfer
-process requires data conversion from source to destination encoding.
-The \textit{IoT\ Hub} is a service hosted in the cloud that supports
-\textit{IoT\ Central} providing a robust messaging solution - it acts as
-a central message hub for bi-directional communication. This
-communication is transparent, i.e.~it is not data types aware allowing
-any devices to exchange any kind of data. This service is responsible to
-manage the devices' identity and it offers the following protocol
-stacks: AMQP, MQTT, HTTPS.
+Following the assumption that interconnection between the cyber-physical system and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler.
+It must be interconnected with the (CPS) using an in-band protocol adhering to communications requirements (i.e.~protocol profile, data encoding, time relationships, etc.) governing communication of the parts making it up.
+At the same time, it must support back-and-forth data transfer to the cloud using out-of-band native for the cloud services.
+The transfer process requires data conversion from source to destination encoding.
+The \textit{IoT\ Hub} is a service hosted in the cloud that supports \textit{IoT\ Central} providing a robust messaging solution - it acts as a central message hub for bi-directional communication.
+This communication is transparent, i.e.~it is not data types aware allowing
+any devices to exchange any kind of data. This service is responsible to manage the devices' identity and it offers the following protocol stacks: AMQP, MQTT, HTTPS.
 
@@
 service. Hence, the payload formatting is determined by the DCM
-associated with the \textit{IoT\ Central} solution. All the mentioned
-protocols are standard ones. Consequently, it is possible to apply any
-available implementation compliant with an appropriate specification to
-achieve connectivity. In this case, all parameters required to establish
-connectivity and security-context is up to the external software
-responsibility. Alternatively, the API offered by the dedicated
-libraries may be used. Using this API the configuration process can be
-reduced significantly. Using these libraries, the selection of the
-communication protocol has an indirect impact on the interoperability
-features, including performance. The connectivity with
-\textit{IoT\ Hub}, for example, can be obtained using:
-
-\begin{itemize}
-      \item \textit{Microsoft.Azure.Devices} - Service SDK for Azure IoT Devices
-      \item \textit{Microsoft.Azure.Devices.Client}- Device SDK for Azure \textit{IoT\ Hub}
-      \item \textit{Microsoft.Azure.Devices.Shared} - Common code for Azure IoT Device and Service SDK
-      \item \textit{Microsoft.Azure.Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
-      \item \textit{Microsoft.Azure.Devices.Provisioning.Transport.Amqp} - Provisioning Device Client AMQP Transport for Azure IoT Devices
-      \item \textit{Microsoft.Azure.Devices.Provisioning.Transport.Http} - Provisioning Device Client Http Transport for Azure IoT Devices
-      \item \textit{Microsoft.Azure.Devices.Provisioning.Transport.Mqtt} - Provisioning Device Client MQTT Transport for Azure IoT Devices
-\end{itemize}
+associated with the \textit{IoT\ Central} solution.
 
@@
 
-\subsection{Preface}
+\subsection{Gateway Implementation Architecture}\label{subsection.GatewayImplementationArchitecture}
 
@@
 
+\begin{figure}
+      \centering
+      \includegraphics[width=\textwidth]{../.Media/ImplementationArchitecture.png}
+      \caption{Implementation Architecture}\label{figure4.ImplementationArchitecture}
+\end{figure}
+
 \begin{enumerate}
@@
 The \textit{PartBindingFactory} implements the \textit{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
-The received data is driven to \textit{CommunicationContext} for further processing and pushing to cloud-based services to the Azure services using configured out-of-band protocol.
+The received data is driven to \textit{CommunicationContext} for further encoding and finally pushing it to the Azure services using configured out-of-band protocol.
 
@@
 In this example, it is assumed that \textit{IServiceLocator} \footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} } is implemented to resolve references to any external services.
+Both interfaces are used to manage interconnection of the node with the \textit{Cyber-physical Network}.
 
-\begin{figure}
-      \centering
-      \includegraphics[width=\textwidth]{../.Media/ImplementationArchitecture.png}
-      \caption{Implementation Architecture}\label{figure4.ImplementationArchitecture}
-\end{figure}
+The Azure interconnection is realized using the \textit{CommunicationContext}. It implements message encoder and establishes the out-of-band communication stack.
 
-\hyphenation{IDTOPro-vider}
+The recovered data from the \textit{Message} is obtained from the \textit{PartBindingFactory} using the \textit{IDTOProvider} that defines a contract used to pull the Data Transfer Object (DTO) created from a selected subscription by the \textit{PartBindingFactory}.
+The transfer process requires data conversion from source to destination encoding, i.e.
+replacing bitstreams used by the CPS by equivalent ones for the cloud-based services.
+The Azure offers a vast variety of built-in types ready to be used in common cases, but not necessarily there are equivalent counterparts in use by the CPS.
+The Azure uses JSON based Data Transfer Object encoding and schema defined based on the solution metadata.
+The pubsub uses json and binary Data Transfer Object encoding.
+In any case the data recovered from the Message pulled from a subscription is stored locally using the object model based on standard .NET types.
+\textit{PartBindingFactory} maps selected object graph onto the JSON message required by the cloud services.
 
-The Azure interconnection is realized using the \textit{CommunicationContext}.
-It establish the out-of-band communication stack and implements message encoder.
-The encoded data is gathered from the \textit{PartBindingFactory} using the \textit{IDTOProvider} that defines a contract used to pull data transfer object created from a selected subscription.
-
-\subsection{Out-of-band Protocol Selection}
-
-\todo{Add any information about available reusable deliverables related to this work.}
-
+The encoded JSON messages must be transferred over the network to Azure using selected protocol stock.
 The Azure supports the HTTP, AMQP, MQTT (Sec.
 \ref*{azure-main-technology-features}).
-On other hand the PubSub supports Ethernet, UDP, AMQP, MQTT {Sect.
-\ref*{ooi-main-technology-features}}.
-If the Ethernet or UDP has been selected to build interconnection based on PubSub direc interoperability between the Azure and PubSub is impossible because the mentioned protocols are not offered as the native communication services.
-
-\subsection{Data Mapping}
-
-For both the schema is different Data Transfer Object encoding
-
-The Azure uses JSON based Data Transfer Object encoding and schema defined based on the solution metadata.
-The pubsub uses json and binary Data Transfer Object encoding.
-If JSON is used possibility to establish semantic context depends on the Azure metadata definition.
-In case PubSub uses binary encoding establishing interconnection is impossible.
-
-\subsection{Security}
-
-Azure and PubSub uses different security mechanism so establishing directly security context is impossible at all
-
-\subsection{Deployment phases}
+All the mentioned protocols are standard ones.
+Consequently, it is possible to apply any available implementation compliant with an appropriate specification to achieve connectivity.
+In this case, all parameters required to establish connectivity and security-context is up to the external software responsibility.
+Alternatively, the API offered by the dedicated libraries may be used.
+Using this API the configuration process may be reduced significantly.
+Using these libraries, the selection of the communication protocol has an indirect impact on the interoperability features, including performance.
+In the proposed gateway implementation the Azure interconnection has been obtained using the following \textit{Microsoft.Azure} libraries:
 
 \begin{itemize}
-      \item Design
+      \item \textit{Devices} - Service SDK for Azure IoT Devices
+      \item \textit{Devices.Client} - Device SDK for Azure \textit{IoT\ Hub}
+      \item \textit{Devices.Shared} - Common code for Azure IoT Device and Service SDK
+      \item \textit{Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
+      \item \textit{Devices.Provisioning.Transport.Amqp} - Provisioning Device Client AMQP Transport for Azure IoT Devices
+      \item \textit{Devices.Provisioning.Transport.Http} - Provisioning Device Client HTTP Transport for Azure IoT Devices
+      \item \textit{Devices.Provisioning.Transport.Mqtt} - Provisioning Device Client MQTT Transport for Azure IoT Devices
+\end{itemize}
+
+Azure and PubSub uses different security mechanism so in the proposed solution establishing security context is realized independently.
+The \textit{CommunicationContext} is responsible to establish this context as an embedded negotiation phase closely coupled with the establishing interconnection.
+In this interconnection the following steps are distinguished:
+
+\begin{itemize}
       \item Gateway and devices registration
@@
 \section{Conclusion}\label{section.conclusion}
+
+The Azure supports the HTTP, AMQP, MQTT (Sec.
+\ref*{azure-main-technology-features}).
+On the other hand the PubSub supports Ethernet, UDP, AMQP, MQTT {Sect.
+\ref*{ooi-main-technology-features}}.
+Sets of supported protocol are not overlapping.
+If the Ethernet or UDP has been selected to build PubSub interconnection the direc interoperability between the Azure and PubSub is impossible because the mentioned protocols are not offered as the native communication services.
+In this case only indirect interconnection is available.
 

### 2020-11-25 Latex/Manuscript.tex
Work out Markdown\60.GatewayImplementation.md #35
- final latex text formating
- fnal review of the .pdf
- ready for review by PS.

@@
 
-\subsection{Gateway Implementation Architecture}\label{subsection.GatewayImplementationArchitecture}
+\subsection{Implementation Architecture}\label{subsection.GatewayImplementationArchitecture}
 
@@
 In the final deployment architecture (Fig.
-\ref*{figure4.ImplementationArchitecture}) the \textit{Consumer} role has been realized by the \textit{PartDataManagementSetup} that is derived from \textit{DatManagementSetup} embedded in the library \textit{Networking} removed from the diagram for the sake of simplicity.
+\ref*{figure4.ImplementationArchitecture}) the \textit{Consumer} role has been realized by the \textit{PartDataManagementSetup} that is derived from \textit{DatManagementSetup} embedded in the library \textit{Networking} removed from this diagram for the sake of simplicity.
 It is a basic step for implementation of the \textit{Consumer} role functionality.
@@
       \item \textit{PartBindingFactory} - to gather the data recovered from the \textit{Message} instances pulled from the wire
-      \item \textit{CommunicationContext} - to handling communication with the Azure services
+      \item \textit{CommunicationContext} - to handle communication with the Azure services
 \end{enumerate}
@@
 In this case, the implementation of the \textit{IConfigurationFactory} interface is based entirely on the \textit{Networking} library.
-In this scenario, this implementation should not be considered for further modification.
+The implementation provided by the library is generic, but it is flexible enough to meet all the requirements in this case and should not be considered for further modification.
 It is ready to provide all necessary configuration parameters to establish semantic and security contexts related to Azure interoperability.
@@
 \textit{IEncodingFactory} and \textit{IMessageHandlerFactory} interfaces (Fig.
-\ref*{figure2.UADataApplicationArchitecture} have been implemented in independent libraries and ae not considered for any modifications to deploy \textit{Embedded Gateway} functionality.
-The current implementation of the mentioned interfaces is localized at run time as services using an instance of the \textit{IServiceLocator}.
-In this example, it is assumed that \textit{IServiceLocator} \footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} } is implemented to resolve references to any external services.
+\ref*{figure2.UADataApplicationArchitecture}) have been implemented in independent libraries and ae not considered for any modifications to deploy \textit{Embedded Gateway} functionality.
+The current implementation of the mentioned interfaces is localized at run time as services using an instance of the \textit{IServiceLocator}\footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} }.
+In this example, it is assumed that \textit{IServiceLocator} is implemented to resolve references to any external services.
 Both interfaces are used to manage interconnection of the node with the \textit{Cyber-physical Network}.
@@
 The Azure uses JSON based Data Transfer Object encoding and schema defined based on the solution metadata.
-The pubsub uses json and binary Data Transfer Object encoding.
+The pubsub uses JSON and binary Data Transfer Object encoding.
 In any case the data recovered from the Message pulled from a subscription is stored locally using the object model based on standard .NET types.
@@
 
-The encoded JSON messages must be transferred over the network to Azure using selected protocol stock.
+The encoded JSON messages must be transferred over the network to Azure using the selected protocol stack.
 The Azure supports the HTTP, AMQP, MQTT (Sec.
@@
 Consequently, it is possible to apply any available implementation compliant with an appropriate specification to achieve connectivity.
-In this case, all parameters required to establish connectivity and security-context is up to the external software responsibility.
-Alternatively, the API offered by the dedicated libraries may be used.
-Using this API the configuration process may be reduced significantly.
-Using these libraries, the selection of the communication protocol has an indirect impact on the interoperability features, including performance.
-In the proposed gateway implementation the Azure interconnection has been obtained using the following \textit{Microsoft.Azure} libraries:
+In this case, all parameters required to establish semantic and security contexts are up to the gateway responsibility.
+Alternatively, the API offered by the dedicated frameworks (libraries) may be used.
+Using a framework the configuration process may be reduced significantly, and the communication protocol selection has an indirect impact only on the interoperability features.
+In the proposed gateway implementation the Azure interconnection has been obtained using the following \textit{Microsoft.Azure} packages:
 
@@
 Azure and PubSub uses different security mechanism so in the proposed solution establishing security context is realized independently.
-The \textit{CommunicationContext} is responsible to establish this context as an embedded negotiation phase closely coupled with the establishing interconnection.
+The \textit{CommunicationContext} is responsible to establish this context as an embedded negotiation phase tightly coupled with establishing interconnection.
 In this interconnection the following steps are distinguished:
@@
             \end{itemize}
-      \item Interconnection - exchange of data
+      \item Data exchange
       \item Communication maintenance
@@
 
-\section{Conclusion}\label{section.conclusion}
+\section{Conclusion (TBD)}\label{section.conclusion}
 

### 2020-11-25 Latex/Manuscript.tex
Update Manuscript.tex

@@
 In the final deployment architecture (Fig.
-\ref*{figure4.ImplementationArchitecture}) the \textit{Consumer} role has been realized by the \textit{PartDataManagementSetup} that is derived from \textit{DatManagementSetup} embedded in the library \textit{Networking} removed from this diagram for the sake of simplicity.
-It is a basic step for implementation of the \textit{Consumer} role functionality.
-The class \textit{PartDataManagementSetup} initializes all properties, which are injection points of all parts composing this role.
-It extents functionality of the \textit{DatManagementSetup} based on the following associated classes
+\ref*{figure4.ImplementationArchitecture}) the \textit{Consumer} role has been realized by the \textit{PartDataManagementSetup} that is derived from \textit{DataManagementSetup} embedded in the library.
+\textit{Networking} was removed from this diagram for the sake of simplicity.
+Invoking \textit{PartDataManagementSetup} is the first step for bootstrapping the \textit{Consumer} role functionality.
+This class initializes all properties, which are injection points of all parts composing this role.
+It extents functionality of the \textit{DataManagementSetup} based on the following associated classes:
 
@@
 In this case, the implementation of the \textit{IConfigurationFactory} interface is based entirely on the \textit{Networking} library.
-The implementation provided by the library is generic, but it is flexible enough to meet all the requirements in this case and should not be considered for further modification.
+The implementation provided by the library is generic, but it is flexible enough to meet all the requirements which warrants no need of further modifications.
 It is ready to provide all necessary configuration parameters to establish semantic and security contexts related to Azure interoperability.
@@
       \item \textit{Devices} - Service SDK for Azure IoT Devices
-      \item \textit{Devices.Client} - Device SDK for Azure \textit{IoT\ Hub}
+      \item \textit{Devices.Client} - Device SDK for Azure \textit{IoT\ Hub} including dependencies implementing MQTT and AMQP communication
       \item \textit{Devices.Shared} - Common code for Azure IoT Device and Service SDK

### 2020-11-26 Latex/Manuscript.tex
Work out Markdown\60.GatewayImplementation.md #35
- fixed reported errors. Item 5 must be additional disused

@@
 \headauthor{Postół M, Szymczak P, Vasters C}
-\affiliation{%
+\affiliation
+{
  \inst{1}Lodz University of Technology\\
@@
  Postal Address with the zip-code\\
- clemensv@microsoft.com}
+ clemensv@microsoft.com
+}
 
@@
 A software development kits for C\#, Java, PHP, and Ruby are available for custom applications.
-Azure provides services supporting data exchange over the OPC UA, but they don't support pubsub compliant with the OPC UA Part-14.
+Azure provides services supporting data exchange over the OPC UA, but they don't support PubSub compliant with the OPC UA Part-14.
 Connectivity services on the network use JSON-based Data Transfer Object encoded based on schema derived from the solution metadata.
@@
 According to proposed architecture (Fig.~\ref*{figure1.StrategyDomainModel}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ Node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
-Additionally it must be assumed that the library used to deploy \textit{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/pubsub gateway functionality.
+Additionally it must be assumed that the library used to deploy \textit{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/PubSub gateway functionality.
 The composition process must be available without modification of the core code of an existing library.
@@
 
-The following subsections cover the description of the current state of technologies with regards to Azure cloud-based IoT enabler and OPC UA pubsub.
+The following subsections cover the description of the current state of technologies with regards to Azure cloud-based IoT enabler and OPC UA PubSub.
 Sect.~\ref*{azure-main-technology-features} analyzes data presentation user interface, available native communication services, and data/metadata model offered by the Microsoft Azure.
@@
 \begin{itemize}
-      \item \textbf{separation of concerns} - to allow an independent development of the parts~\cite{RefWorks:doc:5d92609be4b02eb43d372bd1},
-      \item \textbf{dependency injection} - to allow late binding of separately implemented parts~\cite{RefWorks:doc:5d925b77e4b030b4e0596f5d}.
+      \item \textbf{separation of concerns} - to allow an independent development of the parts~\cite{RefWorks:doc:5d92609be4b02eb43d372bd1}
+      \item \textbf{dependency injection} - to allow late binding of separately implemented parts~\cite{RefWorks:doc:5d925b77e4b030b4e0596f5d}
 \end{itemize}
@@
 The composition is accomplished at run time, and the effective application functionality depends essentially on reusable loosely coupled parts composed applying the dependency injection software engineering and adaptive programming concept.
+
 \todo{cite{RefWorks:doc:5d9796cbe4b0f66c52dccf04}}
@@
 \ref*{figure3.ImplementationDomainModel}.
-In the proposed approach the \textit{Embedded Gateway} is derived from the \textit{Consumer} role embedded as as a composable part aggregated by the \textit{Reactive Application}.
+In the proposed approach the \textit{Embedded Gateway} is derived from the \textit{Consumer} role implemented as as a composable part aggregated by the \textit{Reactive Application}.
 
@@
 
+\hyphenation{PartData-Mana-gement-Setup}
+
 In the final deployment architecture (Fig.
-\ref*{figure4.ImplementationArchitecture}) the \textit{Consumer} role has been realized by the \textit{PartDataManagementSetup} that is derived from \textit{DataManagementSetup} embedded in the library.
+\ref*{figure4.ImplementationArchitecture}) the \textit{Consumer} role has been realized by the \textit{PartDataManagementSetup} that is derived from \textit{DataManagementSetup} provided by the library.
 \textit{Networking} was removed from this diagram for the sake of simplicity.
-Invoking \textit{PartDataManagementSetup} is the first step for bootstrapping the \textit{Consumer} role functionality.
+Instantiating \textit{PartDataManagementSetup} is the first step for bootstrapping process of the \textit{Consumer} role functionality.
 This class initializes all properties, which are injection points of all parts composing this role.
@@
 
+\todo{Overfull}
+
 \begin{figure}
       \centering
-      \includegraphics[width=\textwidth]{../.Media/ImplementationArchitecture.png}
+      \includegraphics[width=10cm]{../.Media/ImplementationArchitecture.png}
       \caption{Implementation Architecture}\label{figure4.ImplementationArchitecture}
@@
 The Azure uses JSON based Data Transfer Object encoding and schema defined based on the solution metadata.
-The pubsub uses JSON and binary Data Transfer Object encoding.
+The PubSub uses JSON and binary Data Transfer Object encodings.
 In any case the data recovered from the Message pulled from a subscription is stored locally using the object model based on standard .NET types.
@@
 Alternatively, the API offered by the dedicated frameworks (libraries) may be used.
-Using a framework the configuration process may be reduced significantly, and the communication protocol selection has an indirect impact only on the interoperability features.
+Using a framework the configuration process may be reduced significantly, and the communication protocol selection has only an indirect impact on the interoperability features.
 In the proposed gateway implementation the Azure interconnection has been obtained using the following \textit{Microsoft.Azure} packages:
@@
 The \textit{CommunicationContext} is responsible to establish this context as an embedded negotiation phase tightly coupled with establishing interconnection.
+
+\todo{consider removing}
+
 In this interconnection the following steps are distinguished:

### 2020-11-26 Latex/Manuscript.tex
Work out Markdown\70.Conclusion.md #36
- started working on
- reviewed text to select conclusions.
- improved text

@@
 \begin{itemize}
-      \item  Human Machine Interface (HNI)
+      \item  Human Machine Interface (HMI)
       \item Supervisory Control and Data Acquisition (SCADA)
@@
 
-Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} cyber-physical system (CPS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios:
-
-\begin{itemize}
-      \item \textbf{direct interconnection} - cloud-based dedicated communication services allow to attache it to the CPS making up a consistent M2M communication network using an in-bound protocol stack
-      \item \textbf{gateway based interconnection} - typical build-in communication services allows to attache the cloud computing to the CPS using an out-of-bound protocol stack
-\end{itemize}
+Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} cyber-physical system (CPS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct interconnection} or \textbf{gateway based interconnection} (Sect.
+\ref*{subs.architecture}).
 
@@
 
-As it was explained in Sect.~\ref*{introduction}, to follow the Industry 4.0 concept a hybrid environment integrating reactive Machine to Machine interconnection and interactive web-based user interface is required (\ref*{introduction}).
+As it was explained in Sect.~\ref*{introduction}, to follow the Industry 4.0 concept a hybrid environment integrating reactive Machine to Machine interconnection and interactive web-based user interface is required (Sect.
+\ref*{introduction}).
 The main challenge of the solution in concern is to design a generic but reusable architecture that addresses interoperability of these diverse interconnection scenarios ruled by different requirements, namely
@@
 In practice, the set of assets embedded in the CPS is very stable.
-On the another hand, the virtualization of services means that they must be very flexible to handle the attachment of new assets proactively (acting in advance) at run time.
+On the other hand, the virtualization of cloud services means that they must be very flexible to handle the attachment of new assets proactively (acting in advance) at run time.
 As a result, by design, the cloud services must be repressible to register and authenticate devices exposing endpoints in the public network to allows the device to access a provisioning cloud service.
@@
 
-\textbf{Edge device} is a device that connects directly to the cloud services but acts as an intermediary for other devices called leaf devices.
+\textbf{Edge device} connects directly to the cloud services but acts as an intermediary for other devices called leaf devices.
 Additionally, it allows the selection of initial data processing and execution of them using local resources.
@@
 The \textbf{embedded gateway} archetype relaxes most of the issues described above: \textit{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security-context differences to name only a few.
-The main goal of this article is to provide proof that the \textbf{embedded gateway} archetype implementation is possible based on a generic subs.architecture that can be used as a foundation for the integration of the heterogenous environments in concern.
+The main goal of this article is to provide proof that the \textbf{embedded gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogenous environments in concern.
 The proposed implementation is designed for selected interoperability standard and cloud product.
@@
 For this study, prototyping addresses Microsoft Azure cloud products.
-There are many reasons for selecting Azure to accomplish cloud-based front-end of Cyber-Physical System (CPS).
+There are many reasons for selecting Azure to accomplish the cloud-based front-end of Cyber-Physical System (CPS).
 Azure offers Infrastructure as a Service (IaaS) and Platform as a Service (PaaS) capabilities.
@@
 Solutions hosted on Azure are scaled up to millions of users without any additional coding.
-For the development of the CPS front-end, it is essential that Azure provides very efficient storage services usefully for real-time process data archival.
+For the development of the CPS front-end, it is essential that Azure provides very efficient storage services usefully for the purpose of real-time process data archival.
 Azure provides a vast variety of hybrid connections including but not limited to virtual private networks (VPNs), caches, content delivery networks (CDNs), ExpressRoute, and IoT dedicated services that can be directly used to implement cloud-based front-end for CPS.
@@
 A software development kits for C\#, Java, PHP, and Ruby are available for custom applications.
-Azure provides services supporting data exchange over the OPC UA, but they don't support PubSub compliant with the OPC UA Part-14.
+Azure provides services supporting data exchange over the OPC UA, but they don't support PubSub compliant with the OPC UA Part-14\cite{RefWorks:doc:5d98837de4b055984c0eecf0}.
 Connectivity services on the network use JSON-based Data Transfer Object encoded based on schema derived from the solution metadata.
@@
 Based on the sessionless and session-oriented communication patterns examination against the IoT requirements \cite{mpostol2020} it could be concluded that the connectionless pattern better suites issues related to the assets mobility and traffic asymmetry that is characteristic for the application domains in concern.
-Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub spec \cite{RefWorks:doc:5d98837de4b055984c0eecf0}.
+Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} specification.
 According to proposed architecture (Fig.~\ref*{figure1.StrategyDomainModel}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ Node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
-Additionally it must be assumed that the library used to deploy \textit{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/PubSub gateway functionality.
+Additionally, it must be assumed that the library used to deploy \textit{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/PubSub gateway functionality.
 The composition process must be available without modification of the core code of an existing library.
-As a result the prototyping is to be limited to implementation of the \textit{Embedded\ Gateway} software part only.
+As a result, the prototyping is to be limited to implementation of the \textit{Embedded\ Gateway} software part only.
 
@@
 
-Following the assumption that interconnection between the cyber-physical system and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler.
+Following the assumption that interconnection between the Cyber-Physical System (CPS) and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler.
 It must be interconnected with the (CPS) using an in-band protocol adhering to communications requirements (i.e.~protocol profile, data encoding, time relationships, etc.) governing communication of the parts making it up.
@@
 \ref*{introduction}) concept.
-A framework compliant with this requirements has been implemented as an open-source library named \textit{UAOOI.Networking.SemanticData} (SDK) under an umbrella of the project Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.
+A framework compliant with these requirements has been implemented as an open-source library named \textit{UAOOI.Networking} (\textit{Networking} for short) under an umbrella of the project Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.
 The library is designed to be a foundation for developing application programs that are taking part in a message-centric communication pattern and interconnected using the reactive networking concept.
-The diagram in Fig.~\ref*{figure2.UADataApplicationArchitecture} shows the relationship between the library \textit{SDK} and external parts composing any reactive networking application (\textit{Reactive\ Application}).
-The \textit{Reactive Application} is an aggregation of \textit{Producer} and \textit{Consumer} parts.
-They must support access to real-time process data, hence they are recognized as an extension of \textit{DataRepository} class.
+The diagram in Fig.~\ref*{figure2.UADataApplicationArchitecture} shows the relationship between the library (\textit{SDK}) and external parts composing any reactive networking application (\textit{Reactive\ Application}).
+The \textit{Reactive Application} is an aggregation of parts implementing the \textit{Producer} and \textit{Consumer} roles.
+By design, they support access to real-time process data, hence they are recognized as an extension of \textit{DataRepository} class.
 To implement the \textit{DataRepository} dedicated implementation of the \textit{IBinding} interface should be provided to create a bridge between CPS and an external row data represented by the \textit{LocalResources} class.
@@
 \begin{itemize}
-      \item \emph{IBindingFactory} - bidirectional data exchange with the underlying process,
-      \item \emph{IConfigurationDataFactory} - the configuration data access,
-      \item \emph{IMessageHandlerFactory} - pushing the \emph{Message} entities to/pulling from the wire,
-      \item \emph{IEncodingFactory} - searching a dictionary containing value converters.
+      \item \emph{IBindingFactory} - bidirectional data exchange with the underlying process
+      \item \emph{IConfigurationDataFactory} - the configuration data access
+      \item \emph{IMessageHandlerFactory} - \emph{Message} entities pushing to/pulling from the wire 
+      \item \emph{IEncodingFactory} - searching a dictionary containing value converters
 \end{itemize}
@@
 
-\todo{cite{RefWorks:doc:5d9796cbe4b0f66c52dccf04}}
+\todo{ cite{RefWorks:doc:5d9796cbe4b0f66c52dccf04} }
+
+\todo{convert textit => emph}
 
@@
 raw data (e.g.
-PLC internal registers), OPC UA Address Space Management, cloud, file, database, graphical user interface.
+PLC internal registers), OPC UA Address Space Management, cloud, file, database, graphical user interface, to name only a few.
 
@@
 \ref*{figure4.ImplementationArchitecture}) the \textit{Consumer} role has been realized by the \textit{PartDataManagementSetup} that is derived from \textit{DataManagementSetup} provided by the library.
-\textit{Networking} was removed from this diagram for the sake of simplicity.
+\textit{Networking} (SDK) was removed from this diagram for the sake of simplicity.
 Instantiating \textit{PartDataManagementSetup} is the first step for bootstrapping process of the \textit{Consumer} role functionality.
-This class initializes all properties, which are injection points of all parts composing this role.
+This class provides an entry point to initialize all properties, which are injection points of all parts composing this role.
 It extents functionality of the \textit{DataManagementSetup} based on the following associated classes:
@@
 In this case, the implementation of the \textit{IConfigurationFactory} interface is based entirely on the \textit{Networking} library.
-The implementation provided by the library is generic, but it is flexible enough to meet all the requirements which warrants no need of further modifications.
+The implementation provided by the library is generic, but it is flexible enough to meet all the requirements, which warrants no need for further modifications for adoption.
 It is ready to provide all necessary configuration parameters to establish semantic and security contexts related to Azure interoperability.
@@
 
-Azure and PubSub uses different security mechanism so in the proposed solution establishing security context is realized independently.
+Azure and PubSub uses different security mechanism so in the proposed solution establishing security-context is realized independently.
 The \textit{CommunicationContext} is responsible to establish this context as an embedded negotiation phase tightly coupled with establishing interconnection.
@@
 
+In this case, multi-vendor integration makes communication standardization especially important, namely it is required that the payload of the message is standardized to be factored on the data  gathering site and consumed on the ultimate destination site.
+
+If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship could relax the problems encountered while the interactive approach is applied.
+
+By design, the direct approach requires that the cloud has to be compliant with the interoperability standard the CPS is built upon - it becomes a consistent part of the CPS.
+Data models, roles, and responsibility differences of both solutions make this approach impractical or even imposable to be applied in typical cases.
+
+The main goal of this article is to provide proof that:
+
+\begin{enumerate}
+      \item  reactive interoperability M2M communication based on the OPC UA standard can be implemented as a powerful standalone library without dependency on the Client/Server session-oriented archetype
+      \item Azure interoperability can be implemented as an external part employing out-of-band communication without dependency on the OPC UA implementation
+      \item the proposed generic architecture allows that the gateway functionality is implemented as composable part at run-time part - no programming required
+\end{enumerate}
+
+The possibility to establish a common semantic-context in the multi-vendor environment makes communication standardization especially important.
+
+Unlike the above described solutions, the \textbf{embedded gateway} is not derived from the middleware concept.
+
 The Azure supports the HTTP, AMQP, MQTT (Sec.
@@
 
+Based on the sessionless and session-oriented communication patterns examination against the IoT requirements \cite{mpostol2020} it could be concluded that the connectionless pattern better suites issues related to the assets mobility and traffic asymmetry that is characteristic for the application domains in concern.
+
 It is worth stressing that based on this approach only dedicated functionality related to communication with the cloud must be implemented. This way, the reusability of the library is promoted.
@@
 This solution is in contrast to to the architecture presented in OPC UA Part 1 and Part 14.
+
+Concluding, decoupling of this functionality implementation using an abstract contract and late binding mechanism allows:
+
+\begin{itemize}
+      \item implementation of practically any configuration management scenario,
+      \item modification of this functionality later after releasing the library or deploying the application program in the production environment.
+\end{itemize}
+
+From the above discussion, we can learn that the main design decisions must concern standardization and flexibility.
+Standardization needs the selection of an international interoperability specification to make the library ready to be adopted by the multi-vendor environment.
+Flexibility requires an architecture that promotes the polymorphic independent implementation of essential functions.
 

### 2020-11-28 Latex/Manuscript.tex
Work out Markdown\70.Conclusion.md #36
- added and formatted the text
- ready to final review

@@
 Internet is a demanding environment for highly distributed process control applications designed atop the M2M communication paradigm because
+
 \begin{itemize}
@@
 The new architecture is proposed for integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end.
-To support the multi-vendor environment OPC Unified Architecture interoperability standard has been selected.
+To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected.
 The proposals are backed by proof of concept reference implementations.
@@
       \includegraphics[width=8cm]{../.Media/StrategyDomainModel.png}
-      \caption{Concept Domain Model}\label{figure1.StrategyDomainModel}
+      \caption{Domain model of a generic interconnection concept}\label{figure1.StrategyDomainModel}
 \end{figure}
@@
 Unlike the above described solutions, the \textbf{embedded gateway} is not derived from the middleware concept.
-The domain model for this archetype is presented in the Fig.~\ref*{figure1.StrategyDomainModel}.
+A generic domain model for this interconnection is presented in the Fig.~\ref*{figure1.StrategyDomainModel}.
 Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \textit{Networking} service of the \textit{Cyber-physical\ node}.
@@
 Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} specification.
-According to proposed architecture (Fig.~\ref*{figure1.StrategyDomainModel}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ Node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
+According to proposed generic architecture (Fig.~\ref*{figure1.StrategyDomainModel}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ Node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
 Additionally, it must be assumed that the library used to deploy \textit{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/PubSub gateway functionality.
@@
 
-A generic domain model presenting relationship between the Azure \textit{Cloud-based\ Front-end} and \textit{Cyber-physical\ node} attached to the \textit{Cyber-physical\ network} is presented in Fig.
+A generic domain model presenting interconnection architecture between the Azure \textit{Cloud-based\ Front-end} and \textit{Cyber-physical\ node} attached to the \textit{Cyber-physical\ network} is presented in Fig.
 \ref*{figure1.StrategyDomainModel}.
@@
 
-\todo{consider removing}
+\section{Conclusion}\label{section.conclusion}
 
-In this interconnection the following steps are distinguished:
+Nowadays, the macro optimization of the industrial processes requires an integration of a vast variety of new distributed applications provided by the Information and Communication Technology over and over.
+It requires further research on the integration of \textbf{machine-centric} Cyber-Physical Systems(CPS) with \textbf{human-centric} front-end in the context of new emerging disciplines, i.e.
+Industry 4.0 (I4.0) and the Internet of Things (IoT) (Sect.
+\ref*{introduction}).
 
-\begin{itemize}
-      \item Gateway and devices registration
-      \item Authentication
-      \item Device/Service association
-      \item Device/Application association
-      \item Establishing session
-            \begin{itemize}
-                  \item Device/Device Template (Device Capability Model) association - establishing a semantic-context
-                  \item Security management - establishing security-context
-            \end{itemize}
-      \item Data exchange
-      \item Communication maintenance
-\end{itemize}
+Cyber-Physical Systems (CPS) are composed using the multi-vendor components interconnected atop of the Machine To Machine (M2M) communication.
+In many applications, the dynamic nature of the CPS must be considered.
+Dynamic nature means that interconnected assets may be added/removed from the network at any time.
+Typically, by design, CPS must fulfill the real-time and assets mobility requirements.
 
-\section{Conclusion (TBD)}\label{section.conclusion}
+Highly-distributed solutions used to control/monitor a set of geographically spread islands of automation (e.g.~virtual power plants producing renewable energy) additionally must leverage public communication infrastructure, namely the Internet.
+If islands of automation must be controlled over the Internet, the cloud computing concept may be recognized as a reasonable answer.
+Following this concept, the cloud-based supervisory control functionality is applied as a set of services employing abstraction and virtualization - two main pillars of the cloud computing paradigm.
+In the cloud computing concept, virtualization is recognized as the possibility to share the services by many users, and abstraction hides implementation details.
 
-In this case, multi-vendor integration makes communication standardization especially important, namely it is required that the payload of the message is standardized to be factored on the data  gathering site and consumed on the ultimate destination site.
+This paper has presented a new generic architecture applicable for the integration of the \textbf{machine-centric} CPS and emerging cloud computing as a \textbf{human-centric} front-end.
 
-If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship could relax the problems encountered while the interactive approach is applied.
-
-By design, the direct approach requires that the cloud has to be compliant with the interoperability standard the CPS is built upon - it becomes a consistent part of the CPS.
-Data models, roles, and responsibility differences of both solutions make this approach impractical or even imposable to be applied in typical cases.
-
-The main goal of this article is to provide proof that:
-
-\begin{enumerate}
-      \item  reactive interoperability M2M communication based on the OPC UA standard can be implemented as a powerful standalone library without dependency on the Client/Server session-oriented archetype
-      \item Azure interoperability can be implemented as an external part employing out-of-band communication without dependency on the OPC UA implementation
-      \item the proposed generic architecture allows that the gateway functionality is implemented as composable part at run-time part - no programming required
-\end{enumerate}
-
-The possibility to establish a common semantic-context in the multi-vendor environment makes communication standardization especially important.
-
-Unlike the above described solutions, the \textbf{embedded gateway} is not derived from the middleware concept.
-
-The Azure supports the HTTP, AMQP, MQTT (Sec.
-\ref*{azure-main-technology-features}).
-On the other hand the PubSub supports Ethernet, UDP, AMQP, MQTT {Sect.
-\ref*{ooi-main-technology-features}}.
-Sets of supported protocol are not overlapping.
-If the Ethernet or UDP has been selected to build PubSub interconnection the direc interoperability between the Azure and PubSub is impossible because the mentioned protocols are not offered as the native communication services.
-In this case only indirect interconnection is available.
-
+If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship\cite{mpostol2020} could relax the problems encountered while the interactive approach is applied.
+The real-time multi-vendor environment makes communication standardization especially important.
+To support this environment OPC Unified Architecture \cite{RefWorks:doc:5ac86c98e4b009947bbb874c} interoperability standard has been selected.
 As it was pointed out in the Sect.
-\ref*{subs.architecture} using OPC UA PubSub the aggregation of nodes by the network is loosely coupled, i.e.
+\ref*{subs.architecture} using OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} the aggregation of nodes by the network is loosely coupled, i.e.
 nodes can be added and removed from the network dynamically, and nodes may represent mobile data holding assets.
 
-Based on the sessionless and session-oriented communication patterns examination against the IoT requirements \cite{mpostol2020} it could be concluded that the connectionless pattern better suites issues related to the assets mobility and traffic asymmetry that is characteristic for the application domains in concern.
+From the analysis covered by the Sect.
+\ref*{subs.architecture} it is concluded that the \textbf{embedded gateway} archetype best suits all requirements described above.
+It relaxes most of the issues related to \textbf{direct interconnection} and solutions inferred from the middleware concept, i.e.
+real-time behavior, data encoding incompatibility, security-context differences, to name only a few.
+The generic domain model for the proposed interconnection archetype is presented in the Fig.~\ref*{figure1.StrategyDomainModel}.
+We have highlighted that to promote the separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \textit{Networking} service of the \textit{Cyber-physical\ node}.
+Main functionality of this component is to transfer selected data between \textit{Cyber-physical\ network} using \textit{Networking} services of an existing \textit{Cyber-physical\ node} and \textit{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
 
-It is worth stressing that based on this approach only dedicated functionality related to communication with the cloud must be implemented. This way, the reusability of the library is promoted.
+To promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub (Sect.
+\ref*{subs.architecture}) and support the \emph{Reactive Interoperability} (Sect.
+\ref*{introduction}) concept.
+We proposed to use an open-source library named \textit{UAOOI.Networking} (\textit{Networking} for short) (Fig.~\ref*{figure2.UADataApplicationArchitecture}) for this purpose.
+It is worth stressing that based on this approach only dedicated functionality related to the communication with the cloud must be implemented.
 
-The OPC UA PubSub to Azure gateway (\textit{AzureGateway}) implementation has been just published on GitHub as the open-source (MIT licensed) as a part of the more general concept of the Object-Oriented Internet reactive networking.
-It is proof of the concept that
+We derived the final model presented in Fig.
+\ref*{figure3.ImplementationDomainModel} by merging selected entities from the library (Fig.~\ref*{figure2.UADataApplicationArchitecture}) into the generic interconnection domain model (Fig.
+\ref*{figure1.StrategyDomainModel}).
+In the proposed approach the \textit{Embedded Gateway} is derived from the \textit{Consumer} role implemented as as a composable part aggregated by the \textit{Reactive Application}.
 
-The propose architecture enable possibility to interconnect the cloud-based services with the Cyber-physical network.
-This solution is in contrast to to the architecture presented in OPC UA Part 1 and Part 14.
+The proposals are backed by proof of concept reference implementations.
+Prototyping addresses Microsoft Azure Cloud as an example.
+The prototyping outcome has been just published on GitHub as the open-source (MIT licensed).
+The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.
 
-Concluding, decoupling of this functionality implementation using an abstract contract and late binding mechanism allows:
+The described results proves that the \textbf{embedded gateway} archetype implementation is possible based on existing standalone framework supporting reactive interoperability atop of the M2M communication compliant with the OPC UA PubSub standard.
+It is worth stressing that there are no dependency on the Client/Server session-oriented relationship.
+It is in contrast to architecture described in the OPC UA Part 1 specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server.
+In the proposed solution the Azure interoperability is obtained by implementation only a dedicated part employing out-of-band communication without dependency on the OPC UA implementation.
+It is worth stressing that the gateway functionality is implemented as composable without programming skills part.
+Because the part is composed at run-time it makes possible to modify its functionality later after releasing the library or deploying the application program in the production environment.
 
-\begin{itemize}
-      \item implementation of practically any configuration management scenario,
-      \item modification of this functionality later after releasing the library or deploying the application program in the production environment.
-\end{itemize}
-
-From the above discussion, we can learn that the main design decisions must concern standardization and flexibility.
-Standardization needs the selection of an international interoperability specification to make the library ready to be adopted by the multi-vendor environment.
-Flexibility requires an architecture that promotes the polymorphic independent implementation of essential functions.
-
-\begin{enumerate}
-      \item OPC UA PubSub can be implemented as a powerful standalone package - no C/S dependency
-      \item Azure interoperability can be implemented as an out-of-band communication (MQTT, AMQP, HTTP) - no PubSub dependency
-      \item Process data functionality can be composable at run-time - no programming required
-\end{enumerate}
+Concluding, it is proof of the concept that applying the proposed architecture and implementation scenario it is possible to interconnect selected cloud services (e.g.
+textit{Azure\  Industrial\ IoT}) with the Cyber-physical Network interconnected as one whole atop of the OPC UA PubSub.
+It is in contrast to interconnecting cloud services with the selected \emph{ Address\ Space} exposed by a selected OPC UA server limiting the PubSub role to data export out of the OPC UA ecosystem functionality.
 

### 2020-11-28 Latex/Manuscript.tex
Work out Markdown\70.Conclusion.md #36
- reviewed - first attempt.

@@
 
-Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} cyber-physical system (CPS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct interconnection} or \textbf{gateway based interconnection} (Sect.
+Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical System (CPS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct interconnection} or \textbf{gateway based interconnection} (Sect.
 \ref*{subs.architecture}).
@@
 
-In practice, the set of assets embedded in the CPS is very stable.
-On the other hand, the virtualization of cloud services means that they must be very flexible to handle the attachment of new assets proactively (acting in advance) at run time.
+The virtualization of cloud services means that they must be very flexible to handle the attachment of new assets proactively (acting in advance) at run time.
 As a result, by design, the cloud services must be repressible to register and authenticate devices exposing endpoints in the public network to allows the device to access a provisioning cloud service.
@@
 Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical Systems (CPS) designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end requires decisions addressing the selection of the services supporting web user interface capable to expose process data.
-In this context, the service is any autonomous (with own identity) software component or module that is interfacing with selected (CPS) for data collection, analysis, and also remote control.
+In this context, the service is any autonomous (with own identity) software component or module that is interfacing with selected CPS for data collection, analysis, and also remote control.
 Microsoft Azure is a cloud-based product.
@@
 
-Following the assumption that interconnection between the Cyber-Physical System (CPS) and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler.
-It must be interconnected with the (CPS) using an in-band protocol adhering to communications requirements (i.e.~protocol profile, data encoding, time relationships, etc.) governing communication of the parts making it up.
+Following the assumption that interconnection between the CPS and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler.
+It must be interconnected with the CPS using an in-band protocol adhering to communications requirements (i.e.~protocol profile, data encoding, time relationships, etc.) governing communication of the parts making it up.
 At the same time, it must support back-and-forth data transfer to the cloud using out-of-band native for the cloud services.
@@
 
-Nowadays, the macro optimization of the industrial processes requires an integration of a vast variety of new distributed applications provided by the Information and Communication Technology over and over.
+Nowadays, the macro optimization of the industrial processes requires an integration of a vast variety of distributed applications provided by the Information and Communication Technology.
 It requires further research on the integration of \textbf{machine-centric} Cyber-Physical Systems(CPS) with \textbf{human-centric} front-end in the context of new emerging disciplines, i.e.
@@
 
-Cyber-Physical Systems (CPS) are composed using the multi-vendor components interconnected atop of the Machine To Machine (M2M) communication.
+CPS is composed using the multi-vendor components interconnected atop of the Machine To Machine (M2M) communication.
 In many applications, the dynamic nature of the CPS must be considered.
 Dynamic nature means that interconnected assets may be added/removed from the network at any time.
-Typically, by design, CPS must fulfill the real-time and assets mobility requirements.
+By design, CPS typically must fulfill the real-time and assets mobility requirements.
 
-Highly-distributed solutions used to control/monitor a set of geographically spread islands of automation (e.g.~virtual power plants producing renewable energy) additionally must leverage public communication infrastructure, namely the Internet.
+Highly-distributed solutions used to control/monitor a set of geographically spread islands of automation (e.g.
+virtual power plants producing renewable energy) additionally must leverage public communication infrastructure, namely the Internet.
 If islands of automation must be controlled over the Internet, the cloud computing concept may be recognized as a reasonable answer.
@@
 The real-time multi-vendor environment makes communication standardization especially important.
-To support this environment OPC Unified Architecture \cite{RefWorks:doc:5ac86c98e4b009947bbb874c} interoperability standard has been selected.
+To support this environment, OPC Unified Architecture \cite{RefWorks:doc:5ac86c98e4b009947bbb874c} interoperability standard has been selected.
 As it was pointed out in the Sect.
@@
 It relaxes most of the issues related to \textbf{direct interconnection} and solutions inferred from the middleware concept, i.e.
-real-time behavior, data encoding incompatibility, security-context differences, to name only a few.
+\textbf{edge device} - remote cloud agent and \textbf{field level gateway} - a dedicated custom agent.
 The generic domain model for the proposed interconnection archetype is presented in the Fig.~\ref*{figure1.StrategyDomainModel}.
-We have highlighted that to promote the separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \textit{Networking} service of the \textit{Cyber-physical\ node}.
-Main functionality of this component is to transfer selected data between \textit{Cyber-physical\ network} using \textit{Networking} services of an existing \textit{Cyber-physical\ node} and \textit{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
+We have highlighted that to promote the separation of concern design principle, the gateway functionality should be implemented as a self-contained dedicated software part embedded in the core \textit{Networking} service of the \textit{Cyber-physical\ node}.
+Main functionality of this component is to transfer process data between \textit{Cyber-physical\ network} using \textit{Networking} services of an existing \textit{Cyber-physical\ node} and \textit{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
 
@@
 \ref*{introduction}) concept.
-We proposed to use an open-source library named \textit{UAOOI.Networking} (\textit{Networking} for short) (Fig.~\ref*{figure2.UADataApplicationArchitecture}) for this purpose.
+We proposed to use an open-source library named \textit{emph.Networking} (\emph{Networking} for short) (Fig.~\ref*{figure2.UADataApplicationArchitecture}) for this purpose.
 It is worth stressing that based on this approach only dedicated functionality related to the communication with the cloud must be implemented.
@@
 We derived the final model presented in Fig.
-\ref*{figure3.ImplementationDomainModel} by merging selected entities from the library (Fig.~\ref*{figure2.UADataApplicationArchitecture}) into the generic interconnection domain model (Fig.
+\ref*{figure3.ImplementationDomainModel} by merging selected entities from the \emph{Networking} library (Fig.~\ref*{figure2.UADataApplicationArchitecture}) into the generic interconnection domain model (Fig.
 \ref*{figure1.StrategyDomainModel}).
@@
 Prototyping addresses Microsoft Azure Cloud as an example.
-The prototyping outcome has been just published on GitHub as the open-source (MIT licensed).
+The prototyping outcome has been just published on GitHub as open-source (MIT licensed).
 The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.
 
-The described results proves that the \textbf{embedded gateway} archetype implementation is possible based on existing standalone framework supporting reactive interoperability atop of the M2M communication compliant with the OPC UA PubSub standard.
-It is worth stressing that there are no dependency on the Client/Server session-oriented relationship.
-It is in contrast to architecture described in the OPC UA Part 1 specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server.
-In the proposed solution the Azure interoperability is obtained by implementation only a dedicated part employing out-of-band communication without dependency on the OPC UA implementation.
-It is worth stressing that the gateway functionality is implemented as composable without programming skills part.
-Because the part is composed at run-time it makes possible to modify its functionality later after releasing the library or deploying the application program in the production environment.
+The described results prove that the \textbf{embedded gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop of the M2M communication compliant with the OPC UA PubSub standard.
+It is worth stressing that there is no dependency on the Client/Server session-oriented relationship.
+It is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server.
+In the proposed approach the cloud interoperability is obtained by implementation only a dedicated part employing out-of-band communication without dependency on the OPC UA implementation.
+It is worth stressing that the gateway functionality is implemented as a part - composable to the whole without programming skills.
+Because the part is composed at run-time it makes it possible to modify its functionality later after releasing the library or deploying the application program in the production environment.
 
-Concluding, it is proof of the concept that applying the proposed architecture and implementation scenario it is possible to interconnect selected cloud services (e.g.
-textit{Azure\  Industrial\ IoT}) with the Cyber-physical Network interconnected as one whole atop of the OPC UA PubSub.
+Concluding, the paper describes a proof of the concept that applying the proposed architecture and implementation scenario it is possible to interconnect selected cloud services (e.g.
+\textbf{Azure\ Industrial\ IoT}) with the \emph{Cyber-physical network} interconnected as one whole atop of the OPC UA PubSub.
 It is in contrast to interconnecting cloud services with the selected \emph{ Address\ Space} exposed by a selected OPC UA server limiting the PubSub role to data export out of the OPC UA ecosystem functionality.

### 2020-11-29 Latex/Manuscript.tex
Work out Markdown\70.Conclusion.md #36
- fixes #36

@@
 Nowadays, the macro optimization of the industrial processes requires an integration of a vast variety of distributed applications provided by the Information and Communication Technology.
-It requires further research on the integration of \textbf{machine-centric} Cyber-Physical Systems(CPS) with \textbf{human-centric} front-end in the context of new emerging disciplines, i.e.
+It requires further research on the integration of \textbf{machine-centric} Cyber-Physical Systems (CPS) with \textbf{human-centric} front-end in the context of new emerging disciplines, i.e.
 Industry 4.0 (I4.0) and the Internet of Things (IoT) (Sect.
@@
 
-CPS is composed using the multi-vendor components interconnected atop of the Machine To Machine (M2M) communication.
+CPS is composed using the multi-vendor components (data holding assets) interconnected atop of the Machine To Machine (M2M) communication.
 In many applications, the dynamic nature of the CPS must be considered.
 Dynamic nature means that interconnected assets may be added/removed from the network at any time.
-By design, CPS typically must fulfill the real-time and assets mobility requirements.
+By design, typically CPS must fulfill the real-time and mobility of the assets requirements.
 
@@
 
-This paper has presented a new generic architecture applicable for the integration of the \textbf{machine-centric} CPS and emerging cloud computing as a \textbf{human-centric} front-end.
+The main goal of this research is working out a new generic architecture and deployment scenario applicable for the integration of the \textbf{machine-centric} CPS and emerging cloud computing as a \textbf{human-centric} front-end.
 
@@
 \ref*{introduction}) concept.
-We proposed to use an open-source library named \textit{emph.Networking} (\emph{Networking} for short) (Fig.~\ref*{figure2.UADataApplicationArchitecture}) for this purpose.
+We proposed to use an open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) (Fig.~\ref*{figure2.UADataApplicationArchitecture}) for this purpose.
 It is worth stressing that based on this approach only dedicated functionality related to the communication with the cloud must be implemented.
@@
 We derived the final model presented in Fig.
-\ref*{figure3.ImplementationDomainModel} by merging selected entities from the \emph{Networking} library (Fig.~\ref*{figure2.UADataApplicationArchitecture}) into the generic interconnection domain model (Fig.
+\ref*{figure4.ImplementationArchitecture} by merging selected entities from the \emph{Networking} library (Fig.~\ref*{figure2.UADataApplicationArchitecture}) into the generic interconnection domain model (Fig.
 \ref*{figure1.StrategyDomainModel}).
@@
 It is worth stressing that there is no dependency on the Client/Server session-oriented relationship.
-It is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server.
-In the proposed approach the cloud interoperability is obtained by implementation only a dedicated part employing out-of-band communication without dependency on the OPC UA implementation.
+This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server.
+In the proposed approach the cloud interoperability is obtained by implementing a dedicated part employing out-of-band communication only without dependency on the OPC UA functionality at all.
 It is worth stressing that the gateway functionality is implemented as a part - composable to the whole without programming skills.
-Because the part is composed at run-time it makes it possible to modify its functionality later after releasing the library or deploying the application program in the production environment.
+Because the part is composed at the runtime it makes it possible to modify its functionality later after releasing the library or even deploying the application program in the production environment.
 
-Concluding, the paper describes a proof of the concept that applying the proposed architecture and implementation scenario it is possible to interconnect selected cloud services (e.g.
+Concluding, the paper describes a proof of the concept that applying the proposed architecture and deployment scenario it is possible to interconnect selected cloud services (e.g.
 \textbf{Azure\ Industrial\ IoT}) with the \emph{Cyber-physical network} interconnected as one whole atop of the OPC UA PubSub.
-It is in contrast to interconnecting cloud services with the selected \emph{ Address\ Space} exposed by a selected OPC UA server limiting the PubSub role to data export out of the OPC UA ecosystem functionality.
+It is in contrast to interconnecting cloud services with the selected \emph{ Address\ Space} exposed by a selected OPC UA server limiting the PubSub role to data exporter transferring the data out of the OPC UA ecosystem.
 

### 2020-11-29 Latex/Manuscript.tex
Prepare Abstract #30
- fixes #30

@@
 \begin{abstract}
-      TBD
+
+      Optimization of the industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Internet of Things.
+This research aims at working out a new generic architecture and deployment scenario applicable to this integration.
+To deal with the network traffic propagation asymmetry or assets mobility the reactive interoperability relationship of the interconnected nodes is proposed.
+Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment.
+The discussion addressing the generic architecture concludes that the embedded gateway archetype best suits all requirements.
+To promote separation of concerns and reusability, the implementation of the embedded gateway archetype has been implemented as a composable part of an existing OPC UA PubSub framework.
+
+      The proposals are backed by proof of concept reference implementations conforming the possibility to interconnect selected cloud services with the cyber-physical system interconnected as one whole atop of the OPC UA by applying the proposed architecture and deployment scenario.
+It is in contrast to interconnecting cloud services with a selected OPC UA server limiting the PubSub role to data export only.
+
 \end{abstract}
@@
 It requires further research on the integration of \textbf{machine-centric} Cyber-Physical Systems (CPS) with \textbf{human-centric} front-end in the context of new emerging disciplines, i.e.
-Industry 4.0 (I4.0) and the Internet of Things (IoT) (Sect.
+Industry 4.0 and the Internet of Things (Sect.
 \ref*{introduction}).

### 2020-11-30 Latex/Manuscript.tex
Final review of the latex text #37
- improved `Abstract`

@@
 This research aims at working out a new generic architecture and deployment scenario applicable to this integration.
-To deal with the network traffic propagation asymmetry or assets mobility the reactive interoperability relationship of the interconnected nodes is proposed.
+The reactive interoperability relationship of the interconnected nodes is proposed to deal with the network traffic propagation asymmetry or assets mobility.
 Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment.
@@
 
-      The proposals are backed by proof of concept reference implementations conforming the possibility to interconnect selected cloud services with the cyber-physical system interconnected as one whole atop of the OPC UA by applying the proposed architecture and deployment scenario.
-It is in contrast to interconnecting cloud services with a selected OPC UA server limiting the PubSub role to data export only.
+      The proposals are backed by proof of concept reference implementations confirming the possibility to interconnect selected cloud services with the cyber-physical system interconnected as one whole atop of the OPC UA by applying the proposed architecture and deployment scenario.
+It is in contrary to interconnecting cloud services with a selected OPC UA server limiting the PubSub role to data export only.
 

### 2020-11-30 Latex/Manuscript.tex
Update Introduction

@@
 Today both obstacles can be overcome, and as examples, we have bank account remote control and voice over IP in daily use.
-The first application must be fine-tuned in the context of data security, and the second is very sensitive on time relationships.
+The first application must be fine-tuned in the context of data security, and the second is very sensitive in regard to time constraints.
 Similar approaches could be applied to adopt the well known in process control industry concepts:
@@
 Similarly, subscribers express interest in one or more topics and only receive messages that are of interest, without knowledge about which publishers, if any, there are.
-In this scenario, the publishers and subscribers are loosely coupled.i.e they are decoupled in time, space and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.
+In this scenario, the publishers and subscribers are loosely coupled i.e they are decoupled in time, space and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.
 
@@
 Prototyping addresses Microsoft Azure Cloud as an example.
-The prototyping outcome has been just published on GitHub as the open-source (MIT licensed).
+The prototyping outcome has been just published on GitHub as the open-source (MIT licensed) [TODO: Add reference?].
 The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.
@@
 
-If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship\cite{mpostol2020} could relax the problems encountered while the interactive approach is applied.
+If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship\cite{mpostol2020} could alleviate the challenges posed by the interactive approach.
 The real-time multi-vendor environment makes communication standardization especially important.

### 2020-12-01 Latex/Manuscript.tex
Update 2.1 Architecture
> Unlike the above described solutions, the \textbf{embedded gateway} is not derived from the middleware concept.

How do we define middleware? One could say that all three kinds of devices act as in-between agents translating data, including the embedded gateway.

> As a result, any product being advertised as Industry 4.0 enabled must be OPC UA-capable somehow

Does OPC UA really have a monopoly on being Industry 4.0 compliant? You mentioned some solution from India lately... Assuming the range of Industry 4.0 solutions must all be interoperable I'd reword it to make

--- 2020-11-30 Latex/Manuscript.tex
@@
 
-Interconnection of the reactive \textbf{machine - centric} and interactive \textbf{human - centric} environments can be implemented by applying one of the following scenarios:
+Interconnection of the reactive \textbf{machine-centric} and interactive \textbf{human-centric} environments can be implemented by applying one of the following scenarios:
 
@@
 The possibility to establish a common semantic-context in the multi-vendor environment makes communication standardization especially important.
-In this case, it is required that the encoding of the messages payload exchanged over the network (Data Transfer Object - TDO) is standardized so that the payload can be factored on the data-gathering site and consumed on the ultimate destination data processing sites.
+In this case, it is required that the encoding of the messages payload exchanged over the network (Data Transfer Object - DTO) is standardized so that the payload can be factored on the data-gathering site and consumed on the ultimate destination data processing sites.
 Security between the data origin and ultimate data destination refers to the protection of messages (security-context) against malicious users.
@@
 The virtualization of cloud services means that they must be very flexible to handle the attachment of new assets proactively (acting in advance) at run time.
-As a result, by design, the cloud services must be repressible to register and authenticate devices exposing endpoints in the public network to allows the device to access a provisioning cloud service.
+As a result, by design, the cloud services must be responsible to register and authenticate devices by exposing endpoints in the public network to allow the device to access a provisioning cloud service.
 It requires that a session over the Internet has to be established by the data holding asset at a preparation step.

### 2020-12-01 Latex/Manuscript.tex
Update Azure
#37 

> Following the assumption that interconnection between the CPS and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler.

In the previous chapter it was said that "the embedded gateway is not derived from the middleware concept" (I've noted it in #43 too, so I guess it should be adjusted earlier?)

> Removed  "called telemetry"

Depending on the context this could be wrong as the azure docs specify various kinds of data including but not limited to telemetry. I think it's best to skip this part.

--- 2020-11-30 Latex/Manuscript.tex
@@
 The transfer process requires data conversion from source to destination encoding.
-The \textit{IoT\ Hub} is a service hosted in the cloud that supports \textit{IoT\ Central} providing a robust messaging solution - it acts as a central message hub for bi-directional communication.
+The \textit{IoT\ Hub} is a service hosted in the cloud that supports \textit{IoT\ Central} providing a robust messaging solution - it acts as a central message hub for bi-directional communication [TODO: Reference].
 This communication is transparent, i.e.~it is not data types aware allowing
-any devices to exchange any kind of data. This service is responsible to manage the devices' identity and it offers the following protocol stacks: AMQP, MQTT, HTTPS.
+any devices to exchange any kind of data. This service is responsible to manage the devices' identity and it offers the following protocol stacks: AMQP, MQTT and HTTPS.
 
@@
 It is hard to assume that the security rules governing the CPS may also apply to the cloud-based services.
-In the gateway scenario, they can be mapped on each other or entirely independent.
+In the gateway scenario, they can be mapped on each other or be entirely independent.
 The \textit{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper service for \textit{IoT\ Hub} that enables devices' connection process management, upon device providing valid identity attestation it assigns the device to an appropriate \textit{IoT\ Hub} instance and returns to the device connection parameters, which allow direct connection with given \textit{IoT\ Hub} service.
@@
 described by the device template. This Device Template (DT) contains
-also metadata describing the data (called telemetry) exchanged over the
+also metadata describing the data exchanged over the
 wire with the CPS called Device Capability Model
@@
 service to handle the network traffic targeting the cyber-physical
-system. This service offers profiles of the AMQP, MQTT, HTTPS protocol
-stacks. In any case, process data (telemetry) is transparently
+system. This service offers profiles of the AMQP, MQTT and HTTPS protocol
+stacks. In any case, process data is transparently
 transferred back-and-forth to the upper layer \textit{IoT\ Central}

### 2020-12-02 Latex/Manuscript.tex

--- 2020-11-30 Latex/Manuscript.tex
@@
 
-      Optimization of the industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Internet of Things.
+      Optimization of the industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Industrial Internet of Things.
 This research aims at working out a new generic architecture and deployment scenario applicable to this integration.
-The reactive interoperability relationship of the interconnected nodes is proposed to deal with the network traffic propagation asymmetry or assets mobility.
+The reactive interoperability relationship of the interconnected nodes is proposed to deal with the network traffic propagation asymmetry or assets' mobility.
 Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment.
 The discussion addressing the generic architecture concludes that the embedded gateway archetype best suits all requirements.
-To promote separation of concerns and reusability, the implementation of the embedded gateway archetype has been implemented as a composable part of an existing OPC UA PubSub framework.
+To promote separation of concerns and reusability, the proposed architecture of the embedded gateway archetype has been implemented as a composable part of an existing OPC UA PubSub framework.
 
@@
 Today both obstacles can be overcome, and as examples, we have bank account remote control and voice over IP in daily use.
-The first application must be fine-tuned in the context of data security, and the second is very sensitive in regard to time constraints.
+The first application must be fine-tuned in the context of data security, and the second is very sensitive on time relationships.
 Similar approaches could be applied to adopt the well known in process control industry concepts:
@@
 Similarly, subscribers express interest in one or more topics and only receive messages that are of interest, without knowledge about which publishers, if any, there are.
-In this scenario, the publishers and subscribers are loosely coupled i.e they are decoupled in time, space and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.
+In this scenario, the publishers and subscribers are loosely coupled.i.e they are decoupled in time, space and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.
 
@@
 Prototyping addresses Microsoft Azure Cloud as an example.
-The prototyping outcome has been just published on GitHub as the open-source (MIT licensed) [TODO: Add reference?].
+The prototyping outcome has been just published on GitHub as the open-source (MIT licensed).
 The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.
@@
 
-If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship\cite{mpostol2020} could alleviate the challenges posed by the interactive approach.
+If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship\cite{mpostol2020} could relax the problems encountered while the interactive approach is applied.
 The real-time multi-vendor environment makes communication standardization especially important.

### 2020-12-02 Latex/Manuscript.tex
Final review of the latex text #37
- Final Abstract review
- Published on RG

--- 2020-12-01 Latex/Manuscript.tex
@@
 
-      Optimization of the industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Internet of Things.
+      Optimization of the industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Industrial Internet of Things.
 This research aims at working out a new generic architecture and deployment scenario applicable to this integration.
-The reactive interoperability relationship of the interconnected nodes is proposed to deal with the network traffic propagation asymmetry or assets mobility.
+The reactive interoperability relationship of the interconnected nodes is proposed to deal with the network traffic propagation asymmetry or assets' mobility.
 Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment.
 The discussion addressing the generic architecture concludes that the embedded gateway archetype best suits all requirements.
-To promote separation of concerns and reusability, the implementation of the embedded gateway archetype has been implemented as a composable part of an existing OPC UA PubSub framework.
+To promote separation of concerns and reusability, the proposed architecture of the embedded gateway archetype has been implemented as a composable part of an existing OPC UA PubSub framework.
 
       The proposals are backed by proof of concept reference implementations confirming the possibility to interconnect selected cloud services with the cyber-physical system interconnected as one whole atop of the OPC UA by applying the proposed architecture and deployment scenario.
-It is in contrary to interconnecting cloud services with a selected OPC UA server limiting the PubSub role to data export only.
+It is contrary to interconnecting cloud services with a selected OPC UA server limiting the PubSub role to data export only.
 

### 2020-12-02 Latex/Manuscript.tex
Final review of the latex text #37
- Review PS proposals - unimportant modification

@@
 Prototyping addresses Microsoft Azure Cloud as an example.
-The prototyping outcome has been just published on GitHub as the open-source (MIT licensed) [TODO: Add reference?].
+The prototyping outcome has been just published on GitHub as the open-source (MIT licensed) \todo{Add reference}.
 The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.
@@
 The transfer process requires data conversion from source to destination encoding.
-The \textit{IoT\ Hub} is a service hosted in the cloud that supports \textit{IoT\ Central} providing a robust messaging solution - it acts as a central message hub for bi-directional communication [TODO: Reference].
+The \textit{IoT\ Hub} is a service hosted in the cloud that supports \textit{IoT\ Central} providing a robust messaging solution - it acts as a central message hub for bi-directional communication \todo{Reference}.
 This communication is transparent, i.e.~it is not data types aware allowing

### 2020-12-02 Latex/Manuscript.tex
Remove CV from the authors list #45
- done - fixes #45

@@
 
-\author{Mariusz Postół\inst{1}, Piotr Szymczak\inst{1}, Clemens Vasters\inst{2}}
+\author{Mariusz Postół\inst{1}, Piotr Szymczak\inst{1}}
 \headauthor{Postół M, Szymczak P, Vasters C}
@@
  mailto:mariusz.postol@p.lodz.pl
- \andinst
- \inst{2}Microsoft\\
- Faculty/Department/Office Name\\
- Postal Address with the zip-code\\
- clemensv@microsoft.com
 }

### 2020-12-02 Latex/Manuscript.tex
Revert formatting to default #46
Update Implemetnation
> The PubSub uses JSON and binary Data Transfer Object encodings.

Does it use JSON? I'm seeing that OPC UA defines such encoding [here](https://reference.opcfoundation.org/v104/Core/docs/Part14/7.2.3/) but is the library supporting them? Assuming we are talking in the _implementation_ context.

I've cut `Devices.Provisioning.Transport.*` list point to save on space. I don't know if it's "legal".

@@
-\documentclass{jacsart}
+\documentclass{article}
+\usepackage{geometry}
+\usepackage{fancyhdr}
+\usepackage{amsmath,amsthm,amssymb}
 \usepackage{hyperref}
@@
 \title{Object-Oriented Internet - Azure Interoperability}
-% \title{Object-Oriented Internet - reactive visualization of asynchronous data using AZURE}
-\headtitle{OOI - Azure Interoperability}
+%\\headtitle{OOI - Azure Interoperability}
 
-\author{Mariusz Postół\inst{1}, Piotr Szymczak\inst{1}}
-\headauthor{Postół M, Szymczak P, Vasters C}
-\affiliation
+\author[1]{Mariusz Postół, Piotr Szymczak}
+%\author[2]{Piotr Szymczak}
+%\headauthor{Postół M, Szymczak P}
+\affil[1]
 {
- \inst{1}Lodz University of Technology\\
+ Lodz University of Technology\\
  Institute of Information Technology\\
@@
 }
-
-\keywords{ Azure, Cloud Computing, Object-Oriented Internet, Industrial communication, Industry 4.0, Internet of Things, Machine to Machine Communication, OPC Unified Architecture,
-           Reactive Networking (RxNetworking)  }
+\date{}
 
@@
 \end{abstract}
+
+\keywords{ Azure, Cloud Computing, Object-Oriented Internet, Industrial communication, Industry 4.0, Internet of Things, Machine to Machine Communication, OPC Unified Architecture,
+Reactive Networking (RxNetworking)  }
 
@@
 This class provides an entry point to initialize all properties, which are injection points of all parts composing this role.
-It extents functionality of the \textit{DataManagementSetup} based on the following associated classes:
+It extends functionality of the \textit{DataManagementSetup} based on the following associated classes:
 
@@
 The encoded JSON messages must be transferred over the network to Azure using the selected protocol stack.
-The Azure supports the HTTP, AMQP, MQTT (Sec.
-\ref*{azure-main-technology-features}).
-All the mentioned protocols are standard ones.
+The Azure supports HTTP, AMQP and MQTT protocols (Sec.
+\ref*{azure-main-technology-features})which are all standard ones.
 Consequently, it is possible to apply any available implementation compliant with an appropriate specification to achieve connectivity.
@@
       \item \textit{Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
-      \item \textit{Devices.Provisioning.Transport.Amqp} - Provisioning Device Client AMQP Transport for Azure IoT Devices
-      \item \textit{Devices.Provisioning.Transport.Http} - Provisioning Device Client HTTP Transport for Azure IoT Devices
-      \item \textit{Devices.Provisioning.Transport.Mqtt} - Provisioning Device Client MQTT Transport for Azure IoT Devices
+      \item \textit{Devices.Provisioning.Transport.*} - Provisioning Device Client Transports (HTTPS, AMQP, MQTT) for Azure IoT Devices
 \end{itemize}

### 2020-12-02 Latex/Manuscript.tex
Update conclusions
Seeing that you've accepted the `Industrial` suggestion to the abstract I've updated the two other occurences for consistency sake.

--- 2020-12-02 Latex/Manuscript.tex
@@
 
-This article addresses further research on the integration of the CPS in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Internet of Things (IoT).
+This article addresses further research on the integration of the CPS in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Industrial Internet of Things (IIoT).
 The new architecture is proposed for integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end.
@@
 It requires further research on the integration of \textbf{machine-centric} Cyber-Physical Systems (CPS) with \textbf{human-centric} front-end in the context of new emerging disciplines, i.e.
-Industry 4.0 and the Internet of Things (Sect.
+Industry 4.0 and the Industrial Internet of Things (Sect.
 \ref*{introduction}).

### 2020-12-03 Latex/Manuscript.tex
Final review of the latex text #37
- fixed formatting
- replaced Industrial IoT by IoT Central.

@@
 
-      The proposals are backed by proof of concept reference implementations confirming the possibility to interconnect selected cloud services with the cyber-physical system interconnected as one whole atop of the OPC UA by applying the proposed architecture and deployment scenario.
+      The proposals are backed by proof of concept reference implementations confirming the possibility to integrate selected cloud services with the cyber-physical system interconnected as one whole atop of the OPC UA by applying the proposed architecture and deployment scenario.
 It is contrary to interconnecting cloud services with a selected OPC UA server limiting the PubSub role to data export only.
@@
 
-This article addresses further research on the integration of the CPS in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Industrial Internet of Things (IIoT).
+This article addresses further research on the integration of the CPS in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Internet of Things (IoT).
 The new architecture is proposed for integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end.
@@
 
-The \textit{IoT\ Central} service provides a process data visualization
+The \textbf{IoT\ Central} service provides a process data visualization
 user interface. To make this interface meaningful metadata called device
@@
 above selection of services must be recognized as an example only. The
-\textit{IoT\ Central} can be also seamlessly integrated with other
+\textbf{IoT\ Central} can be also seamlessly integrated with other
 services as needed. The following services could also be considered to
@@
 
-In \textit{IoT\ Central} a CPS is represented as a set
+In \textbf{IoT\ Central} a CPS is represented as a set
 of devices. The characteristics and behavior of each device kind are
@@
 expressed as a JSON-LD can be imported into a Device Template.
-\textit{IoT\ Central} allows also to create and edit a DCM using the
+\textbf{IoT\ Central} allows also to create and edit a DCM using the
 dedicated web UI. A JSON file containing DCM can be derived from an
@@
 stacks. In any case, process data is transparently
-transferred back-and-forth to the upper layer \textit{IoT\ Central}
+transferred back-and-forth to the upper layer \textbf{IoT\ Central}
 service. Hence, the payload formatting is determined by the DCM
-associated with the \textit{IoT\ Central} solution.
+associated with the \textbf{IoT\ Central} solution.
 
@@
 It requires further research on the integration of \textbf{machine-centric} Cyber-Physical Systems (CPS) with \textbf{human-centric} front-end in the context of new emerging disciplines, i.e.
-Industry 4.0 and the Industrial Internet of Things (Sect.
+Industry 4.0 and the Internet of Things (Sect.
 \ref*{introduction}).
@@
 
-Concluding, the paper describes a proof of the concept that applying the proposed architecture and deployment scenario it is possible to interconnect selected cloud services (e.g.
-\textbf{Azure\ Industrial\ IoT}) with the \emph{Cyber-physical network} interconnected as one whole atop of the OPC UA PubSub.
+Concluding, the paper describes a proof of the concept that applying the proposed architecture and deployment scenario it is possible to integrate selected cloud services (e.g.
+\textbf{Azure\ IoT\ Central}) with the \emph{Cyber-physical network} interconnected as one whole atop of the OPC UA PubSub.
 It is in contrast to interconnecting cloud services with the selected \emph{ Address\ Space} exposed by a selected OPC UA server limiting the PubSub role to data exporter transferring the data out of the OPC UA ecosystem.

### 2020-12-05 Latex/Manuscript.tex
Final review of the latex text #37
- prepared 1.4.3-Shared after PS review
Final review of the latex text #37
- Up to Sect. 2 MP reviewed - working copy

@@
 The discussion addressing the generic architecture concludes that the embedded gateway archetype best suits all requirements.
-To promote separation of concerns and reusability, the proposed architecture of the embedded gateway archetype has been implemented as a composable part of an existing OPC UA PubSub framework.
+To promote separation of concerns and reusability, the proposed architecture of the embedded gateway archetype has been implemented as a composable part of a selected OPC UA PubSub framework.
 
@@
 
-\listoftodos[TODO list]
+%\listoftodos[TODO list]
 
@@
 
-A typical \textbf{human-centric} approach is a web-service supporting, for example, a web user interface (UI) to monitor conditions, and manage millions of devices and their data in a typical cloud-based IoT approach.
-It is characteristic that, in this case, any uncertainty and necessity to make a decision can be relaxed by human interaction.
+A typical \textbf{human-centric} approach is a web-service supporting, for example, a web user interface (UI) to monitor conditions and manage millions of devices and their data in a typical cloud-based IoT approach.
+In this case, it is characteristic that any uncertainty and necessity to make a decision can be relaxed by human interaction.
 Coordination of robots behavior in a work-cell (automation islands) is a \textbf{machine-centric} example.
-In this case, it is essential that any human interaction is impractical or even impossible.
+In this case, any human interaction must be recognized as impractical or even impossible.
 This interconnection scenario requires the machine to machine communication (M2M) demanding multi-vendor devices integration.
 
-From the M2M communication concept, a broader concept of a smart factory can be derived.
+From the M2M communication concept, a broader idea of a smart factory can be derived.
 In this concept, the mentioned robots are only executive assets of an integrated supervisory control system responsible for macro optimization of an industrial process composed into one whole.
 Deployment of the smart factory concept requires a hybrid solution and interconnection of the mentioned above heterogeneous environments.
-This approach is called the fourth industrial revolution and coined as Industry 4.0.
+This approach is called the fourth industrial revolution and was coined as Industry 4.0.
 It is worth stressing that machines - or more general assets - interconnection is not enough, and additionally, assets interoperability has to be expected for the deployment of this concept.
-In this case, multi-vendor integration makes communication standardization especially important, namely it is required that the payload of the message is standardized to be factored on the data  gathering site and consumed on the ultimate destination site.
+In this case, multi-vendor integration makes communication standardization especially important, namely, it is required that the payload of the message is standardized to be factored on the data-gathering site and consumed on the ultimate destination site.
 
@@
 \begin{itemize}
-      \item it is a globally shareable environment and can be also used by malicious users
+      \item it is a globally shareable and can be also used by malicious users
       \item it offers only non-deterministic communication making integration of islands of automation designed against the real-time requirements a difficult task
@@
 In other words, in this case, the interactive communication relationship cannot be directly applied because the control application must be informed on how to pull data from a new source.
-As a result, a plug and produce scenario cannot be seamlessly applied.
+As a result, a plug and produce scenario \cite{PlugProduceByModellingSkills} cannot be seamlessly applied.
 A similar drawback must be overcome if for security reasons suitable protection methods have been applied to make network traffic propagation asymmetric.
@@
 
-Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical System (CPS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct interconnection} or \textbf{gateway based interconnection} (Sect.
+Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical System (CPS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect.
 \ref*{subs.architecture}).
 
-By design, the direct approach requires that the cloud has to be compliant with the interoperability standard the CPS is built upon - it becomes a consistent part of the CPS.
+By design, the \textbf{direct} approach requires that the cloud has to be compliant with the interoperability standard the CPS is built upon - it becomes a consistent part of the CPS.
 Data models, roles, and responsibility differences of both solutions make this approach impractical or even imposable to be applied in typical cases.
@@
 
-This article addresses further research on the integration of the CPS in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Industrial Internet of Things (IIoT).
-The new architecture is proposed for integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end.
+This article addresses further research on the integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M communication and emerging cloud computing as a \textbf{human-centric} front-end in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Industrial Internet of Things (IIoT).
+For this integration, a new architecture is proposed to promote communication parties reactive relationship.
 To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected.
@@
 The prototyping outcome has been just published on GitHub as the open-source (MIT licensed) \todo{Add reference}.
-The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.
+The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.
 
@@
 Using the session-oriented communication pattern it is difficult or even impossible to gather and process mobile data (Sec.~\ref*{introduction} ), which is one of the Internet of Things paradigms.
-OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} \todo{add ref: Mariusz Postol, UA Part 14: PubSub Main Technology Features in Object Oriented Internet, https://github.com/mpostol/OPC-UA-OOI, 2019, DOI: 10.5281/zenodo.1198852} offers the sessionless approach as an additional option to session based client-server interoperability relationship and is a consistent part of the OPC UA specifications suit.
+OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0, UAPart14PubSubMainTechnologyFeatures} offers the sessionless approach as an additional option to session based client-server interoperability relationship and is a consistent part of the OPC UA specifications suit.
 As the result it can be recognized as the IoT ready technology.
@@
 Solutions hosted on Azure are scaled up to millions of users without any additional coding.
-For the development of the CPS front-end, it is essential that Azure provides very efficient storage services usefully for the purpose of real-time process data archival.
+For the development of the todo front-end, it is essential that Azure provides very efficient storage services usefully for the purpose of real-time process data archival.
 Azure provides a vast variety of hybrid connections including but not limited to virtual private networks (VPNs), caches, content delivery networks (CDNs), ExpressRoute, and IoT dedicated services that can be directly used to implement cloud-based front-end for CPS.
@@
 A software development kits for C\#, Java, PHP, and Ruby are available for custom applications.
-Azure provides services supporting data exchange over the OPC UA, but they don't support PubSub compliant with the OPC UA Part-14\cite{RefWorks:doc:5d98837de4b055984c0eecf0}.
+Azure provides services supporting data exchange over the OPC UA, but they don't support PubSub compliant with the OPC UA Part-14.
 Connectivity services on the network use JSON-based Data Transfer Object encoded based on schema derived from the solution metadata.
@@
 Based on the sessionless and session-oriented communication patterns examination against the IoT requirements \cite{mpostol2020} it could be concluded that the connectionless pattern better suites issues related to the assets mobility and traffic asymmetry that is characteristic for the application domains in concern.
-Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} specification.
+Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub  specification.
 According to proposed generic architecture (Fig.~\ref*{figure1.StrategyDomainModel}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ Node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
@@
 A library that meets all these requirements has been implemented consistently with the Object-Oriented Internet paradigm \cite{RefWorks:doc:5c66740ae4b081adf5804596} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }.
-The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the Object-Oriented Internet concept compliant with the OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} international standard.
+The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the Object-Oriented Internet concept compliant with the OPC UA PubSub international standard.
 According to the presented implementation and evaluation, using the dependency injection and late binding, the application program can be seamlessly adapted to the production environment and scales well.

### 2020-12-06 Latex/Manuscript.tex
Final review of the latex text #37
- Verified changes up to sect.2.
- Continue verification of changes starting from sect.2

@@
 From the M2M communication concept, a broader idea of a smart factory can be derived.
-In this concept, the mentioned robots are only executive assets of an integrated supervisory control system responsible for macro optimization of an industrial process composed into one whole.
+In this M2M  deployment approach, the mentioned robots are only executive assets of an integrated supervisory control system responsible for macro optimization of an industrial process composed as one whole.
 Deployment of the smart factory concept requires a hybrid solution and interconnection of the mentioned above heterogeneous environments.
@@
 
-This article addresses further research on the integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M communication and emerging cloud computing as a \textbf{human-centric} front-end in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Industrial Internet of Things (IIoT).
-For this integration, a new architecture is proposed to promote communication parties reactive relationship.
+This article addresses further research on the integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M communication and emerging cloud computing as a \textbf{human-centric} front-end in the context of the Industry 4.0 (I4.0) and Industrial Internet of Things (IIoT) disciplines.
+For this integration, a new architecture is proposed to support the reactive relationship of communicating parties.
 To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected.
-The proposals are backed by proof of concept reference implementations.
 Prototyping addresses Microsoft Azure Cloud as an example.
-The prototyping outcome has been just published on GitHub as the open-source (MIT licensed) \todo{Add reference}.
+The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as the open-source (MIT licensed) \todo{Add reference}.
 The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.
@@
 
-To meet the requirements of real-time distributed control the CPS may use protocols applicable only to local computer networks (e.g.~multicast IP, Ethernet, TSN, etc.).
+To meet the requirements of real-time distributed control the CPS may use protocols applicable only to local computer networks (e.g.~multicast IP, Ethernet, TSN \footnote{Time-Sensitive Networking (TSN) Task Group \url{https://1.ieee802.org/tsn/}}, etc.).
 Because the cloud services support only protocols handling interconnection over the Internet the interaction with the cloud requires remote agents, i.e.~agents attached locally to the M2M network and implemented by applying one of the following archetypes:
@@
 
-The \textbf{field level gateway} is also build atop of the middleware concept.
+The \textbf{field level gateway} is also build atop of the middleware\todo{add ref} concept.
 The only difference compared with the \textbf{edge device} is necessity to use officially supported by the cloud vendor services to get connected.
@@
 
-The presented proposals in the article are backed by proof of concept reference implementations.
+The presented proposals in the article are backed by proof of concept reference implementations\cite{RefWorks:doc:5c66740ae4b081adf5804596} \todo{ref to MP, PS gateway implementation}.
 For this study, prototyping addresses Microsoft Azure cloud products.
@@
 Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub  specification.
-According to proposed generic architecture (Fig.~\ref*{figure1.StrategyDomainModel}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ Node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
+According to proposed generic architecture (Fig.~\ref*{figure1.StrategyDomainModel}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
 Additionally, it must be assumed that the library used to deploy \textit{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/PubSub gateway functionality.
@@
 
-The following subsections cover the description of the current state of technologies with regards to Azure cloud-based IoT enabler and OPC UA PubSub.
-Sect.~\ref*{azure-main-technology-features} analyzes data presentation user interface, available native communication services, and data/metadata model offered by the Microsoft Azure.
+The following subsections cover the description of the current state of technologies concerning Azure cloud-based IoT enabler and OPC UA PubSub.
+Sect.~\ref*{azure-main-technology-features} analyzes data presentation user interface, available native communication services, and data/metadata model offered by Microsoft Azure.
 The discussion covered by this section is the foundation for selecting services utilized to expose process data and suitable protocol stack to support interconnection.
@@
 
-Fortunately, computer science offers a workaround to address that
-impossibility - the information must be represented as a binary stream.
-In consequence, we can usually use both ones as interchangeable terms
-while talking about ICT systems. Unfortunately, these terms must be
-precisely observed in the context of further discussion, because we must
-be aware of the fact that the same information could have many different
-but equivalent representations. In other words, the same information can
-be represented by a vast variety of different binary patterns. For
-example, numbers may be represented using 2's Complement and
-Floating-Point binary representations.
+Fortunately, computer science offers a workaround to address that impossibility - the information must be represented as a binary stream.
+In consequence, we can usually use both terms as interchangeable ones while talking about ICT systems.
+Unfortunately, these terms must be precisely observed in the context of further discussion, because we must be aware of the fact that the same information could have many different but equivalent representations.
+In other words, the same information can be represented by a vast variety of different binary patterns.
+For example, numbers may be represented using 2's Complement and Floating-Point binary representations.
 
@@
 
-Using the data type definitions to describe information interchanged
-between communicating parties allows:
+Using the data type definition to describe information interchange between communicating parties allows:
 
@@
 
-\subsubsection{Connectivity}\label{connectivity}
+\subsubsection{Connectivity}\label{subsubsection.connectivity}
 
-From the cloud side, it is proposed to employ the \textit{IoT\ Hub}
-service to handle the network traffic targeting the cyber-physical
-system. This service offers profiles of the AMQP, MQTT and HTTPS protocol
-stacks. In any case, process data is transparently
-transferred back-and-forth to the upper layer \textbf{IoT\ Central}
-service. Hence, the payload formatting is determined by the DCM
-associated with the \textbf{IoT\ Central} solution.
+From the cloud side, it is proposed to employ the \textit{IoT\ Hub} service to handle the network traffic targeting the cyber-physical system.
+This service offers profiles of the AMQP, MQTT, and HTTPS protocol stacks.
+In any case, process data is transparently transferred back-and-forth to the upper layer \textbf{IoT\ Central} service.
+Hence, the payload formatting is determined by the DCM associated with the \textbf{IoT\ Central} solution.
+
+The Azure supports HTTP, AMQP, and MQTT protocol stacks which are all standard ones.
+Consequently, it is possible to apply any available ones compliant with an appropriate specification to achieve connectivity.
+In this case, all parameters required to establish semantic and security contexts are up to the gateway responsibility.
+Alternatively, the API offered by the dedicated frameworks (libraries) may be used.
+Using a framework the configuration process may be reduced significantly, and the communication protocol selection has only an indirect impact on the interoperability features.
+The Azure interconnection may be obtained using the following \textit{Microsoft.Azure} packages:
+
+\begin{itemize}
+      \item \textit{Devices} - Service SDK for Azure IoT Devices
+      \item \textit{Devices.Client} - Device SDK for Azure \textit{IoT\ Hub} including dependencies implementing MQTT and AMQP communication
+      \item \textit{Devices.Shared} - Common code for Azure IoT Device and Service SDK
+      \item \textit{Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
+      \item \textit{Devices.Provisioning.Transport.*} - Provisioning Device Client Transports (HTTPS, AMQP, MQTT) for Azure IoT Devices
+\end{itemize}
 
@@
 The encoded JSON messages must be transferred over the network to Azure using the selected protocol stack.
-The Azure supports HTTP, AMQP and MQTT protocols (Sec.
-\ref*{azure-main-technology-features})which are all standard ones.
-Consequently, it is possible to apply any available implementation compliant with an appropriate specification to achieve connectivity.
-In this case, all parameters required to establish semantic and security contexts are up to the gateway responsibility.
-Alternatively, the API offered by the dedicated frameworks (libraries) may be used.
-Using a framework the configuration process may be reduced significantly, and the communication protocol selection has only an indirect impact on the interoperability features.
-In the proposed gateway implementation the Azure interconnection has been obtained using the following \textit{Microsoft.Azure} packages:
-
-\begin{itemize}
-      \item \textit{Devices} - Service SDK for Azure IoT Devices
-      \item \textit{Devices.Client} - Device SDK for Azure \textit{IoT\ Hub} including dependencies implementing MQTT and AMQP communication
-      \item \textit{Devices.Shared} - Common code for Azure IoT Device and Service SDK
-      \item \textit{Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
-      \item \textit{Devices.Provisioning.Transport.*} - Provisioning Device Client Transports (HTTPS, AMQP, MQTT) for Azure IoT Devices
-\end{itemize}
+The Azure supports standard protocols (Sec.
+\ref*{azure-main-technology-features}).
+Consequently, it is possible to apply any available ones compliant with an appropriate specification to achieve connectivity.
+In the proposed gateway implementation the Azure interconnection has been obtained using the packages described in Sect.
+\ref*{subsubsection.connectivity}.
 
@@
 \section{Conclusion}\label{section.conclusion}
+
+\todo{vendor products and cannot be recognized as a generic solution that can be used to connect to other clouds at the same time}
 
@@
 The proposals are backed by proof of concept reference implementations.
-Prototyping addresses Microsoft Azure Cloud as an example.
-The prototyping outcome has been just published on GitHub as open-source (MIT licensed).
+Prototyping addresses Microsoft Azure cloud as an example.
+The outcome has been just published on GitHub as the open-source (MIT licensed) repository.
 The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.
@@
 \textbf{Azure\ IoT\ Central}) with the \emph{Cyber-physical network} interconnected as one whole atop of the OPC UA PubSub.
-It is in contrast to interconnecting cloud services with the selected \emph{ Address\ Space} exposed by a selected OPC UA server limiting the PubSub role to data exporter transferring the data out of the OPC UA ecosystem.
+It is in contrast to interconnecting cloud-based front-end services with the selected \emph{ Address\ Space} exposed by a selected OPC UA server limiting the PubSub role to data exporter transferring the data out of the OPC UA ecosystem.
 

### 2020-12-06 Latex/Manuscript.tex
Final review of the latex text #37
- MP review finished.

@@
 
-Using the data type definition to describe information interchange between communicating parties allows:
+Using the data type definitions to describe information interchange between communicating parties allows:
 
 \begin{itemize}
-      \item Development against a type definition of the user interface
-      \item Implementation of the functionality of the bitstreams conversion in advance
+      \item development against a type definition of the user interface
+      \item implementation of the functionality of the bitstreams conversion in advance
 \end{itemize}
@@
 
-\todo{vendor products and cannot be recognized as a generic solution that can be used to connect to other clouds at the same time}
-
 Nowadays, the macro optimization of the industrial processes requires an integration of a vast variety of distributed applications provided by the Information and Communication Technology.
@@
 \textbf{edge device} - remote cloud agent and \textbf{field level gateway} - a dedicated custom agent.
+Additionally, it could be used to connect to many independent clouds at the same time.
 The generic domain model for the proposed interconnection archetype is presented in the Fig.~\ref*{figure1.StrategyDomainModel}.
@@
 This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server.
+The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to embed the \textbf{embedded gateway} component into the OPC UA Client or Server to get connected with the cloud in case of the interactive relationship.
+
 In the proposed approach the cloud interoperability is obtained by implementing a dedicated part employing out-of-band communication only without dependency on the OPC UA functionality at all.

### 2020-12-08 Latex/Manuscript.tex
Final review of the latex text #37
- replace texit by emph

@@
 \providecommand{\tightlist} { \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\providecommand{\keywords}[1]{ \small \textbf{\textit{Keywords---}} #1 }
+\providecommand{\keywords}[1]{ \small \textbf{\emph{Keywords---}} #1 }
 
@@
 A generic domain model for this interconnection is presented in the Fig.~\ref*{figure1.StrategyDomainModel}.
-Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \textit{Networking} service of the \textit{Cyber-physical\ node}.
-Main functionality of this component is to transfer selected data between \textit{Cyber-physical\ network} using \textit{Networking} services of an existing \textit{Cyber-physical\ node} and \textit{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
+Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \emph{Networking} service of the \emph{Cyber-physical\ node}.
+Main functionality of this component is to transfer selected data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
 
-The \textbf{embedded gateway} archetype relaxes most of the issues described above: \textit{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security-context differences to name only a few.
+The \textbf{embedded gateway} archetype relaxes most of the issues described above: \emph{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security-context differences to name only a few.
 The main goal of this article is to provide proof that the \textbf{embedded gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogenous environments in concern.
@@
 Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub  specification.
-According to proposed generic architecture (Fig.~\ref*{figure1.StrategyDomainModel}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
-Additionally, it must be assumed that the library used to deploy \textit{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/PubSub gateway functionality.
+According to proposed generic architecture (Fig.~\ref*{figure1.StrategyDomainModel}) to implement the \emph{Embedded\ Gateway} as a composable part of the \emph{Cyber-physical\ node} a library implementing \emph{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
+Additionally, it must be assumed that the library used to deploy \emph{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/PubSub gateway functionality.
 The composition process must be available without modification of the core code of an existing library.
-As a result, the prototyping is to be limited to implementation of the \textit{Embedded\ Gateway} software part only.
+As a result, the prototyping is to be limited to implementation of the \emph{Embedded\ Gateway} software part only.
 
@@
 
-Sect.~\ref*{ooi-main-technology-features} provides a more detailed description of this library and an external part deployment process that is to be used to implement new functionality supporting \textit{Embedded\ Gateway}.
+Sect.~\ref*{ooi-main-technology-features} provides a more detailed description of this library and an external part deployment process that is to be used to implement new functionality supporting \emph{Embedded\ Gateway}.
 
@@
 The transfer process requires data conversion from source to destination encoding.
-The \textit{IoT\ Hub} is a service hosted in the cloud that supports \textit{IoT\ Central} providing a robust messaging solution - it acts as a central message hub for bi-directional communication \todo{Reference}.
+The \emph{IoT\ Hub} is a service hosted in the cloud that supports \emph{IoT\ Central} providing a robust messaging solution - it acts as a central message hub for bi-directional communication \todo{Reference}.
 This communication is transparent, i.e.~it is not data types aware allowing
@@
 In the gateway scenario, they can be mapped on each other or be entirely independent.
-The \textit{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper service for \textit{IoT\ Hub} that enables devices' connection process management, upon device providing valid identity attestation it assigns the device to an appropriate \textit{IoT\ Hub} instance and returns to the device connection parameters, which allow direct connection with given \textit{IoT\ Hub} service.
-The device proceeds to use the same attestation in \textit{IoT\ Hub} connection and based on it, is granted authorization to selected operations including but not limited to data transfer and updating the user interface.
+The \emph{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper service for \emph{IoT\ Hub} that enables devices' connection process management, upon device providing valid identity attestation it assigns the device to an appropriate \emph{IoT\ Hub} instance and returns to the device connection parameters, which allow direct connection with given \emph{IoT\ Hub} service.
+The device proceeds to use the same attestation in \emph{IoT\ Hub} connection and based on it, is granted authorization to selected operations including but not limited to data transfer and updating the user interface.
 
@@
 \begin{itemize}
-      \item \textit{Industrial\ IoT} - discovering OPC UA enabled servers in a factory network and register them in Azure \textit{IoT\ Hub} implemented using \textit{IoT\ Edge}
-      \item \textit{Digital\ Twins} - managing the graph of digital twins, which are to represent some real-world process or entity
+      \item \emph{Industrial\ IoT} - discovering OPC UA enabled servers in a factory network and register them in Azure \emph{IoT\ Hub} implemented using \emph{IoT\ Edge}
+      \item \emph{Digital\ Twins} - managing the graph of digital twins, which are to represent some real-world process or entity
 \end{itemize}
 
-\textit{Industrial\ IoT} promotes OPC UA client/server archetype used to
+\emph{Industrial\ IoT} promotes OPC UA client/server archetype used to
 achieve direct and interactive interoperability implemented using
-\textit{IoT\ Edge} services that allow extracting initial data
+\emph{IoT\ Edge} services that allow extracting initial data
 processing to local premises based on the edge concept.
-\textit{Digital\ Twins} is an emerging concept to use an observer to
+\emph{Digital\ Twins} is an emerging concept to use an observer to
 replicate selected process state and behavior. The possibility to add
@@
 
-From the cloud side, it is proposed to employ the \textit{IoT\ Hub} service to handle the network traffic targeting the cyber-physical system.
+From the cloud side, it is proposed to employ the \emph{IoT\ Hub} service to handle the network traffic targeting the cyber-physical system.
 This service offers profiles of the AMQP, MQTT, and HTTPS protocol stacks.
@@
 Using a framework the configuration process may be reduced significantly, and the communication protocol selection has only an indirect impact on the interoperability features.
-The Azure interconnection may be obtained using the following \textit{Microsoft.Azure} packages:
+The Azure interconnection may be obtained using the following \emph{Microsoft.Azure} packages:
 
 \begin{itemize}
-      \item \textit{Devices} - Service SDK for Azure IoT Devices
-      \item \textit{Devices.Client} - Device SDK for Azure \textit{IoT\ Hub} including dependencies implementing MQTT and AMQP communication
-      \item \textit{Devices.Shared} - Common code for Azure IoT Device and Service SDK
-      \item \textit{Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
-      \item \textit{Devices.Provisioning.Transport.*} - Provisioning Device Client Transports (HTTPS, AMQP, MQTT) for Azure IoT Devices
+      \item \emph{Devices} - Service SDK for Azure IoT Devices
+      \item \emph{Devices.Client} - Device SDK for Azure \emph{IoT\ Hub} including dependencies implementing MQTT and AMQP communication
+      \item \emph{Devices.Shared} - Common code for Azure IoT Device and Service SDK
+      \item \emph{Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
+      \item \emph{Devices.Provisioning.Transport.*} - Provisioning Device Client Transports (HTTPS, AMQP, MQTT) for Azure IoT Devices
 \end{itemize}
@@
 \ref*{introduction}) concept.
-A framework compliant with these requirements has been implemented as an open-source library named \textit{UAOOI.Networking} (\textit{Networking} for short) under an umbrella of the project Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.
+A framework compliant with these requirements has been implemented as an open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) under an umbrella of the project Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.
 The library is designed to be a foundation for developing application programs that are taking part in a message-centric communication pattern and interconnected using the reactive networking concept.
-The diagram in Fig.~\ref*{figure2.UADataApplicationArchitecture} shows the relationship between the library (\textit{SDK}) and external parts composing any reactive networking application (\textit{Reactive\ Application}).
-The \textit{Reactive Application} is an aggregation of parts implementing the \textit{Producer} and \textit{Consumer} roles.
-By design, they support access to real-time process data, hence they are recognized as an extension of \textit{DataRepository} class.
-To implement the \textit{DataRepository} dedicated implementation of the \textit{IBinding} interface should be provided to create a bridge between CPS and an external row data represented by the \textit{LocalResources} class.
-A more in-depth description of the \textit{OOI Reactive Application} library enabling data exchange over a network using the reactive networking pattern is in \cite{mpostol2020}.
+The diagram in Fig.~\ref*{figure2.UADataApplicationArchitecture} shows the relationship between the library (\emph{SDK}) and external parts composing any reactive networking application (\emph{Reactive\ Application}).
+The \emph{Reactive Application} is an aggregation of parts implementing the \emph{Producer} and \emph{Consumer} roles.
+By design, they support access to real-time process data, hence they are recognized as an extension of \emph{DataRepository} class.
+To implement the \emph{DataRepository} dedicated implementation of the \emph{IBinding} interface should be provided to create a bridge between CPS and an external row data represented by the \emph{LocalResources} class.
+A more in-depth description of the \emph{OOI Reactive Application} library enabling data exchange over a network using the reactive networking pattern is in \cite{mpostol2020}.
 
@@
 
-The \textit{DataRepository} represents data holding assets in the \textit{Reactive Application} implementing the \textit{IBindingFactory} interface.
-It captures functionality responsible for accessing the external process data from \textit{LocalResources}.
-The \textit{LocalResources} represents an external part that has a very broad usage purpose.
+The \emph{DataRepository} represents data holding assets in the \emph{Reactive Application} implementing the \emph{IBindingFactory} interface.
+It captures functionality responsible for accessing the external process data from \emph{LocalResources}.
+The \emph{LocalResources} represents an external part that has a very broad usage purpose.
 For example, it may be any kind of the process data source/destination, i.e.
@@
 \begin{itemize}
-      \item \textit{Consumer} - entities processing data from incoming messages,
-      \item \textit{Producer} - entities gathering process data and populating outgoing messages.
+      \item \emph{Consumer} - entities processing data from incoming messages,
+      \item \emph{Producer} - entities gathering process data and populating outgoing messages.
 \end{itemize}
 
-The \textit{Consumer} and \textit{Producer} classes are derived from the \textit{DataRepository} (Fig.~\ref*{figure2.UADataApplicationArchitecture}).
-The \textit{Consumer} uses the \textit{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
+The \emph{Consumer} and \emph{Producer} classes are derived from the \emph{DataRepository} (Fig.~\ref*{figure2.UADataApplicationArchitecture}).
+The \emph{Consumer} uses the \emph{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
 The received data may be processed or driven to any data destination, e.g.
 cloud-based front-end.
-The \textit{Producer} mirrors the \textit{Consumer} functionality and, after reading data from an associated source, populates the \emph{Message} using the gathered data.
+The \emph{Producer} mirrors the \emph{Consumer} functionality and, after reading data from an associated source, populates the \emph{Message} using the gathered data.
 
-By design, the \textit{DataRepository} and associated entities, i.e.~\textit{Local Resources}, \textit{Consumer}, \textit{Producer} are embedded in external parts, and consequently, the application scope may cover practically any concern that can be separated from the core \textit{Reactive Application} implementation.
+By design, the \emph{DataRepository} and associated entities, i.e.~\emph{Local Resources}, \emph{Consumer}, \emph{Producer} are embedded in external parts, and consequently, the application scope may cover practically any concern that can be separated from the core \emph{Reactive Application} implementation.
 
@@
 The proposed approach to instantiate the application as a set of composable parts is very useful in this respect because it makes it possible to expand the core configuration functionality and adapt it to be helpful also in this case.
-Therefore, the semantic-context may be created based on the configuration using the implementation of the \textit{IConfigurationDataFactory} interface.
+Therefore, the semantic-context may be created based on the configuration using the implementation of the \emph{IConfigurationDataFactory} interface.
 
@@
 
-A generic domain model presenting interconnection architecture between the Azure \textit{Cloud-based\ Front-end} and \textit{Cyber-physical\ node} attached to the \textit{Cyber-physical\ network} is presented in Fig.
+A generic domain model presenting interconnection architecture between the Azure \emph{Cloud-based\ Front-end} and \emph{Cyber-physical\ node} attached to the \emph{Cyber-physical\ network} is presented in Fig.
 \ref*{figure1.StrategyDomainModel}.
-It is proposed to implement the \textit{Cyber-physical\ node} by adopting the \textit{Reactive Application} archetype compliant with the reactive interoperability concept (Fig.
+It is proposed to implement the \emph{Cyber-physical\ node} by adopting the \emph{Reactive Application} archetype compliant with the reactive interoperability concept (Fig.
 \ref*{figure2.UADataApplicationArchitecture}) described in the Sect.
@@
 \ref*{figure3.ImplementationDomainModel}.
-In the proposed approach the \textit{Embedded Gateway} is derived from the \textit{Consumer} role implemented as as a composable part aggregated by the \textit{Reactive Application}.
+In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as as a composable part aggregated by the \emph{Reactive Application}.
 
@@
 In the final deployment architecture (Fig.
-\ref*{figure4.ImplementationArchitecture}) the \textit{Consumer} role has been realized by the \textit{PartDataManagementSetup} that is derived from \textit{DataManagementSetup} provided by the library.
-\textit{Networking} (SDK) was removed from this diagram for the sake of simplicity.
-Instantiating \textit{PartDataManagementSetup} is the first step for bootstrapping process of the \textit{Consumer} role functionality.
+\ref*{figure4.ImplementationArchitecture}) the \emph{Consumer} role has been realized by the \emph{PartDataManagementSetup} that is derived from \emph{DataManagementSetup} provided by the library.
+\emph{Networking} (SDK) was removed from this diagram for the sake of simplicity.
+Instantiating \emph{PartDataManagementSetup} is the first step for bootstrapping process of the \emph{Consumer} role functionality.
 This class provides an entry point to initialize all properties, which are injection points of all parts composing this role.
-It extends functionality of the \textit{DataManagementSetup} based on the following associated classes:
+It extends functionality of the \emph{DataManagementSetup} based on the following associated classes:
 
@@
 \begin{enumerate}
-      \item \textit{PartConfigurationFactory} - to get access to the application configuration
-      \item \textit{PartBindingFactory} - to gather the data recovered from the \textit{Message} instances pulled from the wire
-      \item \textit{CommunicationContext} - to handle communication with the Azure services
+      \item \emph{PartConfigurationFactory} - to get access to the application configuration
+      \item \emph{PartBindingFactory} - to gather the data recovered from the \emph{Message} instances pulled from the wire
+      \item \emph{CommunicationContext} - to handle communication with the Azure services
 \end{enumerate}
 
-In this case, the implementation of the \textit{IConfigurationFactory} interface is based entirely on the \textit{Networking} library.
+In this case, the implementation of the \emph{IConfigurationFactory} interface is based entirely on the \emph{Networking} library.
 The implementation provided by the library is generic, but it is flexible enough to meet all the requirements, which warrants no need for further modifications for adoption.
@@
 
-The \textit{PartBindingFactory} implements the \textit{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
-The received data is driven to \textit{CommunicationContext} for further encoding and finally pushing it to the Azure services using configured out-of-band protocol.
+The \emph{PartBindingFactory} implements the \emph{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
+The received data is driven to \emph{CommunicationContext} for further encoding and finally pushing it to the Azure services using configured out-of-band protocol.
 
-\textit{IEncodingFactory} and \textit{IMessageHandlerFactory} interfaces (Fig.
-\ref*{figure2.UADataApplicationArchitecture}) have been implemented in independent libraries and ae not considered for any modifications to deploy \textit{Embedded Gateway} functionality.
-The current implementation of the mentioned interfaces is localized at run time as services using an instance of the \textit{IServiceLocator}\footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} }.
-In this example, it is assumed that \textit{IServiceLocator} is implemented to resolve references to any external services.
-Both interfaces are used to manage interconnection of the node with the \textit{Cyber-physical Network}.
+\emph{IEncodingFactory} and \emph{IMessageHandlerFactory} interfaces (Fig.
+\ref*{figure2.UADataApplicationArchitecture}) have been implemented in independent libraries and ae not considered for any modifications to deploy \emph{Embedded Gateway} functionality.
+The current implementation of the mentioned interfaces is localized at run time as services using an instance of the \emph{IServiceLocator}\footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} }.
+In this example, it is assumed that \emph{IServiceLocator} is implemented to resolve references to any external services.
+Both interfaces are used to manage interconnection of the node with the \emph{Cyber-physical Network}.
 
-The Azure interconnection is realized using the \textit{CommunicationContext}. It implements message encoder and establishes the out-of-band communication stack.
+The Azure interconnection is realized using the \emph{CommunicationContext}. It implements message encoder and establishes the out-of-band communication stack.
 
-The recovered data from the \textit{Message} is obtained from the \textit{PartBindingFactory} using the \textit{IDTOProvider} that defines a contract used to pull the Data Transfer Object (DTO) created from a selected subscription by the \textit{PartBindingFactory}.
+The recovered data from the \emph{Message} is obtained from the \emph{PartBindingFactory} using the \emph{IDTOProvider} that defines a contract used to pull the Data Transfer Object (DTO) created from a selected subscription by the \emph{PartBindingFactory}.
 The transfer process requires data conversion from source to destination encoding, i.e.
@@
 In any case the data recovered from the Message pulled from a subscription is stored locally using the object model based on standard .NET types.
-\textit{PartBindingFactory} maps selected object graph onto the JSON message required by the cloud services.
+\emph{PartBindingFactory} maps selected object graph onto the JSON message required by the cloud services.
 
@@
 Azure and PubSub uses different security mechanism so in the proposed solution establishing security-context is realized independently.
-The \textit{CommunicationContext} is responsible to establish this context as an embedded negotiation phase tightly coupled with establishing interconnection.
+The \emph{CommunicationContext} is responsible to establish this context as an embedded negotiation phase tightly coupled with establishing interconnection.
 
@@
 The generic domain model for the proposed interconnection archetype is presented in the Fig.~\ref*{figure1.StrategyDomainModel}.
-We have highlighted that to promote the separation of concern design principle, the gateway functionality should be implemented as a self-contained dedicated software part embedded in the core \textit{Networking} service of the \textit{Cyber-physical\ node}.
-Main functionality of this component is to transfer process data between \textit{Cyber-physical\ network} using \textit{Networking} services of an existing \textit{Cyber-physical\ node} and \textit{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
+We have highlighted that to promote the separation of concern design principle, the gateway functionality should be implemented as a self-contained dedicated software part embedded in the core \emph{Networking} service of the \emph{Cyber-physical\ node}.
+Main functionality of this component is to transfer process data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
 
@@
 \ref*{figure1.StrategyDomainModel}).
-In the proposed approach the \textit{Embedded Gateway} is derived from the \textit{Consumer} role implemented as as a composable part aggregated by the \textit{Reactive Application}.
+In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as as a composable part aggregated by the \emph{Reactive Application}.
 

### 2020-12-10 Latex/Manuscript.tex
Final review of the latex text #37
- review and add bibliography

@@
 \usepackage{txfonts}
-\usepackage[textsize=tiny]{todonotes}
+\usepackage{doi}
 
@@
 \maketitle
-
-%\listoftodos[TODO list]
 
@@
 Prototyping addresses Microsoft Azure Cloud as an example.
-The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as the open-source (MIT licensed) \todo{Add reference}.
+The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as the open-source (MIT licensed) \cite{OOINetworkingDataRepositoryAzureGateway}.
 The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.
@@
 
-The \textbf{field level gateway} is also build atop of the middleware\todo{add ref} concept.
+The \textbf{field level gateway} is also build atop of the middleware\cite{Middleware-Sunyaev} concept.
 The only difference compared with the \textbf{edge device} is necessity to use officially supported by the cloud vendor services to get connected.
@@
 
-The presented proposals in the article are backed by proof of concept reference implementations\cite{RefWorks:doc:5c66740ae4b081adf5804596} \todo{ref to MP, PS gateway implementation}.
+The presented proposals in the article are backed by proof of concept reference implementations\cite{RefWorks:doc:5c66740ae4b081adf5804596}.
 For this study, prototyping addresses Microsoft Azure cloud products.
@@
 Solutions hosted on Azure are scaled up to millions of users without any additional coding.
-For the development of the todo front-end, it is essential that Azure provides very efficient storage services usefully for the purpose of real-time process data archival.
+For the development of the CPS front-end, it is essential that Azure provides very efficient storage services usefully for the purpose of real-time process data archival.
 Azure provides a vast variety of hybrid connections including but not limited to virtual private networks (VPNs), caches, content delivery networks (CDNs), ExpressRoute, and IoT dedicated services that can be directly used to implement cloud-based front-end for CPS.
@@
 Following the assumption that interconnection between the CPS and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler.
-It must be interconnected with the CPS using an in-band protocol adhering to communications requirements (i.e.~protocol profile, data encoding, time relationships, etc.) governing communication of the parts making it up.
+It must be interconnected with the CPS using an in-band protocol adhering to communications requirements (i.e.
+protocol profile, data encoding, time relationships, etc.) governing communication of the parts making it up.
 At the same time, it must support back-and-forth data transfer to the cloud using out-of-band native for the cloud services.
 The transfer process requires data conversion from source to destination encoding.
-The \emph{IoT\ Hub} is a service hosted in the cloud that supports \emph{IoT\ Central} providing a robust messaging solution - it acts as a central message hub for bi-directional communication \todo{Reference}.
-This communication is transparent, i.e.~it is not data types aware allowing
-any devices to exchange any kind of data. This service is responsible to manage the devices' identity and it offers the following protocol stacks: AMQP, MQTT and HTTPS.
+The \textbf{IoT\ Hub} is a service hosted in the cloud that supports \textbf{IoT\ Central} services providing a robust messaging solution - it acts as a central message hub for bi-directional communication \cite{MicrosoftAzureIoTPlatform}.
+This communication is transparent, i.e.~it is not data types aware allowing any devices to exchange any kind of data.
+This service is responsible to manage the devices' identity and it offers the following protocol stacks: AMQP, MQTT, and HTTPS.
 
@@
 It is expected that the functionality implementation expressed by these interfaces is provided as independent external composable parts.
-The composition is accomplished at run time, and the effective application functionality depends essentially on reusable loosely coupled parts composed applying the dependency injection software engineering and adaptive programming concept.
-
-\todo{ cite{RefWorks:doc:5d9796cbe4b0f66c52dccf04} }
-
-\todo{convert textit => emph}
+The composition is accomplished at run time, and the effective application functionality depends essentially on reusable loosely coupled parts composed applying the dependency injection software engineering and adaptive programming concept \cite{RefWorks:doc:5d9796cbe4b0f66c52dccf04}.
 
@@
 It extends functionality of the \emph{DataManagementSetup} based on the following associated classes:
-
-\todo{Overfull}
 
@@
 \bibliography{Manuscript.bib}
-\bibliographystyle{aiaa-jacs.bst}
+\bibliographystyle{splncs04} %ieeetr, splncs04
 

### 2020-12-10 Latex/Manuscript.tex
Middleware definition and ref #49
- Research Gate

@@
 Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment.
-The discussion addressing the generic architecture concludes that the embedded gateway archetype best suits all requirements.
-To promote separation of concerns and reusability, the proposed architecture of the embedded gateway archetype has been implemented as a composable part of a selected OPC UA PubSub framework.
+The discussion addressing the generic architecture concludes that the embedded gateway software part best suits all requirements.
+To promote separation of concerns and reusability, the proposed architecture of the embedded gateway has been implemented as a composable part of a selected OPC UA PubSub framework.
 
@@
 \begin{itemize}
-      \item \textbf{edge device} - remote cloud agent acting as an intermediary for nodes of the cyber-physical network
-      \item \textbf{field level gateway} - a dedicated custom agent acting as an intermediary for nodes of the cyber-physical network
-      \item \textbf{embedded gateway} - a software part composed into a selected node of the cyber-physical network
+      \item \textbf{edge device} - remote cloud agent acting as an intermediary for nodes of the CPS
+      \item \textbf{field level gateway} - a dedicated custom agent acting as an intermediary for nodes of the CPS
+      \item \emph{Embedded Gateway} - a software part composed into a selected node of the \emph{Cyber-physical network} (\ref*{figure1.StrategyDomainModel})
 \end{itemize}
@@
 Additionally, it allows the selection of initial data processing and execution of them using local resources.
-The \textbf{edge device} may be located close to the leaf devices and attached to the cyber-physical network using protocols applicable only to local computer networks.
+The \textbf{edge device} may be located close to the leaf devices and attached to the \emph{Cyber-physical network} using protocols applicable only to local computer networks.
 In this scenario, it is possible to use a custom protocol stack to get connected to the \textbf{edge device} with the cloud and helps to save the bandwidth thanks to sending only the results of local processing.
@@
 
-The \textbf{field level gateway} is also build atop of the middleware\cite{Middleware-Sunyaev} concept.
+The \textbf{field level gateway} is also build atop of the middleware\cite{Sunyaev2020} concept.
 The only difference compared with the \textbf{edge device} is necessity to use officially supported by the cloud vendor services to get connected.
@@
 
-Unlike the above described solutions, the \textbf{embedded gateway} is not derived from the middleware concept.
+Unlike the above described solutions, the \emph{Embedded Gateway} is not derived from the middleware concept.
 A generic domain model for this interconnection is presented in the Fig.~\ref*{figure1.StrategyDomainModel}.
@@
 
-The \textbf{embedded gateway} archetype relaxes most of the issues described above: \emph{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security-context differences to name only a few.
-The main goal of this article is to provide proof that the \textbf{embedded gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogenous environments in concern.
+The \emph{Embedded Gateway} archetype relaxes most of the issues described above: \emph{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security-context differences to name only a few.
+The main goal of this article is to provide proof that the \emph{Embedded Gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogenous environments in concern.
 The proposed implementation is designed for selected interoperability standard and cloud product.
@@
 \begin{itemize}
-      \tightlist
       \item \textbf{session-oriented}: requires a session that has to be established before any data can be sent between sender and receiver
@@
 From the analysis covered by the Sect.
-\ref*{subs.architecture} it is concluded that the \textbf{embedded gateway} archetype best suits all requirements described above.
+\ref*{subs.architecture} it is concluded that the \emph{Embedded Gateway} archetype best suits all requirements described above.
 It relaxes most of the issues related to \textbf{direct interconnection} and solutions inferred from the middleware concept, i.e.
@@
 
-The described results prove that the \textbf{embedded gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop of the M2M communication compliant with the OPC UA PubSub standard.
+The described results prove that the \emph{Embedded Gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop of the M2M communication compliant with the OPC UA PubSub standard.
 It is worth stressing that there is no dependency on the Client/Server session-oriented relationship.
 This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server.
-The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to embed the \textbf{embedded gateway} component into the OPC UA Client or Server to get connected with the cloud in case of the interactive relationship.
+The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to embed the \emph{Embedded Gateway} component into the OPC UA Client or Server to get connected with the cloud in case of the interactive relationship.
 

### 2020-12-20 Latex/Manuscript.tex
Final review of the latex text #37
- added running header
- added version information
- ready to be shared on Research Gate
References #23
- added reference to OOI V 6.2.1
- reviewed additional papers

@@
 
+%\pagestyle{headings}
+%\headtitle{OOI - Azure Interoperability}
+
+\pagestyle{fancy}
+\fancyhf{}
+\rhead{Rel 1.4.4-Preprint}
+\lhead{OOI - Azure Interoperability}
+\rfoot{Page \thepage}
+
 \newtheorem{definition}{Definition}
@@
 \title{Object-Oriented Internet - Azure Interoperability}
-%\\headtitle{OOI - Azure Interoperability}
 
@@
 Prototyping addresses Microsoft Azure Cloud as an example.
-The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as the open-source (MIT licensed) \cite{OOINetworkingDataRepositoryAzureGateway}.
-The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.
+The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as the open-source (MIT licensed) \cite{mariusz_postol_2020_4361640}.
+The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet \cite{mariusz_postol_2020_4361640}.
 
@@
 
-The presented proposals in the article are backed by proof of concept reference implementations\cite{RefWorks:doc:5c66740ae4b081adf5804596}.
+The presented proposals in the article are backed by proof of concept reference implementations\cite{mariusz_postol_2020_4361640}.
 For this study, prototyping addresses Microsoft Azure cloud products.
@@
 
-A library that meets all these requirements has been implemented consistently with the Object-Oriented Internet paradigm \cite{RefWorks:doc:5c66740ae4b081adf5804596} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }.
+A library that meets all these requirements has been implemented consistently with the Object-Oriented Internet paradigm \cite{mariusz_postol_2020_4361640} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }.
 The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the Object-Oriented Internet concept compliant with the OPC UA PubSub international standard.
@@
 \ref*{introduction}) concept.
-A framework compliant with these requirements has been implemented as an open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) under an umbrella of the project Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.
+A framework compliant with these requirements has been implemented as an open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) under an umbrella of the project Object-Oriented Internet \cite{mariusz_postol_2020_4361640}.
 The library is designed to be a foundation for developing application programs that are taking part in a message-centric communication pattern and interconnected using the reactive networking concept.

### 2020-12-30 Latex/ICCS21MPostoOOIGateway2Azure.tex
Research on publication journal #50
- prepared working space for ICCS21

--- 2020-12-10 Latex/Manuscript.tex
@@
-\documentclass{article}
-\usepackage{geometry}
-\usepackage{fancyhdr}
-\usepackage{amsmath,amsthm,amssymb}
-\usepackage{hyperref}
-\usepackage{cite}
-\usepackage{stfloats}
-\usepackage{url}
-\usepackage{authblk}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
+\documentclass[runningheads]{llncs}
 \usepackage{graphicx}
-\usepackage{amsthm}
-\usepackage{txfonts}
-\usepackage{doi}
-
-\newtheorem{definition}{Definition}
-\newtheorem{theorem}[definition]{Theorem}
-\newtheorem{corollary}[definition]{Corollary}
-\newtheorem{proposition}[definition]{Proposition}
-\newtheorem{example}[definition]{Example}
-
-\providecommand{\tightlist} { \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\providecommand{\keywords}[1]{ \small \textbf{\emph{Keywords---}} #1 }
-
-\title{Object-Oriented Internet - Azure Interoperability}
-%\\headtitle{OOI - Azure Interoperability}
-
-\author[1]{Mariusz Postół, Piotr Szymczak}
-%\author[2]{Piotr Szymczak}
-%\headauthor{Postół M, Szymczak P}
-\affil[1]
-{
- Lodz University of Technology\\
- Institute of Information Technology\\
- ul. Wólczańska 215, 90-924 Lodz, Poland\\
- mailto:mariusz.postol@p.lodz.pl
-}
-\date{}
 
@@
 
-\maketitle
+\title{Object-Oriented Internet\\ Cloud Interoperability}
+\titlerunning{OOI - Cloud Interoperability}
+
+\author{Mariusz Postół\inst{1}\orcidID{0000-0002-9669-0565}  \and Piotr Szymczak\inst{1}\orcidID{1111-2222-3333-4444} }
+\authorrunning{M. Postół et al.}
+
+\institute
+{ Institute of Information Technology, Lodz University of Technology, Łódź, Poland \\
+    \email{mailto:mariusz.postol@p.lodz.pl}\\
+    \url{http://www.it.p.lodz.pl}
+}
+
+\maketitle              % typeset the header of the contribution
 
@@
 
+    \keywords{Industry 4.0 \and Internet of Things \and Object-Oriented Internet \and Cloud Computing \and Industrial communication \and Reactive Networking (RxNetworking)\and Machine to Machine Communication \and OPC Unified Architecture \and Azure}
+
 \end{abstract}
 
-\keywords{ Azure, Cloud Computing, Object-Oriented Internet, Industrial communication, Industry 4.0, Internet of Things, Machine to Machine Communication, OPC Unified Architecture,
-Reactive Networking (RxNetworking)  }
+\section{First Section}
+\subsection{A Subsection Sample}
 
-\maketitle
+Please note that the first paragraph of a section or subsection is not indented. The first paragraph that follows a table, figure, equation etc. does not need an indent, either.
 
-\section{Introduction}\label{introduction}
+Subsequent paragraphs, however, are indented.
 
-All the time, the Information and Communication Technology is providing society with a vast variety of new distributed applications aimed at micro and macro optimization of the industrial processes.
-Obviously, the design foundation of this kind of application has to focus primarily on communication technologies.
-Based on the role humans take while using these applications they can be grouped as follows:
+\subsubsection{Sample Heading (Third Level)}
 
-\begin{itemize}
-      \item \textbf{human-centric} - information origin or ultimate information destination is an operator,
-      \item \textbf{machine-centric} - information creation, consumption, networking, and processing are achieved entirely without human interaction.
-\end{itemize}
+Only two levels of headings should be numbered. Lower level headings remain unnumbered; they are formatted as run-in headings.
 
-A typical \textbf{human-centric} approach is a web-service supporting, for example, a web user interface (UI) to monitor conditions and manage millions of devices and their data in a typical cloud-based IoT approach.
-In this case, it is characteristic that any uncertainty and necessity to make a decision can be relaxed by human interaction.
-Coordination of robots behavior in a work-cell (automation islands) is a \textbf{machine-centric} example.
-In this case, any human interaction must be recognized as impractical or even impossible.
-This interconnection scenario requires the machine to machine communication (M2M) demanding multi-vendor devices integration.
+\paragraph{Sample Heading (Fourth Level)}
 
-From the M2M communication concept, a broader idea of a smart factory can be derived.
-In this M2M  deployment approach, the mentioned robots are only executive assets of an integrated supervisory control system responsible for macro optimization of an industrial process composed as one whole.
-Deployment of the smart factory concept requires a hybrid solution and interconnection of the mentioned above heterogeneous environments.
-This approach is called the fourth industrial revolution and was coined as Industry 4.0.
-It is worth stressing that machines - or more general assets - interconnection is not enough, and additionally, assets interoperability has to be expected for the deployment of this concept.
-In this case, multi-vendor integration makes communication standardization especially important, namely, it is required that the payload of the message is standardized to be factored on the data-gathering site and consumed on the ultimate destination site.
+The contribution should contain no more than four levels of headings. \cite{LiteratureSurveyOnOpenPlatformCommunications}
 
-Highly-distributed solutions used to control real-time process aggregating islands of automation (e.g.~virtual power plants producing renewable energy) additionally must leverage public communication infrastructure, namely the Internet.
-Internet is a demanding environment for highly distributed process control applications designed atop the M2M communication paradigm because
-
-\begin{itemize}
-      \item it is a globally shareable and can be also used by malicious users
-      \item it offers only non-deterministic communication making integration of islands of automation designed against the real-time requirements a difficult task
-\end{itemize}
-
-Today both obstacles can be overcome, and as examples, we have bank account remote control and voice over IP in daily use.
-The first application must be fine-tuned in the context of data security, and the second is very sensitive in regard to time constraints.
-Similar approaches could be applied to adopt the well known in process control industry concepts:
-
-\begin{itemize}
-      \item  Human Machine Interface (HMI)
-      \item Supervisory Control and Data Acquisition (SCADA)
-      \item Distributed Control Systems (DCS)
-\end{itemize}
-
-A detailed examination of these solutions is far beyond the scope of this article.
-It is only worth stressing that, by design, all of them are designed on the foundation of interactive communication.
-Interactive communication is based on a data polling foundation.
-In this case, the application must follow the interactive behavioral model, because it actively polls the data source for more information by pulling data from a sequence that represents the process state in time.
-The application is active in the data retrieval process - it controls the pace of the retrieval by sending the requests at its convenience.
-Such a polling pattern is similar to visiting the books shop and checking out a book.
-After you are done with the book, you pay another visit to check out another one.
-If the book is not available you must wait, but you may read what you selected.
-The client/server archetype is well suited for the mentioned above applications.
-
-After dynamically attaching a new island of automation the control application (responsible for the data pulling) must be reconfigured for this interoperability scenario.
-In other words, in this case, the interactive communication relationship cannot be directly applied because the control application must be informed on how to pull data from a new source.
-As a result, a plug and produce scenario \cite{PlugProduceByModellingSkills} cannot be seamlessly applied.
-A similar drawback must be overcome if for security reasons suitable protection methods have been applied to make network traffic propagation asymmetric.
-It is accomplished using intermediary devices, for example, firewalls, to enforce traffic selective availability based on predetermined security rules against unauthorized access.
-
-Going further, we shall assume that islands of automation are mobile, e.g.~autonomous cars passing a supervisory controlled service area.
-In this case, the behavior of the interconnected assets is particularly important concerning the environment in which they must interact.
-This way we have entered the Internet of Things domain of Internet-based applications.
-
-If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship could relax the problems encountered while the interactive approach is applied.
-In this case, the sessionless publisher-subscriber communication relationship is a typical pattern to implement the abstract reactive interoperability paradigm.
-The sessionless relationship is a message distribution scenario where senders of messages, called publishers, do not send them directly to specific receivers, called subscribers, but instead, categorize the published messages into topics without knowledge about which subscribers if any, there may be.
-Similarly, subscribers express interest in one or more topics and only receive messages that are of interest, without knowledge about which publishers, if any, there are.
-In this scenario, the publishers and subscribers are loosely coupled i.e they are decoupled in time, space and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.
-
-If the \textbf{machine-centric} interoperability - making up islands of automation - must be monitored and/or controlled by a supervisory system cloud computing concept may be recognized as a beneficial solution to replace or expand the mentioned above applications, i.e.~HMI, SCADA, DCS, etc.
-Cloud computing is a method to provide a requested functionality as a set of services.
-There are many examples that cloud computing is useful to reduce costs and increase robustness.
-It is also valuable in case the process data must be exposed to many stakeholders.
-Following this idea and offering control systems as a service, there is required a mechanism created on the service concept and supporting abstraction and virtualization - two main pillars of the cloud computing paradigm.
-In the cloud computing concept, virtualization is recognized as the possibility to share the services by many users, and abstraction hides implementation details.
-
-Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical System (CPS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect.
-\ref*{subs.architecture}).
-
-By design, the \textbf{direct} approach requires that the cloud has to be compliant with the interoperability standard the CPS is built upon - it becomes a consistent part of the CPS.
-Data models, roles, and responsibility differences of both solutions make this approach impractical or even imposable to be applied in typical cases.
-A more detailed description is covered by the Sect.~\ref*{cloud-to-sensors-field-level-connectivity}.
-
-This article addresses further research on the integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M communication and emerging cloud computing as a \textbf{human-centric} front-end in the context of the Industry 4.0 (I4.0) and Industrial Internet of Things (IIoT) disciplines.
-For this integration, a new architecture is proposed to support the reactive relationship of communicating parties.
-To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected.
-Prototyping addresses Microsoft Azure Cloud as an example.
-The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as the open-source (MIT licensed) \cite{OOINetworkingDataRepositoryAzureGateway}.
-The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.
-
-The main goal of this article is to provide proof that:
-
-\begin{enumerate}
-      \item  reactive interoperability M2M communication based on the OPC UA standard can be implemented as a powerful standalone library without dependency on the Client/Server session-oriented archetype
-      \item Azure interoperability can be implemented as an external part employing out-of-band communication without dependency on the OPC UA implementation
-      \item the proposed generic architecture allows that the gateway functionality is implemented as composable part at run-time part - no programming required
-\end{enumerate}
-
-The remainder of this paper is structured as follows.
-Sect.~\ref*{cloud-to-sensors-field-level-connectivity} presents the proposed open and reusable software model.
-It promotes a reactive interoperability pattern and a generic approach to establishing interoperability-context.
-A reference implementation of this archetype is described in Sect.~\ref*{sect.gateway-implementation}.
-The most important findings and future work are summarized in Sect.~\ref*{section.conclusion}.
-
-\section{Sensors to Cloud Field Level Connectivity}\label{cloud-to-sensors-field-level-connectivity}
-
-\subsection{Architecture}\label{subs.architecture}
-
-As it was explained in Sect.~\ref*{introduction}, to follow the Industry 4.0 concept a hybrid environment integrating reactive Machine to Machine interconnection and interactive web-based user interface is required (Sect.
-\ref*{introduction}).
-The main challenge of the solution in concern is to design a generic but reusable architecture that addresses interoperability of these diverse interconnection scenarios ruled by different requirements, namely
-
-\begin{enumerate}
-      \item \textbf{machine-centric} machine to machine real-time mobile interoperability
-      \item \textbf{human-centric} cloud-based front-end
-\end{enumerate}
-
-Interconnection of the reactive \textbf{machine-centric} and interactive \textbf{human-centric} environments can be implemented by applying one of the following scenarios:
-
-\begin{itemize}
-      \item \textbf{direct interconnection} (tightly coupled scenario) - cloud-based dedicated communication services are engaged to attach it to the CPS making up a consistent M2M communication network using a common protocol stack
-      \item \textbf{gateway based interconnection} (loosely coupled scenario) - native build-in communication services allows attaching the cloud to the CPS using an out-of-bound protocol stack
-\end{itemize}
-
-In the solution in concern, the interconnection of assets is not enough hence their interoperability is expected.
-In this case, using the same communication stack must be recognized as only a necessary condition.
-To support interoperability common data understanding is required.
-By design, the direct approach requires that the cloud has to be compliant with the interoperability standard the CPS uses.
-As a result, it becomes a consistent communication node of the CPS.
-Additionally, to meet this requirement the cloud and CPS have to establish directly the same
-
-\begin{itemize}
-      \item semantic-context
-      \item security-context
-\end{itemize}
-
-The possibility to establish a common semantic-context in the multi-vendor environment makes communication standardization especially important.
-In this case, it is required that the encoding of the messages payload exchanged over the network (Data Transfer Object - DTO) is standardized so that the payload can be factored on the data-gathering site and consumed on the ultimate destination data processing sites.
-Security between the data origin and ultimate data destination refers to the protection of messages (security-context) against malicious users.
-It is required that communicating parties are using the same cyber-security measures.
-
-The decision to follow the \textbf{direct interconnection} scenario must be derived from an analysis of the capabilities of available services in concern.
-However, for the development strategy of this type of solutions this analysis can be done partially taking into account two features that can be considered invariable:
-
-\begin{itemize}
-      \item by design the cloud-based services must be virtual - they are used to handle many solutions at the same time
-      \item by design the M2M communication is usually constrained by the real-time requirements
-\end{itemize}
-
-The virtualization of cloud services means that they must be very flexible to handle the attachment of new assets proactively (acting in advance) at run time.
-As a result, by design, the cloud services must be responsible to register and authenticate devices by exposing endpoints in the public network to allow the device to access a provisioning cloud service.
-It requires that a session over the Internet has to be established by the data holding asset at a preparation step.
-
-To meet the requirements of real-time distributed control the CPS may use protocols applicable only to local computer networks (e.g.~multicast IP, Ethernet, TSN \footnote{Time-Sensitive Networking (TSN) Task Group \url{https://1.ieee802.org/tsn/}}, etc.).
-Because the cloud services support only protocols handling interconnection over the Internet the interaction with the cloud requires remote agents, i.e.~agents attached locally to the M2M network and implemented by applying one of the following archetypes:
-
-\begin{itemize}
-      \item \textbf{edge device} - remote cloud agent acting as an intermediary for nodes of the CPS
-      \item \textbf{field level gateway} - a dedicated custom agent acting as an intermediary for nodes of the CPS
-      \item \emph{Embedded Gateway} - a software part composed into a selected node of the \emph{Cyber-physical network} (\ref*{figure1.StrategyDomainModel})
-\end{itemize}
-
-\textbf{Edge device} connects directly to the cloud services but acts as an intermediary for other devices called leaf devices.
-Additionally, it allows the selection of initial data processing and execution of them using local resources.
-The \textbf{edge device} may be located close to the leaf devices and attached to the \emph{Cyber-physical network} using protocols applicable only to local computer networks.
-In this scenario, it is possible to use a custom protocol stack to get connected to the \textbf{edge device} with the cloud and helps to save the bandwidth thanks to sending only the results of local processing.
-In this approach, the \textbf{edge device} is part of cloud vendor products and cannot be recognized as a generic solution that can be used to connect to other clouds at the same time.
-
-The \textbf{field level gateway} is also build atop of the middleware\cite{Sunyaev2020} concept.
-The only difference compared with the \textbf{edge device} is necessity to use officially supported by the cloud vendor services to get connected.
-In this scenario the process data may be transferred to many clouds at the same time provided that the gateway offers this functionality.
-
-\begin{figure}
-      \centering
-      \includegraphics[width=8cm]{../.Media/StrategyDomainModel.png}
-      \caption{Domain model of a generic interconnection concept}\label{figure1.StrategyDomainModel}
-\end{figure}
-
-Unlike the above described solutions, the \emph{Embedded Gateway} is not derived from the middleware concept.
-A generic domain model for this interconnection is presented in the Fig.~\ref*{figure1.StrategyDomainModel}.
-Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \emph{Networking} service of the \emph{Cyber-physical\ node}.
-Main functionality of this component is to transfer selected data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
-
-The \emph{Embedded Gateway} archetype relaxes most of the issues described above: \emph{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security-context differences to name only a few.
-The main goal of this article is to provide proof that the \emph{Embedded Gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogenous environments in concern.
-The proposed implementation is designed for selected interoperability standard and cloud product.
-
-To comply with the Industry 4.0 communication criterion it is required that any product must be addressable over the network via TCP/UDP or IP and has to support the OPC UA Information Model.
-As a result, any product being advertised as Industry 4.0 enabled must be OPC UA-capable somehow.
-To support the multi-vendor environment OPC Unified Architecture interoperability standard has been selected.
-OPC UA supports the following two patterns to be used to transfer data between communicating parties:
-
-\begin{itemize}
-      \item \textbf{session-oriented}: requires a session that has to be established before any data can be sent between sender and receiver
-      \item \textbf{sessionless-oriented}: the sender may start sending messages (called packets or datagrams) to the destination without any preceding handshake procedure
-\end{itemize}
-
-Using the session-oriented communication pattern it is difficult or even impossible to gather and process mobile data (Sec.~\ref*{introduction} ), which is one of the Internet of Things paradigms.
-OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0, UAPart14PubSubMainTechnologyFeatures} offers the sessionless approach as an additional option to session based client-server interoperability relationship and is a consistent part of the OPC UA specifications suit.
-As the result it can be recognized as the IoT ready technology.
-
-The presented proposals in the article are backed by proof of concept reference implementations\cite{RefWorks:doc:5c66740ae4b081adf5804596}.
-For this study, prototyping addresses Microsoft Azure cloud products.
-There are many reasons for selecting Azure to accomplish the cloud-based front-end of Cyber-Physical System (CPS).
-Azure offers Infrastructure as a Service (IaaS) and Platform as a Service (PaaS) capabilities.
-As a result, the platform can be used not only as a cloud-based front-end for CPS.
-By design, the Azure services are compliant with Security Development Lifecycle (SDL) an industry-leading security process.
-It is also compliant with the new international standard for cloud privacy, namely ISO 27018.
-Solutions hosted on Azure are scaled up to millions of users without any additional coding.
-For the development of the CPS front-end, it is essential that Azure provides very efficient storage services usefully for the purpose of real-time process data archival.
-Azure provides a vast variety of hybrid connections including but not limited to virtual private networks (VPNs), caches, content delivery networks (CDNs), ExpressRoute, and IoT dedicated services that can be directly used to implement cloud-based front-end for CPS.
-Because it is also integrated with other Microsoft tools like Office 365, Outlook, and SharePoint using Azure allows preserving investment and exporting process data to the mentioned tools.
-Azure also offers services supporting analytics and intelligence capabilities for further improving business processes and decision making.
-It is the only cloud platform that offers Blockchain as a Service (BaaS), Machine Learning, Bots, and Cognitive APIs capabilities.
-
-Azure aids Internet protocols and open standards such as JSON, XML, SOAP, REST, MQTT, AMQP, and HTTP.
-A software development kits for C\#, Java, PHP, and Ruby are available for custom applications.
-Azure provides services supporting data exchange over the OPC UA, but they don't support PubSub compliant with the OPC UA Part-14.
-Connectivity services on the network use JSON-based Data Transfer Object encoded based on schema derived from the solution metadata.
-
-More detailed description of the selected Azure features in context of the application in concern are covered by the Sec.~\ref*{azure-main-technology-features}.
-
-Based on the sessionless and session-oriented communication patterns examination against the IoT requirements \cite{mpostol2020} it could be concluded that the connectionless pattern better suites issues related to the assets mobility and traffic asymmetry that is characteristic for the application domains in concern.
-Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub  specification.
-According to proposed generic architecture (Fig.~\ref*{figure1.StrategyDomainModel}) to implement the \emph{Embedded\ Gateway} as a composable part of the \emph{Cyber-physical\ node} a library implementing \emph{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
-Additionally, it must be assumed that the library used to deploy \emph{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/PubSub gateway functionality.
-The composition process must be available without modification of the core code of an existing library.
-As a result, the prototyping is to be limited to implementation of the \emph{Embedded\ Gateway} software part only.
-
-A library that meets all these requirements has been implemented consistently with the Object-Oriented Internet paradigm \cite{RefWorks:doc:5c66740ae4b081adf5804596} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }.
-The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the Object-Oriented Internet concept compliant with the OPC UA PubSub international standard.
-According to the presented implementation and evaluation, using the dependency injection and late binding, the application program can be seamlessly adapted to the production environment and scales well.
-This approach also improves flexibility and adaptability of the existing solutions against any modification of the production environment including but not limited to the selected interoperability standard change.
-
-Sect.~\ref*{ooi-main-technology-features} provides a more detailed description of this library and an external part deployment process that is to be used to implement new functionality supporting \emph{Embedded\ Gateway}.
-
-The following subsections cover the description of the current state of technologies concerning Azure cloud-based IoT enabler and OPC UA PubSub.
-Sect.~\ref*{azure-main-technology-features} analyzes data presentation user interface, available native communication services, and data/metadata model offered by Microsoft Azure.
-The discussion covered by this section is the foundation for selecting services utilized to expose process data and suitable protocol stack to support interconnection.
-In Sect.~\ref*{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a foundation for further decisions addressing the systematic design of the interoperability of the CPS and cloud-based front-end.
-
-\subsection{Azure Main Technology Features}\label{azure-main-technology-features}
-
-\subsubsection{Services}\label{services}
-
-Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical Systems (CPS) designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end requires decisions addressing the selection of the services supporting web user interface capable to expose process data.
-In this context, the service is any autonomous (with own identity) software component or module that is interfacing with selected CPS for data collection, analysis, and also remote control.
-Microsoft Azure is a cloud-based product.
-It offers a vast variety of services.
-This virtual environment handles an unlimited number of users and devices organized using a solution container concept.
-The solution aggregates users, devices, services, and required additional resources scoping on a selected scenario.
-It also serves as a context that provides a scope to the identifiers (the names of devices, users, process data entities, etc) inside it.
-Solutions are used to organize deployment entities into logical groups and prevent identity collisions.
-
-The \textbf{IoT\ Central} service provides a process data visualization
-user interface. To make this interface meaningful metadata called device
-template is used to describe devices.
-
-Following the assumption that interconnection between the CPS and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler.
-It must be interconnected with the CPS using an in-band protocol adhering to communications requirements (i.e.
-protocol profile, data encoding, time relationships, etc.) governing communication of the parts making it up.
-At the same time, it must support back-and-forth data transfer to the cloud using out-of-band native for the cloud services.
-The transfer process requires data conversion from source to destination encoding.
-The \textbf{IoT\ Hub} is a service hosted in the cloud that supports \textbf{IoT\ Central} services providing a robust messaging solution - it acts as a central message hub for bi-directional communication \cite{MicrosoftAzureIoTPlatform}.
-This communication is transparent, i.e.~it is not data types aware allowing any devices to exchange any kind of data.
-This service is responsible to manage the devices' identity and it offers the following protocol stacks: AMQP, MQTT, and HTTPS.
-
-Before process data can be exposed using a web user interface the data source must be associated with an appropriate solution and validated to make sure that the security rules are not violated.
-It is hard to assume that the security rules governing the CPS may also apply to the cloud-based services.
-In the gateway scenario, they can be mapped on each other or be entirely independent.
-The \emph{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper service for \emph{IoT\ Hub} that enables devices' connection process management, upon device providing valid identity attestation it assigns the device to an appropriate \emph{IoT\ Hub} instance and returns to the device connection parameters, which allow direct connection with given \emph{IoT\ Hub} service.
-The device proceeds to use the same attestation in \emph{IoT\ Hub} connection and based on it, is granted authorization to selected operations including but not limited to data transfer and updating the user interface.
-
-It is worth stressing that interaction of the offered by the Azure
-services can be configured flexibly, and as a result, the presented
-above selection of services must be recognized as an example only. The
-\textbf{IoT\ Central} can be also seamlessly integrated with other
-services as needed. The following services could also be considered to
-build cloud-based automation solution:
-
-\begin{itemize}
-      \item \emph{Industrial\ IoT} - discovering OPC UA enabled servers in a factory network and register them in Azure \emph{IoT\ Hub} implemented using \emph{IoT\ Edge}
-      \item \emph{Digital\ Twins} - managing the graph of digital twins, which are to represent some real-world process or entity
-\end{itemize}
-
-\emph{Industrial\ IoT} promotes OPC UA client/server archetype used to
-achieve direct and interactive interoperability implemented using
-\emph{IoT\ Edge} services that allow extracting initial data
-processing to local premises based on the edge concept.
-\emph{Digital\ Twins} is an emerging concept to use an observer to
-replicate selected process state and behavior. The possibility to add
-value as a result of using these services must be subject to further
-research.
-
-\subsubsection{Data Interchange}\label{data-interchange}
-
-System components interoperability means the necessity of the
-information exchange between them. The main challenge of
-interoperability implementation is that information is abstract -- it is
-knowledge describing the process in concern state and behavior,
-e.g.~temperature in a boiler, a car speed, an account balance, etc.
-Obviously, abstraction cannot be processed by the cyber-physical
-machines. It is also impossible to transfer abstraction from one place
-to another over the network.
-
-Fortunately, computer science offers a workaround to address that impossibility - the information must be represented as a binary stream.
-In consequence, we can usually use both terms as interchangeable ones while talking about ICT systems.
-Unfortunately, these terms must be precisely observed in the context of further discussion, because we must be aware of the fact that the same information could have many different but equivalent representations.
-In other words, the same information can be represented by a vast variety of different binary patterns.
-For example, numbers may be represented using 2's Complement and Floating-Point binary representations.
-
-It should be nothing new for us, as it is obvious that the same
-information printed as a text in regional newspapers in English, German,
-Polish, etc. does not resemble one another, but the text meaning should
-always be the same. To understand a newspaper we must learn the
-appropriate language. To understand the binary data we must have defined
-a data type -- a description of how to create an appropriate bits
-pattern (syntax) and rules needed to assign the information (semantics),
-i.e.~make any correct bitstream meaningful. Concluding, to make two
-systems interoperable, a semantic-context must be established. The type
-plays the role of metadata, a set of data that describes other data.
-Metadata term is frequently used if the semantic-context is defined
-using a native language to select built-in types engaging a
-general-purpose graphical user interface.
-
-Using the data type definitions to describe information interchange between communicating parties allows:
-
-\begin{itemize}
-      \item development against a type definition of the user interface
-      \item implementation of the functionality of the bitstreams conversion in advance
-\end{itemize}
-
-Having defined types in advance, a gateway may provide dedicated conversions functionality, i.e.~replacing bitstreams used by the CPS by equivalent ones for the cloud-based services.
-The Azure offers a vast variety of built-in types ready to be used in common cases, but not necessarily there are equivalent counterparts in use by the CPS.
-Additionally, the data conversion must address the following issues:
-
-\begin{itemize}
-      \item usually to covert data from source to destination representation, the middleware software native types must be used
-      \item if the out of the box set of types is not capable of fulfilling more demanding needs, custom data types must be defined
-\end{itemize}
-
-Although the data conversion is a run-time gateway task the
-implementation of the conversion algorithms must be recognized as an
-engineering task, and therefore this topic is not considered for further
-discussion.
-
-In \textbf{IoT\ Central} a CPS is represented as a set
-of devices. The characteristics and behavior of each device kind are
-described by the device template. This Device Template (DT) contains
-also metadata describing the data exchanged over the
-wire with the CPS called Device Capability Model
-(DCM). Additionally, the DT contains properties, customization, and
-views definitions used by the service locally. As an option, DCM
-expressed as a JSON-LD can be imported into a Device Template.
-\textbf{IoT\ Central} allows also to create and edit a DCM using the
-dedicated web UI. A JSON file containing DCM can be derived from an
-information model used as a foundation to establish the semantic-context
-applied to achieve interoperability of the devices interconnected as the
-CPS. DCM development against any external information
-model is a design-time task and should be supported by dedicated
-development tools. In any case, the data interchanged between the cloud
-and the gateway must be compliant with the DCM, hence the middleware
-software must be aware of conversions that must be applied to achieve
-this interoperability.
-
-\subsubsection{Connectivity}\label{subsubsection.connectivity}
-
-From the cloud side, it is proposed to employ the \emph{IoT\ Hub} service to handle the network traffic targeting the cyber-physical system.
-This service offers profiles of the AMQP, MQTT, and HTTPS protocol stacks.
-In any case, process data is transparently transferred back-and-forth to the upper layer \textbf{IoT\ Central} service.
-Hence, the payload formatting is determined by the DCM associated with the \textbf{IoT\ Central} solution.
-
-The Azure supports HTTP, AMQP, and MQTT protocol stacks which are all standard ones.
-Consequently, it is possible to apply any available ones compliant with an appropriate specification to achieve connectivity.
-In this case, all parameters required to establish semantic and security contexts are up to the gateway responsibility.
-Alternatively, the API offered by the dedicated frameworks (libraries) may be used.
-Using a framework the configuration process may be reduced significantly, and the communication protocol selection has only an indirect impact on the interoperability features.
-The Azure interconnection may be obtained using the following \emph{Microsoft.Azure} packages:
-
-\begin{itemize}
-      \item \emph{Devices} - Service SDK for Azure IoT Devices
-      \item \emph{Devices.Client} - Device SDK for Azure \emph{IoT\ Hub} including dependencies implementing MQTT and AMQP communication
-      \item \emph{Devices.Shared} - Common code for Azure IoT Device and Service SDK
-      \item \emph{Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
-      \item \emph{Devices.Provisioning.Transport.*} - Provisioning Device Client Transports (HTTPS, AMQP, MQTT) for Azure IoT Devices
-\end{itemize}
-
-\subsection{OOI Main Technology Features}\label{ooi-main-technology-features}
-
-To promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub (Sect.
-\ref*{subs.architecture}) and support the \emph{Reactive Interoperability} (Sect.
-\ref*{introduction}) concept.
-A framework compliant with these requirements has been implemented as an open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) under an umbrella of the project Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.
-The library is designed to be a foundation for developing application programs that are taking part in a message-centric communication pattern and interconnected using the reactive networking concept.
-The diagram in Fig.~\ref*{figure2.UADataApplicationArchitecture} shows the relationship between the library (\emph{SDK}) and external parts composing any reactive networking application (\emph{Reactive\ Application}).
-The \emph{Reactive Application} is an aggregation of parts implementing the \emph{Producer} and \emph{Consumer} roles.
-By design, they support access to real-time process data, hence they are recognized as an extension of \emph{DataRepository} class.
-To implement the \emph{DataRepository} dedicated implementation of the \emph{IBinding} interface should be provided to create a bridge between CPS and an external row data represented by the \emph{LocalResources} class.
-A more in-depth description of the \emph{OOI Reactive Application} library enabling data exchange over a network using the reactive networking pattern is in \cite{mpostol2020}.
-
-\begin{figure}
-      \centering
-      \includegraphics[width=8cm]{../.Media/UADataApplicationArchitecture.png}
-      \caption{Reactive interoperability implementation}\label{figure2.UADataApplicationArchitecture}
-\end{figure}
-
-From the above discussion, we can learn that the main design decisions must concern standardization and flexibility.
-Standardization needs the selection of an international interoperability specification to make the library ready to be adopted by the multi-vendor environment.
-Flexibility requires an architecture that promotes the polymorphic independent implementation of essential functions.
-
-Piece by piece integration of a cyber-physical system using multi-vendor products requires that M2M communication employs international standards as the interoperability foundation.
-OPC Unified Architecture Part 14 PubSub has been selected in this respect (Sect.
-\ref*{subs.architecture}).
-By design, this standard should support the required publisher-subscriber communication pattern.
-It must be stressed, that by design, the specification provides only an abstract interoperability definition.
-Abstract means that the standard must not limit the implementation strategy.
-
-Many parts in the domain model presented in Fig.~\ref*{figure2.UADataApplicationArchitecture} requires a polymorphic approach to implementation.
-To promote the polymorphic ready solution the following concepts have been adopted:
-
-\begin{itemize}
-      \item \textbf{separation of concerns} - to allow an independent development of the parts~\cite{RefWorks:doc:5d92609be4b02eb43d372bd1}
-      \item \textbf{dependency injection} - to allow late binding of separately implemented parts~\cite{RefWorks:doc:5d925b77e4b030b4e0596f5d}
-\end{itemize}
-
-To promote the polymorphic approach, the library has a factory class called \emph{DataManagementSetup} that is a placeholder to gather all injection points used to compose external parts.
-To be injected the parts must be compliant with an appropriate contract expressed as the following interfaces:
-
-\begin{itemize}
-      \item \emph{IBindingFactory} - bidirectional data exchange with the underlying process
-      \item \emph{IConfigurationDataFactory} - the configuration data access
-      \item \emph{IMessageHandlerFactory} - \emph{Message} entities pushing to/pulling from the wire
-      \item \emph{IEncodingFactory} - searching a dictionary containing value converters
-\end{itemize}
-
-It is expected that the functionality implementation expressed by these interfaces is provided as independent external composable parts.
-The composition is accomplished at run time, and the effective application functionality depends essentially on reusable loosely coupled parts composed applying the dependency injection software engineering and adaptive programming concept \cite{RefWorks:doc:5d9796cbe4b0f66c52dccf04}.
-
-The \emph{DataRepository} represents data holding assets in the \emph{Reactive Application} implementing the \emph{IBindingFactory} interface.
-It captures functionality responsible for accessing the external process data from \emph{LocalResources}.
-The \emph{LocalResources} represents an external part that has a very broad usage purpose.
-For example, it may be any kind of the process data source/destination, i.e.
-raw data (e.g.
-PLC internal registers), OPC UA Address Space Management, cloud, file, database, graphical user interface, to name only a few.
-
-Depending on the expected network role the library supports the implementation of:
-
-\begin{itemize}
-      \item \emph{Consumer} - entities processing data from incoming messages,
-      \item \emph{Producer} - entities gathering process data and populating outgoing messages.
-\end{itemize}
-
-The \emph{Consumer} and \emph{Producer} classes are derived from the \emph{DataRepository} (Fig.~\ref*{figure2.UADataApplicationArchitecture}).
-The \emph{Consumer} uses the \emph{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
-The received data may be processed or driven to any data destination, e.g.
-cloud-based front-end.
-The \emph{Producer} mirrors the \emph{Consumer} functionality and, after reading data from an associated source, populates the \emph{Message} using the gathered data.
-
-By design, the \emph{DataRepository} and associated entities, i.e.~\emph{Local Resources}, \emph{Consumer}, \emph{Producer} are embedded in external parts, and consequently, the application scope may cover practically any concern that can be separated from the core \emph{Reactive Application} implementation.
-
-The application startup phase concerns all the parts composed to make a running instance of the application program using the dependency injection approach to allow separate development and late binding.
-This approach makes any modification straightforward at any development and maintenance stage.
-From the end-user point of view, the composition process of the running program using independently developed parts is invisible.
-Because in any case a single program instance is created in a typical approach, we shall expect a commonly shared configuration mechanism providing mutually exclusive parameters to separately developed parts.
-This scenario has been addressed by the proposed implementation thanks to making the configuration expandable.
-
-From the discussion covered by the Sect.
-\ref*{subs.architecture} we can infer that the interoperability of communicating parties requires establishing a semantic-context and security-context between them.
-If the received data is driven to any external data destination (e.g.
-cloud-based front-end) using out-of-band protocol semantic-context and security-context must be defined for this interoperability relationship.
-There are a vast variety of possibilities for how to define these contexts.
-Anyway, the most common starting point is the configuration.
-The proposed approach to instantiate the application as a set of composable parts is very useful in this respect because it makes it possible to expand the core configuration functionality and adapt it to be helpful also in this case.
-Therefore, the semantic-context may be created based on the configuration using the implementation of the \emph{IConfigurationDataFactory} interface.
-
-Concluding, decoupling of this functionality implementation using an abstract contract and late binding mechanism allows:
-
-\begin{itemize}
-      \item implementation of practically any configuration management scenario,
-      \item modification of this functionality later after releasing the library or deploying the application program in the production environment.
-\end{itemize}
-
-\section{Azure - Object-Oriented Internet Interoperability Implementation}\label{sect.gateway-implementation}
-
-\subsection{Implementation Architecture}\label{subsection.GatewayImplementationArchitecture}
-
-A generic domain model presenting interconnection architecture between the Azure \emph{Cloud-based\ Front-end} and \emph{Cyber-physical\ node} attached to the \emph{Cyber-physical\ network} is presented in Fig.
-\ref*{figure1.StrategyDomainModel}.
-It is proposed to implement the \emph{Cyber-physical\ node} by adopting the \emph{Reactive Application} archetype compliant with the reactive interoperability concept (Fig.
-\ref*{figure2.UADataApplicationArchitecture}) described in the Sect.
-\ref*{ooi-main-technology-features}.
-Merging selected entities of this archetype into the proposed domain model (Fig.
-\ref*{figure1.StrategyDomainModel}) lead to a model expressed as the diagram presented in Fig.
-\ref*{figure3.ImplementationDomainModel}.
-In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as as a composable part aggregated by the \emph{Reactive Application}.
-
-\begin{figure}
-      \centering
-      \includegraphics[width=8cm]{../.Media/ImplementationDomainModel.png}
-      \caption{Architecture Domain Model}\label{figure3.ImplementationDomainModel}
-\end{figure}
-
-\hyphenation{PartData-Mana-gement-Setup}
-
-In the final deployment architecture (Fig.
-\ref*{figure4.ImplementationArchitecture}) the \emph{Consumer} role has been realized by the \emph{PartDataManagementSetup} that is derived from \emph{DataManagementSetup} provided by the library.
-\emph{Networking} (SDK) was removed from this diagram for the sake of simplicity.
-Instantiating \emph{PartDataManagementSetup} is the first step for bootstrapping process of the \emph{Consumer} role functionality.
-This class provides an entry point to initialize all properties, which are injection points of all parts composing this role.
-It extends functionality of the \emph{DataManagementSetup} based on the following associated classes:
-
-\begin{figure}
-      \centering
-      \includegraphics[width=10cm]{../.Media/ImplementationArchitecture.png}
-      \caption{Implementation Architecture}\label{figure4.ImplementationArchitecture}
-\end{figure}
-
-\begin{enumerate}
-      \item \emph{PartConfigurationFactory} - to get access to the application configuration
-      \item \emph{PartBindingFactory} - to gather the data recovered from the \emph{Message} instances pulled from the wire
-      \item \emph{CommunicationContext} - to handle communication with the Azure services
-\end{enumerate}
-
-In this case, the implementation of the \emph{IConfigurationFactory} interface is based entirely on the \emph{Networking} library.
-The implementation provided by the library is generic, but it is flexible enough to meet all the requirements, which warrants no need for further modifications for adoption.
-It is ready to provide all necessary configuration parameters to establish semantic and security contexts related to Azure interoperability.
-
-The \emph{PartBindingFactory} implements the \emph{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
-The received data is driven to \emph{CommunicationContext} for further encoding and finally pushing it to the Azure services using configured out-of-band protocol.
-
-\emph{IEncodingFactory} and \emph{IMessageHandlerFactory} interfaces (Fig.
-\ref*{figure2.UADataApplicationArchitecture}) have been implemented in independent libraries and ae not considered for any modifications to deploy \emph{Embedded Gateway} functionality.
-The current implementation of the mentioned interfaces is localized at run time as services using an instance of the \emph{IServiceLocator}\footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} }.
-In this example, it is assumed that \emph{IServiceLocator} is implemented to resolve references to any external services.
-Both interfaces are used to manage interconnection of the node with the \emph{Cyber-physical Network}.
-
-The Azure interconnection is realized using the \emph{CommunicationContext}. It implements message encoder and establishes the out-of-band communication stack.
-
-The recovered data from the \emph{Message} is obtained from the \emph{PartBindingFactory} using the \emph{IDTOProvider} that defines a contract used to pull the Data Transfer Object (DTO) created from a selected subscription by the \emph{PartBindingFactory}.
-The transfer process requires data conversion from source to destination encoding, i.e.
-replacing bitstreams used by the CPS by equivalent ones for the cloud-based services.
-The Azure offers a vast variety of built-in types ready to be used in common cases, but not necessarily there are equivalent counterparts in use by the CPS.
-The Azure uses JSON based Data Transfer Object encoding and schema defined based on the solution metadata.
-The PubSub uses JSON and binary Data Transfer Object encodings.
-In any case the data recovered from the Message pulled from a subscription is stored locally using the object model based on standard .NET types.
-\emph{PartBindingFactory} maps selected object graph onto the JSON message required by the cloud services.
-
-The encoded JSON messages must be transferred over the network to Azure using the selected protocol stack.
-The Azure supports standard protocols (Sec.
-\ref*{azure-main-technology-features}).
-Consequently, it is possible to apply any available ones compliant with an appropriate specification to achieve connectivity.
-In the proposed gateway implementation the Azure interconnection has been obtained using the packages described in Sect.
-\ref*{subsubsection.connectivity}.
-
-Azure and PubSub uses different security mechanism so in the proposed solution establishing security-context is realized independently.
-The \emph{CommunicationContext} is responsible to establish this context as an embedded negotiation phase tightly coupled with establishing interconnection.
-
-\section{Conclusion}\label{section.conclusion}
-
-Nowadays, the macro optimization of the industrial processes requires an integration of a vast variety of distributed applications provided by the Information and Communication Technology.
-It requires further research on the integration of \textbf{machine-centric} Cyber-Physical Systems (CPS) with \textbf{human-centric} front-end in the context of new emerging disciplines, i.e.
-Industry 4.0 and the Industrial Internet of Things (Sect.
-\ref*{introduction}).
-
-CPS is composed using the multi-vendor components (data holding assets) interconnected atop of the Machine To Machine (M2M) communication.
-In many applications, the dynamic nature of the CPS must be considered.
-Dynamic nature means that interconnected assets may be added/removed from the network at any time.
-By design, typically CPS must fulfill the real-time and mobility of the assets requirements.
-
-Highly-distributed solutions used to control/monitor a set of geographically spread islands of automation (e.g.
-virtual power plants producing renewable energy) additionally must leverage public communication infrastructure, namely the Internet.
-If islands of automation must be controlled over the Internet, the cloud computing concept may be recognized as a reasonable answer.
-Following this concept, the cloud-based supervisory control functionality is applied as a set of services employing abstraction and virtualization - two main pillars of the cloud computing paradigm.
-In the cloud computing concept, virtualization is recognized as the possibility to share the services by many users, and abstraction hides implementation details.
-
-The main goal of this research is working out a new generic architecture and deployment scenario applicable for the integration of the \textbf{machine-centric} CPS and emerging cloud computing as a \textbf{human-centric} front-end.
-
-If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship\cite{mpostol2020} could alleviate the challenges posed by the interactive approach.
-The real-time multi-vendor environment makes communication standardization especially important.
-To support this environment, OPC Unified Architecture \cite{RefWorks:doc:5ac86c98e4b009947bbb874c} interoperability standard has been selected.
-As it was pointed out in the Sect.
-\ref*{subs.architecture} using OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} the aggregation of nodes by the network is loosely coupled, i.e.
-nodes can be added and removed from the network dynamically, and nodes may represent mobile data holding assets.
-
-From the analysis covered by the Sect.
-\ref*{subs.architecture} it is concluded that the \emph{Embedded Gateway} archetype best suits all requirements described above.
-It relaxes most of the issues related to \textbf{direct interconnection} and solutions inferred from the middleware concept, i.e.
-\textbf{edge device} - remote cloud agent and \textbf{field level gateway} - a dedicated custom agent.
-Additionally, it could be used to connect to many independent clouds at the same time.
-The generic domain model for the proposed interconnection archetype is presented in the Fig.~\ref*{figure1.StrategyDomainModel}.
-We have highlighted that to promote the separation of concern design principle, the gateway functionality should be implemented as a self-contained dedicated software part embedded in the core \emph{Networking} service of the \emph{Cyber-physical\ node}.
-Main functionality of this component is to transfer process data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
-
-To promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub (Sect.
-\ref*{subs.architecture}) and support the \emph{Reactive Interoperability} (Sect.
-\ref*{introduction}) concept.
-We proposed to use an open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) (Fig.~\ref*{figure2.UADataApplicationArchitecture}) for this purpose.
-It is worth stressing that based on this approach only dedicated functionality related to the communication with the cloud must be implemented.
-
-We derived the final model presented in Fig.
-\ref*{figure4.ImplementationArchitecture} by merging selected entities from the \emph{Networking} library (Fig.~\ref*{figure2.UADataApplicationArchitecture}) into the generic interconnection domain model (Fig.
-\ref*{figure1.StrategyDomainModel}).
-In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as as a composable part aggregated by the \emph{Reactive Application}.
-
-The proposals are backed by proof of concept reference implementations.
-Prototyping addresses Microsoft Azure cloud as an example.
-The outcome has been just published on GitHub as the open-source (MIT licensed) repository.
-The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.
-
-The described results prove that the \emph{Embedded Gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop of the M2M communication compliant with the OPC UA PubSub standard.
-It is worth stressing that there is no dependency on the Client/Server session-oriented relationship.
-This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server.
-The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to embed the \emph{Embedded Gateway} component into the OPC UA Client or Server to get connected with the cloud in case of the interactive relationship.
-
-In the proposed approach the cloud interoperability is obtained by implementing a dedicated part employing out-of-band communication only without dependency on the OPC UA functionality at all.
-It is worth stressing that the gateway functionality is implemented as a part - composable to the whole without programming skills.
-Because the part is composed at the runtime it makes it possible to modify its functionality later after releasing the library or even deploying the application program in the production environment.
-
-Concluding, the paper describes a proof of the concept that applying the proposed architecture and deployment scenario it is possible to integrate selected cloud services (e.g.
-\textbf{Azure\ IoT\ Central}) with the \emph{Cyber-physical network} interconnected as one whole atop of the OPC UA PubSub.
-It is in contrast to interconnecting cloud-based front-end services with the selected \emph{ Address\ Space} exposed by a selected OPC UA server limiting the PubSub role to data exporter transferring the data out of the OPC UA ecosystem.
-
-\bibliography{Manuscript.bib}
-\bibliographystyle{splncs04} %ieeetr, splncs04
+\bibliography{Manuscript}
+\bibliographystyle{splncs04}
 

### 2020-12-30 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Research on publication journal #50
- setup for ICCS21 finished - ready to copy text from the master file Manuscript.tex
Research on publication journal #50
- working on ICCS21

--- 2020-12-30 Latex/ICCS21MPostoOOIGateway2Azure.tex
@@
 \usepackage{graphicx}
+\usepackage{cite}
+\usepackage{hyperref}
 
@@
 
-\section{First Section}
-\subsection{A Subsection Sample}
+section{Introduction}\label{introduction}
 
-Please note that the first paragraph of a section or subsection is not indented. The first paragraph that follows a table, figure, equation etc. does not need an indent, either.
+All the time, the Information and Communication Technology is providing society with a vast variety of new distributed applications aimed at micro and macro optimization of the industrial processes.
+Obviously, the design foundation of this kind of application has to focus primarily on communication technologies.
+Based on the role humans take while using these applications they can be grouped as follows:
 
-Subsequent paragraphs, however, are indented.
+\begin{itemize}
+      \item \textbf{human-centric} - information origin or ultimate information destination is an operator,
+      \item \textbf{machine-centric} - information creation, consumption, networking, and processing are achieved entirely without human interaction.
+\end{itemize}
 
-\subsubsection{Sample Heading (Third Level)}
+A typical \textbf{human-centric} approach is a web-service supporting, for example, a web user interface (UI) to monitor conditions and manage millions of devices and their data in a typical cloud-based IoT approach.
+In this case, it is characteristic that any uncertainty and necessity to make a decision can be relaxed by human interaction.
+Coordination of robots behavior in a work-cell (automation islands) is a \textbf{machine-centric} example.
+In this case, any human interaction must be recognized as impractical or even impossible.
+This interconnection scenario requires the machine to machine communication (M2M) demanding multi-vendor devices integration.
 
-Only two levels of headings should be numbered. Lower level headings remain unnumbered; they are formatted as run-in headings.
+From the M2M communication concept, a broader idea of a smart factory can be derived.
+In this M2M  deployment approach, the mentioned robots are only executive assets of an integrated supervisory control system responsible for macro optimization of an industrial process composed as one whole.
+Deployment of the smart factory concept requires a hybrid solution and interconnection of the mentioned above heterogeneous environments.
+This approach is called the fourth industrial revolution and was coined as Industry 4.0.
+It is worth stressing that machines - or more general assets - interconnection is not enough, and additionally, assets interoperability has to be expected for the deployment of this concept.
+In this case, multi-vendor integration makes communication standardization especially important, namely, it is required that the payload of the message is standardized to be factored on the data-gathering site and consumed on the ultimate destination site.
 
-\paragraph{Sample Heading (Fourth Level)}
+Highly-distributed solutions used to control real-time process aggregating islands of automation (e.g.~virtual power plants producing renewable energy) additionally must leverage public communication infrastructure, namely the Internet.
+Internet is a demanding environment for highly distributed process control applications designed atop the M2M communication paradigm because
 
-The contribution should contain no more than four levels of headings. \cite{LiteratureSurveyOnOpenPlatformCommunications}
+\begin{itemize}
+      \item it is a globally shareable and can be also used by malicious users
+      \item it offers only non-deterministic communication making integration of islands of automation designed against the real-time requirements a difficult task
+\end{itemize}
 
-\bibliography{Manuscript}
+Today both obstacles can be overcome, and as examples, we have bank account remote control and voice over IP in daily use.
+The first application must be fine-tuned in the context of data security, and the second is very sensitive in regard to time constraints.
+Similar approaches could be applied to adopt the well known in process control industry concepts:
+
+\begin{itemize}
+      \item  Human Machine Interface (HMI)
+      \item Supervisory Control and Data Acquisition (SCADA)
+      \item Distributed Control Systems (DCS)
+\end{itemize}
+
+A detailed examination of these solutions is far beyond the scope of this article.
+It is only worth stressing that, by design, all of them are designed on the foundation of interactive communication.
+Interactive communication is based on a data polling foundation.
+In this case, the application must follow the interactive behavioral model, because it actively polls the data source for more information by pulling data from a sequence that represents the process state in time.
+The application is active in the data retrieval process - it controls the pace of the retrieval by sending the requests at its convenience.
+Such a polling pattern is similar to visiting the books shop and checking out a book.
+After you are done with the book, you pay another visit to check out another one.
+If the book is not available you must wait, but you may read what you selected.
+The client/server archetype is well suited for the mentioned above applications.
+
+After dynamically attaching a new island of automation the control application (responsible for the data pulling) must be reconfigured for this interoperability scenario.
+In other words, in this case, the interactive communication relationship cannot be directly applied because the control application must be informed on how to pull data from a new source.
+As a result, a plug and produce scenario \cite{PlugProduceByModellingSkills} cannot be seamlessly applied.
+A similar drawback must be overcome if for security reasons suitable protection methods have been applied to make network traffic propagation asymmetric.
+It is accomplished using intermediary devices, for example, firewalls, to enforce traffic selective availability based on predetermined security rules against unauthorized access.
+
+Going further, we shall assume that islands of automation are mobile, e.g.~autonomous cars passing a supervisory controlled service area.
+In this case, the behavior of the interconnected assets is particularly important concerning the environment in which they must interact.
+This way we have entered the Internet of Things domain of Internet-based applications.
+
+If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship could relax the problems encountered while the interactive approach is applied.
+In this case, the sessionless publisher-subscriber communication relationship is a typical pattern to implement the abstract reactive interoperability paradigm.
+The sessionless relationship is a message distribution scenario where senders of messages, called publishers, do not send them directly to specific receivers, called subscribers, but instead, categorize the published messages into topics without knowledge about which subscribers if any, there may be.
+Similarly, subscribers express interest in one or more topics and only receive messages that are of interest, without knowledge about which publishers, if any, there are.
+In this scenario, the publishers and subscribers are loosely coupled i.e they are decoupled in time, space and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.
+
+If the \textbf{machine-centric} interoperability - making up islands of automation - must be monitored and/or controlled by a supervisory system cloud computing concept may be recognized as a beneficial solution to replace or expand the mentioned above applications, i.e.~HMI, SCADA, DCS, etc.
+Cloud computing is a method to provide a requested functionality as a set of services.
+There are many examples that cloud computing is useful to reduce costs and increase robustness.
+It is also valuable in case the process data must be exposed to many stakeholders.
+Following this idea and offering control systems as a service, there is required a mechanism created on the service concept and supporting abstraction and virtualization - two main pillars of the cloud computing paradigm.
+In the cloud computing concept, virtualization is recognized as the possibility to share the services by many users, and abstraction hides implementation details.
+
+Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical System (CPS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect.
+\ref*{subs.architecture}).
+
+By design, the \textbf{direct} approach requires that the cloud has to be compliant with the interoperability standard the CPS is built upon - it becomes a consistent part of the CPS.
+Data models, roles, and responsibility differences of both solutions make this approach impractical or even imposable to be applied in typical cases.
+A more detailed description is covered by the Sect.~\ref*{cloud-to-sensors-field-level-connectivity}.
+
+This article addresses further research on the integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M communication and emerging cloud computing as a \textbf{human-centric} front-end in the context of the Industry 4.0 (I4.0) and Industrial Internet of Things (IIoT) disciplines.
+For this integration, a new architecture is proposed to support the reactive relationship of communicating parties.
+To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected.
+Prototyping addresses Microsoft Azure Cloud as an example.
+The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as the open-source (MIT licensed) \cite{mariusz_postol_2020_4361640}.
+The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet \cite{mariusz_postol_2020_4361640}.
+
+The main goal of this article is to provide proof that:
+
+\begin{enumerate}
+      \item  reactive interoperability M2M communication based on the OPC UA standard can be implemented as a powerful standalone library without dependency on the Client/Server session-oriented archetype
+      \item Azure interoperability can be implemented as an external part employing out-of-band communication without dependency on the OPC UA implementation
+      \item the proposed generic architecture allows that the gateway functionality is implemented as composable part at run-time part - no programming required
+\end{enumerate}
+
+The remainder of this paper is structured as follows.
+Sect.~\ref*{cloud-to-sensors-field-level-connectivity} presents the proposed open and reusable software model.
+It promotes a reactive interoperability pattern and a generic approach to establishing interoperability-context.
+A reference implementation of this archetype is described in Sect.~\ref*{sect.gateway-implementation}.
+The most important findings and future work are summarized in Sect.~\ref*{section.conclusion}.
+
+\section{Sensors to Cloud Field Level Connectivity}\label{cloud-to-sensors-field-level-connectivity}
+
+\subsection{Architecture}\label{subs.architecture}
+
+subsection
+
+\subsection{Azure Main Technology Features}\label{azure-main-technology-features}
+
+subsection
+
+subsubsection
+
+subsubsection
+
+subsubsection
+
+\subsection{OOI Main Technology Features} %\label{ooi-main-technology-features}
+
+subsection
+
+\section{Azure - Object-Oriented Internet Interoperability Implementation}\label{sect.gateway-implementation}
+
+section
+
+\section{Conclusion}\label{section.conclusion}
+
+section
+
+\bibliography{ICCS21MPostoOOIGateway2Azure}
 \bibliographystyle{splncs04}

### 2021-01-01 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Research on publication journal #50
- working on ICCS21

@@
 \usepackage{cite}
-\usepackage{hyperref}
+%\usepackage{hyperref}
 
@@
 
-\author{Mariusz Postół\inst{1}\orcidID{0000-0002-9669-0565}  \and Piotr Szymczak\inst{1}\orcidID{1111-2222-3333-4444} }
+\author{Mariusz Postół\inst{1}\orcidID{0000-0002-9669-0565}  \and Piotr Szymczak\inst{1}\orcidID{0000-0001-6790-3878} }
 \authorrunning{M. Postół et al.}
@@
 { Institute of Information Technology, Lodz University of Technology, Łódź, Poland \\
-    \email{mailto:mariusz.postol@p.lodz.pl}\\
-    \url{http://www.it.p.lodz.pl}
+      \email{mailto:mariusz.postol@p.lodz.pl} %\\ \url{http://www.it.p.lodz.pl}
 }
 
-\maketitle              % typeset the header of the contribution
+\maketitle
 
@@
 
-section{Introduction}\label{introduction}
+\section{Introduction}\label{introduction}
 
@@
 Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical System (CPS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect.
-\ref*{subs.architecture}).
+\ref{subs.architecture}).
 
@@
 Data models, roles, and responsibility differences of both solutions make this approach impractical or even imposable to be applied in typical cases.
-A more detailed description is covered by the Sect.~\ref*{cloud-to-sensors-field-level-connectivity}.
+A more detailed description is covered by the Sect.~\ref{cloud-to-sensors-field-level-connectivity}.
 
@@
 The remainder of this paper is structured as follows.
-Sect.~\ref*{cloud-to-sensors-field-level-connectivity} presents the proposed open and reusable software model.
+Sect.~\ref{cloud-to-sensors-field-level-connectivity} presents the proposed open and reusable software model.
 It promotes a reactive interoperability pattern and a generic approach to establishing interoperability-context.
-A reference implementation of this archetype is described in Sect.~\ref*{sect.gateway-implementation}.
-The most important findings and future work are summarized in Sect.~\ref*{section.conclusion}.
+A reference implementation of this archetype is described in Sect.~\ref{sect.gateway-implementation}.
+The most important findings and future work are summarized in Sect.~\ref{section.conclusion}.
 
@@
 
-subsection
+As it was explained in Sect.~\ref{introduction}, to follow the Industry 4.0 concept a hybrid environment integrating reactive Machine to Machine interconnection and the interactive web-based user interface is required (Sect.
+\ref{introduction}).
+The main challenge of the solution in concern is to design a generic but reusable architecture that addresses interoperability of these diverse interconnection scenarios ruled by different requirements, namely:
+
+\begin{enumerate}
+      \item \textbf{machine-centric} machine to machine real-time mobile interoperability
+      \item \textbf{human-centric} cloud-based front-end
+\end{enumerate}
+
+Interconnection of the reactive \textbf{machine-centric} and interactive \textbf{human-centric} environments can be implemented by applying one of the following scenarios:
+
+\begin{itemize}
+      \item \textbf{direct interconnection} (tightly coupled scenario) - cloud-based dedicated communication services are engaged to attach it to the CPS making up a consistent M2M communication network using a common protocol stack
+      \item \textbf{gateway based interconnection} (loosely coupled scenario) - native build-in communication services allows attaching the cloud to the CPS using an out-of-bound protocol stack
+\end{itemize}
+
+In the solution in concern, the interconnection of assets is not enough  hence their interoperability is expected.
+In this case, using the same communication stack must be recognized as only a necessary condition.
+To support interoperability common data understanding is required.
+By design, the direct approach requires that the cloud has to be compliant with the interoperability standard the CPS uses.
+As a result, it becomes a consistent communication node of the CPS.
+Additionally, to meet this requirement the cloud and CPS have to establish directly the same:
+
+\begin{itemize}
+      \item semantic-context
+      \item security-context
+\end{itemize}
+
+The possibility to establish a common semantic-context in the multi-vendor environment makes communication standardization especially important.
+In this case, it is required that the encoding of the payload exchanged over the network (Data Transfer Object - DTO) is standardized so that the appropriate messages can be factored on the data-gathering site and consumed on the ultimate destination data processing sites.
+Security between the data origin and ultimate data destination refers to the protection of messages (security-context) against malicious users.
+It is required that communicating parties are using the same cyber-security measures.
+
+The decision to follow the \textbf{direct interconnection} scenario must be derived from an analysis of the capabilities of available services in concern.
+However, for the development strategy of this type of solutions this analysis can be done partially taking into account two features that can be considered invariable:
+
+\begin{itemize}
+      \item by design the cloud-based services must be virtual - they are used to handle many solutions at the same time
+      \item by design the M2M communication is usually constrained by the real-time requirements
+\end{itemize}
+
+The virtualization of cloud services means that they must be very flexible to handle the attachment of new assets proactively (acting in advance) at run time.
+As a result, by design, the cloud services must be responsible to register and authenticate devices by exposing endpoints in the public network to allow the device to access a provisioning cloud service.
+It requires that a session over the Internet has to be established by the data holding asset at a preparation step.
+
+To meet the requirements of real-time distributed control the CPS may use protocols applicable only to local computer networks (e.g.~multicast IP, Ethernet, TSN \footnote{Time-Sensitive Networking (TSN) Task Group \url{https://1.ieee802.org/tsn/}}, etc.).
+Because the cloud services support only protocols handling interconnection over the Internet the interaction with the cloud requires remote agents, i.e.~agents attached locally to the M2M network and implemented by applying one of the following archetypes:
+
+\begin{itemize}
+      \item \textbf{edge device} - remote cloud agent acting as an intermediary for nodes of the CPS
+      \item \textbf{field level gateway} - a dedicated custom agent acting as an intermediary for nodes of the CPS
+      \item \emph{Embedded Gateway} - a software part composed into a selected node of the \emph{Cyber-physical network} (\ref{figure1.StrategyDomainModel})
+\end{itemize}
+
+\begin{figure}
+      \centering
+      \includegraphics[width=8cm]{../../.Media/StrategyDomainModel.png}
+      \caption{Domain model of a generic interconnection concept}\label{figure1.StrategyDomainModel}
+\end{figure}
+
+\textbf{Edge device} connects directly to the cloud services but acts as an intermediary for other devices called leaf devices.
+Additionally, it allows the selection of initial data processing and execution of them using local resources.
+The \textbf{edge device} may be located close to the leaf devices and attached to the \emph{Cyber-physical network} using protocols applicable only to local computer networks.
+In this scenario, it is possible to use a custom protocol stack to get connected to the \textbf{edge device} with the cloud and helps to save the bandwidth thanks to sending only the results of local processing.
+In this approach, the \textbf{edge device} is part of cloud vendor products and cannot be recognized as a generic solution that can be used to connect to other clouds at the same time.
+
+The \textbf{field level gateway} is also build atop of the middleware concept \cite{Sunyaev2020}.
+The only difference compared with the \textbf{edge device} is a necessity to use officially supported by the cloud vendor services to get connected.
+In this scenario, the process data simultaneously may be transferred to many clouds provided that the gateway offers this functionality.
+
+Unlike the above-described solutions, the \emph{Embedded Gateway} is not derived from the middleware concept.
+A generic domain model for this interconnection is presented in the Fig.~\ref{figure1.StrategyDomainModel}.
+Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \emph{Networking} service of the \emph{Cyber-physical\ node}.
+The main functionality of this component is to transfer selected data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
+
+The \emph{Embedded Gateway} archetype relaxes most of the issues described above: \emph{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security - context differences to name only a few.
+The main goal of this article is to provide proof that the \emph{Embedded Gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogeneous environments in concern.
+The proposed implementation is designed for a selected interoperability standard and cloud product.
+
+To comply with the Industry 4.0 communication criterion it is required that any product must be addressable over the network via TCP/UDP or IP and has to support the OPC UA Information Model.
+As a result, any product being advertised as Industry 4.0 enabled must be OPC UA-capable somehow.
+To support the multi-vendor environment OPC Unified Architecture interoperability standard has been selected.
+OPC UA supports the following two patterns to be used to transfer data between communicating parties:
+
+\begin{itemize}
+      \item \textbf{session-oriented}: requires a session that has to be established before any data can be sent between sender and receiver
+      \item \textbf{sessionless-oriented}: the sender may start sending messages (called packets or datagrams) to the destination without any preceding handshake procedure
+\end{itemize}
+
+Using the session-oriented communication pattern it is difficult or even impossible to gather and process mobile data (Sec.~\ref{introduction} ), which is one of the Internet of Things paradigms.
+OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0, UAPart14PubSubMainTechnologyFeatures} offers the sessionless approach as an additional option to session-based client-server interoperability relationship and is a consistent part of the OPC UA specifications suit.
+As the result, it can be recognized as the IoT ready technology.
+
+The presented proposals in the article are backed by proof of concept reference implementations\cite{mariusz_postol_2020_4361640}.
+For this study, prototyping addresses Microsoft Azure cloud products.
+There are many reasons for selecting Azure to accomplish the cloud-based front-end of Cyber-Physical System (CPS).
+Azure offers Infrastructure as a Service (IaaS) and Platform as a Service (PaaS) capabilities.
+As a result, the platform can be used not only as a cloud-based front-end for CPS.
+By design, the Azure services are compliant with Security Development Lifecycle (SDL) an industry-leading security process.
+It is also compliant with the new international standard for cloud privacy, namely ISO 27018.
+Solutions hosted on Azure are scaled up to millions of users without any additional coding.
+For the development of the CPS front-end, it is essential that Azure provides very efficient storage services usefully for the purpose of real-time process data archival.
+Azure provides a vast variety of hybrid connections including but not limited to virtual private networks (VPNs), caches, content delivery networks (CDNs), ExpressRoute, and IoT dedicated services that can be directly used to implement cloud-based front-end for CPS.
+Because it is also integrated with other Microsoft tools like Office 365, Outlook, and SharePoint using Azure allows preserving investment and exporting process data to the mentioned tools.
+Azure also offers services supporting analytics and intelligence capabilities for further improving business processes and decision making.
+It is the only cloud platform that offers Blockchain as a Service (BaaS), Machine Learning, Bots, and Cognitive APIs capabilities.
+
+Azure aids Internet protocols and open standards such as JSON, XML, SOAP, REST, MQTT, AMQP, and HTTP.
+A software development kits for C\#, Java, PHP, and Ruby are available for custom applications.
+Azure provides services supporting data exchange over the OPC UA, but they don't support PubSub compliant with the OPC UA Part-14.
+Connectivity services on the network use JSON-based Data Transfer Object encoded based on schema derived from the solution metadata.
+
+A more detailed description of the selected Azure features in the context of the application in concern is covered by the Sec.~\ref{azure-main-technology-features}.
+
+Based on the sessionless and session-oriented communication patterns examination against the IoT requirements \cite{mpostol2020} it could be concluded that the connectionless pattern better suites issues related to the assets mobility and traffic asymmetry that is characteristic for the application domains in concern.
+Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub  specification.
+According to proposed generic architecture (Fig.~\ref{figure1.StrategyDomainModel}) to implement the \emph{Embedded\ Gateway} as a composable part of the \emph{Cyber-physical\ node} a library implementing \emph{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
+Additionally, it must be assumed that the library used to deploy \emph{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/PubSub gateway functionality.
+The composition process must be available without modification of the core code of an existing library.
+As a result, the prototyping is to be limited to implementation of the \emph{Embedded\ Gateway} software part only.
+
+A library that meets all these requirements has been implemented consistently with the Object-Oriented Internet paradigm \cite{mariusz_postol_2020_4361640} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }.
+The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the Object-Oriented Internet concept compliant with the OPC UA PubSub international standard.
+According to the presented implementation and evaluation, using the dependency injection and late binding, the application program can be seamlessly adapted to the production environment and scales well.
+This approach also improves flexibility and adaptability of the existing solutions against any modification of the production environment, including but not limited to the selected interoperability standard change.
+
+Sect.~\ref{ooi-main-technology-features} provides a more detailed description of this library and an external part deployment process that is to be used to implement new functionality supporting \emph{Embedded\ Gateway}.
+
+The following subsections cover the description of the current state of technologies concerning Azure cloud-based IoT enabler and OPC UA PubSub.
+Sect.
+\ref{azure-main-technology-features} analyzes data presentation user interface, available native communication services, and data/metadata model offered by Microsoft Azure.
+The discussion covered by this section is the foundation for selecting services utilized to expose process data and suitable protocol stack to support interconnection.
+In Sect.
+\ref{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a foundation for further decisions addressing the systematic design of the interoperability of the CPS and cloud-based front-end.
 
@@
 
-subsection
+Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical Systems (CPS) designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end requires decisions addressing the selection of the services supporting web user interface capable to expose process data.
+In this context, the service is any autonomous (with its own identity) software component or module that is interfacing with selected CPS for data collection, analysis, and also remote control.
+Microsoft Azure is a cloud-based product.
+It offers a vast variety of services.
+This virtual environment handles an unlimited number of users and devices organized using a solution container concept.
+The solution aggregates users, devices, services, and required additional resources scoping on a selected scenario.
+It also serves as a context that provides a scope to the identifiers (the names of devices, users, process data entities, etc) inside it.
+Solutions are used to organize deployment entities into logical groups and prevent identity collisions.
 
-subsubsection
+The \textbf{IoT\ Central} service provides a user interface of process data visualization. To make this interface meaningful, metadata called device template is used to describe devices.
 
-subsubsection
+Following the assumption that interconnection between the CPS and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler.
+It must be interconnected with the CPS using an in-band protocol adhering to communications requirements (i.e.
+protocol profile, data encoding, time relationships, etc.) governing communication of the parts making it up.
+At the same time, it must support back-and-forth data transfer to the cloud using out-of-band native for the cloud services.
+The transfer process requires data conversion from source to destination encoding.
+The \textbf{IoT\ Hub} is a service hosted in the cloud that supports \textbf{IoT\ Central} services providing a robust messaging solution - it acts as a central message hub for bi-directional communication \cite{MicrosoftAzureIoTPlatform}.
+This communication is transparent, i.e.~it is not data types aware allowing any devices to exchange any kind of data.
+This service is responsible to manage the devices' identity and it offers the following protocol stacks: AMQP, MQTT, and HTTPS.
 
-subsubsection
+Before process data can be exposed using a web user interface the data source must be associated with an appropriate solution and validated to make sure that the security rules are not violated.
+It is hard to assume that the security rules governing the CPS may also apply to the cloud-based services.
+In the gateway scenario, they can be mapped on each other or be entirely independent.
+The \emph{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper service for \emph{IoT\ Hub} that enables devices' connection process management, upon device providing valid identity attestation it assigns the device to an appropriate \emph{IoT\ Hub} instance and returns to the device connection parameters, which allow direct connection with given \emph{IoT\ Hub} service.
+The device proceeds to use the same attestation in \emph{IoT\ Hub} connection and based on it, is granted authorization to selected operations including but not limited to data transfer and updating the user interface.
 
-\subsection{OOI Main Technology Features} %\label{ooi-main-technology-features}
+It is worth stressing that interaction of the offered by the Azure services can be configured flexibly, and as a result, the presented above selection of services must be recognized as an example only.
+The \textbf{IoT\ Central} can be also seamlessly integrated with other services as needed.
+The following services could also be considered to build a cloud-based automation solution:
+
+\begin{itemize}
+      \item \emph{Industrial\ IoT} - discovering OPC UA enabled servers in a factory network and register them in Azure \emph{IoT\ Hub} implemented using \emph{IoT\ Edge}
+      \item \emph{Digital\ Twins} - managing the graph of digital twins, which are to represent some real-world process or entity
+\end{itemize}
+
+\emph{Industrial\ IoT} promotes OPC UA client/server archetype used to achieve direct and interactive interoperability implemented using \emph{IoT\ Edge} services that allow extracting initial data processing to local premises based on the edge concept.
+\emph{Digital\ Twins} is an emerging concept to use an observer to replicate selected process state and behavior.
+The possibility to add value as a result of using these services must be subject to further research.
+
+\subsection{OOI Main Technology Features}\label{ooi-main-technology-features}
 

### 2021-01-01 Latex/Manuscript.tex
Research on publication journal #50
- working on ICCS21

@@
 
-As it was explained in Sect.~\ref*{introduction}, to follow the Industry 4.0 concept a hybrid environment integrating reactive Machine to Machine interconnection and interactive web-based user interface is required (Sect.
+As it was explained in Sect.~\ref*{introduction}, to follow the Industry 4.0 concept a hybrid environment integrating reactive Machine to Machine interconnection and the interactive web-based user interface is required (Sect.
 \ref*{introduction}).
-The main challenge of the solution in concern is to design a generic but reusable architecture that addresses interoperability of these diverse interconnection scenarios ruled by different requirements, namely
+The main challenge of the solution in concern is to design a generic but reusable architecture that addresses interoperability of these diverse interconnection scenarios ruled by different requirements, namely:
 

### 2021-01-02 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Research on publication journal #50
- finished moving text to the ICCS21 version

@@
 
-Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical System (CPS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect.
+Deployment of the hybrid solution providing interoperability of the \textbf{machine - centric} Cyber-Physical System (CPS) and \textbf{human - centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect.
 \ref{subs.architecture}).
@@
 The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as the open-source (MIT licensed) \cite{mariusz_postol_2020_4361640}.
-The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet \cite{mariusz_postol_2020_4361640}.
+The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet (OOI) \cite{mariusz_postol_2020_4361640}.
 
-The main goal of this article is to provide proof that:
+The main goal of this article is to provide proof that
 
-\begin{enumerate}
+\begin{itemize}
       \item reactive interoperability M2M communication based on the OPC UA standard can be implemented as a powerful standalone library without dependency on the Client/Server session-oriented archetype
@@
       \item the proposed generic architecture allows that the gateway functionality is implemented as composable part at run-time part - no programming required
-\end{enumerate}
+\end{itemize}
 
@@
 
-\begin{enumerate}
+\begin{itemize}
       \item \textbf{machine-centric} machine to machine real-time mobile interoperability
       \item \textbf{human-centric} cloud-based front-end
-\end{enumerate}
+\end{itemize}
 
@@
       \item \textbf{field level gateway} - a dedicated custom agent acting as an intermediary for nodes of the CPS
-      \item \emph{Embedded Gateway} - a software part composed into a selected node of the \emph{Cyber-physical network} (\ref{figure1.StrategyDomainModel})
+      \item \emph{Embedded Gateway} - a software part composed into a selected node of the \emph{Cyber-physical network} (Fig. \ref{figure1.StrategyDomainModel})
 \end{itemize}
@@
 
-A library that meets all these requirements has been implemented consistently with the Object-Oriented Internet paradigm \cite{mariusz_postol_2020_4361640} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }.
-The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the Object-Oriented Internet concept compliant with the OPC UA PubSub international standard.
+A library that meets all these requirements has been implemented consistently with the Object-Oriented Internet (OOI) paradigm \cite{mariusz_postol_2020_4361640} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }.
+The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the OOI concept compliant with the OPC UA PubSub international standard.
 According to the presented implementation and evaluation, using the dependency injection and late binding, the application program can be seamlessly adapted to the production environment and scales well.
@@
 
+Fortunately, computer science offers a workaround to address that impossibility - the information must be represented as a binary stream.
+In consequence, we can usually use both terms as interchangeable ones while talking about ICT systems.
+Unfortunately, these terms must be precisely observed in the context of further discussion, because we must be aware of the fact that the same information could have many different but equivalent representations.
+In other words, the same information can be represented by a vast variety of different binary patterns.
+For example, numbers may be represented using 2's Complement and Floating-Point binary representations.
+
+It should be nothing new for us, as it is obvious that the same information printed as a text in regional newspapers in English, German, Polish, etc.
+does not resemble one another, but the text meaning should always be the same.
+To understand a newspaper we must learn the appropriate language.
+To understand the binary data we must have defined a data type -- a description of how to create an appropriate bits pattern (syntax) and rules needed to assign the information (semantics), i.e.
+make any correct bitstream meaningful.
+Concluding, to make two systems interoperable, a semantic-context must be established.
+The type plays the role of metadata, a set of data that describes other data.
+Metadata term is frequently used if the semantic-context is defined using a native language to select built-in types engaging a general-purpose graphical user interface.
+
+Using the data type definitions to describe information interchange between communicating parties allows:
+
+\begin{itemize}
+      \item development against a type definition of the user interface
+      \item implementation of the functionality of the bitstreams conversion in advance
+\end{itemize}
+
+Having defined types in advance, a gateway may provide dedicated conversions functionality, i.e.
+replacing bitstreams used by the CPS with equivalent ones for the cloud-based services.
+The Azure offers a vast variety of built-in types ready to be used in common cases, but not necessarily there are equivalent counterparts in use by the CPS.
+Additionally, the data conversion must address the following issues:
+
+\begin{itemize}
+      \item usually to covert data from source to destination representation, the middleware software native types must be used
+      \item if the out of the box set of types is not capable of fulfilling more demanding needs, custom data types must be defined
+\end{itemize}
+
+System components interoperability means the necessity of the information exchange between them.
+The main challenge of interoperability implementation is that information is abstract -- it is knowledge describing the process in concern state and behavior, e.g.~temperature in a boiler, a car speed, an account balance, etc.
+Obviously, abstraction cannot be processed by cyber-physical machines.
+It is also impossible to transfer abstraction from one place to another over the network.
+
+Although the data conversion is a run-time gateway task the implementation of the conversion algorithms must be recognized as an engineering task, and therefore this topic is not considered for further discussion.
+
+In \textbf{IoT\ Central} a CPS is represented as a set of devices.
+The characteristics and behavior of each device kind are described by the device template.
+This Device Template (DT) contains also metadata describing the data exchanged over the wire with the CPS called Device Capability Model (DCM).
+Additionally, the DT contains properties, customization, and views definitions used by the service locally.
+As an option, DCM expressed as a JSON-LD can be imported into a Device Template.
+\textbf{IoT\ Central} also allows to create and edit a DCM using the dedicated web UI.
+A JSON file containing DCM can be derived from an information model used as a foundation to establish the semantic-context applied to achieve interoperability of the devices interconnected as the CPS.
+DCM development against any external information model is a design-time task and should be supported by dedicated development tools.
+In any case, the data interchanged between the cloud and the gateway must be compliant with the DCM, hence, the middleware software must be aware of conversions that must be applied to achieve this interoperability.
+
+From the cloud side, it is proposed to engage the \emph{IoT\ Hub} service to handle the network traffic targeting the cyber-physical system.
+This service offers profiles of the AMQP, MQTT, and HTTPS protocol stacks.
+In any case, process data is transparently transferred back-and-forth to the upper layer \textbf{IoT\ Central} service.
+Hence, the DCM associated with the \textbf{IoT\ Central} solution determines the payload formatting.
+
+The Azure supports HTTP, AMQP, and MQTT protocol stacks, which are all standard ones.
+Consequently, it is possible to apply any available implementation compliant with an appropriate specification to achieve connectivity.
+In this case, all parameters required to establish semantic and security contexts are up to the gateway responsibility.
+Alternatively, the API offered by the dedicated frameworks (libraries) may be used.
+Using a framework the configuration process may be reduced significantly, and the communication protocol selection has only an indirect impact on the interoperability features.
+The Azure interconnection may be obtained using the following \emph{Microsoft.Azure} packages:
+
+\begin{itemize}
+      \item \emph{Devices} - Service SDK for Azure IoT Devices
+      \item \emph{Devices.Client} - Device SDK for Azure \emph{IoT\ Hub} including dependencies implementing MQTT and AMQP communication
+      \item \emph{Devices.Shared} - Common code for Azure IoT Device and Service SDK
+      \item \emph{Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
+      \item \emph{Devices.Provisioning.Transport.*} - Provisioning Device Client Transports (HTTPS, AMQP, MQTT) for Azure IoT Devices
+\end{itemize}
+
 \subsection{OOI Main Technology Features}\label{ooi-main-technology-features}
 
-subsection
+To promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub (Sect.
+\ref{subs.architecture}) and support the \emph{Reactive Interoperability} (Sect.
+\ref{introduction}) concept.
+A framework compliant with these requirements has been implemented as an open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) under an umbrella of the project Object-Oriented Internet  (OOI)\cite{mariusz_postol_2020_4361640}.
+The library is designed to be a foundation for developing application programs that are taking part in a message-centric communication pattern and interconnected using the reactive networking concept.
+The diagram in Fig.~\ref{figure2.UADataApplicationArchitecture} shows the relationship between the library (\emph{SDK}) and external parts composing any reactive networking application (\emph{Reactive\ Application}).
+The \emph{Reactive Application} is an aggregation of parts implementing the \emph{Producer} and \emph{Consumer} roles.
+By design, they support access to real-time process data, hence they are recognized as an extension of \emph{DataRepository} class.
+To implement the \emph{DataRepository} dedicated implementation of the \emph{IBinding} interface should be provided to create a bridge between CPS and an external row data represented by the \emph{LocalResources} class.
+A more in-depth description of the \emph{OOI Reactive Application} library enabling data exchange over a network using the reactive networking pattern is in \cite{mpostol2020}.
 
-\section{Azure - Object-Oriented Internet Interoperability Implementation}\label{sect.gateway-implementation}
+\begin{figure}
+      \centering
+      \includegraphics[width=8cm]{../../.Media/UADataApplicationArchitecture.png}
+      \caption{Reactive interoperability implementation}\label{figure2.UADataApplicationArchitecture}
+\end{figure}
 
-section
+From the above discussion, we can learn that the main design decisions must concern standardization and flexibility.
+Standardization needs the selection of an international interoperability specification to make the library ready to be adopted by the multi-vendor environment.
+Flexibility requires an architecture that promotes the polymorphic independent implementation of essential functions.
+
+Piece by piece integration of a cyber-physical system using multi-vendor products requires that M2M communication employs international standards as the interoperability foundation.
+OPC Unified Architecture Part 14 PubSub has been selected in this respect (Sect.
+\ref{subs.architecture}).
+By design, this standard should support the required publisher-subscriber communication pattern.
+It must be stressed, that by design, the specification provides only an abstract interoperability definition.
+Abstract means that the standard must not limit the implementation strategy.
+
+Many parts in the domain model presented in Fig.~\ref{figure2.UADataApplicationArchitecture} requires a polymorphic approach to implementation.
+To promote the polymorphic ready solution the following concepts have been adopted:
+
+\begin{itemize}
+      \item \textbf{separation of concerns} - to allow an independent development of the parts~\cite{RefWorks:doc:5d92609be4b02eb43d372bd1}
+      \item \textbf{dependency injection} - to allow late binding of separately implemented parts~\cite{RefWorks:doc:5d925b77e4b030b4e0596f5d}
+\end{itemize}
+
+To promote the polymorphic approach, the library has a factory class called \emph{DataManagementSetup} that is a placeholder to gather all injection points used to compose external parts.
+To be injected the parts must be compliant with an appropriate contract expressed as the following interfaces:
+
+\begin{itemize}
+      \item \emph{IBindingFactory} - bidirectional data exchange with the underlying process
+      \item \emph{IConfigurationDataFactory} - the configuration data access
+      \item \emph{IMessageHandlerFactory} - \textbf{Message} entities pushing to/pulling from the wire
+      \item \emph{IEncodingFactory} - searching a dictionary containing value converters
+\end{itemize}
+
+It is expected that the functionality implementation expressed by these interfaces is provided as independent external composable parts.
+The composition is accomplished at run time, and the effective application functionality depends essentially on reusable loosely coupled parts composed applying the dependency injection software engineering and adaptive programming concept \cite{RefWorks:doc:5d9796cbe4b0f66c52dccf04}.
+
+The \emph{DataRepository} represents data holding assets in the \emph{Reactive Application} implementing the \emph{IBindingFactory} interface.
+It captures functionality responsible for accessing the external process data from \emph{LocalResources}.
+The \emph{LocalResources} represents an external part that has a very broad usage purpose.
+For example, it may be any kind of the process data source/destination, i.e.
+raw data (e.g.
+PLC internal registers), OPC UA Address Space Management, cloud, file, database, graphical user interface, to name only a few.
+
+Depending on the expected network role the library supports the implementation of:
+
+\begin{itemize}
+      \item \emph{Consumer} - entities processing data from incoming messages,
+      \item \emph{Producer} - entities gathering process data and populating outgoing messages.
+\end{itemize}
+
+The \emph{Consumer} and \emph{Producer} classes are derived from the \emph{DataRepository} (Fig.~\ref{figure2.UADataApplicationArchitecture}).
+The \emph{Consumer} uses the \emph{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
+The received data may be processed or driven to any data destination, e.g.
+cloud-based front-end.
+The \emph{Producer} mirrors the \emph{Consumer} functionality and, after reading data from an associated source, populates the \emph{Message} using the gathered data.
+
+By design, the \emph{DataRepository} and associated entities, i.e.~\emph{Local Resources}, \emph{Consumer}, \emph{Producer} are embedded in external parts, and consequently, the application scope may cover practically any concern that can be separated from the core \emph{Reactive Application} implementation.
+
+The application startup phase concerns all the parts composed to make a running instance of the application program using the dependency injection approach to allow separate development and late binding.
+This approach makes any modification straightforward at any development and maintenance stage.
+From the end-user point of view, the composition process of the running program using independently developed parts is invisible.
+Because in any case a single program instance is created in a typical approach, we shall expect a commonly shared configuration mechanism providing mutually exclusive parameters to separately developed parts.
+This scenario has been addressed by the proposed implementation thanks to making the configuration expandable.
+
+From the discussion covered by the Sect.
+\ref{subs.architecture} we can infer that the interoperability of communicating parties requires establishing a semantic-context and security-context between them.
+If the received data is driven to any external data destination (e.g.
+cloud-based front-end) using out-of-band protocol semantic-context and security-context must be defined for this interoperability relationship.
+There are a vast variety of possibilities for how to define these contexts.
+Anyway, the most common starting point is the configuration.
+The proposed approach to instantiate the application as a set of composable parts is very useful in this respect because it makes it possible to expand the core configuration functionality and adapt it to be helpful also in this case.
+Therefore, the semantic-context may be created based on the configuration using the implementation of the \emph{IConfigurationDataFactory} interface.
+
+\begin{itemize}
+      \item implementation of practically any configuration management scenario,
+      \item modification of this functionality later after releasing the library or deploying the application program in the production environment.
+\end{itemize}
+
+Concluding, decoupling of this functionality implementation using an abstract contract and late binding mechanism allows:
+
+\begin{itemize}
+      \item implementation of practically any configuration management scenario,
+      \item modification of this functionality later after releasing the library or deploying the application program in the production environment.
+\end{itemize}
+
+\section{Azure - OOI Implementation}\label{sect.gateway-implementation}
+
+A generic domain model presenting interconnection architecture between the Azure \emph{Cloud-based\ Front-end} and \emph{Cyber-physical\ node} attached to the \emph{Cyber-physical\ network} is presented in Fig.~\ref{figure1.StrategyDomainModel}.
+It is proposed to implement the \emph{Cyber-physical\ node} by adopting the \emph{Reactive Application} archetype compliant with the reactive interoperability concept (Fig.
+\ref{figure2.UADataApplicationArchitecture}) described in the Sect.
+\ref{ooi-main-technology-features}.
+Merging selected entities of this archetype into the proposed domain model (Fig.
+\ref{figure1.StrategyDomainModel}) lead to a model expressed as the diagram presented in Fig.
+\ref{figure3.ImplementationDomainModel}.
+In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as as a composable part aggregated by the \emph{Reactive Application}.
+
+\begin{figure}
+      \centering
+      \includegraphics[width=8cm]{../../.Media/ImplementationDomainModel.png}
+      \caption{Architecture Domain Model}\label{figure3.ImplementationDomainModel}
+\end{figure}
+
+In the final deployment architecture (Fig.
+\ref{figure4.ImplementationArchitecture}) the \emph{Consumer} role has been realized by the \emph{PartDataManagementSetup} that is derived from \emph{DataManagementSetup} provided by the library.
+\emph{Networking} (SDK) was removed from this diagram for the sake of simplicity.
+Instantiating \emph{PartDataManagementSetup} is the first step for bootstrapping process of the \emph{Consumer} role functionality.
+This class provides an entry point to initialize all properties, which are injection points of all parts composing this role.
+It extends the functionality of the \emph{DataManagementSetup} based on the following associated classes:
+
+\begin{figure}
+      \centering
+      \includegraphics[width=10cm]{../../.Media/ImplementationArchitecture.png}
+      \caption{Implementation Architecture}\label{figure4.ImplementationArchitecture}
+\end{figure}
+
+\begin{itemize}
+      \item \emph{PartConfigurationFactory} - to get access to the application configuration
+      \item \emph{PartBindingFactory} - to gather the data recovered from the \emph{Message} instances pulled from the wire
+      \item \emph{CommunicationContext} - to handle communication with the Azure services
+\end{itemize}
+
+In this case, the implementation of the \emph{IConfigurationFactory} interface is based entirely on the \emph{Networking} library.
+The implementation provided by the library is generic, but it is flexible enough to meet all the requirements, which warrants no need for further modifications for adoption.
+It is ready to provide all necessary configuration parameters to establish semantic and security contexts related to Azure interoperability.
+
+The \emph{PartBindingFactory} implements the \emph{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
+The received data is driven to \emph{CommunicationContext} for further encoding and finally pushing it to the Azure services using the configured out-of-band protocol.
+
+\emph{IEncodingFactory} and \emph{IMessageHandlerFactory} interfaces (Fig.
+\ref{figure2.UADataApplicationArchitecture}) have been implemented in independent libraries and ae not considered for any modifications to deploy \emph{Embedded Gateway} functionality.
+The current implementation of the mentioned interfaces is localized at run time as services using an instance of the \emph{IServiceLocator}\footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} }.
+In this example, it is assumed that \emph{IServiceLocator} is implemented to resolve references to any external services.
+Both interfaces are used to manage the interconnection of the node with the \emph{Cyber-physical Network}.
+
+The Azure interconnection is realized using the \emph{CommunicationContext}. It implements a message encoder and establishes the out-of-band communication stack.
+
+The recovered data from the \emph{Message} is obtained from the \emph{PartBindingFactory} using the \emph{IDTOProvider} that defines a contract used to pull the Data Transfer Object (DTO) created from a selected subscription by the \emph{PartBindingFactory}.
+The transfer process requires data conversion from source to destination encoding, i.e.
+replacing bitstreams used by the CPS with equivalent ones for the cloud-based services.
+The Azure offers a vast variety of built-in types ready to be used in common cases, but not necessarily there are equivalent counterparts in use by the CPS.
+The Azure uses JSON based Data Transfer Object encoding and schema defined based on the solution metadata.
+The PubSub uses JSON and binary Data Transfer Object encodings.
+In any case, the data recovered from the Message pulled from a subscription is stored locally using the object model based on standard .NET types.
+\emph{PartBindingFactory} maps selected object graph onto the JSON message required by the cloud services.
+
+The encoded JSON messages must be transferred over the network to Azure using the selected protocol stack.
+The Azure supports standard protocols (Sec.
+\ref{azure-main-technology-features}).
+Consequently, it is possible to apply any available ones compliant with an appropriate specification to achieve connectivity.
+In the proposed gateway implementation, the Azure interconnection has been obtained using the packages described in Sect.
+\ref{azure-main-technology-features}.
+
+Azure and PubSub use different security mechanisms so in the proposed solution establishing security-context is realized independently.
+The \emph{CommunicationContext} is responsible to establish this context as an embedded negotiation phase tightly coupled with establishing interconnection.
 
@@
 
-section
+Nowadays, the macro optimization of the industrial processes requires an integration of a vast variety of distributed applications provided by Information and Communication Technology.
+It requires further research on the integration of \textbf{machine - centric} Cyber-Physical Systems (CPS) with \textbf{human - centric} front-end in the context of new emerging disciplines, i.e.
+Industry 4.0 and the Industrial Internet of Things (Sect.
+\ref{introduction}).
+
+CPS is composed using the multi-vendor components (data holding assets) interconnected atop of the Machine To Machine (M2M) communication.
+In many applications, the dynamic nature of the CPS must be considered.
+Dynamic nature means that interconnected assets may be added/removed from the network at any time.
+By design, typically CPS must fulfill the real-time and mobility of the assets requirements.
+
+Highly-distributed solutions used to control/monitor a set of geographically spread islands of automation (e.g.
+virtual power plants producing renewable energy) additionally must leverage public communication infrastructure, namely the Internet.
+If islands of automation must be controlled over the Internet, the cloud computing concept may be recognized as a reasonable answer.
+Following this concept, the cloud-based supervisory control functionality is applied as a set of services employing abstraction and virtualization - two main pillars of the cloud computing paradigm.
+In the cloud computing concept, virtualization is recognized as the possibility to share the services by many users, and abstraction hides implementation details.
+
+The main goal of this research is working out a new generic architecture and deployment scenario applicable for the integration of the \textbf{machine-centric} CPS and emerging cloud computing as a \textbf{human-centric} front-end.
+
+If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship\cite{mpostol2020} could alleviate the challenges posed by the interactive approach.
+The real-time multi-vendor environment makes communication standardization especially important.
+To support this environment, OPC Unified Architecture \cite{RefWorks:doc:5ac86c98e4b009947bbb874c} interoperability standard has been selected.
+As it was pointed out in the Sect.
+\ref{subs.architecture} using OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} the aggregation of nodes by the network is loosely coupled, i.e.
+nodes can be added and removed from the network dynamically, and nodes may represent mobile data holding assets.
+
+From the analysis covered by the Sect.
+\ref{subs.architecture} it is concluded that the \emph{Embedded Gateway} archetype best suits all requirements described above.
+It relaxes most of the issues related to \textbf{direct interconnection} and solutions inferred from the middleware concept, i.e.
+\textbf{edge device} - remote cloud agent and \textbf{field level gateway} - a dedicated custom agent.
+Additionally, it could be used to connect to many independent clouds at the same time.
+The generic domain model for the proposed interconnection archetype is presented in the Fig.~\ref{figure1.StrategyDomainModel}.
+We have highlighted that to promote the separation of concern design principle, the gateway functionality should be implemented as a self-contained dedicated software part embedded in the core \emph{Networking} service of the \emph{Cyber-physical\ node}.
+The main functionality of this component is to transfer process data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
+
+To promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub (Sect.
+\ref{subs.architecture}) and support the \emph{Reactive Interoperability} (Sect.
+\ref{introduction}) concept.
+We proposed to use an open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) (Fig.~\ref{figure2.UADataApplicationArchitecture}) for this purpose.
+It is worth stressing that based on this approach only dedicated functionality related to the communication with the cloud must be implemented.
+
+We derived the final model presented in Fig.
+\ref{figure4.ImplementationArchitecture} by merging selected entities from the \emph{Networking} library (Fig.~\ref{figure2.UADataApplicationArchitecture}) into the generic interconnection domain model (Fig.
+\ref{figure1.StrategyDomainModel}).
+In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as as a composable part aggregated by the \emph{Reactive Application}.
+
+The proposals are backed by proof of concept reference implementations.
+Prototyping addresses Microsoft Azure cloud as an example.
+The outcome has been just published on GitHub as the open-source (MIT licensed) repository.
+The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.
+
+The described results prove that the \emph{Embedded Gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop of the M2M communication compliant with the OPC UA PubSub standard.
+It is worth stressing that there is no dependency on the Client/Server session-oriented relationship.
+This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server.
+The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to embed the \emph{Embedded Gateway} component into the OPC UA Client or Server to get connected with the cloud in case of the interactive relationship.
+
+In the proposed approach the cloud interoperability is obtained by implementing a dedicated part employing out-of-band communication only without dependency on the OPC UA functionality at all.
+It is worth stressing that the gateway functionality is implemented as a part - composable to the whole without programming skills.
+Because the part is composed at the runtime it makes it possible to modify its functionality later after releasing the library or even deploying the application program in the production environment.
+
+Concluding, the paper describes a proof of the concept that applying the proposed architecture and deployment scenario it is possible to integrate selected cloud services (e.g.
+\textbf{Azure\ IoT\ Central}) with the \emph{Cyber-physical network} interconnected as one whole atop of the OPC UA PubSub.
+It is in contrast to interconnecting cloud-based front-end services with the selected \emph{ Address\ Space} exposed by a selected OPC UA server limiting the PubSub role to data exporter transferring the data out of the OPC UA ecosystem.
 

### 2021-01-02 Latex/Manuscript.tex
Research on publication journal #50
- Harmonized latex files

@@
 \fancyhf{}
-\rhead{Rel 1.4.4-Preprint}
-\lhead{OOI - Azure Interoperability}
+\rhead{Preliminary}
+\lhead{OOI - OOI Azure Interoperability}
 \rfoot{Page \thepage}
@@
 
-\title{Object-Oriented Internet - Azure Interoperability}
+\title{Object-Oriented Internet\\ Cloud Interoperability}
 
@@
 
-Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical System (CPS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect.
-\ref*{subs.architecture}).
+Deployment of the hybrid solution providing interoperability of the \textbf{machine - centric} Cyber-Physical System (CPS) and \textbf{human - centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect.
+\ref{subs.architecture}).
 
@@
       \item the proposed generic architecture allows that the gateway functionality is implemented as composable part at run-time part - no programming required
-\end{enumerate}
+\end{itemize}
 
 The remainder of this paper is structured as follows.
-Sect.~\ref*{cloud-to-sensors-field-level-connectivity} presents the proposed open and reusable software model.
+Sect.~\ref{cloud-to-sensors-field-level-connectivity} presents the proposed open and reusable software model.
 It promotes a reactive interoperability pattern and a generic approach to establishing interoperability-context.
-A reference implementation of this archetype is described in Sect.~\ref*{sect.gateway-implementation}.
-The most important findings and future work are summarized in Sect.~\ref*{section.conclusion}.
+A reference implementation of this archetype is described in Sect.~\ref{sect.gateway-implementation}.
+The most important findings and future work are summarized in Sect.~\ref{section.conclusion}.
 
@@
 
-As it was explained in Sect.~\ref*{introduction}, to follow the Industry 4.0 concept a hybrid environment integrating reactive Machine to Machine interconnection and the interactive web-based user interface is required (Sect.
-\ref*{introduction}).
+As it was explained in Sect.~\ref{introduction}, to follow the Industry 4.0 concept a hybrid environment integrating reactive Machine to Machine interconnection and the interactive web-based user interface is required (Sect.
+\ref{introduction}).
 The main challenge of the solution in concern is to design a generic but reusable architecture that addresses interoperability of these diverse interconnection scenarios ruled by different requirements, namely:
 
-\begin{enumerate}
+\begin{itemize}
       \item \textbf{machine-centric} machine to machine real-time mobile interoperability
       \item \textbf{human-centric} cloud-based front-end
-\end{enumerate}
+\end{itemize}
 
@@
 As a result, it becomes a consistent communication node of the CPS.
-Additionally, to meet this requirement the cloud and CPS have to establish directly the same
+Additionally, to meet this requirement the cloud and CPS have to establish directly the same:
 
@@
 The possibility to establish a common semantic-context in the multi-vendor environment makes communication standardization especially important.
-In this case, it is required that the encoding of the messages payload exchanged over the network (Data Transfer Object - DTO) is standardized so that the payload can be factored on the data-gathering site and consumed on the ultimate destination data processing sites.
+In this case, it is required that the encoding of the payload exchanged over the network (Data Transfer Object - DTO) is standardized so that the appropriate messages can be factored on the data-gathering site and consumed on the ultimate destination data processing sites.
 Security between the data origin and ultimate data destination refers to the protection of messages (security-context) against malicious users.
@@
       \item \textbf{field level gateway} - a dedicated custom agent acting as an intermediary for nodes of the CPS
-      \item \emph{Embedded Gateway} - a software part composed into a selected node of the \emph{Cyber-physical network} (\ref*{figure1.StrategyDomainModel})
+      \item \emph{Embedded Gateway} - a software part composed into a selected node of the \emph{Cyber-physical network} (Fig. \ref{figure1.StrategyDomainModel})
 \end{itemize}
+
+\begin{figure}
+      \centering
+      \includegraphics[width=8cm]{../.Media/StrategyDomainModel.png}
+      \caption{Domain model of a generic interconnection concept}\label{figure1.StrategyDomainModel}
+\end{figure}
 
@@
 
-The \textbf{field level gateway} is also build atop of the middleware\cite{Sunyaev2020} concept.
-The only difference compared with the \textbf{edge device} is necessity to use officially supported by the cloud vendor services to get connected.
-In this scenario the process data may be transferred to many clouds at the same time provided that the gateway offers this functionality.
+The \textbf{field level gateway} is also build atop of the middleware concept \cite{Sunyaev2020}.
+The only difference compared with the \textbf{edge device} is a necessity to use officially supported by the cloud vendor services to get connected.
+In this scenario, the process data simultaneously may be transferred to many clouds provided that the gateway offers this functionality.
 
-\begin{figure}
-      \centering
-      \includegraphics[width=8cm]{../.Media/StrategyDomainModel.png}
-      \caption{Domain model of a generic interconnection concept}\label{figure1.StrategyDomainModel}
-\end{figure}
+Unlike the above-described solutions, the \emph{Embedded Gateway} is not derived from the middleware concept.
+A generic domain model for this interconnection is presented in the Fig.~\ref{figure1.StrategyDomainModel}.
+Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \emph{Networking} service of the \emph{Cyber-physical\ node}.
+The main functionality of this component is to transfer selected data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
 
-Unlike the above described solutions, the \emph{Embedded Gateway} is not derived from the middleware concept.
-A generic domain model for this interconnection is presented in the Fig.~\ref*{figure1.StrategyDomainModel}.
-Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \emph{Networking} service of the \emph{Cyber-physical\ node}.
-Main functionality of this component is to transfer selected data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
-
-The \emph{Embedded Gateway} archetype relaxes most of the issues described above: \emph{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security-context differences to name only a few.
-The main goal of this article is to provide proof that the \emph{Embedded Gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogenous environments in concern.
-The proposed implementation is designed for selected interoperability standard and cloud product.
+The \emph{Embedded Gateway} archetype relaxes most of the issues described above: \emph{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security - context differences to name only a few.
+The main goal of this article is to provide proof that the \emph{Embedded Gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogeneous environments in concern.
+The proposed implementation is designed for a selected interoperability standard and cloud product.
 
@@
 
-Using the session-oriented communication pattern it is difficult or even impossible to gather and process mobile data (Sec.~\ref*{introduction} ), which is one of the Internet of Things paradigms.
-OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0, UAPart14PubSubMainTechnologyFeatures} offers the sessionless approach as an additional option to session based client-server interoperability relationship and is a consistent part of the OPC UA specifications suit.
-As the result it can be recognized as the IoT ready technology.
+Using the session-oriented communication pattern it is difficult or even impossible to gather and process mobile data (Sec.~\ref{introduction} ), which is one of the Internet of Things paradigms.
+OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0, UAPart14PubSubMainTechnologyFeatures} offers the sessionless approach as an additional option to session-based client-server interoperability relationship and is a consistent part of the OPC UA specifications suit.
+As the result, it can be recognized as the IoT ready technology.
 
@@
 
-More detailed description of the selected Azure features in context of the application in concern are covered by the Sec.~\ref*{azure-main-technology-features}.
+A more detailed description of the selected Azure features in the context of the application in concern is covered by the Sec.~\ref{azure-main-technology-features}.
 
@@
 Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub  specification.
-According to proposed generic architecture (Fig.~\ref*{figure1.StrategyDomainModel}) to implement the \emph{Embedded\ Gateway} as a composable part of the \emph{Cyber-physical\ node} a library implementing \emph{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
+According to proposed generic architecture (Fig.~\ref{figure1.StrategyDomainModel}) to implement the \emph{Embedded\ Gateway} as a composable part of the \emph{Cyber-physical\ node} a library implementing \emph{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
 Additionally, it must be assumed that the library used to deploy \emph{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/PubSub gateway functionality.
@@
 
-A library that meets all these requirements has been implemented consistently with the Object-Oriented Internet paradigm \cite{mariusz_postol_2020_4361640} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }.
-The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the Object-Oriented Internet concept compliant with the OPC UA PubSub international standard.
+A library that meets all these requirements has been implemented consistently with the Object-Oriented Internet (OOI) paradigm \cite{mariusz_postol_2020_4361640} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }.
+The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the OOI concept compliant with the OPC UA PubSub international standard.
 According to the presented implementation and evaluation, using the dependency injection and late binding, the application program can be seamlessly adapted to the production environment and scales well.
-This approach also improves flexibility and adaptability of the existing solutions against any modification of the production environment including but not limited to the selected interoperability standard change.
+This approach also improves flexibility and adaptability of the existing solutions against any modification of the production environment, including but not limited to the selected interoperability standard change.
 
-Sect.~\ref*{ooi-main-technology-features} provides a more detailed description of this library and an external part deployment process that is to be used to implement new functionality supporting \emph{Embedded\ Gateway}.
+Sect.~\ref{ooi-main-technology-features} provides a more detailed description of this library and an external part deployment process that is to be used to implement new functionality supporting \emph{Embedded\ Gateway}.
 
 The following subsections cover the description of the current state of technologies concerning Azure cloud-based IoT enabler and OPC UA PubSub.
-Sect.~\ref*{azure-main-technology-features} analyzes data presentation user interface, available native communication services, and data/metadata model offered by Microsoft Azure.
+Sect.
+\ref{azure-main-technology-features} analyzes data presentation user interface, available native communication services, and data/metadata model offered by Microsoft Azure.
 The discussion covered by this section is the foundation for selecting services utilized to expose process data and suitable protocol stack to support interconnection.
-In Sect.~\ref*{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a foundation for further decisions addressing the systematic design of the interoperability of the CPS and cloud-based front-end.
+In Sect.
+\ref{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a foundation for further decisions addressing the systematic design of the interoperability of the CPS and cloud-based front-end.
 
@@
 
-\subsubsection{Services}\label{services}
-
 Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical Systems (CPS) designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end requires decisions addressing the selection of the services supporting web user interface capable to expose process data.
-In this context, the service is any autonomous (with own identity) software component or module that is interfacing with selected CPS for data collection, analysis, and also remote control.
+In this context, the service is any autonomous (with its own identity) software component or module that is interfacing with selected CPS for data collection, analysis, and also remote control.
 Microsoft Azure is a cloud-based product.
@@
 
-The \textbf{IoT\ Central} service provides a process data visualization
-user interface. To make this interface meaningful metadata called device
-template is used to describe devices.
+The \textbf{IoT\ Central} service provides a user interface of process data visualization. To make this interface meaningful, metadata called device template is used to describe devices.
 
@@
 
-It is worth stressing that interaction of the offered by the Azure
-services can be configured flexibly, and as a result, the presented
-above selection of services must be recognized as an example only. The
-\textbf{IoT\ Central} can be also seamlessly integrated with other
-services as needed. The following services could also be considered to
-build cloud-based automation solution:
+It is worth stressing that interaction of the offered by the Azure services can be configured flexibly, and as a result, the presented above selection of services must be recognized as an example only.
+The \textbf{IoT\ Central} can be also seamlessly integrated with other services as needed.
+The following services could also be considered to build a cloud-based automation solution:
 
@@
 
-\emph{Industrial\ IoT} promotes OPC UA client/server archetype used to
-achieve direct and interactive interoperability implemented using
-\emph{IoT\ Edge} services that allow extracting initial data
-processing to local premises based on the edge concept.
-\emph{Digital\ Twins} is an emerging concept to use an observer to
-replicate selected process state and behavior. The possibility to add
-value as a result of using these services must be subject to further
-research.
+\emph{Industrial\ IoT} promotes OPC UA client/server archetype used to achieve direct and interactive interoperability implemented using \emph{IoT\ Edge} services that allow extracting initial data processing to local premises based on the edge concept.
+\emph{Digital\ Twins} is an emerging concept to use an observer to replicate selected process state and behavior.
+The possibility to add value as a result of using these services must be subject to further research.
 
-\subsubsection{Data Interchange}\label{data-interchange}
-
-System components interoperability means the necessity of the
-information exchange between them. The main challenge of
-interoperability implementation is that information is abstract -- it is
-knowledge describing the process in concern state and behavior,
-e.g.~temperature in a boiler, a car speed, an account balance, etc.
-Obviously, abstraction cannot be processed by the cyber-physical
-machines. It is also impossible to transfer abstraction from one place
-to another over the network.
+System components interoperability means the necessity of the information exchange between them.
+The main challenge of interoperability implementation is that information is abstract -- it is knowledge describing the process in concern state and behavior, e.g.~temperature in a boiler, a car speed, an account balance, etc.
+Obviously, abstraction cannot be processed by cyber-physical machines.
+It is also impossible to transfer abstraction from one place to another over the network.
 
@@
 
-It should be nothing new for us, as it is obvious that the same
-information printed as a text in regional newspapers in English, German,
-Polish, etc. does not resemble one another, but the text meaning should
-always be the same. To understand a newspaper we must learn the
-appropriate language. To understand the binary data we must have defined
-a data type -- a description of how to create an appropriate bits
-pattern (syntax) and rules needed to assign the information (semantics),
-i.e.~make any correct bitstream meaningful. Concluding, to make two
-systems interoperable, a semantic-context must be established. The type
-plays the role of metadata, a set of data that describes other data.
-Metadata term is frequently used if the semantic-context is defined
-using a native language to select built-in types engaging a
-general-purpose graphical user interface.
+It should be nothing new for us, as it is obvious that the same information printed as a text in regional newspapers in English, German, Polish, etc.
+does not resemble one another, but the text meaning should always be the same.
+To understand a newspaper we must learn the appropriate language.
+To understand the binary data we must have defined a data type -- a description of how to create an appropriate bits pattern (syntax) and rules needed to assign the information (semantics), i.e.
+make any correct bitstream meaningful.
+Concluding, to make two systems interoperable, a semantic-context must be established.
+The type plays the role of metadata, a set of data that describes other data.
+Metadata term is frequently used if the semantic-context is defined using a native language to select built-in types engaging a general-purpose graphical user interface.
 
@@
 
-Having defined types in advance, a gateway may provide dedicated conversions functionality, i.e.~replacing bitstreams used by the CPS by equivalent ones for the cloud-based services.
+Having defined types in advance, a gateway may provide dedicated conversions functionality, i.e.
+replacing bitstreams used by the CPS with equivalent ones for the cloud-based services.
 The Azure offers a vast variety of built-in types ready to be used in common cases, but not necessarily there are equivalent counterparts in use by the CPS.
@@
 
-Although the data conversion is a run-time gateway task the
-implementation of the conversion algorithms must be recognized as an
-engineering task, and therefore this topic is not considered for further
-discussion.
+Although the data conversion is a run-time gateway task the implementation of the conversion algorithms must be recognized as an engineering task, and therefore this topic is not considered for further discussion.
 
-In \textbf{IoT\ Central} a CPS is represented as a set
-of devices. The characteristics and behavior of each device kind are
-described by the device template. This Device Template (DT) contains
-also metadata describing the data exchanged over the
-wire with the CPS called Device Capability Model
-(DCM). Additionally, the DT contains properties, customization, and
-views definitions used by the service locally. As an option, DCM
-expressed as a JSON-LD can be imported into a Device Template.
-\textbf{IoT\ Central} allows also to create and edit a DCM using the
-dedicated web UI. A JSON file containing DCM can be derived from an
-information model used as a foundation to establish the semantic-context
-applied to achieve interoperability of the devices interconnected as the
-CPS. DCM development against any external information
-model is a design-time task and should be supported by dedicated
-development tools. In any case, the data interchanged between the cloud
-and the gateway must be compliant with the DCM, hence the middleware
-software must be aware of conversions that must be applied to achieve
-this interoperability.
+In \textbf{IoT\ Central} a CPS is represented as a set of devices.
+The characteristics and behavior of each device kind are described by the device template.
+This Device Template (DT) contains also metadata describing the data exchanged over the wire with the CPS called Device Capability Model (DCM).
+Additionally, the DT contains properties, customization, and views definitions used by the service locally.
+As an option, DCM expressed as a JSON-LD can be imported into a Device Template.
+\textbf{IoT\ Central} also allows to create and edit a DCM using the dedicated web UI.
+A JSON file containing DCM can be derived from an information model used as a foundation to establish the semantic-context applied to achieve interoperability of the devices interconnected as the CPS.
+DCM development against any external information model is a design-time task and should be supported by dedicated development tools.
+In any case, the data interchanged between the cloud and the gateway must be compliant with the DCM, hence, the middleware software must be aware of conversions that must be applied to achieve this interoperability.
 
-\subsubsection{Connectivity}\label{subsubsection.connectivity}
-
-From the cloud side, it is proposed to employ the \emph{IoT\ Hub} service to handle the network traffic targeting the cyber-physical system.
+From the cloud side, it is proposed to engage the \emph{IoT\ Hub} service to handle the network traffic targeting the cyber-physical system.
 This service offers profiles of the AMQP, MQTT, and HTTPS protocol stacks.
 In any case, process data is transparently transferred back-and-forth to the upper layer \textbf{IoT\ Central} service.
-Hence, the payload formatting is determined by the DCM associated with the \textbf{IoT\ Central} solution.
+Hence, the DCM associated with the \textbf{IoT\ Central} solution determines the payload formatting.
 
-The Azure supports HTTP, AMQP, and MQTT protocol stacks which are all standard ones.
-Consequently, it is possible to apply any available ones compliant with an appropriate specification to achieve connectivity.
+The Azure supports HTTP, AMQP, and MQTT protocol stacks, which are all standard ones.
+Consequently, it is possible to apply any available implementation compliant with an appropriate specification to achieve connectivity.
 In this case, all parameters required to establish semantic and security contexts are up to the gateway responsibility.
@@
 To promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub (Sect.
-\ref*{subs.architecture}) and support the \emph{Reactive Interoperability} (Sect.
-\ref*{introduction}) concept.
-A framework compliant with these requirements has been implemented as an open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) under an umbrella of the project Object-Oriented Internet \cite{mariusz_postol_2020_4361640}.
+\ref{subs.architecture}) and support the \emph{Reactive Interoperability} (Sect.
+\ref{introduction}) concept.
+A framework compliant with these requirements has been implemented as an open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) under an umbrella of the project Object-Oriented Internet  (OOI)\cite{mariusz_postol_2020_4361640}.
 The library is designed to be a foundation for developing application programs that are taking part in a message-centric communication pattern and interconnected using the reactive networking concept.
-The diagram in Fig.~\ref*{figure2.UADataApplicationArchitecture} shows the relationship between the library (\emph{SDK}) and external parts composing any reactive networking application (\emph{Reactive\ Application}).
+The diagram in Fig.~\ref{figure2.UADataApplicationArchitecture} shows the relationship between the library (\emph{SDK}) and external parts composing any reactive networking application (\emph{Reactive\ Application}).
 The \emph{Reactive Application} is an aggregation of parts implementing the \emph{Producer} and \emph{Consumer} roles.
@@
 OPC Unified Architecture Part 14 PubSub has been selected in this respect (Sect.
-\ref*{subs.architecture}).
+\ref{subs.architecture}).
 By design, this standard should support the required publisher-subscriber communication pattern.
@@
 
-Many parts in the domain model presented in Fig.~\ref*{figure2.UADataApplicationArchitecture} requires a polymorphic approach to implementation.
+Many parts in the domain model presented in Fig.~\ref{figure2.UADataApplicationArchitecture} requires a polymorphic approach to implementation.
 To promote the polymorphic ready solution the following concepts have been adopted:
@@
       \item \emph{IConfigurationDataFactory} - the configuration data access
-      \item \emph{IMessageHandlerFactory} - \emph{Message} entities pushing to/pulling from the wire
+      \item \emph{IMessageHandlerFactory} - \textbf{Message} entities pushing to/pulling from the wire
       \item \emph{IEncodingFactory} - searching a dictionary containing value converters
@@
 
-The \emph{Consumer} and \emph{Producer} classes are derived from the \emph{DataRepository} (Fig.~\ref*{figure2.UADataApplicationArchitecture}).
+The \emph{Consumer} and \emph{Producer} classes are derived from the \emph{DataRepository} (Fig.~\ref{figure2.UADataApplicationArchitecture}).
 The \emph{Consumer} uses the \emph{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
@@
 From the discussion covered by the Sect.
-\ref*{subs.architecture} we can infer that the interoperability of communicating parties requires establishing a semantic-context and security-context between them.
+\ref{subs.architecture} we can infer that the interoperability of communicating parties requires establishing a semantic-context and security-context between them.
 If the received data is driven to any external data destination (e.g.
@@
 
-\section{Azure - Object-Oriented Internet Interoperability Implementation}\label{sect.gateway-implementation}
+\section{Azure - OOI Implementation}\label{sect.gateway-implementation}
 
-\subsection{Implementation Architecture}\label{subsection.GatewayImplementationArchitecture}
-
-A generic domain model presenting interconnection architecture between the Azure \emph{Cloud-based\ Front-end} and \emph{Cyber-physical\ node} attached to the \emph{Cyber-physical\ network} is presented in Fig.
-\ref*{figure1.StrategyDomainModel}.
+A generic domain model presenting interconnection architecture between the Azure \emph{Cloud-based\ Front-end} and \emph{Cyber-physical\ node} attached to the \emph{Cyber-physical\ network} is presented in Fig.~\ref{figure1.StrategyDomainModel}.
 It is proposed to implement the \emph{Cyber-physical\ node} by adopting the \emph{Reactive Application} archetype compliant with the reactive interoperability concept (Fig.
-\ref*{figure2.UADataApplicationArchitecture}) described in the Sect.
-\ref*{ooi-main-technology-features}.
+\ref{figure2.UADataApplicationArchitecture}) described in the Sect.
+\ref{ooi-main-technology-features}.
 Merging selected entities of this archetype into the proposed domain model (Fig.
-\ref*{figure1.StrategyDomainModel}) lead to a model expressed as the diagram presented in Fig.
-\ref*{figure3.ImplementationDomainModel}.
+\ref{figure1.StrategyDomainModel}) lead to a model expressed as the diagram presented in Fig.
+\ref{figure3.ImplementationDomainModel}.
 In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as as a composable part aggregated by the \emph{Reactive Application}.
@@
 In the final deployment architecture (Fig.
-\ref*{figure4.ImplementationArchitecture}) the \emph{Consumer} role has been realized by the \emph{PartDataManagementSetup} that is derived from \emph{DataManagementSetup} provided by the library.
+\ref{figure4.ImplementationArchitecture}) the \emph{Consumer} role has been realized by the \emph{PartDataManagementSetup} that is derived from \emph{DataManagementSetup} provided by the library.
 \emph{Networking} (SDK) was removed from this diagram for the sake of simplicity.
@@
 This class provides an entry point to initialize all properties, which are injection points of all parts composing this role.
-It extends functionality of the \emph{DataManagementSetup} based on the following associated classes:
+It extends the functionality of the \emph{DataManagementSetup} based on the following associated classes:
 
@@
 
-\begin{enumerate}
+\begin{itemize}
       \item \emph{PartConfigurationFactory} - to get access to the application configuration
@@
       \item \emph{CommunicationContext} - to handle communication with the Azure services
-\end{enumerate}
+\end{itemize}
 
@@
 The \emph{PartBindingFactory} implements the \emph{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
-The received data is driven to \emph{CommunicationContext} for further encoding and finally pushing it to the Azure services using configured out-of-band protocol.
+The received data is driven to \emph{CommunicationContext} for further encoding and finally pushing it to the Azure services using the configured out-of-band protocol.
 
 \emph{IEncodingFactory} and \emph{IMessageHandlerFactory} interfaces (Fig.
-\ref*{figure2.UADataApplicationArchitecture}) have been implemented in independent libraries and ae not considered for any modifications to deploy \emph{Embedded Gateway} functionality.
+\ref{figure2.UADataApplicationArchitecture}) have been implemented in independent libraries and ae not considered for any modifications to deploy \emph{Embedded Gateway} functionality.
 The current implementation of the mentioned interfaces is localized at run time as services using an instance of the \emph{IServiceLocator}\footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} }.
 In this example, it is assumed that \emph{IServiceLocator} is implemented to resolve references to any external services.
-Both interfaces are used to manage interconnection of the node with the \emph{Cyber-physical Network}.
+Both interfaces are used to manage the interconnection of the node with the \emph{Cyber-physical Network}.
 
-The Azure interconnection is realized using the \emph{CommunicationContext}. It implements message encoder and establishes the out-of-band communication stack.
+The Azure interconnection is realized using the \emph{CommunicationContext}. It implements a message encoder and establishes the out-of-band communication stack.
 
@@
 The transfer process requires data conversion from source to destination encoding, i.e.
-replacing bitstreams used by the CPS by equivalent ones for the cloud-based services.
+replacing bitstreams used by the CPS with equivalent ones for the cloud-based services.
 The Azure offers a vast variety of built-in types ready to be used in common cases, but not necessarily there are equivalent counterparts in use by the CPS.
@@
 The PubSub uses JSON and binary Data Transfer Object encodings.
-In any case the data recovered from the Message pulled from a subscription is stored locally using the object model based on standard .NET types.
+In any case, the data recovered from the Message pulled from a subscription is stored locally using the object model based on standard .NET types.
 \emph{PartBindingFactory} maps selected object graph onto the JSON message required by the cloud services.
@@
 The Azure supports standard protocols (Sec.
-\ref*{azure-main-technology-features}).
+\ref{azure-main-technology-features}).
 Consequently, it is possible to apply any available ones compliant with an appropriate specification to achieve connectivity.
-In the proposed gateway implementation the Azure interconnection has been obtained using the packages described in Sect.
-\ref*{subsubsection.connectivity}.
+In the proposed gateway implementation, the Azure interconnection has been obtained using the packages described in Sect.
+\ref{azure-main-technology-features}.
 
-Azure and PubSub uses different security mechanism so in the proposed solution establishing security-context is realized independently.
+Azure and PubSub use different security mechanisms so in the proposed solution establishing security-context is realized independently.
 The \emph{CommunicationContext} is responsible to establish this context as an embedded negotiation phase tightly coupled with establishing interconnection.
@@
 
-Nowadays, the macro optimization of the industrial processes requires an integration of a vast variety of distributed applications provided by the Information and Communication Technology.
-It requires further research on the integration of \textbf{machine-centric} Cyber-Physical Systems (CPS) with \textbf{human-centric} front-end in the context of new emerging disciplines, i.e.
+Nowadays, the macro optimization of the industrial processes requires an integration of a vast variety of distributed applications provided by Information and Communication Technology.
+It requires further research on the integration of \textbf{machine - centric} Cyber-Physical Systems (CPS) with \textbf{human - centric} front-end in the context of new emerging disciplines, i.e.
 Industry 4.0 and the Industrial Internet of Things (Sect.
-\ref*{introduction}).
+\ref{introduction}).
 
@@
 As it was pointed out in the Sect.
-\ref*{subs.architecture} using OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} the aggregation of nodes by the network is loosely coupled, i.e.
+\ref{subs.architecture} using OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} the aggregation of nodes by the network is loosely coupled, i.e.
 nodes can be added and removed from the network dynamically, and nodes may represent mobile data holding assets.
@@
 From the analysis covered by the Sect.
-\ref*{subs.architecture} it is concluded that the \emph{Embedded Gateway} archetype best suits all requirements described above.
+\ref{subs.architecture} it is concluded that the \emph{Embedded Gateway} archetype best suits all requirements described above.
 It relaxes most of the issues related to \textbf{direct interconnection} and solutions inferred from the middleware concept, i.e.
@@
 Additionally, it could be used to connect to many independent clouds at the same time.
-The generic domain model for the proposed interconnection archetype is presented in the Fig.~\ref*{figure1.StrategyDomainModel}.
+The generic domain model for the proposed interconnection archetype is presented in the Fig.~\ref{figure1.StrategyDomainModel}.
 We have highlighted that to promote the separation of concern design principle, the gateway functionality should be implemented as a self-contained dedicated software part embedded in the core \emph{Networking} service of the \emph{Cyber-physical\ node}.
-Main functionality of this component is to transfer process data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
+The main functionality of this component is to transfer process data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
 
 To promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub (Sect.
-\ref*{subs.architecture}) and support the \emph{Reactive Interoperability} (Sect.
-\ref*{introduction}) concept.
-We proposed to use an open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) (Fig.~\ref*{figure2.UADataApplicationArchitecture}) for this purpose.
+\ref{subs.architecture}) and support the \emph{Reactive Interoperability} (Sect.
+\ref{introduction}) concept.
+We proposed to use an open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) (Fig.~\ref{figure2.UADataApplicationArchitecture}) for this purpose.
 It is worth stressing that based on this approach only dedicated functionality related to the communication with the cloud must be implemented.
@@
 We derived the final model presented in Fig.
-\ref*{figure4.ImplementationArchitecture} by merging selected entities from the \emph{Networking} library (Fig.~\ref*{figure2.UADataApplicationArchitecture}) into the generic interconnection domain model (Fig.
-\ref*{figure1.StrategyDomainModel}).
+\ref{figure4.ImplementationArchitecture} by merging selected entities from the \emph{Networking} library (Fig.~\ref{figure2.UADataApplicationArchitecture}) into the generic interconnection domain model (Fig.
+\ref{figure1.StrategyDomainModel}).
 In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as as a composable part aggregated by the \emph{Reactive Application}.

### 2021-01-03 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Research on publication journal #50
- Harmonized latex files
References #23
- add ref related to M2M communication

@@
 In this case, any human interaction must be recognized as impractical or even impossible.
-This interconnection scenario requires the machine to machine communication (M2M) demanding multi-vendor devices integration.
+This interconnection scenario requires the machine to machine communication (M2M) \cite{RefWorks:doc:5d6cdbbbe4b082ad50f3a83e, mpostol2020, RefWorks:doc:5d8f6d9ee4b058d660094a94, RefWorks:doc:5d868e46e4b030b4e0569e60, RefWorks:doc:5d8f7275e4b0bc72a68f4dcb} demanding multi-vendor devices integration.
 
@@
 
+System components interoperability means the necessity of the information exchange between them.
+The main challenge of interoperability implementation is that information is abstract -- it is knowledge describing the process in concern state and behavior, e.g.~temperature in a boiler, a car speed, an account balance, etc.
+Obviously, abstraction cannot be processed by cyber-physical machines.
+It is also impossible to transfer abstraction from one place to another over the network.
+
 Fortunately, computer science offers a workaround to address that impossibility - the information must be represented as a binary stream.
@@
 \end{itemize}
-
-System components interoperability means the necessity of the information exchange between them.
-The main challenge of interoperability implementation is that information is abstract -- it is knowledge describing the process in concern state and behavior, e.g.~temperature in a boiler, a car speed, an account balance, etc.
-Obviously, abstraction cannot be processed by cyber-physical machines.
-It is also impossible to transfer abstraction from one place to another over the network.
 
@@
 
-\begin{itemize}
-      \item implementation of practically any configuration management scenario,
-      \item modification of this functionality later after releasing the library or deploying the application program in the production environment.
-\end{itemize}
-
 Concluding, decoupling of this functionality implementation using an abstract contract and late binding mechanism allows:
@@
 \end{figure}
+
+\hyphenation{PartData-Mana-gement-Setup}
 

### 2021-01-03 Latex/ReferenceVersionDocumentclassArticle/Manuscript.tex
Research on publication journal #50
- moved base document to separate folder. There are problems with references.
References #23
- add ref related to M2M communication

--- 2021-01-02 Latex/Manuscript.tex
@@
       \centering
-      \includegraphics[width=8cm]{../.Media/StrategyDomainModel.png}
+      \includegraphics[width=8cm]{../../.Media/StrategyDomainModel.png}
       \caption{Domain model of a generic interconnection concept}\label{figure1.StrategyDomainModel}
@@
       \centering
-      \includegraphics[width=8cm]{../.Media/UADataApplicationArchitecture.png}
+      \includegraphics[width=8cm]{../../.Media/UADataApplicationArchitecture.png}
       \caption{Reactive interoperability implementation}\label{figure2.UADataApplicationArchitecture}
@@
       \centering
-      \includegraphics[width=8cm]{../.Media/ImplementationDomainModel.png}
+      \includegraphics[width=8cm]{../../.Media/ImplementationDomainModel.png}
       \caption{Architecture Domain Model}\label{figure3.ImplementationDomainModel}
@@
       \centering
-      \includegraphics[width=10cm]{../.Media/ImplementationArchitecture.png}
+      \includegraphics[width=10cm]{../../.Media/ImplementationArchitecture.png}
       \caption{Implementation Architecture}\label{figure4.ImplementationArchitecture}

### 2021-01-03 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
References #23
- added all references from existing bib file ( ICCS20 ).

@@
 
-A typical \textbf{human-centric} approach is a web-service supporting, for example, a web user interface (UI) to monitor conditions and manage millions of devices and their data in a typical cloud-based IoT approach.
+A typical \textbf{human-centric} approach is a web-service supporting, for example, a web user interface (UI) to monitor conditions and manage millions of devices and their data in a typical cloud-based IoT approach \cite{RefWorks:doc:5d87d02be4b0e88bdacab9a7, RefWorks:doc:5d87d1c9e4b0bc72a68d7b46, RefWorks:doc:5d9216c9e4b03ba5e075a855}.
 In this case, it is characteristic that any uncertainty and necessity to make a decision can be relaxed by human interaction.
@@
 
-Deployment of the hybrid solution providing interoperability of the \textbf{machine - centric} Cyber-Physical System (CPS) and \textbf{human - centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect.
+Deployment of the hybrid solution providing interoperability of the \textbf{machine - centric} Cyber-Physical System (CPS) \cite{RefWorks:doc:5c458659e4b014f3944f6969} and \textbf{human - centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect.
 \ref{subs.architecture}).
@@
 For this integration, a new architecture is proposed to support the reactive relationship of communicating parties.
-To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected.
+To support the multi-vendor environment OPC Unified Architecture \cite{RefWorks:doc:5ac86c99e4b009947bbb87c6, LiteratureSurveyOnOpenPlatformCommunications, RefWorks:doc:5ac86c99e4b009947bbb87d2} interoperability standard has been selected.
 Prototyping addresses Microsoft Azure Cloud as an example.
 The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as the open-source (MIT licensed) \cite{mariusz_postol_2020_4361640}.
-The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet (OOI) \cite{mariusz_postol_2020_4361640}.
+The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet (OOI) \cite{mariusz_postol_2020_4361640, RefWorks:doc:5c6912c9e4b0a562a3fc7f5b, RefWorks:doc:5c66740ae4b081adf5804596}.
 
@@
 
-To comply with the Industry 4.0 communication criterion it is required that any product must be addressable over the network via TCP/UDP or IP and has to support the OPC UA Information Model.
+To comply with the Industry 4.0 communication criterion it is required that any product must be addressable over the network via TCP/UDP \cite{RefWorks:doc:5d8e1874e4b0bc72a68f0d11} or IP \cite{RefWorks:doc:5ac86c98e4b009947bbb8730} and has to support the OPC UA Information Model \cite{OPCUAPart5, RefWorks:doc:5ac86c99e4b009947bbb87c9, RefWorks:doc:5d986a28e4b0b0c862c0d184}.
 As a result, any product being advertised as Industry 4.0 enabled must be OPC UA-capable somehow.
@@
 
-Azure aids Internet protocols and open standards such as JSON, XML, SOAP, REST, MQTT, AMQP, and HTTP.
+Azure aids Internet protocols and open standards such as JSON, XML, SOAP, REST, MQTT\cite{RefWorks:doc:5d91e158e4b02eb43d36bb97}, AMQP\cite{RefWorks:doc:5d91d2d9e4b0bc72a68ffe06}, and HTTP.
 A software development kits for C\#, Java, PHP, and Ruby are available for custom applications.
@@
 raw data (e.g.
-PLC internal registers), OPC UA Address Space Management, cloud, file, database, graphical user interface, to name only a few.
+PLC internal registers), OPC UA Address Space Management \cite{mpostol2020}, cloud, file, database, graphical user interface, to name only a few.
 
@@
 It is worth stressing that there is no dependency on the Client/Server session-oriented relationship.
-This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server.
+This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} \cite{RefWorks:doc:5ac86c97e4b009947bbb8728} embedded component of the OPC UA Server.
 The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to embed the \emph{Embedded Gateway} component into the OPC UA Client or Server to get connected with the cloud in case of the interactive relationship.

### 2021-01-06 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Final review of the latex text #37
- refactored headers of the tex files.

@@
 It promotes a reactive interoperability pattern and a generic approach to establishing interoperability-context.
-A reference implementation of this archetype is described in Sect.~\ref{sect.gateway-implementation}.
+A reference implementation of this archetype is described in Sect.~\ref{section.gateway-implementation}.
 The most important findings and future work are summarized in Sect.~\ref{section.conclusion}.
@@
 
-\section{Azure - OOI Implementation}\label{sect.gateway-implementation}
+\section{Azure - OOI Implementation}\label{section.gateway-implementation}
 

### 2021-01-06 Latex/ReferenceVersionDocumentclassArticle/Manuscript.tex
Final review of the latex text #37
- refactored headers of the tex files.

@@
 \documentclass{article}
+\usepackage{graphicx}
+\usepackage{cite}
+\usepackage{hyperref}
 \usepackage{geometry}
@@
 \usepackage{amsmath,amsthm,amssymb}
-\usepackage{hyperref}
-\usepackage{cite}
 \usepackage{stfloats}
@@
 
-%\pagestyle{headings}
-%\headtitle{OOI - Azure Interoperability}
-
 \pagestyle{fancy}
@@
 \rfoot{Page \thepage}
+\providecommand{\keywords}[1]{ \small \textbf{\emph{Keywords---}} #1 }
 
-\newtheorem{definition}{Definition}
-\newtheorem{theorem}[definition]{Theorem}
-\newtheorem{corollary}[definition]{Corollary}
-\newtheorem{proposition}[definition]{Proposition}
-\newtheorem{example}[definition]{Example}
-
-\providecommand{\tightlist} { \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\providecommand{\keywords}[1]{ \small \textbf{\emph{Keywords---}} #1 }
+\begin{document}
 
@@
 \author[1]{Mariusz Postół, Piotr Szymczak}
-%\author[2]{Piotr Szymczak}
-%\headauthor{Postół M, Szymczak P}
 \affil[1]
@@
 }
-\date{}
-
-\begin{document}
 
@@
 
+      \keywords{Industry 4.0 \and Internet of Things \and Object-Oriented Internet \and Cloud Computing \and Industrial communication \and Reactive Networking (RxNetworking)\and Machine to Machine Communication \and OPC Unified Architecture \and Azure}
+
 \end{abstract}
-
-\keywords{ Azure, Cloud Computing, Object-Oriented Internet, Industrial communication, Industry 4.0, Internet of Things, Machine to Machine Communication, OPC Unified Architecture,
-Reactive Networking (RxNetworking)  }
-
-\maketitle
 

### 2021-01-07 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Final review of the latex text #37
- working copy

@@
 
-A typical \textbf{human-centric} approach is a web-service supporting, for example, a web user interface (UI) to monitor conditions and manage millions of devices and their data in a typical cloud-based IoT approach \cite{RefWorks:doc:5d87d02be4b0e88bdacab9a7, RefWorks:doc:5d87d1c9e4b0bc72a68d7b46, RefWorks:doc:5d9216c9e4b03ba5e075a855}.
+A typical \textbf{human-centric} approach is a web-service supporting, for example, a web user interface (UI) to monitor conditions and manage millions of devices and their data in a typical cloud-based IoT approach \cite{RefWorks:doc:5d87d02be4b0e88bdacab9a7, RefWorks:doc:5d87d1c9e4b0bc72a68d7b46, RefWorks:doc:5d9216c9e4b03ba5e075a855, 10.1007/978-3-030-50426-7_22}.
 In this case, it is characteristic that any uncertainty and necessity to make a decision can be relaxed by human interaction.

### 2021-01-08 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Final review of the latex text #37
- MP final review of ICCS21MPostoOOIGateway2Azure

@@
 
-If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship could relax the problems encountered while the interactive approach is applied.
+If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship could relax the problems encountered while the interactive approach is applied \cite{mpostol2020}.
 In this case, the sessionless publisher-subscriber communication relationship is a typical pattern to implement the abstract reactive interoperability paradigm.
@@
 To support the multi-vendor environment OPC Unified Architecture \cite{RefWorks:doc:5ac86c99e4b009947bbb87c6, LiteratureSurveyOnOpenPlatformCommunications, RefWorks:doc:5ac86c99e4b009947bbb87d2} interoperability standard has been selected.
-Prototyping addresses Microsoft Azure Cloud as an example.
+Prototyping addresses Microsoft Azure Cloud \cite{MicrosoftAzureIoTPlatform} as an example.
 The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as the open-source (MIT licensed) \cite{mariusz_postol_2020_4361640}.
@@
 \begin{itemize}
-      \item reactive interoperability M2M communication based on the OPC UA standard can be implemented as a powerful standalone library without dependency on the Client/Server session-oriented archetype
+      \item reactive M2M interoperability based on the OPC UA standard can be implemented as a powerful standalone library without dependency on the Client/Server session-oriented archetype
       \item Azure interoperability can be implemented as an external part employing out-of-band communication without dependency on the OPC UA implementation
@@
 
-As it was explained in Sect.~\ref{introduction}, to follow the Industry 4.0 concept a hybrid environment integrating reactive Machine to Machine interconnection and the interactive web-based user interface is required (Sect.
+To follow the Industry 4.0 concept a hybrid environment integrating reactive Machine to Machine interconnection and the interactive web-based user interface is required (Sect.
 \ref{introduction}).
@@
 \textbf{Edge device} connects directly to the cloud services but acts as an intermediary for other devices called leaf devices.
-Additionally, it allows the selection of initial data processing and execution of them using local resources.
+Additionally, it allows the selection of initial data and processing of them using local resources.
 The \textbf{edge device} may be located close to the leaf devices and attached to the \emph{Cyber-physical network} using protocols applicable only to local computer networks.
@@
 
-A library that meets all these requirements has been implemented consistently with the Object-Oriented Internet (OOI) paradigm \cite{mariusz_postol_2020_4361640} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }.
+An open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) that meets all these requirements has been implemented consistently with the Object-Oriented Internet (OOI) paradigm \cite{mariusz_postol_2020_4361640} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }.
 The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the OOI concept compliant with the OPC UA PubSub international standard.
@@
 protocol profile, data encoding, time relationships, etc.) governing communication of the parts making it up.
-At the same time, it must support back-and-forth data transfer to the cloud using out-of-band native for the cloud services.
+At the same time, it must support data transfer to the cloud using out-of-band native for the cloud services.
 The transfer process requires data conversion from source to destination encoding.
@@
       \item development against a type definition of the user interface
-      \item implementation of the functionality of the bitstreams conversion in advance
+      \item implementation of the  bitstreams conversion functionality in advance
 \end{itemize}
@@
 To implement the \emph{DataRepository} dedicated implementation of the \emph{IBinding} interface should be provided to create a bridge between CPS and an external row data represented by the \emph{LocalResources} class.
-A more in-depth description of the \emph{OOI Reactive Application} library enabling data exchange over a network using the reactive networking pattern is in \cite{mpostol2020}.
+A more in-depth description of the \emph{OOI Reactive Application} library enabling data exchange over a network using the reactive networking pattern is covered in \cite{mpostol2020}.
 
@@
 By design, this standard should support the required publisher-subscriber communication pattern.
-It must be stressed, that by design, the specification provides only an abstract interoperability definition.
+It must be stressed that the specification provides only an abstract interoperability definition.
 Abstract means that the standard must not limit the implementation strategy.
@@
 
-The recovered data from the \emph{Message} is obtained from the \emph{PartBindingFactory} using the \emph{IDTOProvider} that defines a contract used to pull the Data Transfer Object (DTO) created from a selected subscription by the \emph{PartBindingFactory}.
+The recovered data from the \emph{Message} is obtained from the \emph{PartBindingFactory} using the \emph{IDTOProvider} that defines a contract used to pull the Data Transfer Object (DTO) created from a subscription by the \emph{PartBindingFactory}.
 The transfer process requires data conversion from source to destination encoding, i.e.
@@
 \ref{azure-main-technology-features}).
-Consequently, it is possible to apply any available ones compliant with an appropriate specification to achieve connectivity.
+Consequently, it is possible to apply any available implementation compliant with an appropriate specification to achieve connectivity.
 In the proposed gateway implementation, the Azure interconnection has been obtained using the packages described in Sect.
@@
 
-Highly-distributed solutions used to control/monitor a set of geographically spread islands of automation (e.g.
+Highly-distributed solutions used to control/monitor a set of geographically dispersed islands of automation (e.g.
 virtual power plants producing renewable energy) additionally must leverage public communication infrastructure, namely the Internet.
@@
 
-If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship\cite{mpostol2020} could alleviate the challenges posed by the interactive approach.
+If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship \cite{mpostol2020} could alleviate the challenges posed by the interactive approach.
 The real-time multi-vendor environment makes communication standardization especially important.
@@
 
-The described results prove that the \emph{Embedded Gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop of the M2M communication compliant with the OPC UA PubSub standard.
+The described results prove that the \emph{Embedded Gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop the M2M communication compliant with the OPC UA PubSub standard.
 It is worth stressing that there is no dependency on the Client/Server session-oriented relationship.
 This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} \cite{RefWorks:doc:5ac86c97e4b009947bbb8728} embedded component of the OPC UA Server.
-The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to embed the \emph{Embedded Gateway} component into the OPC UA Client or Server to get connected with the cloud in case of the interactive relationship.
+The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to inject the \emph{Embedded Gateway} part into the OPC UA Client/Server to get connected with the cloud in case of the interactive relationship.
 
@@
 
-Concluding, the paper describes a proof of the concept that applying the proposed architecture and deployment scenario it is possible to integrate selected cloud services (e.g.
+Concluding, the paper describes a proof of the concept that applying the proposed architecture and deployment scenario it is possible to integrate cloud services (e.g.
 \textbf{Azure\ IoT\ Central}) with the \emph{Cyber-physical network} interconnected as one whole atop of the OPC UA PubSub.
-It is in contrast to interconnecting cloud-based front-end services with the selected \emph{ Address\ Space} exposed by a selected OPC UA server limiting the PubSub role to data exporter transferring the data out of the OPC UA ecosystem.
+It is in contrast to interconnecting cloud-based front-end services with the \emph{ Address\ Space} instance exposed by a selected OPC UA server limiting the PubSub role to data exporter transferring the data out of the OPC UA ecosystem.
 

### 2021-01-08 Latex/ReferenceVersionDocumentclassArticle/Manuscript.tex
Final review of the latex text #37
- MP final review of ICCS21MPostoOOIGateway2Azure

@@
 \usepackage[T1]{fontenc}
-\usepackage{graphicx}
 \usepackage{amsthm}

### 2021-01-09 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Apply LLNCS formatting and rules #52
- llncsdoc.pdf has been applied

@@
 \title{Object-Oriented Internet\\ Cloud Interoperability}
-\titlerunning{OOI - Cloud Interoperability}
+%\titlerunning{OOI - Cloud Interoperability}
 
 \author{Mariusz Postół\inst{1}\orcidID{0000-0002-9669-0565}  \and Piotr Szymczak\inst{1}\orcidID{0000-0001-6790-3878} }
-\authorrunning{M. Postół et al.}
+%\authorrunning{M. Postół et al.}
 
@@
 
-      \keywords{Industry 4.0 \and Internet of Things \and Object-Oriented Internet \and Cloud Computing \and Industrial communication \and Reactive Networking (RxNetworking)\and Machine to Machine Communication \and OPC Unified Architecture \and Azure}
+      \keywords{Industry 4.0 \and Internet of Things \and Object-Oriented Internet \and Cloud Computing \and Industrial communication \and Reactive networking \and Machine to Machine Communication \and OPC Unified Architecture \and Azure}
 
@@
 
+\begin{proposition}
 Unlike the above-described solutions, the \emph{Embedded Gateway} is not derived from the middleware concept.
@@
 The main functionality of this component is to transfer selected data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
+\end{proposition}
 
@@
 
-\section{Azure - OOI Implementation}\label{section.gateway-implementation}
+\section{Azure - OOI Interoperability Implementation}\label{section.gateway-implementation}
 

### 2021-01-09 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
ICCS21 - high-resolution graphics #53
- used wrapfigure
ICCS21 - high-resolution graphics #53
- creted eps files and and added them to the paper folder.
ICCS21 - high-resolution graphics #53
- fixes #53
Make the manuscripts of up to 14 pages long #58
- working copy

@@
 \usepackage{cite}
+\usepackage[verbose]{wrapfig}
 %\usepackage{hyperref}
@@
 Highly-distributed solutions used to control real-time process aggregating islands of automation (e.g.~virtual power plants producing renewable energy) additionally must leverage public communication infrastructure, namely the Internet.
-Internet is a demanding environment for highly distributed process control applications designed atop the M2M communication paradigm because
-
-\begin{itemize}
-      \item it is a globally shareable and can be also used by malicious users
-      \item it offers only non-deterministic communication making integration of islands of automation designed against the real-time requirements a difficult task
-\end{itemize}
+Internet is a demanding environment for highly distributed process control applications designed atop the M2M communication paradigm because it is globally shareable and can be also used by malicious users.
+Furthermore, it offers only non-deterministic communication making integration of islands of automation designed against the real-time requirements a demanding task.
 
 Today both obstacles can be overcome, and as examples, we have bank account remote control and voice over IP in daily use.
-The first application must be fine-tuned in the context of data security, and the second is very sensitive in regard to time constraints.
-Similar approaches could be applied to adopt the well known in process control industry concepts:
-
-\begin{itemize}
-      \item  Human Machine Interface (HMI)
-      \item Supervisory Control and Data Acquisition (SCADA)
-      \item Distributed Control Systems (DCS)
-\end{itemize}
-
-A detailed examination of these solutions is far beyond the scope of this article.
-It is only worth stressing that, by design, all of them are designed on the foundation of interactive communication.
+The first application must be fine-tuned in the context of data security, and the second is very sensitive concerning time constraints.
+Similar approaches could be applied to adopt the well known in process control industry concepts, namely Human Machine Interface (HMI), Supervisory Control and Data Acquisition (SCADA), and Distributed Control Systems (DCS).
+It is worth stressing that, by design, all of them are designed based on interactive communication.
 Interactive communication is based on a data polling foundation.
@@
 The application is active in the data retrieval process - it controls the pace of the retrieval by sending the requests at its convenience.
-Such a polling pattern is similar to visiting the books shop and checking out a book.
-After you are done with the book, you pay another visit to check out another one.
-If the book is not available you must wait, but you may read what you selected.
-The client/server archetype is well suited for the mentioned above applications.
-
 After dynamically attaching a new island of automation the control application (responsible for the data pulling) must be reconfigured for this interoperability scenario.
@@
 
-If the \textbf{machine-centric} interoperability - making up islands of automation - must be monitored and/or controlled by a supervisory system cloud computing concept may be recognized as a beneficial solution to replace or expand the mentioned above applications, i.e.~HMI, SCADA, DCS, etc.
+If the \textbf{machine-centric} interoperability - making up islands of automation - must be monitored and/or controlled by a supervisory system, the cloud computing concept may be recognized as a beneficial solution to replace or expand the mentioned above applications, i.e.~HMI, SCADA, DCS, etc.
 Cloud computing is a method to provide a requested functionality as a set of services.
@@
 
-Deployment of the hybrid solution providing interoperability of the \textbf{machine - centric} Cyber-Physical System (CPS) \cite{RefWorks:doc:5c458659e4b014f3944f6969} and \textbf{human - centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect.
-\ref{subs.architecture}).
-
+%Deployment of the hybrid solution providing interoperability of the \textbf{machine - centric} Cyber-Physical System (CPS) \cite{RefWorks:doc:5c458659e4b014f3944f6969} and \textbf{human - centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect.
+\ref{cloud-to-sensors-field-level-connectivity}).
 By design, the \textbf{direct} approach requires that the cloud has to be compliant with the interoperability standard the CPS is built upon - it becomes a consistent part of the CPS.
@@
 
-\section{Sensors to Cloud Field Level Connectivity}\label{cloud-to-sensors-field-level-connectivity}
+\section{Sensors to Cloud Interconnection - Architecture}\label{cloud-to-sensors-field-level-connectivity}
 
-\subsection{Architecture}\label{subs.architecture}
+%\subsection{Architecture}\label{cloud-to-sensors-field-level-connectivity}
 
@@
 
-In the solution in concern, the interconnection of assets is not enough  hence their interoperability is expected.
-In this case, using the same communication stack must be recognized as only a necessary condition.
-To support interoperability common data understanding is required.
-By design, the direct approach requires that the cloud has to be compliant with the interoperability standard the CPS uses.
+ By design, the \textbf{direct interconnection} approach requires that the cloud has to be compliant with the interoperability standard the CPS uses.
 As a result, it becomes a consistent communication node of the CPS.
-Additionally, to meet this requirement the cloud and CPS have to establish directly the same:
+The decision to follow the \textbf{direct interconnection} scenario must be derived from an analysis of the capabilities of available services in concern.
+However, for the development strategy of this type of solutions this analysis can be done partially taking into account the following features that can be considered invariable.
+By design the cloud-based services must be virtual - they are used to handle many solutions at the same time.
+Furthermore, the M2M communication is usually constrained by the real-time requirements.
+The virtualization of cloud services means that they must be very flexible to handle the attachment of new assets proactively (acting in advance) at run time.
+As a result, the cloud services must be responsible to register and authenticate devices by exposing endpoints in the public network to allow the device to access a provisioning cloud service.
+It requires that a session over the Internet has to be established by the data holding asset at a preparation step.
+To meet the requirements of real-time distributed control the CPS may use protocols applicable only to local computer networks (e.g.~multicast IP, Ethernet, TSN \footnote{Time-Sensitive Networking (TSN) Task Group \url{https://1.ieee802.org/tsn/}}, etc.).
+Because the cloud services support only protocols handling interconnection over the Internet the \textbf{direct interconnection} cannot be applied in this case.
 
-\begin{itemize}
-      \item semantic-context
-      \item security-context
-\end{itemize}
-
-The possibility to establish a common semantic-context in the multi-vendor environment makes communication standardization especially important.
-In this case, it is required that the encoding of the payload exchanged over the network (Data Transfer Object - DTO) is standardized so that the appropriate messages can be factored on the data-gathering site and consumed on the ultimate destination data processing sites.
-Security between the data origin and ultimate data destination refers to the protection of messages (security-context) against malicious users.
-It is required that communicating parties are using the same cyber-security measures.
-
-The decision to follow the \textbf{direct interconnection} scenario must be derived from an analysis of the capabilities of available services in concern.
-However, for the development strategy of this type of solutions this analysis can be done partially taking into account two features that can be considered invariable:
-
-\begin{itemize}
-      \item by design the cloud-based services must be virtual - they are used to handle many solutions at the same time
-      \item by design the M2M communication is usually constrained by the real-time requirements
-\end{itemize}
-
-The virtualization of cloud services means that they must be very flexible to handle the attachment of new assets proactively (acting in advance) at run time.
-As a result, by design, the cloud services must be responsible to register and authenticate devices by exposing endpoints in the public network to allow the device to access a provisioning cloud service.
-It requires that a session over the Internet has to be established by the data holding asset at a preparation step.
-
-To meet the requirements of real-time distributed control the CPS may use protocols applicable only to local computer networks (e.g.~multicast IP, Ethernet, TSN \footnote{Time-Sensitive Networking (TSN) Task Group \url{https://1.ieee802.org/tsn/}}, etc.).
-Because the cloud services support only protocols handling interconnection over the Internet the interaction with the cloud requires remote agents, i.e.~agents attached locally to the M2M network and implemented by applying one of the following archetypes:
+To support also a local network attachment point, the interaction with the cloud requires remote agents, i.e.~agents attached locally to the M2M network and implemented by applying one of the following archetypes:
 
@@
 \end{itemize}
-
-\begin{figure}
-      \centering
-      \includegraphics[width=8cm]{../../.Media/StrategyDomainModel.png}
-      \caption{Domain model of a generic interconnection concept}\label{figure1.StrategyDomainModel}
-\end{figure}
 
@@
 
-The \emph{Embedded Gateway} archetype relaxes most of the issues described above: \emph{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security - context differences to name only a few.
+\begin{wrapfigure}{t}{0.55\textwidth}
+      \includegraphics[width=0.53\textwidth]{StrategyDomainModel.eps}
+      \caption{Generic interconnection concept}\label{figure1.StrategyDomainModel}
+\end{wrapfigure}
+
+% The \emph{Embedded Gateway} archetype relaxes most of the issues described above: \emph{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security - context differences to name only a few.
 The main goal of this article is to provide proof that the \emph{Embedded Gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogeneous environments in concern.
@@
 
+The interconnection of assets is not enough hence their interoperability is expected.
+In this case, using the same communication stack must be recognized as only a necessary condition.
+To support interoperability common data understanding is required.
+Additionally, to meet this requirement the cloud and CPS have to establish directly the same semantic-context and security-context.
+The possibility to establish a common semantic-context in the multi-vendor environment makes communication standardization especially important.
+In this case, it is required that the encoding of the payload exchanged over the network (Data Transfer Object - DTO) is standardized so that the appropriate messages can be factored on the data-gathering site and consumed on the ultimate destination data processing sites.
+Security between the data origin and ultimate data destination refers to the protection of messages (security-context) against malicious users.
+It is required that communicating parties are using the same cyber-security measures.
 To comply with the Industry 4.0 communication criterion it is required that any product must be addressable over the network via TCP/UDP \cite{RefWorks:doc:5d8e1874e4b0bc72a68f0d11} or IP \cite{RefWorks:doc:5ac86c98e4b009947bbb8730} and has to support the OPC UA Information Model \cite{OPCUAPart5, RefWorks:doc:5ac86c99e4b009947bbb87c9, RefWorks:doc:5d986a28e4b0b0c862c0d184}.
@@
 To promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub (Sect.
-\ref{subs.architecture}) and support the \emph{Reactive Interoperability} (Sect.
+\ref{cloud-to-sensors-field-level-connectivity}) and support the \emph{Reactive Interoperability} (Sect.
 \ref{introduction}) concept.
@@
 
-\begin{figure}
+\begin{wrapfigure}{r}{0.55\textwidth}
       \centering
-      \includegraphics[width=8cm]{../../.Media/UADataApplicationArchitecture.png}
-      \caption{Reactive interoperability implementation}\label{figure2.UADataApplicationArchitecture}
-\end{figure}
+      \includegraphics[width=0.53\textwidth]{UADataApplicationArchitecture.eps}
+      \caption{Reactive interoperability architecture}\label{figure2.UADataApplicationArchitecture}
+\end{wrapfigure}
 
@@
 OPC Unified Architecture Part 14 PubSub has been selected in this respect (Sect.
-\ref{subs.architecture}).
+\ref{cloud-to-sensors-field-level-connectivity}).
 By design, this standard should support the required publisher-subscriber communication pattern.
@@
 
+\begin{wrapfigure}{t}{0.55\textwidth}
+      \centering
+      \includegraphics[width=0.53\textwidth]{ImplementationDomainModel.eps}
+      \caption{Architecture Domain Model}\label{figure3.ImplementationDomainModel}
+\end{wrapfigure}
+
 From the discussion covered by the Sect.
-\ref{subs.architecture} we can infer that the interoperability of communicating parties requires establishing a semantic-context and security-context between them.
+\ref{cloud-to-sensors-field-level-connectivity} we can infer that the interoperability of communicating parties requires establishing a semantic-context and security-context between them.
 If the received data is driven to any external data destination (e.g.
@@
 
-\begin{figure}
-      \centering
-      \includegraphics[width=8cm]{../../.Media/ImplementationDomainModel.png}
-      \caption{Architecture Domain Model}\label{figure3.ImplementationDomainModel}
-\end{figure}
-
 \hyphenation{PartData-Mana-gement-Setup}
@@
 It extends the functionality of the \emph{DataManagementSetup} based on the following associated classes:
-
-\begin{figure}
-      \centering
-      \includegraphics[width=10cm]{../../.Media/ImplementationArchitecture.png}
-      \caption{Implementation Architecture}\label{figure4.ImplementationArchitecture}
-\end{figure}
 
@@
 It is ready to provide all necessary configuration parameters to establish semantic and security contexts related to Azure interoperability.
+
+\begin{figure}
+      \centering
+      \includegraphics[width=11cm]{ImplementationArchitecture.eps}
+      \caption{Implementation Architecture}\label{figure4.ImplementationArchitecture}
+\end{figure}
 
@@
 As it was pointed out in the Sect.
-\ref{subs.architecture} using OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} the aggregation of nodes by the network is loosely coupled, i.e.
+\ref{cloud-to-sensors-field-level-connectivity} using OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} the aggregation of nodes by the network is loosely coupled, i.e.
 nodes can be added and removed from the network dynamically, and nodes may represent mobile data holding assets.
@@
 From the analysis covered by the Sect.
-\ref{subs.architecture} it is concluded that the \emph{Embedded Gateway} archetype best suits all requirements described above.
+\ref{cloud-to-sensors-field-level-connectivity} it is concluded that the \emph{Embedded Gateway} archetype best suits all requirements described above.
 It relaxes most of the issues related to \textbf{direct interconnection} and solutions inferred from the middleware concept, i.e.

### 2021-01-10 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Make the manuscripts of up to 14 pages long #58
- removed Azure Main Technology Features

@@
 By design, the \textbf{direct} approach requires that the cloud has to be compliant with the interoperability standard the CPS is built upon - it becomes a consistent part of the CPS.
-Data models, roles, and responsibility differences of both solutions make this approach impractical or even imposable to be applied in typical cases.
+Data models, roles, and responsibility differences of both solutions make this approach impractical or even imposable to be applied in a general case.
 A more detailed description is covered by the Sect.~\ref{cloud-to-sensors-field-level-connectivity}.
@@
 The decision to follow the \textbf{direct interconnection} scenario must be derived from an analysis of the capabilities of available services in concern.
-However, for the development strategy of this type of solutions this analysis can be done partially taking into account the following features that can be considered invariable.
+However, for the development strategy of this type of solution, this analysis can be done partially taking into account the following features that can be considered invariable.
 By design the cloud-based services must be virtual - they are used to handle many solutions at the same time.
-Furthermore, the M2M communication is usually constrained by the real-time requirements.
+Furthermore, M2M communication is usually constrained by real-time requirements.
 The virtualization of cloud services means that they must be very flexible to handle the attachment of new assets proactively (acting in advance) at run time.
@@
 To meet the requirements of real-time distributed control the CPS may use protocols applicable only to local computer networks (e.g.~multicast IP, Ethernet, TSN \footnote{Time-Sensitive Networking (TSN) Task Group \url{https://1.ieee802.org/tsn/}}, etc.).
-Because the cloud services support only protocols handling interconnection over the Internet the \textbf{direct interconnection} cannot be applied in this case.
+Because the cloud services support only protocols handling interconnection over the Internet the \textbf{direct interconnection} cannot be applied in a general case.
 
-To support also a local network attachment point, the interaction with the cloud requires remote agents, i.e.~agents attached locally to the M2M network and implemented by applying one of the following archetypes:
+To support also a local network attachment point, the interaction with the cloud requires remote agents implemented by applying one of the following archetypes:
 
@@
 The possibility to establish a common semantic-context in the multi-vendor environment makes communication standardization especially important.
-In this case, it is required that the encoding of the payload exchanged over the network (Data Transfer Object - DTO) is standardized so that the appropriate messages can be factored on the data-gathering site and consumed on the ultimate destination data processing sites.
+In this case, it is required that the encoding of the payload exchanged over the network (Data Transfer Object) is standardized so that the appropriate messages can be factored on the data-gathering site and consumed on the ultimate destination data processing sites.
 Security between the data origin and ultimate data destination refers to the protection of messages (security-context) against malicious users.
 It is required that communicating parties are using the same cyber-security measures.
-To comply with the Industry 4.0 communication criterion it is required that any product must be addressable over the network via TCP/UDP \cite{RefWorks:doc:5d8e1874e4b0bc72a68f0d11} or IP \cite{RefWorks:doc:5ac86c98e4b009947bbb8730} and has to support the OPC UA Information Model \cite{OPCUAPart5, RefWorks:doc:5ac86c99e4b009947bbb87c9, RefWorks:doc:5d986a28e4b0b0c862c0d184}.
+To comply with the Industry 4.0 communication criterion it is required that any product must be addressable over the network via TCP/UDP or IP and has to support the OPC UA Information Model \cite{OPCUAPart5, RefWorks:doc:5ac86c99e4b009947bbb87c9, RefWorks:doc:5d986a28e4b0b0c862c0d184}.
 As a result, any product being advertised as Industry 4.0 enabled must be OPC UA-capable somehow.
+
 To support the multi-vendor environment OPC Unified Architecture interoperability standard has been selected.
@@
 As a result, the platform can be used not only as a cloud-based front-end for CPS.
-By design, the Azure services are compliant with Security Development Lifecycle (SDL) an industry-leading security process.
-It is also compliant with the new international standard for cloud privacy, namely ISO 27018.
-Solutions hosted on Azure are scaled up to millions of users without any additional coding.
-For the development of the CPS front-end, it is essential that Azure provides very efficient storage services usefully for the purpose of real-time process data archival.
-Azure provides a vast variety of hybrid connections including but not limited to virtual private networks (VPNs), caches, content delivery networks (CDNs), ExpressRoute, and IoT dedicated services that can be directly used to implement cloud-based front-end for CPS.
-Because it is also integrated with other Microsoft tools like Office 365, Outlook, and SharePoint using Azure allows preserving investment and exporting process data to the mentioned tools.
-Azure also offers services supporting analytics and intelligence capabilities for further improving business processes and decision making.
-It is the only cloud platform that offers Blockchain as a Service (BaaS), Machine Learning, Bots, and Cognitive APIs capabilities.
-
 Azure aids Internet protocols and open standards such as JSON, XML, SOAP, REST, MQTT\cite{RefWorks:doc:5d91e158e4b02eb43d36bb97}, AMQP\cite{RefWorks:doc:5d91d2d9e4b0bc72a68ffe06}, and HTTP.
 A software development kits for C\#, Java, PHP, and Ruby are available for custom applications.
-Azure provides services supporting data exchange over the OPC UA, but they don't support PubSub compliant with the OPC UA Part-14.
-Connectivity services on the network use JSON-based Data Transfer Object encoded based on schema derived from the solution metadata.
-
-A more detailed description of the selected Azure features in the context of the application in concern is covered by the Sec.~\ref{azure-main-technology-features}.
 
@@
 
-An open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) that meets all these requirements has been implemented consistently with the Object-Oriented Internet (OOI) paradigm \cite{mariusz_postol_2020_4361640} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }.
+An open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) that meets all these requirements has been implemented consistently with the Object-Oriented Internet (OOI) paradigm \cite{RefWorks:doc:5c66740ae4b081adf5804596} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }.
 The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the OOI concept compliant with the OPC UA PubSub international standard.
@@
 This approach also improves flexibility and adaptability of the existing solutions against any modification of the production environment, including but not limited to the selected interoperability standard change.
-
-Sect.~\ref{ooi-main-technology-features} provides a more detailed description of this library and an external part deployment process that is to be used to implement new functionality supporting \emph{Embedded\ Gateway}.
-
-The following subsections cover the description of the current state of technologies concerning Azure cloud-based IoT enabler and OPC UA PubSub.
-Sect.
-\ref{azure-main-technology-features} analyzes data presentation user interface, available native communication services, and data/metadata model offered by Microsoft Azure.
-The discussion covered by this section is the foundation for selecting services utilized to expose process data and suitable protocol stack to support interconnection.
-In Sect.
-\ref{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a foundation for further decisions addressing the systematic design of the interoperability of the CPS and cloud-based front-end.
-
-\subsection{Azure Main Technology Features}\label{azure-main-technology-features}
-
-Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical Systems (CPS) designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end requires decisions addressing the selection of the services supporting web user interface capable to expose process data.
-In this context, the service is any autonomous (with its own identity) software component or module that is interfacing with selected CPS for data collection, analysis, and also remote control.
-Microsoft Azure is a cloud-based product.
-It offers a vast variety of services.
-This virtual environment handles an unlimited number of users and devices organized using a solution container concept.
-The solution aggregates users, devices, services, and required additional resources scoping on a selected scenario.
-It also serves as a context that provides a scope to the identifiers (the names of devices, users, process data entities, etc) inside it.
-Solutions are used to organize deployment entities into logical groups and prevent identity collisions.
-
-The \textbf{IoT\ Central} service provides a user interface of process data visualization. To make this interface meaningful, metadata called device template is used to describe devices.
-
-Following the assumption that interconnection between the CPS and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler.
-It must be interconnected with the CPS using an in-band protocol adhering to communications requirements (i.e.
-protocol profile, data encoding, time relationships, etc.) governing communication of the parts making it up.
-At the same time, it must support data transfer to the cloud using out-of-band native for the cloud services.
-The transfer process requires data conversion from source to destination encoding.
-The \textbf{IoT\ Hub} is a service hosted in the cloud that supports \textbf{IoT\ Central} services providing a robust messaging solution - it acts as a central message hub for bi-directional communication \cite{MicrosoftAzureIoTPlatform}.
-This communication is transparent, i.e.~it is not data types aware allowing any devices to exchange any kind of data.
-This service is responsible to manage the devices' identity and it offers the following protocol stacks: AMQP, MQTT, and HTTPS.
-
-Before process data can be exposed using a web user interface the data source must be associated with an appropriate solution and validated to make sure that the security rules are not violated.
-It is hard to assume that the security rules governing the CPS may also apply to the cloud-based services.
-In the gateway scenario, they can be mapped on each other or be entirely independent.
-The \emph{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper service for \emph{IoT\ Hub} that enables devices' connection process management, upon device providing valid identity attestation it assigns the device to an appropriate \emph{IoT\ Hub} instance and returns to the device connection parameters, which allow direct connection with given \emph{IoT\ Hub} service.
-The device proceeds to use the same attestation in \emph{IoT\ Hub} connection and based on it, is granted authorization to selected operations including but not limited to data transfer and updating the user interface.
-
-It is worth stressing that interaction of the offered by the Azure services can be configured flexibly, and as a result, the presented above selection of services must be recognized as an example only.
-The \textbf{IoT\ Central} can be also seamlessly integrated with other services as needed.
-The following services could also be considered to build a cloud-based automation solution:
-
-\begin{itemize}
-      \item \emph{Industrial\ IoT} - discovering OPC UA enabled servers in a factory network and register them in Azure \emph{IoT\ Hub} implemented using \emph{IoT\ Edge}
-      \item \emph{Digital\ Twins} - managing the graph of digital twins, which are to represent some real-world process or entity
-\end{itemize}
-
-\emph{Industrial\ IoT} promotes OPC UA client/server archetype used to achieve direct and interactive interoperability implemented using \emph{IoT\ Edge} services that allow extracting initial data processing to local premises based on the edge concept.
-\emph{Digital\ Twins} is an emerging concept to use an observer to replicate selected process state and behavior.
-The possibility to add value as a result of using these services must be subject to further research.
-
-System components interoperability means the necessity of the information exchange between them.
-The main challenge of interoperability implementation is that information is abstract -- it is knowledge describing the process in concern state and behavior, e.g.~temperature in a boiler, a car speed, an account balance, etc.
-Obviously, abstraction cannot be processed by cyber-physical machines.
-It is also impossible to transfer abstraction from one place to another over the network.
-
-Fortunately, computer science offers a workaround to address that impossibility - the information must be represented as a binary stream.
-In consequence, we can usually use both terms as interchangeable ones while talking about ICT systems.
-Unfortunately, these terms must be precisely observed in the context of further discussion, because we must be aware of the fact that the same information could have many different but equivalent representations.
-In other words, the same information can be represented by a vast variety of different binary patterns.
-For example, numbers may be represented using 2's Complement and Floating-Point binary representations.
-
-It should be nothing new for us, as it is obvious that the same information printed as a text in regional newspapers in English, German, Polish, etc.
-does not resemble one another, but the text meaning should always be the same.
-To understand a newspaper we must learn the appropriate language.
-To understand the binary data we must have defined a data type -- a description of how to create an appropriate bits pattern (syntax) and rules needed to assign the information (semantics), i.e.
-make any correct bitstream meaningful.
-Concluding, to make two systems interoperable, a semantic-context must be established.
-The type plays the role of metadata, a set of data that describes other data.
-Metadata term is frequently used if the semantic-context is defined using a native language to select built-in types engaging a general-purpose graphical user interface.
-
-Using the data type definitions to describe information interchange between communicating parties allows:
-
-\begin{itemize}
-      \item development against a type definition of the user interface
-      \item implementation of the  bitstreams conversion functionality in advance
-\end{itemize}
-
-Having defined types in advance, a gateway may provide dedicated conversions functionality, i.e.
-replacing bitstreams used by the CPS with equivalent ones for the cloud-based services.
-The Azure offers a vast variety of built-in types ready to be used in common cases, but not necessarily there are equivalent counterparts in use by the CPS.
-Additionally, the data conversion must address the following issues:
-
-\begin{itemize}
-      \item usually to covert data from source to destination representation, the middleware software native types must be used
-      \item if the out of the box set of types is not capable of fulfilling more demanding needs, custom data types must be defined
-\end{itemize}
-
-Although the data conversion is a run-time gateway task the implementation of the conversion algorithms must be recognized as an engineering task, and therefore this topic is not considered for further discussion.
-
-In \textbf{IoT\ Central} a CPS is represented as a set of devices.
-The characteristics and behavior of each device kind are described by the device template.
-This Device Template (DT) contains also metadata describing the data exchanged over the wire with the CPS called Device Capability Model (DCM).
-Additionally, the DT contains properties, customization, and views definitions used by the service locally.
-As an option, DCM expressed as a JSON-LD can be imported into a Device Template.
-\textbf{IoT\ Central} also allows to create and edit a DCM using the dedicated web UI.
-A JSON file containing DCM can be derived from an information model used as a foundation to establish the semantic-context applied to achieve interoperability of the devices interconnected as the CPS.
-DCM development against any external information model is a design-time task and should be supported by dedicated development tools.
-In any case, the data interchanged between the cloud and the gateway must be compliant with the DCM, hence, the middleware software must be aware of conversions that must be applied to achieve this interoperability.
-
-From the cloud side, it is proposed to engage the \emph{IoT\ Hub} service to handle the network traffic targeting the cyber-physical system.
-This service offers profiles of the AMQP, MQTT, and HTTPS protocol stacks.
-In any case, process data is transparently transferred back-and-forth to the upper layer \textbf{IoT\ Central} service.
-Hence, the DCM associated with the \textbf{IoT\ Central} solution determines the payload formatting.
-
-The Azure supports HTTP, AMQP, and MQTT protocol stacks, which are all standard ones.
-Consequently, it is possible to apply any available implementation compliant with an appropriate specification to achieve connectivity.
-In this case, all parameters required to establish semantic and security contexts are up to the gateway responsibility.
-Alternatively, the API offered by the dedicated frameworks (libraries) may be used.
-Using a framework the configuration process may be reduced significantly, and the communication protocol selection has only an indirect impact on the interoperability features.
-The Azure interconnection may be obtained using the following \emph{Microsoft.Azure} packages:
-
-\begin{itemize}
-      \item \emph{Devices} - Service SDK for Azure IoT Devices
-      \item \emph{Devices.Client} - Device SDK for Azure \emph{IoT\ Hub} including dependencies implementing MQTT and AMQP communication
-      \item \emph{Devices.Shared} - Common code for Azure IoT Device and Service SDK
-      \item \emph{Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
-      \item \emph{Devices.Provisioning.Transport.*} - Provisioning Device Client Transports (HTTPS, AMQP, MQTT) for Azure IoT Devices
-\end{itemize}
 
@@
 
-The recovered data from the \emph{Message} is obtained from the \emph{PartBindingFactory} using the \emph{IDTOProvider} that defines a contract used to pull the Data Transfer Object (DTO) created from a subscription by the \emph{PartBindingFactory}.
+The recovered data from the \emph{Message} is obtained from the \emph{PartBindingFactory} using the \emph{IDTOProvider} that defines a contract used to pull the Data Transfer Object created from a subscription by the \emph{PartBindingFactory}.
 The transfer process requires data conversion from source to destination encoding, i.e.
@@
 
+%TBD
+The Azure supports HTTP, AMQP, and MQTT protocol stacks, which are all standard ones.
+Consequently, it is possible to apply any available implementation compliant with an appropriate specification to achieve connectivity.
+In this case, all parameters required to establish semantic and security contexts are up to the gateway responsibility.
+Alternatively, the API offered by the dedicated frameworks (libraries) may be used.
+Using a framework the configuration process may be reduced significantly, and the communication protocol selection has only an indirect impact on the interoperability features.
+The Azure interconnection may be obtained using the following \emph{Microsoft.Azure} packages:
+
+\begin{itemize}
+      \item \emph{Devices} - Service SDK for Azure IoT Devices
+      \item \emph{Devices.Client} - Device SDK for Azure \emph{IoT\ Hub} including dependencies implementing MQTT and AMQP communication
+      \item \emph{Devices.Shared} - Common code for Azure IoT Device and Service SDK
+      \item \emph{Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
+      \item \emph{Devices.Provisioning.Transport.*} - Provisioning Device Client Transports (HTTPS, AMQP, MQTT) for Azure IoT Devices
+\end{itemize}
+
+%____________________
+
 The encoded JSON messages must be transferred over the network to Azure using the selected protocol stack.
-The Azure supports standard protocols (Sec.
-\ref{azure-main-technology-features}).
+The Azure supports standard protocols.
 Consequently, it is possible to apply any available implementation compliant with an appropriate specification to achieve connectivity.
 In the proposed gateway implementation, the Azure interconnection has been obtained using the packages described in Sect.
-\ref{azure-main-technology-features}.
 

### 2021-01-10 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Make the manuscripts of up to 14 pages long #58
- reviewed section 3
- now the manuscripts contains 14 pages

@@
 
-%\subsection{Architecture}\label{cloud-to-sensors-field-level-connectivity}
-
 To follow the Industry 4.0 concept a hybrid environment integrating reactive Machine to Machine interconnection and the interactive web-based user interface is required (Sect.
@@
 \begin{itemize}
-      \item \textbf{direct interconnection} (tightly coupled scenario) - cloud-based dedicated communication services are engaged to attach it to the CPS making up a consistent M2M communication network using a common protocol stack
-      \item \textbf{gateway based interconnection} (loosely coupled scenario) - native build-in communication services allows attaching the cloud to the CPS using an out-of-bound protocol stack
+      \item \textbf{direct interconnection} (tightly coupled)-using a common protocol stack
+      \item \textbf{gateway based interconnection} (loosely coupled)-using an out-of-bound protocol stack
 \end{itemize}
@@
 In this scenario, it is possible to use a custom protocol stack to get connected to the \textbf{edge device} with the cloud and helps to save the bandwidth thanks to sending only the results of local processing.
-In this approach, the \textbf{edge device} is part of cloud vendor products and cannot be recognized as a generic solution that can be used to connect to other clouds at the same time.
+In this approach, the \textbf{edge device} is part of cloud vendor products and cannot be recognized as a generic solution that can be used to connect to other clouds supporting many-to-many relationship.
 
@@
 The only difference compared with the \textbf{edge device} is a necessity to use officially supported by the cloud vendor services to get connected.
-In this scenario, the process data simultaneously may be transferred to many clouds provided that the gateway offers this functionality.
+In this scenario, the process data simultaneously may be transferred to many clouds.
 
@@
 According to proposed generic architecture (Fig.~\ref{figure1.StrategyDomainModel}) to implement the \emph{Embedded\ Gateway} as a composable part of the \emph{Cyber-physical\ node} a library implementing \emph{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
-Additionally, it must be assumed that the library used to deploy \emph{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/PubSub gateway functionality.
+Additionally, it must be assumed that the library used to deploy \emph{Embedded\ Gateway} supports dependency injection and is capable to compose an external part supporting Azure/PubSub gateway functionality.
 The composition process must be available without modification of the core code of an existing library.
@@
 
-An open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) that meets all these requirements has been implemented consistently with the Object-Oriented Internet (OOI) paradigm \cite{RefWorks:doc:5c66740ae4b081adf5804596} worked out in an open-source project \footnote{ \url{https://github.com/mpostol/OPC-UA-OOI} }.
-The paper \cite{mpostol2020} covers the description of a reference application program implementation proving that it is possible to design universal architecture targeting reactive interoperability as a consistent part of the OOI concept compliant with the OPC UA PubSub international standard.
-According to the presented implementation and evaluation, using the dependency injection and late binding, the application program can be seamlessly adapted to the production environment and scales well.
-This approach also improves flexibility and adaptability of the existing solutions against any modification of the production environment, including but not limited to the selected interoperability standard change.
-
-\subsection{OOI Main Technology Features}\label{ooi-main-technology-features}
-
-To promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub (Sect.
-\ref{cloud-to-sensors-field-level-connectivity}) and support the \emph{Reactive Interoperability} (Sect.
+To promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub and support the \emph{Reactive Interoperability} (Sect.
 \ref{introduction}) concept.
-A framework compliant with these requirements has been implemented as an open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) under an umbrella of the project Object-Oriented Internet  (OOI)\cite{mariusz_postol_2020_4361640}.
+A framework compliant with these requirements has been implemented as an open-source library\footnote{\url{https://github.com/mpostol/OPC-UA-OOI}} named \emph{UAOOI.Networking} (\emph{Networking} for short) under an umbrella of the Object-Oriented Internet project \cite{mariusz_postol_2020_4361640}.
 The library is designed to be a foundation for developing application programs that are taking part in a message-centric communication pattern and interconnected using the reactive networking concept.
@@
 By design, they support access to real-time process data, hence they are recognized as an extension of \emph{DataRepository} class.
-To implement the \emph{DataRepository} dedicated implementation of the \emph{IBinding} interface should be provided to create a bridge between CPS and an external row data represented by the \emph{LocalResources} class.
+To implement the \emph{DataRepository} dedicated implementation of the \emph{IBindingFactory} interface should be provided to create a bridge between CPS and an external row data represented by the \emph{LocalResources} class.
 A more in-depth description of the \emph{OOI Reactive Application} library enabling data exchange over a network using the reactive networking pattern is covered in \cite{mpostol2020}.
@@
 \begin{wrapfigure}{r}{0.55\textwidth}
-      \centering
       \includegraphics[width=0.53\textwidth]{UADataApplicationArchitecture.eps}
@@
 
-From the above discussion, we can learn that the main design decisions must concern standardization and flexibility.
-Standardization needs the selection of an international interoperability specification to make the library ready to be adopted by the multi-vendor environment.
-Flexibility requires an architecture that promotes the polymorphic independent implementation of essential functions.
-
-Piece by piece integration of a cyber-physical system using multi-vendor products requires that M2M communication employs international standards as the interoperability foundation.
-OPC Unified Architecture Part 14 PubSub has been selected in this respect (Sect.
-\ref{cloud-to-sensors-field-level-connectivity}).
-By design, this standard should support the required publisher-subscriber communication pattern.
-It must be stressed that the specification provides only an abstract interoperability definition.
-Abstract means that the standard must not limit the implementation strategy.
-
-Many parts in the domain model presented in Fig.~\ref{figure2.UADataApplicationArchitecture} requires a polymorphic approach to implementation.
-To promote the polymorphic ready solution the following concepts have been adopted:
-
-\begin{itemize}
-      \item \textbf{separation of concerns} - to allow an independent development of the parts~\cite{RefWorks:doc:5d92609be4b02eb43d372bd1}
-      \item \textbf{dependency injection} - to allow late binding of separately implemented parts~\cite{RefWorks:doc:5d925b77e4b030b4e0596f5d}
-\end{itemize}
-
 To promote the polymorphic approach, the library has a factory class called \emph{DataManagementSetup} that is a placeholder to gather all injection points used to compose external parts.
-To be injected the parts must be compliant with an appropriate contract expressed as the following interfaces:
-
-\begin{itemize}
-      \item \emph{IBindingFactory} - bidirectional data exchange with the underlying process
-      \item \emph{IConfigurationDataFactory} - the configuration data access
-      \item \emph{IMessageHandlerFactory} - \textbf{Message} entities pushing to/pulling from the wire
-      \item \emph{IEncodingFactory} - searching a dictionary containing value converters
-\end{itemize}
-
-It is expected that the functionality implementation expressed by these interfaces is provided as independent external composable parts.
-The composition is accomplished at run time, and the effective application functionality depends essentially on reusable loosely coupled parts composed applying the dependency injection software engineering and adaptive programming concept \cite{RefWorks:doc:5d9796cbe4b0f66c52dccf04}.
+To be injected the part supporting data exchange with the underlying process must be compliant with the \emph{IBindingFactory} interfaces.
+It is expected that the functionality implementation expressed by this interface is provided as an independent external composable part.
+The composition is accomplished at run time, and the effective application functionality depends essentially on reusable loosely coupled parts composed applying the dependency injection software engineering concept.
 
@@
 The \emph{Producer} mirrors the \emph{Consumer} functionality and, after reading data from an associated source, populates the \emph{Message} using the gathered data.
-
 By design, the \emph{DataRepository} and associated entities, i.e.~\emph{Local Resources}, \emph{Consumer}, \emph{Producer} are embedded in external parts, and consequently, the application scope may cover practically any concern that can be separated from the core \emph{Reactive Application} implementation.
 
-The application startup phase concerns all the parts composed to make a running instance of the application program using the dependency injection approach to allow separate development and late binding.
-This approach makes any modification straightforward at any development and maintenance stage.
-From the end-user point of view, the composition process of the running program using independently developed parts is invisible.
-Because in any case a single program instance is created in a typical approach, we shall expect a commonly shared configuration mechanism providing mutually exclusive parameters to separately developed parts.
-This scenario has been addressed by the proposed implementation thanks to making the configuration expandable.
+\section{Azure - OOI Interoperability Implementation}\label{section.gateway-implementation}
 
 \begin{wrapfigure}{t}{0.55\textwidth}
-      \centering
       \includegraphics[width=0.53\textwidth]{ImplementationDomainModel.eps}
@@
 
-From the discussion covered by the Sect.
-\ref{cloud-to-sensors-field-level-connectivity} we can infer that the interoperability of communicating parties requires establishing a semantic-context and security-context between them.
-If the received data is driven to any external data destination (e.g.
-cloud-based front-end) using out-of-band protocol semantic-context and security-context must be defined for this interoperability relationship.
-There are a vast variety of possibilities for how to define these contexts.
-Anyway, the most common starting point is the configuration.
-The proposed approach to instantiate the application as a set of composable parts is very useful in this respect because it makes it possible to expand the core configuration functionality and adapt it to be helpful also in this case.
-Therefore, the semantic-context may be created based on the configuration using the implementation of the \emph{IConfigurationDataFactory} interface.
-
-Concluding, decoupling of this functionality implementation using an abstract contract and late binding mechanism allows:
-
-\begin{itemize}
-      \item implementation of practically any configuration management scenario,
-      \item modification of this functionality later after releasing the library or deploying the application program in the production environment.
-\end{itemize}
-
-\section{Azure - OOI Interoperability Implementation}\label{section.gateway-implementation}
-
 A generic domain model presenting interconnection architecture between the Azure \emph{Cloud-based\ Front-end} and \emph{Cyber-physical\ node} attached to the \emph{Cyber-physical\ network} is presented in Fig.~\ref{figure1.StrategyDomainModel}.
 It is proposed to implement the \emph{Cyber-physical\ node} by adopting the \emph{Reactive Application} archetype compliant with the reactive interoperability concept (Fig.
-\ref{figure2.UADataApplicationArchitecture}) described in the Sect.
-\ref{ooi-main-technology-features}.
+\ref{figure2.UADataApplicationArchitecture}).
 Merging selected entities of this archetype into the proposed domain model (Fig.
@@
 \ref{figure3.ImplementationDomainModel}.
-In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as as a composable part aggregated by the \emph{Reactive Application}.
+In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as a composable part aggregated by the \emph{Reactive Application}.
 
@@
 \begin{itemize}
-      \item \emph{PartConfigurationFactory} - to get access to the application configuration
       \item \emph{PartBindingFactory} - to gather the data recovered from the \emph{Message} instances pulled from the wire
@@
 
-In this case, the implementation of the \emph{IConfigurationFactory} interface is based entirely on the \emph{Networking} library.
-The implementation provided by the library is generic, but it is flexible enough to meet all the requirements, which warrants no need for further modifications for adoption.
-It is ready to provide all necessary configuration parameters to establish semantic and security contexts related to Azure interoperability.
-
-\begin{figure}
-      \centering
-      \includegraphics[width=11cm]{ImplementationArchitecture.eps}
-      \caption{Implementation Architecture}\label{figure4.ImplementationArchitecture}
-\end{figure}
-
 The \emph{PartBindingFactory} implements the \emph{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
@@
 
-\emph{IEncodingFactory} and \emph{IMessageHandlerFactory} interfaces (Fig.
+%\emph{IEncodingFactory} and \emph{IMessageHandlerFactory} interfaces (Fig.
 \ref{figure2.UADataApplicationArchitecture}) have been implemented in independent libraries and ae not considered for any modifications to deploy \emph{Embedded Gateway} functionality.
@@
 Both interfaces are used to manage the interconnection of the node with the \emph{Cyber-physical Network}.
+
+\begin{wrapfigure}{t}{0.55\textwidth}
+      \includegraphics[width=0.53\textwidth]{ImplementationArchitecture.eps}
+      \caption{Implementation Architecture}\label{figure4.ImplementationArchitecture}
+\end{wrapfigure}
 
@@
 
-%TBD
+The encoded JSON messages must be transferred to Azure over the network using the selected protocol stack.
 The Azure supports HTTP, AMQP, and MQTT protocol stacks, which are all standard ones.
@@
 Using a framework the configuration process may be reduced significantly, and the communication protocol selection has only an indirect impact on the interoperability features.
-The Azure interconnection may be obtained using the following \emph{Microsoft.Azure} packages:
-
-\begin{itemize}
-      \item \emph{Devices} - Service SDK for Azure IoT Devices
-      \item \emph{Devices.Client} - Device SDK for Azure \emph{IoT\ Hub} including dependencies implementing MQTT and AMQP communication
-      \item \emph{Devices.Shared} - Common code for Azure IoT Device and Service SDK
-      \item \emph{Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
-      \item \emph{Devices.Provisioning.Transport.*} - Provisioning Device Client Transports (HTTPS, AMQP, MQTT) for Azure IoT Devices
-\end{itemize}
-
-%____________________
-
-The encoded JSON messages must be transferred over the network to Azure using the selected protocol stack.
-The Azure supports standard protocols.
-Consequently, it is possible to apply any available implementation compliant with an appropriate specification to achieve connectivity.
-In the proposed gateway implementation, the Azure interconnection has been obtained using the packages described in Sect.
+In the proposed implementation, the Azure interconnection has been obtained using the mentioned above frameworks.
 

### 2021-01-10 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Make the manuscripts of up to 14 pages long #58
- reviewed full text
- now it contains 14 pages
- improved graphics against text modification
Make the manuscripts of up to 14 pages long #58
- replaced Azure by cloud where possible
- added environment proposition} to stress our outcome
- fixes #58

@@
 
-%Deployment of the hybrid solution providing interoperability of the \textbf{machine - centric} Cyber-Physical System (CPS) \cite{RefWorks:doc:5c458659e4b014f3944f6969} and \textbf{human - centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect.
-\ref{cloud-to-sensors-field-level-connectivity}).
-By design, the \textbf{direct} approach requires that the cloud has to be compliant with the interoperability standard the CPS is built upon - it becomes a consistent part of the CPS.
-Data models, roles, and responsibility differences of both solutions make this approach impractical or even imposable to be applied in a general case.
-A more detailed description is covered by the Sect.~\ref{cloud-to-sensors-field-level-connectivity}.
-
 This article addresses further research on the integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M communication and emerging cloud computing as a \textbf{human-centric} front-end in the context of the Industry 4.0 (I4.0) and Industrial Internet of Things (IIoT) disciplines.
@@
       \item reactive M2M interoperability based on the OPC UA standard can be implemented as a powerful standalone library without dependency on the Client/Server session-oriented archetype
-      \item Azure interoperability can be implemented as an external part employing out-of-band communication without dependency on the OPC UA implementation
+      \item cloud interoperability can be implemented as an external part employing out-of-band communication without dependency on the OPC UA implementation
       \item the proposed generic architecture allows that the gateway functionality is implemented as composable part at run-time part - no programming required
@@
 
-% The \emph{Embedded Gateway} archetype relaxes most of the issues described above: \emph{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security - context differences to name only a few.
-The main goal of this article is to provide proof that the \emph{Embedded Gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogeneous environments in concern.
-The proposed implementation is designed for a selected interoperability standard and cloud product.
-
 The interconnection of assets is not enough hence their interoperability is expected.
@@
 According to proposed generic architecture (Fig.~\ref{figure1.StrategyDomainModel}) to implement the \emph{Embedded\ Gateway} as a composable part of the \emph{Cyber-physical\ node} a library implementing \emph{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
-Additionally, it must be assumed that the library used to deploy \emph{Embedded\ Gateway} supports dependency injection and is capable to compose an external part supporting Azure/PubSub gateway functionality.
+Additionally, it must be assumed that the library used to deploy \emph{Embedded\ Gateway} supports dependency injection and is capable to compose an external part supporting cloud/PubSub gateway functionality.
 The composition process must be available without modification of the core code of an existing library.
@@
 \begin{wrapfigure}{r}{0.55\textwidth}
-      \includegraphics[width=0.53\textwidth]{UADataApplicationArchitecture.eps}
+      \includegraphics[width=0.53\textwidth]{UADataApplicationArchitectureAzure.eps}
       \caption{Reactive interoperability architecture}\label{figure2.UADataApplicationArchitecture}
@@
 
-\section{Azure - OOI Interoperability Implementation}\label{section.gateway-implementation}
+\section{Cloud - OOI Interoperability Implementation}\label{section.gateway-implementation}
 
-\begin{wrapfigure}{t}{0.55\textwidth}
-      \includegraphics[width=0.53\textwidth]{ImplementationDomainModel.eps}
-      \caption{Architecture Domain Model}\label{figure3.ImplementationDomainModel}
-\end{wrapfigure}
-
-A generic domain model presenting interconnection architecture between the Azure \emph{Cloud-based\ Front-end} and \emph{Cyber-physical\ node} attached to the \emph{Cyber-physical\ network} is presented in Fig.~\ref{figure1.StrategyDomainModel}.
+\begin{proposition}
+      A generic domain model presenting interconnection architecture between the \emph{Cloud-based\ Front-end} and \emph{Cyber-physical\ node} attached to the \emph{Cyber-physical\ network} is presented in Fig.~\ref{figure1.StrategyDomainModel}.
 It is proposed to implement the \emph{Cyber-physical\ node} by adopting the \emph{Reactive Application} archetype compliant with the reactive interoperability concept (Fig.
@@
 In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as a composable part aggregated by the \emph{Reactive Application}.
+\end{proposition}
+
+\begin{wrapfigure}{t}{0.55\textwidth}
+      \includegraphics[width=0.53\textwidth]{ImplementationDomainModel.eps}
+      \caption{Architecture Domain Model}\label{figure3.ImplementationDomainModel}
+\end{wrapfigure}
 
@@
 This class provides an entry point to initialize all properties, which are injection points of all parts composing this role.
-It extends the functionality of the \emph{DataManagementSetup} based on the following associated classes:
-
-\begin{itemize}
-      \item \emph{PartBindingFactory} - to gather the data recovered from the \emph{Message} instances pulled from the wire
-      \item \emph{CommunicationContext} - to handle communication with the Azure services
-\end{itemize}
+It extends the functionality of the \emph{DataManagementSetup} based on the following associated classes: \emph{PartBindingFactory} and \emph{CommunicationContext}.
 
 The \emph{PartBindingFactory} implements the \emph{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network.
-The received data is driven to \emph{CommunicationContext} for further encoding and finally pushing it to the Azure services using the configured out-of-band protocol.
+The received data is driven to \emph{CommunicationContext} for further encoding and finally pushing it to the cloud services using the configured out-of-band protocol.
 
-%\emph{IEncodingFactory} and \emph{IMessageHandlerFactory} interfaces (Fig.
-\ref{figure2.UADataApplicationArchitecture}) have been implemented in independent libraries and ae not considered for any modifications to deploy \emph{Embedded Gateway} functionality.
-The current implementation of the mentioned interfaces is localized at run time as services using an instance of the \emph{IServiceLocator}\footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} }.
-In this example, it is assumed that \emph{IServiceLocator} is implemented to resolve references to any external services.
-Both interfaces are used to manage the interconnection of the node with the \emph{Cyber-physical Network}.
+The cloud interconnection is realized using the \emph{CommunicationContext}. It implements a message encoder and establishes the out-of-band communication stack.
 
-\begin{wrapfigure}{t}{0.55\textwidth}
-      \includegraphics[width=0.53\textwidth]{ImplementationArchitecture.eps}
+\begin{wrapfigure}{t}{0.5\textwidth}
+      \includegraphics[width=0.49\textwidth]{ImplementationArchitecture.eps}
       \caption{Implementation Architecture}\label{figure4.ImplementationArchitecture}
 \end{wrapfigure}
-
-The Azure interconnection is realized using the \emph{CommunicationContext}. It implements a message encoder and establishes the out-of-band communication stack.
 
@@
 
-The encoded JSON messages must be transferred to Azure over the network using the selected protocol stack.
+The encoded JSON messages must be transferred to cloud over the network using the selected protocol stack.
 The Azure supports HTTP, AMQP, and MQTT protocol stacks, which are all standard ones.
@@
 \ref{figure1.StrategyDomainModel}).
-In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as as a composable part aggregated by the \emph{Reactive Application}.
+In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as a composable part aggregated by the \emph{Reactive Application}.
 

### 2021-01-12 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Final language corrections #59
- fixes #59

@@
 
-      Optimization of the industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Industrial Internet of Things.
-This research aims at working out a new generic architecture and deployment scenario applicable to this integration.
+      Optimization of industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Industrial Internet of Things.
+The research aims at working out a new generic architecture and deployment scenario applicable to that integration.
 The reactive interoperability relationship of the interconnected nodes is proposed to deal with the network traffic propagation asymmetry or assets' mobility.
-Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment.
-The discussion addressing the generic architecture concludes that the embedded gateway software part best suits all requirements.
-To promote separation of concerns and reusability, the proposed architecture of the embedded gateway has been implemented as a composable part of a selected OPC UA PubSub framework.
+The described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment.
+The discussion addressing generic architecture concludes that the embedded gateway software part best suits all requirements.
+To promote separation of concerns and reusability, the proposed architecture of the embedded gateway has been implemented as a composable part of the selected OPC UA PubSub framework.
 
       The proposals are backed by proof of concept reference implementations confirming the possibility to integrate selected cloud services with the cyber-physical system interconnected as one whole atop of the OPC UA by applying the proposed architecture and deployment scenario.
-It is contrary to interconnecting cloud services with a selected OPC UA server limiting the PubSub role to data export only.
+It is contrary to interconnecting cloud services with the selected OPC UA server limiting the PubSub role to data export only.
 
@@
 
-All the time, the Information and Communication Technology is providing society with a vast variety of new distributed applications aimed at micro and macro optimization of the industrial processes.
-Obviously, the design foundation of this kind of application has to focus primarily on communication technologies.
-Based on the role humans take while using these applications they can be grouped as follows:
+All the time, Information and Communication Technology is providing society with a vast variety of new distributed applications aimed at micro and macro optimization of the industrial processes.
+The design foundation of this kind of application must focus primarily on communication technologies.
+Based on the role humans take while using those applications they can be grouped as follows:
 
@@
 In this case, it is characteristic that any uncertainty and necessity to make a decision can be relaxed by human interaction.
-Coordination of robots behavior in a work-cell (automation islands) is a \textbf{machine-centric} example.
+Coordination of robot behaviors in a work-cell (automation islands) is a \textbf{machine-centric} example.
 In this case, any human interaction must be recognized as impractical or even impossible.
-This interconnection scenario requires the machine to machine communication (M2M) \cite{RefWorks:doc:5d6cdbbbe4b082ad50f3a83e, mpostol2020, RefWorks:doc:5d8f6d9ee4b058d660094a94, RefWorks:doc:5d868e46e4b030b4e0569e60, RefWorks:doc:5d8f7275e4b0bc72a68f4dcb} demanding multi-vendor devices integration.
+The interconnection scenario requires machine to machine communication (M2M) \cite{RefWorks:doc:5d6cdbbbe4b082ad50f3a83e, mpostol2020, RefWorks:doc:5d8f6d9ee4b058d660094a94, RefWorks:doc:5d868e46e4b030b4e0569e60, RefWorks:doc:5d8f7275e4b0bc72a68f4dcb} demanding the integration of multi-vendor devices.
 
@@
 In this M2M  deployment approach, the mentioned robots are only executive assets of an integrated supervisory control system responsible for macro optimization of an industrial process composed as one whole.
-Deployment of the smart factory concept requires a hybrid solution and interconnection of the mentioned above heterogeneous environments.
+Deployment of the smart factory concept requires a hybrid solution and interconnection of the above mentioned heterogeneous environments.
 This approach is called the fourth industrial revolution and was coined as Industry 4.0.
-It is worth stressing that machines - or more general assets - interconnection is not enough, and additionally, assets interoperability has to be expected for the deployment of this concept.
+It is worth stressing that interconnection of machines - or more general assets - is not enough, and additionally, assets interoperability must be expected for the deployment of this concept.
 In this case, multi-vendor integration makes communication standardization especially important, namely, it is required that the payload of the message is standardized to be factored on the data-gathering site and consumed on the ultimate destination site.
 
-Highly-distributed solutions used to control real-time process aggregating islands of automation (e.g.~virtual power plants producing renewable energy) additionally must leverage public communication infrastructure, namely the Internet.
-Internet is a demanding environment for highly distributed process control applications designed atop the M2M communication paradigm because it is globally shareable and can be also used by malicious users.
-Furthermore, it offers only non-deterministic communication making integration of islands of automation designed against the real-time requirements a demanding task.
+Highly-distributed solutions used to control any real-time process aggregating islands of automation (e.g.~virtual power plants producing renewable energy) must, additionally, leverage public communication infrastructure, namely the Internet.
+The Internet is a demanding environment for highly distributed process control applications designed atop the M2M communication paradigm because it is globally shareable and can be also used by malicious users.
+Furthermore, it offers only non-deterministic communication making the integration of islands of automation designed against the real-time requirements a demanding task.
 
@@
 The first application must be fine-tuned in the context of data security, and the second is very sensitive concerning time constraints.
-Similar approaches could be applied to adopt the well known in process control industry concepts, namely Human Machine Interface (HMI), Supervisory Control and Data Acquisition (SCADA), and Distributed Control Systems (DCS).
+Similar approaches could be applied to adopt the concepts well known in process control industry, namely Human Machine Interface (HMI), Supervisory Control and Data Acquisition (SCADA), and Distributed Control Systems (DCS).
 It is worth stressing that, by design, all of them are designed based on interactive communication.
 Interactive communication is based on a data polling foundation.
-In this case, the application must follow the interactive behavioral model, because it actively polls the data source for more information by pulling data from a sequence that represents the process state in time.
+If that is the case, the application must follow the interactive behavioral model, because it actively polls the data source for more information by pulling data from a sequence that represents the process state in time.
 The application is active in the data retrieval process - it controls the pace of the retrieval by sending the requests at its convenience.
 After dynamically attaching a new island of automation the control application (responsible for the data pulling) must be reconfigured for this interoperability scenario.
-In other words, in this case, the interactive communication relationship cannot be directly applied because the control application must be informed on how to pull data from a new source.
+In other words the interactive communication relationship cannot be directly applied because the control application must be informed on how to pull data from a new source.
 As a result, a plug and produce scenario \cite{PlugProduceByModellingSkills} cannot be seamlessly applied.
@@
 
-Going further, we shall assume that islands of automation are mobile, e.g.~autonomous cars passing a supervisory controlled service area.
-In this case, the behavior of the interconnected assets is particularly important concerning the environment in which they must interact.
+Going further, we shall assume that the islands of automation are mobile, e.g.~autonomous cars passing a supervisory controlled service area.
+Here, the behavior of the interconnected assets is particularly important concerning the environment in which they must interact.
 This way we have entered the Internet of Things domain of Internet-based applications.
@@
 In this case, the sessionless publisher-subscriber communication relationship is a typical pattern to implement the abstract reactive interoperability paradigm.
-The sessionless relationship is a message distribution scenario where senders of messages, called publishers, do not send them directly to specific receivers, called subscribers, but instead, categorize the published messages into topics without knowledge about which subscribers if any, there may be.
+The sessionless relationship is a message distribution scenario where senders of messages, called publishers, do not send them directly to specific receivers, called subscribers, but instead, categorize the published messages into topics without knowledge about which subscribers, if any, there may be.
 Similarly, subscribers express interest in one or more topics and only receive messages that are of interest, without knowledge about which publishers, if any, there are.
-In this scenario, the publishers and subscribers are loosely coupled i.e they are decoupled in time, space and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.
+In this scenario, the publishers and subscribers are loosely coupled, i.e.
+they are decoupled in time, space and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.
 
-If the \textbf{machine-centric} interoperability - making up islands of automation - must be monitored and/or controlled by a supervisory system, the cloud computing concept may be recognized as a beneficial solution to replace or expand the mentioned above applications, i.e.~HMI, SCADA, DCS, etc.
-Cloud computing is a method to provide a requested functionality as a set of services.
+If the \textbf{machine-centric} interoperability - making up islands of automation - must be monitored and/or controlled by a supervisory system, the cloud computing concept may be recognized as a beneficial solution to replace or expand the above mentioned applications, i.e.~HMI, SCADA, DCS, etc.
+Cloud computing is a method to provide the requested functionality as a set of services.
 There are many examples that cloud computing is useful to reduce costs and increase robustness.
@@
 Following this idea and offering control systems as a service, there is required a mechanism created on the service concept and supporting abstraction and virtualization - two main pillars of the cloud computing paradigm.
-In the cloud computing concept, virtualization is recognized as the possibility to share the services by many users, and abstraction hides implementation details.
+In the cloud computing concept, virtualization is recognized as the possibility of sharing the services by many users, and abstraction hides implementation details.
 
@@
 For this integration, a new architecture is proposed to support the reactive relationship of communicating parties.
-To support the multi-vendor environment OPC Unified Architecture \cite{RefWorks:doc:5ac86c99e4b009947bbb87c6, LiteratureSurveyOnOpenPlatformCommunications, RefWorks:doc:5ac86c99e4b009947bbb87d2} interoperability standard has been selected.
+To support the multi-vendor environment the OPC Unified Architecture \cite{RefWorks:doc:5ac86c99e4b009947bbb87c6, LiteratureSurveyOnOpenPlatformCommunications, RefWorks:doc:5ac86c99e4b009947bbb87d2} interoperability standard has been selected.
 Prototyping addresses Microsoft Azure Cloud \cite{MicrosoftAzureIoTPlatform} as an example.
-The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as the open-source (MIT licensed) \cite{mariusz_postol_2020_4361640}.
+The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as an open-source (MIT licensed) \cite{mariusz_postol_2020_4361640}.
 The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet (OOI) \cite{mariusz_postol_2020_4361640, RefWorks:doc:5c6912c9e4b0a562a3fc7f5b, RefWorks:doc:5c66740ae4b081adf5804596}.
 
-The main goal of this article is to provide proof that
+The main goal of this article is to provide proof that:
 
 \begin{itemize}
-      \item reactive M2M interoperability based on the OPC UA standard can be implemented as a powerful standalone library without dependency on the Client/Server session-oriented archetype
-      \item cloud interoperability can be implemented as an external part employing out-of-band communication without dependency on the OPC UA implementation
-      \item the proposed generic architecture allows that the gateway functionality is implemented as composable part at run-time part - no programming required
+      \item reactive M2M interoperability based on the OPC UA standard can be implemented as a powerful standalone library without dependency on the Client/Server session-oriented archetype,
+      \item cloud interoperability can be implemented as an external part employing out-of-band communication without dependency on the OPC UA implementation,
+      \item the proposed generic architecture allows that the gateway functionality is implemented as a composable part at run-time part - no programming required.
 \end{itemize}
@@
 \ref{introduction}).
-The main challenge of the solution in concern is to design a generic but reusable architecture that addresses interoperability of these diverse interconnection scenarios ruled by different requirements, namely:
+The main challenge of the solution in concern is to design a generic but reusable architecture that addresses interoperability of those diverse interconnection scenarios ruled by different requirements, namely:
 
@@
 The decision to follow the \textbf{direct interconnection} scenario must be derived from an analysis of the capabilities of available services in concern.
-However, for the development strategy of this type of solution, this analysis can be done partially taking into account the following features that can be considered invariable.
-By design the cloud-based services must be virtual - they are used to handle many solutions at the same time.
+However, for the development strategy of this type of solution, the analysis can be done partially taking into account the following features that can be considered invariable.
+By design, the cloud-based services must be virtual - they are used to handle many solutions at the same time.
 Furthermore, M2M communication is usually constrained by real-time requirements.
@@
 \begin{itemize}
-      \item \textbf{edge device} - remote cloud agent acting as an intermediary for nodes of the CPS
+      \item \textbf{edge device} - a remote cloud agent acting as an intermediary for nodes of the CPS
       \item \textbf{field level gateway} - a dedicated custom agent acting as an intermediary for nodes of the CPS
@@
 \textbf{Edge device} connects directly to the cloud services but acts as an intermediary for other devices called leaf devices.
-Additionally, it allows the selection of initial data and processing of them using local resources.
+Additionally, it allows the selection of initial data and their processing using local resources.
 The \textbf{edge device} may be located close to the leaf devices and attached to the \emph{Cyber-physical network} using protocols applicable only to local computer networks.
-In this scenario, it is possible to use a custom protocol stack to get connected to the \textbf{edge device} with the cloud and helps to save the bandwidth thanks to sending only the results of local processing.
-In this approach, the \textbf{edge device} is part of cloud vendor products and cannot be recognized as a generic solution that can be used to connect to other clouds supporting many-to-many relationship.
+In this scenario, it is possible to use a custom protocol stack to get connected to the \textbf{edge device} with the cloud and to help to save the bandwidth thanks to sending only the results of local processing.
+In this approach, the \textbf{edge device} is part of cloud vendor products and cannot be recognized as a generic solution that can be used to connect to other clouds supporting a many-to-many relationship.
 
-The \textbf{field level gateway} is also build atop of the middleware concept \cite{Sunyaev2020}.
-The only difference compared with the \textbf{edge device} is a necessity to use officially supported by the cloud vendor services to get connected.
-In this scenario, the process data simultaneously may be transferred to many clouds.
+The \textbf{field level gateway} is also built atop of the middleware concept \cite{Sunyaev2020}.
+The only difference as compared with the \textbf{edge device} is a necessity to use services officially supported by the cloud vendor to get connected.
+In this scenario, the process data may be transferred to many clouds simultaneously.
 
@@
 A generic domain model for this interconnection is presented in the Fig.~\ref{figure1.StrategyDomainModel}.
-Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \emph{Networking} service of the \emph{Cyber-physical\ node}.
-The main functionality of this component is to transfer selected data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
+Promoting separation of concerns design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \emph{Networking} service of the \emph{Cyber-physical\ node}.
+The main functionality of this component is to transfer selected data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using interconnection services officially supported by the cloud vendor.
 \end{proposition}
@@
 In this case, using the same communication stack must be recognized as only a necessary condition.
-To support interoperability common data understanding is required.
-Additionally, to meet this requirement the cloud and CPS have to establish directly the same semantic-context and security-context.
-The possibility to establish a common semantic-context in the multi-vendor environment makes communication standardization especially important.
-In this case, it is required that the encoding of the payload exchanged over the network (Data Transfer Object) is standardized so that the appropriate messages can be factored on the data-gathering site and consumed on the ultimate destination data processing sites.
+To support interoperability, common data understanding is required.
+Additionally, to meet this requirement, the cloud and CPS have to establish directly the same semantic-context and security-context.
+The possibility of establishing a common semantic-context in the multi-vendor environment makes communication standardization especially important.
+If that is the case, it is required that the encoding of the payload exchanged over the network (Data Transfer Object) is standardized so that the appropriate messages can be factored on the data-gathering site and consumed on the ultimate destination data processing sites.
 Security between the data origin and ultimate data destination refers to the protection of messages (security-context) against malicious users.
 It is required that communicating parties are using the same cyber-security measures.
-To comply with the Industry 4.0 communication criterion it is required that any product must be addressable over the network via TCP/UDP or IP and has to support the OPC UA Information Model \cite{OPCUAPart5, RefWorks:doc:5ac86c99e4b009947bbb87c9, RefWorks:doc:5d986a28e4b0b0c862c0d184}.
+To comply with the Industry 4.0 communication criterion, it is required that any product must be addressable over the network via TCP/UDP or IP and has to support the OPC UA Information Model \cite{OPCUAPart5, RefWorks:doc:5ac86c99e4b009947bbb87c9, RefWorks:doc:5d986a28e4b0b0c862c0d184}.
 As a result, any product being advertised as Industry 4.0 enabled must be OPC UA-capable somehow.
 
-To support the multi-vendor environment OPC Unified Architecture interoperability standard has been selected.
+The OPC Unified Architecture interoperability standard has been selected to support the multi-vendor environment.
 OPC UA supports the following two patterns to be used to transfer data between communicating parties:
@@
 \begin{itemize}
-      \item \textbf{session-oriented}: requires a session that has to be established before any data can be sent between sender and receiver
+      \item \textbf{session-oriented}: requires a session that must be established before any data can be sent between sender and receiver
       \item \textbf{sessionless-oriented}: the sender may start sending messages (called packets or datagrams) to the destination without any preceding handshake procedure
@@
 OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0, UAPart14PubSubMainTechnologyFeatures} offers the sessionless approach as an additional option to session-based client-server interoperability relationship and is a consistent part of the OPC UA specifications suit.
-As the result, it can be recognized as the IoT ready technology.
+As a result, it can be recognized as the IoT ready technology.
 
-The presented proposals in the article are backed by proof of concept reference implementations\cite{mariusz_postol_2020_4361640}.
+The proposals presented in the article are backed by proof of concept reference implementations \cite{mariusz_postol_2020_4361640}.
 For this study, prototyping addresses Microsoft Azure cloud products.
-There are many reasons for selecting Azure to accomplish the cloud-based front-end of Cyber-Physical System (CPS).
+There are many reasons for selecting Azure to accomplish the cloud-based front-end of a Cyber-Physical System (CPS).
 Azure offers Infrastructure as a Service (IaaS) and Platform as a Service (PaaS) capabilities.
@@
 Azure aids Internet protocols and open standards such as JSON, XML, SOAP, REST, MQTT\cite{RefWorks:doc:5d91e158e4b02eb43d36bb97}, AMQP\cite{RefWorks:doc:5d91d2d9e4b0bc72a68ffe06}, and HTTP.
-A software development kits for C\#, Java, PHP, and Ruby are available for custom applications.
+Software development kits for C\#, Java, PHP, and Ruby are available for custom applications.
 
-Based on the sessionless and session-oriented communication patterns examination against the IoT requirements \cite{mpostol2020} it could be concluded that the connectionless pattern better suites issues related to the assets mobility and traffic asymmetry that is characteristic for the application domains in concern.
-Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub  specification.
-According to proposed generic architecture (Fig.~\ref{figure1.StrategyDomainModel}) to implement the \emph{Embedded\ Gateway} as a composable part of the \emph{Cyber-physical\ node} a library implementing \emph{Networking} functionality in compliance with mentioned above specification is a starting point for further development.
-Additionally, it must be assumed that the library used to deploy \emph{Embedded\ Gateway} supports dependency injection and is capable to compose an external part supporting cloud/PubSub gateway functionality.
+Based on the sessionless and session-oriented communication patterns examination against the IoT requirements \cite{mpostol2020} it could be concluded that the connectionless pattern better suites issues related to assets mobility and traffic asymmetry that is characteristic for the application domains in concern.
+Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment, the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub  specification.
+According to proposed generic architecture (Fig.~\ref{figure1.StrategyDomainModel}) to implement the \emph{Embedded\ Gateway} as a composable part of the \emph{Cyber-physical\ node} a library implementing \emph{Networking} functionality in compliance with above mentioned specification is a starting point for further development.
+Additionally, it must be assumed that the library used to deploy \emph{Embedded\ Gateway} supports dependency injection and is capable of composing an external part supporting cloud/PubSub gateway functionality.
 The composition process must be available without modification of the core code of an existing library.
@@
 By design, they support access to real-time process data, hence they are recognized as an extension of \emph{DataRepository} class.
-To implement the \emph{DataRepository} dedicated implementation of the \emph{IBindingFactory} interface should be provided to create a bridge between CPS and an external row data represented by the \emph{LocalResources} class.
+To implement the \emph{DataRepository} dedicated implementation of the \emph{IBindingFactory} interface should be provided to create a bridge between CPS and an external raw data represented by the \emph{LocalResources} class.
 A more in-depth description of the \emph{OOI Reactive Application} library enabling data exchange over a network using the reactive networking pattern is covered in \cite{mpostol2020}.
@@
 To promote the polymorphic approach, the library has a factory class called \emph{DataManagementSetup} that is a placeholder to gather all injection points used to compose external parts.
-To be injected the part supporting data exchange with the underlying process must be compliant with the \emph{IBindingFactory} interfaces.
+To be injected, the part supporting data exchange with the underlying process must be compliant with the \emph{IBindingFactory} interfaces.
 It is expected that the functionality implementation expressed by this interface is provided as an independent external composable part.
@@
 The \emph{Producer} mirrors the \emph{Consumer} functionality and, after reading data from an associated source, populates the \emph{Message} using the gathered data.
-By design, the \emph{DataRepository} and associated entities, i.e.~\emph{Local Resources}, \emph{Consumer}, \emph{Producer} are embedded in external parts, and consequently, the application scope may cover practically any concern that can be separated from the core \emph{Reactive Application} implementation.
+By design, the \emph{DataRepository} and associated entities, i.e.~\emph{Local Resources}, \emph{Consumer}, \emph{Producer} are embedded in external parts, and, consequently, the application scope may cover practically any concern that can be separated from the core \emph{Reactive Application} implementation.
 
@@
 Merging selected entities of this archetype into the proposed domain model (Fig.
-\ref{figure1.StrategyDomainModel}) lead to a model expressed as the diagram presented in Fig.
+\ref{figure1.StrategyDomainModel}) leads to a model expressed as the diagram presented in Fig.
 \ref{figure3.ImplementationDomainModel}.
@@
 
-The recovered data from the \emph{Message} is obtained from the \emph{PartBindingFactory} using the \emph{IDTOProvider} that defines a contract used to pull the Data Transfer Object created from a subscription by the \emph{PartBindingFactory}.
+The data recovered from the \emph{Message} is obtained from the \emph{PartBindingFactory} using the \emph{IDTOProvider} that defines a contract used to pull the Data Transfer Object created from a subscription by the \emph{PartBindingFactory}.
 The transfer process requires data conversion from source to destination encoding, i.e.
@@
 Alternatively, the API offered by the dedicated frameworks (libraries) may be used.
-Using a framework the configuration process may be reduced significantly, and the communication protocol selection has only an indirect impact on the interoperability features.
-In the proposed implementation, the Azure interconnection has been obtained using the mentioned above frameworks.
+Using a framework, the configuration process may be reduced significantly, and the communication protocol selection has only an indirect impact on the interoperability features.
+In the proposed implementation, the Azure interconnection has been obtained using the above mentioned frameworks.
 
 Azure and PubSub use different security mechanisms so in the proposed solution establishing security-context is realized independently.
-The \emph{CommunicationContext} is responsible to establish this context as an embedded negotiation phase tightly coupled with establishing interconnection.
+The \emph{CommunicationContext} is responsible for establishing this context as an embedded negotiation phase tightly coupled with establishing interconnection.
 
@@
 Dynamic nature means that interconnected assets may be added/removed from the network at any time.
-By design, typically CPS must fulfill the real-time and mobility of the assets requirements.
+By design, CPS must typically fulfill the real-time and mobility of the assets requirements.
 
 Highly-distributed solutions used to control/monitor a set of geographically dispersed islands of automation (e.g.
-virtual power plants producing renewable energy) additionally must leverage public communication infrastructure, namely the Internet.
+virtual power plants producing renewable energy) must additionally leverage public communication infrastructure, namely the Internet.
 If islands of automation must be controlled over the Internet, the cloud computing concept may be recognized as a reasonable answer.
 Following this concept, the cloud-based supervisory control functionality is applied as a set of services employing abstraction and virtualization - two main pillars of the cloud computing paradigm.
-In the cloud computing concept, virtualization is recognized as the possibility to share the services by many users, and abstraction hides implementation details.
+In the cloud computing concept, virtualization is recognized as the possibility of sharing the services by many users, and abstraction hides implementation details.
 
@@
 
-If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship \cite{mpostol2020} could alleviate the challenges posed by the interactive approach.
+If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment points the reactive relationship \cite{mpostol2020} could alleviate the challenges posed by the interactive approach.
 The real-time multi-vendor environment makes communication standardization especially important.
-To support this environment, OPC Unified Architecture \cite{RefWorks:doc:5ac86c98e4b009947bbb874c} interoperability standard has been selected.
-As it was pointed out in the Sect.
+To support this environment, the OPC Unified Architecture \cite{RefWorks:doc:5ac86c98e4b009947bbb874c} interoperability standard has been selected.
+As it was pointed out in Sect.
 \ref{cloud-to-sensors-field-level-connectivity} using OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} the aggregation of nodes by the network is loosely coupled, i.e.
@@
 
-From the analysis covered by the Sect.
+From the analysis covered by Sect.
 \ref{cloud-to-sensors-field-level-connectivity} it is concluded that the \emph{Embedded Gateway} archetype best suits all requirements described above.
 It relaxes most of the issues related to \textbf{direct interconnection} and solutions inferred from the middleware concept, i.e.
-\textbf{edge device} - remote cloud agent and \textbf{field level gateway} - a dedicated custom agent.
+\textbf{edge device} - a remote cloud agent and \textbf{field level gateway} - a dedicated custom agent.
 Additionally, it could be used to connect to many independent clouds at the same time.
-The generic domain model for the proposed interconnection archetype is presented in the Fig.~\ref{figure1.StrategyDomainModel}.
-We have highlighted that to promote the separation of concern design principle, the gateway functionality should be implemented as a self-contained dedicated software part embedded in the core \emph{Networking} service of the \emph{Cyber-physical\ node}.
-The main functionality of this component is to transfer process data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.
+The generic domain model for the proposed interconnection archetype is presented in Fig.~\ref{figure1.StrategyDomainModel}.
+We have highlighted that to promote the separation of concerns design principle, the gateway functionality should be implemented as a self-contained dedicated software part embedded in the core \emph{Networking} service of the \emph{Cyber-physical\ node}.
+The main functionality of this component is to transfer process data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using interconnection services officially supported by the cloud vendor.
 
@@
 
-Concluding, the paper describes a proof of the concept that applying the proposed architecture and deployment scenario it is possible to integrate cloud services (e.g.
+Concluding, the paper describes a proof of concept that applying the proposed architecture and deployment scenario it is possible to integrate cloud services (e.g.
 \textbf{Azure\ IoT\ Central}) with the \emph{Cyber-physical network} interconnected as one whole atop of the OPC UA PubSub.

### 2021-03-23 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Review ICCS 2021 notification for paper 136 #60
- Review 1 - improved abstract

@@
 
-      Optimization of industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Industrial Internet of Things.
-The research aims at working out a new generic architecture and deployment scenario applicable to that integration.
-The reactive interoperability relationship of the interconnected nodes is proposed to deal with the network traffic propagation asymmetry or assets' mobility.
-The described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment.
-The discussion addressing generic architecture concludes that the embedded gateway software part best suits all requirements.
-To promote separation of concerns and reusability, the proposed architecture of the embedded gateway has been implemented as a composable part of the selected OPC UA PubSub framework.
+      Optimization of industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely the fourth industrial revolution coined as Industry 4.0 and Industrial Internet of Things.
+The following research aims at working out a new generic architecture and deployment scenario applicable to that integration.
+A~reactive interoperability relationship of the communication parties is proposed to deal with the network traffic propagation asymmetry or assets’ mobility.
+Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment.
+The discussion  concludes that the embedded gateway software component best suits all requirements and thus has been implemented as a composable part of the selected reactive OPC UA framework which promotes separation of concerns and reusability.
 
-      The proposals are backed by proof of concept reference implementations confirming the possibility to integrate selected cloud services with the cyber-physical system interconnected as one whole atop of the OPC UA by applying the proposed architecture and deployment scenario.
-It is contrary to interconnecting cloud services with the selected OPC UA server limiting the PubSub role to data export only.
+      The proposals are backed by proof-of-concept reference implementations confirming the possibility of integrating selected cloud services with the OPC UA based cyber-physical system by applying the proposed architecture and deployment scenario.
+It is contrary to interconnecting cloud services with the selected OPC UA Server limiting the PubSub role to data export only.
 

### 2021-04-01 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Review ICCS 2021 notification for paper 136 #60
- reviewed the text - for me it works and is ready to be published

@@
 %\authorrunning{M. Postół et al.}
-
-\institute
-{ Institute of Information Technology, Lodz University of Technology, Łódź, Poland \\
-      \email{mailto:mariusz.postol@p.lodz.pl} %\\ \url{http://www.it.p.lodz.pl}
-}
 
@@
 It is worth stressing that, by design, all of them are designed based on interactive communication.
-Interactive communication is based on a data polling foundation.
+Interactive communication is based on a data polling relationship.
 If that is the case, the application must follow the interactive behavioral model, because it actively polls the data source for more information by pulling data from a sequence that represents the process state in time.
@@
 If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship could relax the problems encountered while the interactive approach is applied \cite{mpostol2020}.
-In this case, the sessionless publisher-subscriber communication relationship is a typical pattern to implement the abstract reactive interoperability paradigm.
+In this case, the sessionless publisher-subscriber communication relationship is a typical pattern to implement the reactive interoperability paradigm.
 The sessionless relationship is a message distribution scenario where senders of messages, called publishers, do not send them directly to specific receivers, called subscribers, but instead, categorize the published messages into topics without knowledge about which subscribers, if any, there may be.
@@
 
-If the \textbf{machine-centric} interoperability - making up islands of automation - must be monitored and/or controlled by a supervisory system, the cloud computing concept may be recognized as a beneficial solution to replace or expand the above mentioned applications, i.e.~HMI, SCADA, DCS, etc.
+If the \textbf{machine-centric} Cyber-Physical System (CPS) - making up islands of automation - must be monitored and/or controlled by a supervisory system, the cloud computing concept may be recognized as a beneficial solution to replace or expand the above mentioned applications, i.e.~HMI, SCADA, DCS, etc.
 Cloud computing is a method to provide the requested functionality as a set of services.
@@
 To support the multi-vendor environment the OPC Unified Architecture \cite{RefWorks:doc:5ac86c99e4b009947bbb87c6, LiteratureSurveyOnOpenPlatformCommunications, RefWorks:doc:5ac86c99e4b009947bbb87d2} interoperability standard has been selected.
+The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as an open-source (MIT licensed) \cite{mariusz_postol_2020_4361640}.
 Prototyping addresses Microsoft Azure Cloud \cite{MicrosoftAzureIoTPlatform} as an example.
-The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as an open-source (MIT licensed) \cite{mariusz_postol_2020_4361640}.
 The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet (OOI) \cite{mariusz_postol_2020_4361640, RefWorks:doc:5c6912c9e4b0a562a3fc7f5b, RefWorks:doc:5c66740ae4b081adf5804596}.
@@
       \item cloud interoperability can be implemented as an external part employing out-of-band communication without dependency on the OPC UA implementation,
-      \item the proposed generic architecture allows that the gateway functionality is implemented as a composable part at run-time part - no programming required.
+      \item the proposed generic architecture allows that the gateway functionality is implemented as a composable part at run-time - no programming required.
 \end{itemize}
@@
 This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} \cite{RefWorks:doc:5ac86c97e4b009947bbb8728} embedded component of the OPC UA Server.
-The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to inject the \emph{Embedded Gateway} part into the OPC UA Client/Server to get connected with the cloud in case of the interactive relationship.
+The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to inject the \emph{Embedded Gateway} part into the OPC UA Client/Server to get connected with the cloud addressing the interactive relationship.
 
 In the proposed approach the cloud interoperability is obtained by implementing a dedicated part employing out-of-band communication only without dependency on the OPC UA functionality at all.
-It is worth stressing that the gateway functionality is implemented as a part - composable to the whole without programming skills.
+It is worth stressing that the gateway functionality is implemented as a part composable to the whole without programming skills.
 Because the part is composed at the runtime it makes it possible to modify its functionality later after releasing the library or even deploying the application program in the production environment.
